### 2019-10-31 analysis_and_paper/manuscript.Rmd
add analysis and paper folder

---
title           : "Of Two Minds: A registered replication"
shorttitle      : "Replication of Rydell et al."

author: 
  - name          : Tobias Heycke
    affiliation   : 1, 2
    corresponding : yes    
    address       : "P.O. 122155, 68072 Mannheim, Germany"
    email         : "tobias.heycke@gesis.org"
  - name          : Frederik Aust
    affiliation   : 1
  - name          : Mahzarin R. Banaji
    affiliation   : 3
  - name          : Pieter Van Dessel
    affiliation   : 5
  - name          : Xiaoqing Hu
    affiliation   : 6    
  - name          : Congjiao Jiang
    affiliation   : 4    
  - name          : Benedek Kurdi
    affiliation   : 3    
  - name          : Robert Rydell
    affiliation   : 7
  - name          : Lisa Spitzer
    affiliation   : 1
  - name          : Christoph Stahl
    affiliation   : 1
  - name          : Christine Vitiello
    affiliation   : 4
  - name          : Jan De Houwer
    affiliation   : 5

affiliation:
  - id            : 1
    institution   : University of Cologne
  - id            : 2
    institution   : GESIS - Leibniz Institute for the Social Sciences
  - id            : 3
    institution   : Harvard University 
  - id            : 4
    institution   : University of Florida 
  - id            : 5
    institution   : Ghent University 
  - id            : 6
    institution   : The University of Hong Kong 
  - id            : 7
    institution   : Indiana University

abstract: |
  Findings of dissociations between implicit (i.e., automatic) and explicit (i.e., non-automatic) evaluations that are based on distinct associative (i.e., co-occurrence based) and propositional (i.e., rule-based) learning procedures have fueled the dominance of dual-process theories of evaluative learning for decades.  Arguably the most influential evidence has been found in a study by Rydell, McConnell, Mackie, and Strain (2006) in which participants learned about a person named Bob. It was observed that implicit evaluations reflected the valence of brief pairings of valenced words with the image of Bob whereas explicit evaluations reflected the (opposite) valence of the behavioral statements that were instructed to be characteristic of Bob. A recent study by Heycke and colleagues (2018) was unable to reproduce this data pattern independently. Given the theoretical importance of the findings by Rydell and colleagues, we present a series of additional replication attempts conducted by an international collective of researchers including the first author of the original finding.

authornote: |
  All data, analysis scripts and materials can be found at https://osf.io/8m3xb/

keywords          : "evaluative conditioning, subliminal influence, implicit learning, replication"
#wordcount         : "X"

bibliography      : ["references.bib", "r-references.bib"]
#appendix          : "appendix.Rmd"

header-includes:
  - \interfootnotelinepenalty=10000

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE, warning=FALSE}
library("magrittr")
library("tidyr")
library("dplyr")
library("assertthat")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("afex")
library("emmeans")
library("BayesFactor")
library("MBESS")

source("https://gist.githubusercontent.com/crsh/bd4d1f62d300462ea0c0f44b9ad38616/raw/edd9c74e24b68f42433c2526cafc888509b1b8bc/batch_download_github.R")
source("https://gist.githubusercontent.com/crsh/357458c41fd3d554fb24/raw/f7725d5c4894a055a1b2e461dc5c39f3db23b2b8/batch_read.R")
source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")

source("modal_frame_rate.R")
```

```{r analysis-preferences}
# Data wrangling
process_rawdata <- TRUE
download_bornopen_data <- FALSE

# Data location
raw_data_path <- "../otm1/results/data_raw/"
processed_data_path <- "../otm1/results/data_processed/"

# Set seed for random number generator
set.seed(315054738)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Use multivariate models for emmeans contrasts and post-hoc tests
afex_options(emmeans_model = "multivariate")

# Configure df approximation for mixed model contrasts and post-hoc tests
emm_options(
  lmer.df = "satterthwaite"
  , lmerTest.limit = 22384
)

# Default ggplot theme
theme_set(theme_apa())

## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
# assignInNamespace("theme_nothing", function() {
#     theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
# }, "cowplot")

# Number of MCMC samples for Bayesian analysis
otm1_n_mcmc_samples <- 1e6
```

```{r cache-preferences}
# Automatically manage cache dependencies
knitr::opts_chunk$set(autodep = TRUE)
knitr::dep_auto()

# Ignore changes to comments in cached chunks
knitr::opts_chunk$set(cache.comments = FALSE)

# Discard cache if random seed changes
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

<!--
Guideline:
Authors of a PDR must make a convincing case that the replication will make a valuable contribution to understanding a phenomenon and/or theory of broad current interest to psychologists. As with all Psychological Science submissions, the primary criterion is general theoretical significance. Direct replications should reproduce the original methods and procedures as closely as possible, with the goal of measuring the same effect under essentially (but not necessarily superficially) the same conditions as in the original study

Word limit: 
Intro + Discussion + notes + acknowledgements + appendices = 1500

Max Figures/tables:
3

Max references:
30
-->

Evaluative conditioning (EC) refers to the robust finding of a change in liking of a stimulus, referred to as conditioned stimulus (CS), that is due to its pairing with a stimulus of positive or negative valence, referred to as unconditioned stimulus (US) [@dehouwerConceptualTheoreticalAnalysis2007; @hofmannEvaluativeConditioningHumans2010]. 
Dual-process theories postulate that EC can depend both on a mechanism via which co-occurrences between stimuli result in the automatic formation of mental associations as well as a second mechanism via which propositional beliefs are formed [e.g., @gawronskiAssociativePropositionalProcesses2006; @rydellUnderstandingImplicitExplicit2006].
Though dual-process theories have had a huge impact, it has been argued that there is actually little evidence for automatic association formation as a distinct mechanism for EC [see @corneilleAssociativeAttitudeLearning2018a].
This conclusion is in line with propositional single-process views [e.g., @mitchellPropositionalNatureHuman2009] which postulate that all associative (evaluative) learning (including EC) is based on propositional processes.

One finding, however, is particularly difficult to reconcile with propositional single-process accounts: 
@rydell_two_2006 reported that participants exhibited conflicting explicit and implicit evaluations (e.g., positive explicit and negative implicit evaluations) of a single target person after the presentation of rapid stimulus-stimulus pairings and behavioral statements that implied the opposite valence. 
In this study, participants engaged in a learning task about a person named Bob in which they determined whether Bob was a good or bad person by guessing whether positive and negative behavioral statements were characteristic of Bob. 
They received feedback about the accuracy of each of their guesses.
Unbeknownst to the participants, on each trial, a valent word (US) was presented briefly (25 ms) prior to the presentation of a picture of Bob and the behavioral statement. 
Critically, the valence of the US words was always opposite to the behavioral information (e.g., USs were always positive when negative behavioral statements were characteristic of Bob).
Following the learning task, explicit evaluations of Bob, assessed with a trait rating task, reflected the valence of the learned behavioral information, while implicit evaluations, assessed with an Implicit Association Test [IAT: @greenwaldMeasuringIndividualDifferences1998] reflected the valence of the USs.
These results were conceptually replicated by the original authors using similar methods [@rydellConsequencesDiscrepantExplicit2008; @rydellUnderstandingImplicitExplicit2006].
The @rydell_two_2006 article has been referred to as providing strong evidence for numerous dual-process theories [@gawronskiAssociativePropositionalEvaluation2011; @rydellUnderstandingImplicitExplicit2006] and has been cited more than 320 times overall (Google Scholar, 10.15.2019).

Judging from its impact, the reported effect is generally assumed to be robust and replicable.
A recent study, composed of two experiments, however, could not replicate the dissociative effect [@heycke_two_2018].
Instead, both implicit and explicit evaluations consistently reflected the valence of the learned behavioral information.
At present, it remains unclear whether these unsuccessful attempts call into question the replicability of the original study or point towards boundary conditions.
This ambiguity is due to the modifications made to the original materials and procedure in the replication studies: First, some words were replaced to ensure that no words presented in the learning phase served as distractors in the US memory assessment at the end of the study [see @heycke_two_2018].
Second, one experiment used German translations of the verbal material (rather than the original English material).
Third, the other experiment, while using the original material, was conducted with a modified procedure: Because  a subset of participants correctly identified USs after the learning task in the first experiment, the presentation duration of USs was reduced from 25 ms to 16 ms to ensure at-chance post-learning US recognition.

In the current study we will rigorously test the replicability of the original findings reported by @rydell_two_2006 by closely adhering to the original procedure.
To ensure its informativeness, the current replication attempt was a joint effort that involved researchers from different labs that all have expertise in studying evaluative conditioning and implicit measures.
Moreover, both the first author of the original study and authors of the unsuccessful replication attempts collaborated on the studies presented here.
To explore the generality of our results, data were collected in multiple countries and languages.
In a first, already concluded,  experiment we have conducted a close replication in three different locations. 
In a second experiment, for which the data has not been collected yet, we will use the knowledge gained from the first experiment to adjust the procedure to closely replicate the psychological conditions of the original study.

# Experiment 1

```{r otm1-load-data, cache = TRUE, warning = FALSE}
# Process raw data
if(process_rawdata) {

  # Born-open data from Cologne
  if(download_bornopen_data) {
    batch_download_github(
      "https://github.com/methexp/rawdata/tree/master/OTM"
      , pattern = "\\.dat"
      , paste0(raw_data_path, "cologne/")
    ) %>%
      is.null %>%
      assert_that(msg = "Download of born-open data failed.")
  }

  # Merge raw data
  otm1_eval <- batch_read(
    raw_data_path
    , pattern = "Eval"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm1_iat <- batch_read(
    raw_data_path
    , pattern = "IAT"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm1_mem <- batch_read(
    raw_data_path
    , pattern = "MemTest"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm1_demo <- batch_read(
    raw_data_path
    , pattern = "Demographics"
    , recursive = TRUE
    , read_fun = read.delim
    , quote = "~" # Participants used " in their input
  )

  otm1_log <- batch_read(
    raw_data_path
    , pattern = "ScreenLog"
    , recursive = TRUE
    , read_fun = read.csv
    , header = FALSE
  )

  # Recode, calculate indices, and filter data
  otm1_eval <- otm1_eval %>%
    mutate_at(vars(starts_with("Eval")), scale) %>%
    select(starts_with("Eval")) %>%
    rowwise %>%
    do(data.frame(Eval = sum(unlist(.)))) %>% 
    bind_cols(otm1_eval, .) %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
    )

  otm1_iat <- otm1_iat %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
      , IATBlock = factor(paste0("Block", IATBlock))

      # Wolsiefer et al. (2017, p. 1198; doi: 10.3758/s13428-016-0779-0)
      , imageType = ifelse(Category == "Image", ifelse(Type == "Bob", 1, -1), 0)
      , wordType = ifelse(Category == "Text", ifelse(Type == "neg", 1, -1), 0)
    ) %>%
    filter(IATBlock %in% c("Block34", "Block67")) %>%
    mutate(
      Correct = ifelse(Correct == "correct", 1, 0)
      , RT = ifelse(Correct == 1, RT, RTafterError)
      , cleanRT = ifelse(RT < 0.3, 0.3, RT)
      , cleanRT = ifelse(cleanRT > 3, 3, cleanRT)
      , logCleanRT = log(cleanRT)

      # Wolsiefer et al. (2017, p. 1198; doi: 10.3758/s13428-016-0779-0)
      # Combination 1: Combination 1 (Bob = negative) in Block 3 & 4
      # Combination 2: Combination 1 (Bob = negative) in Block 6 & 7
      , Congruent = ifelse(
        # Bob = negative
        (Combination == 1 & IATBlock == "Block34") |
        (Combination == 2 & IATBlock == "Block67")
        # # Bob = positive
        , "Bob & negative" # -1
        , "Bob & positive" # 1
      ) %>% factor(levels = c("Bob & negative", "Bob & positive"))
    )

  otm1_stimulus_translations <- read.delim("../otm1/results/IAT_word_translations.tab", header = FALSE)[-1, ] %>%
    set_colnames(c("German", "Dutch", "English"))

  german_iat_words <- match(otm1_iat$Stimulus, otm1_stimulus_translations$German)
  dutch_iat_words <- match(otm1_iat$Stimulus, otm1_stimulus_translations$Dutch)

  otm1_iat$translatedStimulus <- otm1_iat$Stimulus
  otm1_iat$translatedStimulus[!is.na(german_iat_words)] <- otm1_stimulus_translations$English[
    na.omit(german_iat_words)
  ]
  otm1_iat$translatedStimulus[!is.na(dutch_iat_words)] <- otm1_stimulus_translations$English[
    na.omit(dutch_iat_words)
  ]

  otm1_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")

  otm1_attitudes <- otm1_iat %>%
    group_by(ParticipantNumber, Location, MeasureOrder, Block, IATBlock, Combination, ValenceBlock) %>%
    summarize(meanRT = mean(logCleanRT), nRT = length(logCleanRT)) %>%
    ungroup %>%
    spread(IATBlock, meanRT) %>%
    # Combination 1: Combination 1 (Bob = negative) in Block 3 & 4
    # Combination 2: Combination 1 (Bob = negative) in Block 6 & 7
    mutate(IATscore = ifelse(Combination == 1, Block34 - Block67, Block67 - Block34)) %>%
    select(c(otm1_analysis_factors, "IATscore")) %>%
    left_join(
      select(otm1_eval, c(otm1_analysis_factors, "Eval"))
      , by = otm1_analysis_factors
    ) # %>%
    # mutate(
    #   Eval = scale(Eval) %>% as.vector
    #   , IATscore = scale(IATscore) %>% as.vector
    # )

  otm1_demo$frameRate <- modal_frame_rate(otm1_log)
  otm1_mem <- left_join(otm1_mem, otm1_demo, by = "ParticipantNumber")

  otm1_mem <- otm1_mem %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , Sex = gsub("^w|weiblich|v|vrouw|woman|f$", "female", Gender, ignore.case = TRUE) %>% tolower
      , Age = as.numeric(gsub("\\W", "", Age))
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
      , Accuracy = NumbercorrectIdent / 20
    )

  rm("otm1_log", "otm1_demo")

  # Save processed data
  saveRDS(otm1_attitudes, paste0(processed_data_path, "otm1_attitudes.rds"))
  saveRDS(otm1_iat, paste0(processed_data_path, "otm1_iat_trial_data.rds"))
  saveRDS(otm1_mem, paste0(processed_data_path, "otm1_memory.rds"))
} else {
  otm1_attitudes <- readRDS(paste0(processed_data_path, "otm1_attitudes.rds"))
  otm1_iat <- readRDS(paste0(processed_data_path, "otm1_iat_trial_data.rds"))
  otm1_mem <- readRDS(paste0(processed_data_path, "otm1_memory.rds"))
}
```

As the results reported by @heycke_two_2018 could have been the result of the modifications to the experimental procedure, we conducted a replication study using the unmodified experimental procedure of the original study.

## Methods

Materials and procedure were inspected by the first author of the original study to ensure that they closely corresponded to the original.
The experiment was preregistered (https://osf.io/xe8au/) and data were collected in Germany, Belgium, and the United States.
All data files, materials and analysis files are available at https://osf.io/8m3xb/.

### Material & Procedure

The experimental procedure consisted of three components: learning task, evaluation task, and US recognition task.

As in the original study, the learning task was a modified version of the evaluative learning paradigm by @kerpelmanPartialReinforcementEffects1971. 
We briefly presented a US followed by a longer presentation of a picture of Bob together with a statement that described the behavior of Bob.
Presentation durations differed across labs due to the availability of different refresh rates of the CRT monitors (85 Hz in the United States and 75 Hz in Belgium and Germany).
In the following we will describe the setup of a trial with the presentation durations at a 75 Hz-refresh rate; deviating durations for a 85 Hz-refresh rate are given in brackets.

On each trial, a central fixation cross was displayed for 200 ms followed by a US displayed for 27 ms (24 ms; 2 frames).
USs were immediately replaced by the picture of Bob, which served as a backward mask.
The picture of Bob was presented in the center of the screen for 253 ms (247 ms) before the behavioral information was added underneath.
The screen background was black and text was colored white and set in Times New Roman font. 
Participants’ task was to press the "c" (= "characteristic") or "u" (= "uncharacteristic") key to judge whether the behavioral information was characteristic or uncharacteristic of Bob, which was displayed on the screen during the judgment phase. 
After every judgment, the image of Bob, the behavioral statement, and the key labels were replaced with either the word "Correct" displayed in green letters or the word "False" in red letters, displayed for 5000 ms. 
Each trial ended with a blank screen presented for 1000 ms.

As US valence was manipulated within participants, they completed two 100-trial-blocks of the learning task.
Each block consisted of trials with either only positive or negative USs and the order of USs was randomized. 
In blocks with positive USs, positive behavioral information was always uncharacteristic of Bob and negative information was characteristic. 
These contingencies were reversed in the blocks with negative USs. 
We used 10 positive and 10 negative words as USs each of which was presented 10 times. 
For behavioral information, we used 100 positive and 100 negative statements. 
50 positive and 50 negative statements were randomly selected for the first block, the remaining statements were assigned to the second block. 
The order of USs and behavioral information was randomized for each participant anew, whereas the order of blocks was counterbalanced across participants. 
A different picture of Bob was randomly selected from six pictures of white males for each participant. 
The remaining five images were used in the implicit evaluation measure (see below). 
All materials were taken from the original study, with the sole exception that US words, behavioral information, and instructions were translated to German and Dutch for use in Germany and Belgium.

After each block, participants completed implicit and explicit evaluation measures. 
As in the original study, the order of the measures was the same for both blocks but counterbalanced across participants.

The explicit evaluation consisted of three parts, each presented on a single screen:
First, participants rated Bob's likableness on a 9-point slider with the anchors labelled *Very Unlikable* and *Very Likable*.
Next, again using 9-point sliders, they judged Bob on the dimensions *Bad--Good*, *Mean--Pleasant*, *Disagreeable--Agreeable*, *Uncaring--Caring*, and *Cruel--Kind*. 
Finally, they judged Bob on a 'feeling thermometer' by entering a number between 0 (*Extremely unfavorable*) and 100 (*Extremely favorable*).
Deviating from the original protocol, we collected explicit evaluations as part of the computer task rather than using a paper-pencil questionnaire.

We assessed the implicit evaluations using the IAT described by @rydell_two_2006. 
Participants initially completed two types of training blocks with 20 trials each to familiarize themselves with the task. 
In one block, images of Bob and other white men had to be classified as Bob vs. not-Bob; in another block, positive and negative words had to be classified as positive vs. negative. 
In a subsequent critical block with 40 trials we intermixed the two classification tasks: 
Participants used one key to respond to both the images of Bob and negative words; they used another key to respond to images of other white men and positive words. 
After the first critical block, participants completed another training block with 20 trials of Bob vs. not-Bob with reversed key position and afterwards a second critical block with 40 trials with the reversed key mapping compared to the first critical block. 
It was counterbalanced whether participants completed the IAT with the key mappings described above or with key mappings in reversed order [for a detailed description see @heycke_two_2018, p. 1712].

After completing the explicit and implicit evaluation measures, participants completed the second learning block and again completed implicit and explicit evaluations.
Following the second set of evaluations, participants completed a surprise US recognition task.
We presented 40 words in random order on a computer screen.
Half of the words were the briefly presented USs from the learning task, the other half were new distractor words.
We informed participants that 20 words were presented briefly during the learning task, asked them to select the briefly presented words from the list, and encouraged them to guess if they did not know the correct answer.
Participants could only proceed with the experiment once they had selected exactly 20 words.

The experiment ended with a demographic questionnaire (age, field of study/profession, gender, goal of the experiment, and comments).
Our procedure was identical to the original procedure, with the exception that participants completed explicit evaluation and US recognition tasks at the computer rather than using paper and pencil.
In Belgium and Germany, we furthermore used Dutch and German translations of the original material.
The procedure took approximately 50 minutes to complete.

### Participants

```{r otm1-check-data-integrity, cache = TRUE}
# Exclude participants due to technical failures
otm1_technical_failure <- c("345", "347")
otm1_technical_failure_expression <- expression(!as.character(ParticipantNumber) %in% otm1_technical_failure)

otm1_attitudes <- filter(otm1_attitudes, eval(otm1_technical_failure_expression)) %>%
  mutate(ParticipantNumber = factor(ParticipantNumber))
otm1_iat <- filter(otm1_iat, eval(otm1_technical_failure_expression)) %>% droplevels
otm1_mem <- filter(otm1_mem, eval(otm1_technical_failure_expression)) %>% droplevels

# Check for incomplete data
otm1_n_trials <- aggregate(Eval ~ ParticipantNumber, otm1_attitudes, length) %>%
  full_join(
    aggregate(RT ~ ParticipantNumber, otm1_iat, length)
    , by = "ParticipantNumber"
    ) %>%
  full_join(
    aggregate(NumbercorrectIdent ~ ParticipantNumber, otm1_mem, length)
    , by = "ParticipantNumber"
  )

otm1_incomplete_data <- otm1_n_trials$ParticipantNumber[
  with(
    otm1_n_trials
    , Eval != 2 ||
      RT != 160 ||
      NumbercorrectIdent != 1
  )
]

if(length(otm1_incomplete_data) > 0) warning(
  "Incomplete datasets: "
  , paste(otm1_incomplete_data, collapse = ", ")
)

# Check frame rate
otm1_frame_rate <- otm1_mem$ParticipantNumber[
  with(
    otm1_mem
    , (Location == "Cologne" & frameRate != 75) ||
      (Location == "Ghent" & frameRate != 75) ||
      (Location == "Harvard" & frameRate != 85)
  )
]

if(length(otm1_frame_rate) > 0) warning(
  "Incorrect frame rates: "
  , paste(otm1_frame_rate, collapse = ", ")
)
```

```{r otm1-exclusion, cache = TRUE}
otm1_noncompliance <- c()
otm1_exclude <- c(otm1_incomplete_data, otm1_frame_rate) %>%
  unique

otm1_n_excluded <- as.integer(length(c(otm1_exclude, otm1_technical_failure)))

otm1_exclusion_expression <- expression(!ParticipantNumber %in% otm1_exclude)

otm1_attitudes <- filter(otm1_attitudes, eval(otm1_exclusion_expression)) %>% droplevels
otm1_iat <- filter(otm1_iat, eval(otm1_exclusion_expression)) %>% droplevels
otm1_mem <- filter(otm1_mem, eval(otm1_exclusion_expression)) %>% droplevels

# Save cleaned data
saveRDS(otm1_attitudes, paste0(processed_data_path, "otm1_attitudes_cleaned.rds"))
saveRDS(otm1_iat, paste0(processed_data_path, "otm1_iat_trial_data_cleaned.rds"))
saveRDS(otm1_mem, paste0(processed_data_path, "otm1_memory_cleaned.rds"))

otm1_n <- as.integer(nlevels(otm1_attitudes$ParticipantNumber))
```

We set out to collect $N = 50$ participants at each location [@rydell_two_2006].
For each evaluation measure, the data from all three labs ($N = 150$) provides 95% power to observe two-way interaction effects as small as $f = 0.15$ ($d = 0.30$) and contrasts between blocks of the learning task as small as $d_z = 0.27$ [$\alpha = \beta = .05$, repeated-measures correlation $r = .5$, @nosek_implicit_2007].
Our design was, thus, adequately powered to detect effects half the size of those reported by @rydell_two_2006.
We recruited `r otm1_n + otm1_n_excluded` participants (aged `r paste(range(otm1_mem$Age), collapse = "-")` years, $M = `r mean(otm1_mem$Age)`$; `r sum(grepl("female", otm1_mem$Sex)) / nrow(otm1_mem) * 100`% female, `r printnum(sum(grepl("nonbinary", otm1_mem$Sex)) / nrow(otm1_mem) * 100)`% nonbinary; see supplementary online material (SOM) for details); `r printnum(otm1_n_excluded, numerals = otm1_n_excluded > 10, capitalize = TRUE)` participants were excluded due to technical failure<!-- or noncompliance with instructions-->.
Hence, the following results are based on data from `r otm1_n` participants.
We compensated all participants with either € 8/10 (Cologne/Ghent), or partial course credit (Cologne/Harvard).

### Data analysis

How to evaluate the success of a replication attempt statistically is subject of current debate [e.g., @fabrigar_conceptualizing_2016; @simonsohn_small_2013; @verhagen_bayesian_2014]. 
Whether a pattern of results has been replicated is challenging to assess directly if the to-be-replicated pattern consists of more than two cells of a factorial design.
One elegant approach is to instantiate a pattern of mean differences (i.e., the rank order of means), predicted by a theory or observed in a previous study, as order constraints in a statistical model [e.g., @hoijtink_informative_2012; @rouder_theories_2018].
With the model in hand, replication success can be quantified as predictive accuracy of this model relative to a competing model, such as a null model or an encompassing unconstrained model [e.g., @rouder_theories_2018].

Based on previously reported results, there are two competing predictions for the current paradigm:
(1) @rydell_two_2006 found that across both measurement times explicit ratings were congruent with the learned behavioral information about Bob, whereas IAT scores were incongruent with learned behavioral information ($\mathcal{H}_\textrm{Two minds}$).
(2) In contrast, @heycke_two_2018 observed the same pattern for explicit ratings and IAT scores; across both measurement times both measures were congruent with the learned behavioral information ($\mathcal{H}_\textrm{One mind}$).
We considered two additional predictions: no effect of the manipulation ($\mathcal{H}_\textrm{No effect}$) and the all-encompassing prediction of any outcome ($\mathcal{H}_\textrm{Any effect}$).
If, of all predictions considered, our results are best described by the prediction of no effect, our experimental manipulations did not succeed.
The prediction of any effects serves as a control and reflects the possibility that we may observe an entirely unexpected outcome that is neither in line with the results reported by @rydell_two_2006 or @heycke_two_2018.

We implemented all predictions as order (or null) constraints in an ANOVA model with default (multivariate) Cauchy priors [$r = 0.5$ for fixed effects and $r = 1$ for random participant effects, see SOM for details; @rouder_default_2012; @rouder_theories_2018].
To evaluate the relative predictive accuracy of these models we performed Bayesian model comparison using Bayes factors.
To test whether recognition memory performance was above chance we used a one-tailed Bayesian $t$ test with default Cauchy prior [$r = \sqrt2/2$; @rouder_bayesian_2009].
We also report the results of the analyses described by @rydell_two_2006 to facilitate comparisons with previously reported statistics.

For both analyses, we processed the IAT response times as described in the original study [for details see @rydell_two_2006; @heycke_two_2018].
To ensure that our conclusions are robust to stimulus effects, we additionally supplemented the ANOVA analysis of IAT scores by a frequentist linear mixed model analysis, see SOM.
To simplify the presentation of the Bayesian model comparison results, we collapsed data across valence orders by reversing the coding of the blocks when learned behaviors were first negative and subsequently positive.
Thus, for both explicit and implicit evaluation measures we contrasted the first with the second block, such that positive values represent a more positive evaluation following the block in which learned behaviors were positive and USs negative.
We used `r cite_r("r-references.bib", pkgs = c("papaja", "afex", "emmeans", "BayesFactor"), withhold = FALSE)` for all our analyses.

## Results

In the following, *valence order* refers to the joint order of learned behaviors and briefly presented USs.
Any time we refer to one valence order (e.g., positive-negative) we specify the order of the learned behavior; the corresponding briefly presented USs were always of the opposite valence.

```{r otm1-rating-plot, warning = FALSE}
otm1_results_legend <- guide_legend(
    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
    title = expression(atop("Valence order", atop(scriptstyle("Learned behaviors"), scriptstyle("(Briefly presented USs)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
  )

otm1_rating_plot <- otm1_attitudes %>%
  mutate(ValenceBlock = ifelse(ValenceBlock == "Positive-negative", " Positive-negative\n(Negative-positive)", " Negative-positive\n(Positive-negative)")) %>%
  ggplot(aes(x = Block, y = Eval, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
  geom_violin(position = position_dodge(0.1), alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(position = position_dodge(0.1), maxwidth = 0.35, alpha = 0.5, size = 0.5) +
  stat_summary(fun.y = mean, aes(group = ValenceBlock, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000), geom = "pointrange", size = 0.6) +
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1)) +
  scale_color_viridis_d(option = "C", begin = 0.1, end = 0.9, guide = otm1_results_legend) +
  scale_fill_viridis_d(option = "C", begin = 0.1, end = 0.9, guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23), guide = otm1_results_legend) +
  labs(
    x = "Learning block"
    # , y = " \nExplicit attitude score"
    , y = expression(atop(phantom(group("[", Delta~log(s), "]")), "Rating score"))
  ) +
  guides(linetype = otm1_results_legend) +
  facet_wrap(~ Location) +
  theme(
    legend.position = "top"
    , legend.justification = "center"
  )
```

```{r otm1-iatscore-plot, fig.cap = "(ref:omt1-iatscore-plot)", warning = FALSE}
otm1_iatscore_plot <- otm1_attitudes %>%
  mutate(ValenceBlock = ifelse(ValenceBlock == "Positive-negative", " Positive-negative\n(Negative-positive)", " Negative-positive\n(Positive-negative)")) %>%
  ggplot(aes(x = Block, y = IATscore, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
  geom_violin(position = position_dodge(0.1), alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(position = position_dodge(0.1), maxwidth = 0.35, alpha = 0.5, size = 0.5) +
  stat_summary(fun.y = mean, aes(group = ValenceBlock, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000), geom = "pointrange", size = 0.6) +
  scale_color_viridis_d(option = "C", begin = 0.1, end = 0.9, guide = otm1_results_legend) +
  scale_fill_viridis_d(option = "C", begin = 0.1, end = 0.9, guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23)) +
  labs(
    x = "Learning block"
    # , y = "IAT response time\ndifference [log(s)]"
    , y = expression(atop("IAT response time", "difference"~group("[", Delta~log(s), "]")))
  ) +
  facet_wrap(~ Location) +
  theme(legend.position = "none")
```

(ref:otm1-factorial-results-plot) Evaluative rating and IAT scores for Experiments 1 (**A**) and Experiment 2 (**B**).
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participants' responses, and violins represent kernel density estimates of sample distributions.

```{r otm1-factorial-results-plot, fig.cap = "(ref:otm1-factorial-results-plot)", fig.height = 10, fig.width = 8, warning = FALSE}
plot_grid(
  gglegend(otm1_rating_plot)
  , NULL
  , otm1_rating_plot +
    theme(
      axis.title.x = element_blank()
      , axis.ticks.x = element_blank()
      , axis.text.x = element_blank()
      , axis.title.y = element_text(lineheight = 1.7)
      , strip.background = element_blank()
      , legend.position = "none"
    ) 
  , NULL
  , otm1_iatscore_plot + 
    theme(strip.text.x = element_blank())
  , NULL
  , otm1_rating_plot +
    theme(
      axis.title.x = element_blank()
      , axis.ticks.x = element_blank()
      , axis.text.x = element_blank()
      , axis.title.y = element_text(lineheight = 1.7)
      , strip.background = element_blank()
      , strip.text.x = element_text(color = "white")
      , legend.position = "none"
    ) + geom_rect(xmin = -5, xmax = 5, ymin = -10, ymax = 10, fill = "white", color = "white")
  , NULL
  , otm1_iatscore_plot + 
    theme(strip.text.x = element_blank()) + geom_rect(xmin = -5, xmax = 5, ymin = -10, ymax = 10, fill = "white", color = "white")
  , ncol = 1
  , rel_heights = c(0.5, 0.05, 0.95, 0.05, 1, 0.05, 0.95, 0.05, 1)
  , labels = c("", "", "A", "", "", "", "B", "", "")
)
```

```{r otm1-rydell-analysis-overall, results = "asis"}
otm1_attitudes_aov <- otm1_attitudes %>%
  mutate(
    Eval = scale(Eval) %>% as.numeric
    , IATscore = scale(IATscore) %>% as.numeric
  ) %>%
  gather("Measure", "Attitude", Eval, IATscore) %>%
  mutate(Measure = factor(Measure)) %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Attitude"
    , within = c("Block", "Measure")
    # , between = "ValenceBlock"
    , between = c("ValenceBlock", "Location")
    , data = .
  )

otm1_attitudes_aov_res <- otm1_attitudes_aov %>%
  apa_print

# Split analyses by Location
otm1_attitudes_location_aov <- otm1_attitudes_aov %>% 
  ref_grid %>% 
  joint_tests(by = "Location") %>%
  filter(`model term` == "ValenceBlock:Measure:Block")
```

In the joint analysis of implicit and explicit evaluations, we found the three-way interaction between valence order, learning block, and evaluation measure, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Block_Measure` previously reported by @rydell_two_2006 (Figure\ \@ref(fig:otm1-factorial-results-plot)).
Moreover, we found that the three-way interaction was significant in each lab (all $F(`r unique(otm1_attitudes_location_aov$df1)`, `r unique(otm1_attitudes_location_aov$df2)`) > `r min(otm1_attitudes_location_aov$F.ratio)`$, $p `r printp(max(otm1_attitudes_location_aov$p.value))`$), but differed slightly in magnitude, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Location_Block_Measure`. 
The direction of the effect was consistent across labs.
As in the original analysis we examined the significant three-way interaction with separate analyses of each evaluation measure.

### Explicit evaluation

```{r otm1-rydell-analysis-explicit, results = "asis"}
otm1_explicit_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "Eval"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Location")
  , data = otm1_attitudes
)

otm1_explicit_aov_res <- otm1_explicit_aov %>%
  apa_print

# Split analyses by Location
otm1_explicit_location_aov <- otm1_explicit_aov %>% 
  ref_grid %>% 
  joint_tests(by = "Location") %>%
  filter(`model term` == "ValenceBlock:Block")
```

```{r otm1-rydell-analysis-explicit2, results = "asis"}
otm1_explicit_contrasts <- emmeans(otm1_explicit_aov, ~ Block | ValenceBlock) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  ) %>%
  apa_print

# Split analyses by Location
otm1_explicit_location_contrasts <- emmeans(otm1_explicit_aov, ~ Block | ValenceBlock * Location) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  )

otm1_explicit_location_contrasts_res <- otm1_explicit_location_contrasts %>%
  apa_print

otm1_explicit_location_contrasts <- otm1_explicit_location_contrasts %>%
  as.data.frame

otm1_explicit_location_pos_neg_contrasts <- otm1_explicit_location_contrasts %>%
    filter(ValenceBlock == "Positive-negative")

otm1_explicit_location_neg_pos_contrasts <- otm1_explicit_location_contrasts %>%
    filter(ValenceBlock == "Negative-positive")
```

As in the previous studies, we found a two-way interaction between valence order and learning block, `r otm1_explicit_aov_res$full_result$ValenceBlock_Block`.
This interaction was significant in each lab (all $F(`r unique(otm1_explicit_location_aov$df1)`, `r unique(otm1_explicit_location_aov$df2)`) > `r min(otm1_explicit_location_aov$F.ratio)`$, $p `r printp(max(otm1_explicit_location_aov$p.value))`$), but also differed between labs, `r otm1_explicit_aov_res$full_result$ValenceBlock_Location_Block`.
In all labs, ratings of Bob were more favorable after the first than after the second block when learned behaviors were first positive and later negative, 
Cologne: `r otm1_explicit_location_contrasts_res$estimate$Positive_negative_Cologne_Block2_Block1`; 
Ghent: `r otm1_explicit_location_contrasts_res$estimate$Positive_negative_Ghent_Block2_Block1`; 
Harvard: `r otm1_explicit_location_contrasts_res$estimate$Positive_negative_Harvard_Block2_Block1`; 
all $t(`r unique(otm1_explicit_location_pos_neg_contrasts$df)`) < `r max(otm1_explicit_location_pos_neg_contrasts$t.ratio)`$, $p$ `r printp(max(otm1_explicit_location_pos_neg_contrasts$p.value))`.
Vice versa, in all labs, ratings of Bob were more favorable after the second than after the first block when learned behaviors were first negative and later positive, 
Cologne: `r otm1_explicit_location_contrasts_res$estimate$Negative_positive_Cologne_Block2_Block1`; 
Ghent: `r otm1_explicit_location_contrasts_res$estimate$Negative_positive_Ghent_Block2_Block1`; 
Harvard: `r otm1_explicit_location_contrasts_res$estimate$Negative_positive_Harvard_Block2_Block1`; 
all $t(`r unique(otm1_explicit_location_neg_pos_contrasts$df)`) < `r max(otm1_explicit_location_neg_pos_contrasts$t.ratio)`$, $p$ `r printp(max(otm1_explicit_location_neg_pos_contrasts$p.value))`.
Hence, the predicted differences were consistently detectable in all labs but differed in magnitude.
No other effects were significant.

### Implicit evaluation

```{r otm1-rydell-analysis-implicit, results = "asis"}
otm1_iat_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "IATscore"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Location")
  , data = otm1_attitudes
)

otm1_iat_aov_res <- otm1_iat_aov %>%
  apa_print
```

```{r otm1-rydell-analysis-implicit2, results = "asis"}
otm1_implicit_contrasts <- emmeans(otm1_iat_aov, ~ Block | ValenceBlock) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  ) %>%
  apa_print 
```

For IAT scores, we found a two-way interaction between valence order and learning block, `r otm1_iat_aov_res$full_result$ValenceBlock_Block`; in this case we detected no differences between labs, `r otm1_iat_aov_res$full_result$ValenceBlock_Location_Block`.
IAT scores for Bob were larger, indicating a more favorable attitude, after the first than after the second block when learned behaviors were first positive and later negative, `r otm1_implicit_contrasts$full_result$Positive_negative_Block2_Block1`.
Vice versa, IAT scores for Bob were larger after the second than after the first block when learned behaviors were first negative and later positive, `r otm1_implicit_contrasts$full_result$Negative_positive_Block2_Block1`.
The results of the mixed model analysis were in line with the conclusions from the ANOVA analysis, see SOM.
Hence, evaluations of Bob assessed with the IAT corresponded to the valence of the learned behaviors and contradicted the valence of the briefly presented USs.
Explicit ratings and IAT scores did not dissociate.

### Differences between implicit and explicit evaluations

As in the original study, we additionally compared participants' $z$ standardized evaluations toward Bob assessed by ratings and IAT scores.

```{r otm1-rydell-attitude-differences, results = "asis"}
otm1_attitudes_measure_contrasts <- otm1_attitudes_aov %>% 
  emmeans(~ Measure | ValenceBlock * Block) %>% 
  pairs %>%
  apa_print
```

Evaluations assessed by rating and IAT scores differed in all conditions.
Ratings of Bob were more favorable than IAT scores in the first block, `r otm1_attitudes_measure_contrasts$full_result$Positive_negative_X1_Eval_IATscore`, but less favorable in the second block when learned behaviors were first positive and later negative, `r otm1_attitudes_measure_contrasts$full_result$Positive_negative_X2_Eval_IATscore`.
Conversely, ratings of Bob were less favorable than IAT scores in the first block, `r otm1_attitudes_measure_contrasts$full_result$Negative_positive_X1_Eval_IATscore`, but more favorable in the second block when learned behaviors were first positive and later negative, `r otm1_attitudes_measure_contrasts$full_result$Negative_positive_X2_Eval_IATscore`.
Given that evaluations were consistent in valence across measures, these differences indicate that evaluations assessed by ratings were more extreme than those assessed by IAT scores.

### Bayesian model comparisons

```{r otm1-bayesian-replication-restructure, cache = TRUE, warning=FALSE}
# Collapse across ValcenceOrder
otm1_attitudes_collapsed <- otm1_attitudes %>% 
  mutate(
    Block = ifelse(ValenceBlock == "Negative-positive", 3 - as.numeric(as.character(Block)), Block) %>% factor
  ) %>%
  select(-ValenceBlock) %>%
  mutate(Eval = scale(Eval) %>% as.vector, IATscore = scale(IATscore) %>% as.vector) %>%
  gather("Measure", "Attitude", Eval, IATscore)
```

```{r otm1-bayesian-replication-design-matrix, cache = TRUE, warning=FALSE}
# Participant random intercepts
otm1_random_participant_intercept_matrix <- BayesFactor:::oneDesignMatrix(
  trm = "ParticipantNumber"
  , data = otm1_attitudes_collapsed
  , dataTypes = c("ParticipantNumber" = "random")
) %>% as.matrix

# Fixed effects
## No main effect of attitude measure due to z standardization
unconstrained_effect_model <- function(x, a, b = NULL) {
  coding <- c(
    eta1 = 0, eta2 = 0
    , alpha = 0, tau1 = 0, tau2 = 0
    , beta = 0, upsilon1 = 0, upsilon2 = 0
  )

  # Main effect Location
  if(!is.null(b)) {
    switch(
      x["Location"]
      , Cologne = coding[c("eta1", "eta2")] <- b[1, ]
      , Ghent = coding[c("eta1", "eta2")] <- b[2, ]
      , Harvard = coding[c("eta1", "eta2")] <- b[3, ]
    )
  } else {
    coding <- coding[, c("alpha", "beta")]
  }

  # Simple block effects
  if(x["Measure"] == "Eval") {

    # alpha = Simple block effect for ratings
    if(x["Block"] == "1") {
      coding["alpha"] <- a[2, 1]
    } else {
      coding["alpha"] <- a[1, 1]
    }

    # tau = Interaction of alpha with location location
    if(!is.null(b)) {
      coding[c("tau1", "tau2")] <- coding[c("eta1", "eta2")] * coding["alpha"]
    }

  } else {

    # beta = Simple block effect for IATscore
    if(x["Block"] == "1") {
      coding["beta"] <- a[2, 1]
    } else {
      coding["beta"] <- a[1, 1]
    }

    # upsilon = Interaction of beta with location location
    if(!is.null(b)) {
      coding[c("upsilon1", "upsilon2")] <- coding[c("eta1", "eta2")] * coding["beta"]
    }
  }

  coding
}

a <- BayesFactor:::fixedFromRandomProjection(nlevels(otm1_attitudes_collapsed$Block))
b <- BayesFactor:::fixedFromRandomProjection(nlevels(otm1_attitudes_collapsed$Location))

otm1_fixed_effects_matrix <- t(apply(
  otm1_attitudes_collapsed
  , 1
  , unconstrained_effect_model
  , a = a
  , b = b
))

otm1_unconstrained_model_matrix <- cbind(
  otm1_fixed_effects_matrix
  , otm1_random_participant_intercept_matrix
)

otm1_no_lab_effect_model_matrix <- otm1_unconstrained_model_matrix[, -which(colnames(otm1_unconstrained_model_matrix) %in% c("tau1", "tau2", "upsilon1", "upsilon2"))]

otm1_null_model_matrix <- otm1_unconstrained_model_matrix[, -which(colnames(otm1_unconstrained_model_matrix) %in% c("alpha", "tau1", "tau2", "beta", "upsilon1", "upsilon2"))]
```

```{r otm1-bayesian-replication-analysis, cache = TRUE, warning=FALSE}
# No effect model
otm1_no_effect <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_null_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , nu = rep(1, otm1_n)
  )
  , rscale = c(fixed = 0.5, random = 1)
  , iterations = otm1_n_mcmc_samples
)

# Fixed effect model
otm1_unconstrained <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_unconstrained_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1, tau = rep(2, 2)
    , beta = 3, upsilon = rep(4, 2)
    , nu = rep(5, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , iterations = otm1_n_mcmc_samples
)
otm1_unconstrained_bf <- exp(otm1_unconstrained$bf - otm1_no_effect$bf)

# otm1_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_unconstrained_bf
#   , ratio_subscript = "\\mathcal{M}_\\textrm{unconstrained effect}/\\mathcal{M}_\\textrm{no effect}"
#   , escape = FALSE
# )

# No lab effects model
otm1_no_lab_effect <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_no_lab_effect_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1
    , beta = 2
    , nu = rep(3, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 3), random = 1)
  , iterations = otm1_n_mcmc_samples
)
otm1_no_lab_effect_bf <- exp(otm1_no_lab_effect$bf - otm1_no_effect$bf)

# otm1_no_lab_effect_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_no_lab_effect_bf
#   , ratio_subscript = "\\mathcal{M}_\\textrm{no lab effects}/\\mathcal{M}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm1-bayesian-replication-analysis-samples, cache = TRUE, warning=FALSE}
# Fixed effect model
otm1_unconstrained_samples <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_unconstrained_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1, tau = rep(2, 2)
    , beta = 3, upsilon = rep(4, 2)
    , nu = rep(5, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , posterior = TRUE
  , iterations = otm1_n_mcmc_samples
)
colnames(otm1_unconstrained_samples)[1:ncol(otm1_fixed_effects_matrix) + 1] <- colnames(otm1_fixed_effects_matrix)

otm1_unconstrained_samples <- otm1_unconstrained_samples %>%
  as.data.frame %>%
  mutate(
    alpha_cologne = alpha + tau1
    , alpha_ghent =  alpha + tau1 - tau2
    , alpha_harvard = alpha - tau1 - tau2
    , beta_cologne = beta + upsilon1
    , beta_ghent = beta + upsilon1 - upsilon2
    , beta_harvard = beta - upsilon1 - upsilon2
  ) %>%
  as.matrix
```

```{r otm1-bayesian-replication-analysis-same, warning=FALSE}
# Fixed effect model
otm1_same_direction_boost <- 4 * (
  (sum(
    otm1_unconstrained_samples[, "alpha"] > 0 &
    otm1_unconstrained_samples[, "beta"] > 0
  ) + 1) / (nrow(otm1_unconstrained_samples) + 2)
)
otm1_same_direction_bf <- otm1_unconstrained_bf * otm1_same_direction_boost

otm1_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_same_direction_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{No effect}"
  , escape = FALSE
)

## Same direction in all labs
otm1_all_labs_same_direction_boost <- 12 * (
  (sum(
    otm1_unconstrained_samples[, "alpha_cologne"] > 0 &
    otm1_unconstrained_samples[, "beta_cologne"] > 0 &
    otm1_unconstrained_samples[, "alpha_ghent"] > 0 &
    otm1_unconstrained_samples[, "beta_ghent"] > 0 &
    otm1_unconstrained_samples[, "alpha_harvard"] > 0 &
    otm1_unconstrained_samples[, "beta_harvard"] > 0
  ) + 1) / (nrow(otm1_unconstrained_samples) + 2)
)
otm1_all_labs_same_direction_bf <- otm1_unconstrained_bf * otm1_all_labs_same_direction_boost

# otm1_all_labs_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_all_labs_same_direction_bf
#   , ratio_subscript = "\\mathcal{M}_\\textrm{same direction}/\\mathcal{M}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm1-bayesian-replication-analysis-opposite, warning=FALSE}
# Fixed effect model
otm1_opposite_direction_boost <- 4 * (
  (sum(
    otm1_unconstrained_samples[, "alpha"] > 0 &
    otm1_unconstrained_samples[, "beta"] < 0
  ) + 1) / (nrow(otm1_unconstrained_samples) + 2)
)
otm1_opposite_direction_bf <- otm1_unconstrained_bf * otm1_opposite_direction_boost

otm1_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_opposite_direction_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{Two minds}/\\mathcal{M}_\\textrm{No effect}"
  , escape = FALSE
  , auto_invert = FALSE
)

## Opposite direction in all locations
otm1_all_labs_opposite_direction_boost <- 12 * (
  (sum(
    otm1_unconstrained_samples[, "alpha_cologne"] > 0 &
    otm1_unconstrained_samples[, "beta_cologne"] < 0 &
    otm1_unconstrained_samples[, "alpha_ghent"] > 0 &
    otm1_unconstrained_samples[, "beta_ghent"] < 0 &
    otm1_unconstrained_samples[, "alpha_harvard"] > 0 &
    otm1_unconstrained_samples[, "beta_harvard"] < 0
  ) + 1) / (nrow(otm1_unconstrained_samples) + 2)
)
otm1_all_labs_opposite_direction_bf <- otm1_unconstrained_bf * otm1_all_labs_opposite_direction_boost

# otm1_all_labs_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_all_opposite_direction_bf
#   , ratio_subscript = "\\mathcal{M}_\\textrm{opposite direction}/\\mathcal{M}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm1-bayesian-replication-analysis-targeted-comparisons, warning=FALSE}
otm1_same_vs_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_same_direction_bf / otm1_opposite_direction_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Two minds}"
  , escape = FALSE
)

otm1_same_direction_vs_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_same_direction_bf / otm1_unconstrained_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Any effect}"
  , escape = FALSE
)

# In all labs
otm1_all_labs_same_direction_vs_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_all_labs_same_direction_bf / otm1_unconstrained_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{One mind everywhere}/\\mathcal{M}_\\textrm{Any effect}"
  , escape = FALSE
)

otm1_all_labs_same_vs_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_all_labs_same_direction_bf / otm1_same_direction_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{One mind everywhere}/\\mathcal{M}_\\textrm{One mind}"
  , escape = FALSE
)

otm1_no_lab_effect_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_no_lab_effect_bf / otm1_unconstrained_bf
  , ratio_subscript = "\\mathcal{M}_\\textrm{No lab effects}/\\mathcal{M}_\\textrm{Any effect}"
  , escape = FALSE
)
```

(ref:bayesian-replication-analysis-plot) Predictions of the four models of primary interest (**A**) and results of Experiment 1 and Experiment 2 (**B**).
Black-rimmed points represent means of observed attitude differences between learning blocks with positive and negative learned behaviors.
Positive values indicate that attitudes correspond to the valence of learned behaviors and contradict the valence of the briefly presented USs.
Ellipses represent 95% Bayesian credible intervals based on the unconstrained model $\mathcal{M}_\textrm{Any effect}$.

```{r otm1-effects-plot, cache = TRUE, warning=FALSE}
otm1_unconstrained_pp <- otm1_unconstrained_samples %>%
  as.data.frame %>%
  select(alpha:upsilon2) %>%
  mutate(
    Eval_Cologne =   a[2, 1] * alpha + b[1, 1] * a[2, 1] * tau1 + b[1, 2] * a[2, 1] * tau2 -
                    (a[1, 1] * alpha + b[1, 1] * a[1, 1] * tau1 + b[1, 2] * a[1, 1] * tau2)
    , Eval_Ghent =   a[2, 1] * alpha + b[2, 1] * a[2, 1] * tau1 + b[2, 2] * a[2, 1] * tau2 -
                    (a[1, 1] * alpha + b[2, 1] * a[1, 1] * tau1 + b[2, 2] * a[1, 1] * tau2)
    , Eval_Harvard = a[2, 1] * alpha + b[3, 1] * a[2, 1] * tau1 + b[3, 2] * a[2, 1] * tau2 -
                    (a[1, 1] * alpha + b[3, 1] * a[1, 1] * tau1 + b[3, 2] * a[1, 1] * tau2)

    , IATscore_Cologne =  a[2, 1] * beta  + b[1, 1] * a[2, 1] * upsilon1 + b[1, 2] * a[2, 1] * upsilon2 -
                         (a[1, 1] * beta  + b[1, 1] * a[1, 1] * upsilon1 + b[1, 2] * a[1, 1] * upsilon2)
    , IATscore_Ghent =    a[2, 1] * beta  + b[2, 1] * a[2, 1] * upsilon1 + b[2, 2] * a[2, 1] * upsilon2 -
                         (a[1, 1] * beta  + b[2, 1] * a[1, 1] * upsilon1 + b[2, 2] * a[1, 1] * upsilon2)
    , IATscore_Harvard =  a[2, 1] * beta  + b[3, 1] * a[2, 1] * upsilon1 + b[3, 2] * a[2, 1] * upsilon2 -
                         (a[1, 1] * beta  + b[3, 1] * a[1, 1] * upsilon1 + b[3, 2] * a[1, 1] * upsilon2)

    , Eval_Overall =     a[2, 1] * alpha - (a[1, 1] * alpha)
    , IATscore_Overall = a[2, 1] * beta  - (a[1, 1] * beta)
  ) %>%
  select(-c(alpha:upsilon2)) %>%
  gather(effect, value) %>%
  mutate(iteration = rep(1:nrow(otm1_unconstrained_samples), 8)) %>%
  separate(effect, c("Measure", "Location")) %>%
  spread(Measure, value)

otm1_attitudes_delta <- otm1_attitudes_collapsed %>%
  spread(Block, Attitude) %>%
  mutate(delta = `1` - `2`) %>%
  select(-`1`, -`2`)

otm1_attitudes_delta_summary <- otm1_attitudes_delta %>%
  group_by(Measure) %>%
  summarize(delta = mean(delta)) %>%
  ungroup %>%
  spread(Measure, delta)

otm1_attitudes_delta_summary <- otm1_attitudes_delta %>%
  group_by(Measure, Location) %>%
  summarize(delta = mean(delta)) %>%
  ungroup %>%
  spread(Measure, delta) %>%
  rbind(cbind(Location = "Overall", otm1_attitudes_delta_summary))

# heycke_descriptives <- data.frame(
#     Eval = c(0.99, -0.8, -0.85, 0.75)
#     # Eval_mean = c(0.99, -0.8, -0.85, 0.75)
#     # , Explicit_se = c(0.12, 0.15, 0.12, 0.15)
#     , IATscore = c(0.6, -0.21, -0.3, -0.1)
#     # , IATscore_mean = c(0.6, -0.21, -0.3, -0.1)
#     # , Implicit_se = c(0.15, 0.23, 0.15, 0.23)
# ) %>%
#     gather(key = "attitude", value = "score") %>%
#     mutate(
#         description_valence = rep(c("positive", "positive", "negative", "negative"), 2) # 4)
#         , block = rep(c("1", "2", "1", "2"), 2) # 4)
#     ) %>%
#     group_by(attitude, description_valence) %>%
#     summarize(mean = diff(rev(score))) %>%
#     group_by(attitude) %>%
#     summarize(mean = mean(abs(mean))) %>%
#     spread(key = "attitude", value = "mean")

otm1_effects_plot <- otm1_attitudes_delta_summary %>%
  ggplot(aes(x = Eval, y = IATscore, color = Location, fill = Location, shape = Location)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  # stat_density_2d(
  #   data = otm1_unconstrained_effect_fixed_pp
  #   , aes(x = alpha, y = beta, color = Location)
  #   , bins = 5
  #   , inherit.aes = FALSE
  # ) +
  stat_ellipse(
    data = otm1_unconstrained_pp
    , type = "norm"
    , level = 0.95
  ) +
  geom_point(size = 3, color = "black") +
  # geom_point(
  #   data = otm1_unconstrained_effect_fixed_pp %>%
  #     summarize(alpha = median(alpha), beta = median(beta))
  #   , aes(x = alpha, y = beta)
  #   , color = "black"
  #   , inherit.aes = FALSE
  # ) +
  # geom_point(size = 4, shape = 1, data = heycke_descriptives, aes(x = Eval, y = IATscore), inherit.aes = FALSE) +
  annotate(geom = "text", x = 1.17, y = 2, label = "One mind", hjust = 0.5, size = 4, color = "gray50") +
  annotate(geom = "text", x = 1.17, y = -2, label = "Two minds", hjust = 0.5, size = 4, color = "gray50") +
  scale_color_viridis_d() +
  scale_fill_viridis_d() +
  scale_shape_manual(values = c(21, 23, 24, 22)) +
  labs(
    x = expression("Rating score difference"~group("[", Delta~italic(z)~score, "]"))
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  coord_fixed(xlim = c(-2.15, 2.15), ylim = c(-2.15, 2.15)) +
  theme_apa(box = TRUE) +
  theme(
    legend.justification = c(0, 1)
    , legend.position = c(-0.01, 1.03)
    , legend.background = element_blank()
    , legend.key.height = unit(1.1, "line")
    , legend.key.width = unit(1.5, "line")
  )
```

```{r otm1-prediction-plots, child = "prediction_plots.Rmd"}
```

```{r otm1-bayesian-replication-analysis-plot, fig.cap = "(ref:bayesian-replication-analysis-plot)", fig.dim = c(10, 4)}
plot_grid(
  otm1_prediction_plot
  , NULL
  , otm1_effects_plot + ggtitle("Experiment 1") + theme(plot.title = element_text(size = 12, hjust = 0.5, margin = margin(b = rel(8))))
  , otm1_effects_plot + ggtitle("Experiment 2") + theme(plot.title = element_text(size = 12, hjust = 0.5, margin = margin(b = rel(8)))) + guides(color = guide_legend(), fill = guide_legend(), shape = guide_legend()) + geom_rect(xmin = -5, xmax = 5, ymin = -5, ymax = 5, fill = "white", color = "white")
  + geom_vline(xintercept = 0, linetype = "dotted") + geom_hline(yintercept = 0, linetype = "dotted") + annotate(geom = "text", x = 1.17, y = 2, label = "One mind", hjust = 0.5, size = 4, color = "gray50") +
  annotate(geom = "text", x = 1.17, y = -2, label = "Two minds", hjust = 0.5, size = 4, color = "gray50") +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.ticks.y = element_blank(), axis.text.y = element_blank())
  , ncol = 4
  , labels = c("A", "", "B", "")
  , rel_widths = c(0.9, 0.05, 1, 0.825)
)

# plot_grid(
#   otm1_prediction_plot
#   , NULL
#   , plot_grid(
#     otm1_effects_plot + theme(plot.title = element_text(margin = margin(b = rel(22))))
#     , NULL
#     , otm1_effects_plot + theme(plot.title = element_text(margin = margin(b = rel(22)))) + guides(color = guide_legend(), fill = guide_legend(), shape = guide_legend()) + geom_rect(xmin = -5, xmax = 5, ymin = -5, ymax = 5, fill = "white", color = "white") 
#   + geom_vline(xintercept = 0, linetype = "dotted") + geom_hline(yintercept = 0, linetype = "dotted") + annotate(geom = "text", x = 1.17, y = 2, label = "One mind", hjust = 0.5, size = 4, color = "gray50") +
#   annotate(geom = "text", x = 1.17, y = -2, label = "Two minds", hjust = 0.5, size = 4, color = "gray50") +
#   theme(legend.position = "none")
#     , ncol = 3
#     , labels = c("B", "", "C")
#     , rel_widths = c(1, 0.05, 1)
#   )
#   , nrow = 3
#   , labels = c("A", "", "")
#   , rel_heights = c(0.5, 0.05, 1)
# )
```

The direct comparison of predictive accuracy indicated that our data overwhelmingly favored the result patterns reported by @heycke_two_2018 over those reported by @rydell_two_2006, `r otm1_same_vs_opposite_direction_bf_res`, Table\ \@ref(tab:otm1-bayesian-replication-analysis-table).
Additional comparisons with the control models confirmed that the experimental manipulations were effective (`r otm1_same_direction_bf_res`) and did not produce an unexpected result pattern (`r otm1_same_direction_vs_unconstrained_bf_res`, $\in [0, 4]$[^bf_range]).

We additionally assessed whether all labs produced the same result pattern.
We implemented a model that enforced the order constraint of $\mathcal{M}_\textrm{One mind}$ not only on the average block effects but on each lab's block effect.
Our data provide strong evidence for consistent result patterns across labs relative to the less-constrained models, `r otm1_all_labs_same_vs_same_direction_bf_res` ($\in [0, 3]$) and `r otm1_all_labs_same_direction_vs_unconstrained_bf_res` ($\in [0, 12]$[^bf_range2]).
Prior sensitivity analyses confirmed that the above results are robust to a wide range of priors, see SOM.

[^bf_range]:
The comparison of these models is asymmetric.
If, as in this case, the data are perfectly consistent with $\mathcal{M}_\textrm{One mind}$, they are also consistent with $\mathcal{M}_\textrm{Any effect}$.
The order restriction enforced by $\mathcal{M}_\textrm{One mind}$ limits the prediction of the model to 1/4 of the outcome space predicted by $\mathcal{M}_\textrm{Any effect}$ (i.e., the upper right quadrant of Figure \ \@ref(fig:otm1-bayesian-replication-analysis-plot)).
This four-fold greater parsimony of $\mathcal{M}_\textrm{One mind}$ constitutes the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{One mind}/\mathcal{M}_\textrm{Any effect}}$ (assuming all regions of the outcome space are equally likely a priori).
Hence, for this model comparison we could not have obtained stronger evidence (given numerical imprecision of the MCMC sampling approach).
Conversely, if the data had fallen outside the predicted outcome space of $\mathcal{M}_\textrm{One mind}$ there is no upper bound to the evidence in favor of $\mathcal{M}_\textrm{Any effect}$.

[^bf_range2]:
The additional order constraints enforced by $\mathcal{M}_\textrm{One mind everywhere}$ limits the prediction of the model to 1/12 of the outcome space predicted by the unconstrained model.
Hence, for this model comparison the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{One mind everywhere}/\mathcal{M}_\textrm{Any effect}}$ is 12 (assuming all regions of the outcome space are equally likely a priori).
Baring the transitivity of Bayes factors in mind this implies that the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{One mind everywhere}/\mathcal{M}_\textrm{One mind}}$ is 3.
Hence, in both model comparisons we could not have obtained much stronger evidence in favor of $\mathcal{M}_\textrm{One mind everywhere}$.

(ref:otm1-bayesian-replication-analysis-table-caption) Summary of Bayesian model comparisons.

(ref:otm1-bayesian-replication-analysis-table-note) The Bayes factors (BF) in favor of $\mathcal{M}_\textrm{One mind}$ and $\mathcal{M}_\textrm{One mind everywhere}$ relative to $\mathcal{M}_\textrm{Any effect}$ are bounded within the range of $[0, 4]$^1^<!--[^bf_range]--> and $[0, 12]$^2^<!--[^bf_range2]-->, respectively.
Hence, in both model comparisons we could not have obtained much stronger evidence against $\mathcal{M}_\textrm{Any effect}$.
The direct comparison of the models of primary interest overwhelmingly favored $\mathcal{M}_\textrm{One mind}$ over $\mathcal{M}_\textrm{Two minds}$, `r otm1_same_vs_opposite_direction_bf_res`.
The naive posterior probability (NPP) quantifies the probability of each model given the data assuming that all models are equally likely a priori.

```{r otm1-bayesian-replication-analysis-table, results="asis"}
otm1_bfs <- c(1, otm1_same_direction_bf, otm1_all_labs_same_direction_bf, otm1_opposite_direction_bf, 0, otm1_unconstrained_bf)

bf_table <- data.frame(
    Model = c(
      "No effect"
      , "One mind"
      , "... everywhere"
      , "Two minds"
      , "... everywhere"
      , "Any effect"
    )
    , BF = c(
      # NA
      # , otm1_same_direction_bf
      # , otm1_all_labs_same_direction_bf
      # , otm1_opposite_direction_bf
      # , otm1_all_labs_opposite_direction_bf
      # , otm1_unconstrained_bf
      1/otm1_unconstrained_bf
      , otm1_same_direction_bf/otm1_unconstrained_bf
      , otm1_all_labs_same_direction_bf/otm1_unconstrained_bf
      , otm1_opposite_direction_bf/otm1_unconstrained_bf
      , otm1_all_labs_opposite_direction_bf/otm1_unconstrained_bf
      , NA
    ) %>% 
      printnum(na_string = "") # %>% # format = "e", 
      # papaja:::typeset_scientific() %>%
      # paste0("$", ., "$")
    , NPP = printnum(otm1_bfs / sum(otm1_bfs), gt1 = FALSE, digits = 2)
)

variable_labels(bf_table) <- c(
  # "BF" = "$\\textrm{BF}_{\\mathcal{M}_i/\\mathcal{M}_{\\textrm{No effect}}}$"
  "Model" = "Model ($\\mathcal{M}_i$)"
  , "BF" = "$\\textrm{BF}_{\\mathcal{M}_i/\\mathcal{M}_{\\textrm{Any effect}}}$"
)

bf_table2 <- bf_table[, c("BF", "NPP")]
bf_table2$BF <- NA
bf_table2$NPP <- NA
variable_labels(bf_table2) <- c(
  "BF" = "$\\textrm{BF}_{\\mathcal{M}_i/\\mathcal{M}_{\\textrm{Any effect}}}$"
)

bf_table %>%
  cbind(bf_table2) %>%
  printnum(na_string = "") %>%
  apa_table(
   escape = FALSE
  , align = "lcccc"
  , col_spanners = list("Experiment 1" = 2:3, "Experiment 2" = 4:5)
  , stub_indents = list(3, 5)
  , caption = "(ref:otm1-bayesian-replication-analysis-table-caption)"
  , note = "(ref:otm1-bayesian-replication-analysis-table-note)"
)
```

### Recognition task

```{r otm1-rydell-recognition, results = "asis"}
otm1_mem_ttest <- t.test(otm1_mem$Accuracy, mu = 0.5, alternative = "greater", rscale = "medium") %>%
  apa_print(gt1 = FALSE) %$%
  full_result

otm1_mem_aov <- otm1_mem %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  droplevels %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Accuracy"
    , between = "Location"
    , data = .
    , anova_table = list(intercept = TRUE)
  ) %>%
  apa_print(intercept = TRUE) %$%
  full_result
```

```{r otm1-bayesian-recognition, warning = FALSE, message = FALSE}
otm1_mem_bayesian_ttest <- ttestBF(otm1_mem$Accuracy - 0.5, mu = 0, rscale = "medium", nullInterval = c(0, Inf))[1] %>%
  apa_print(gt1 = FALSE) %$%
  full_result %>%
  gsub("\\.0", ".5", .)

otm1_mem_bayesian_aov <- otm1_mem %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  droplevels %>%
  anovaBF(
    Accuracy ~ Location
    , data = .
  ) %>%
  apa_print %$%
  statistic
```

Finally, we examined participants' recognition memory for the words that we presented briefly as USs during the learning procedure.
Recognition accuracy was better than chance, `r otm1_mem_ttest`, `r otm1_mem_bayesian_ttest`.
Hence, we cannot assume that the stimulus presentation was subliminal.
It remained unclear, however, whether recognition accuracy differed between labs, `r otm1_mem_aov$Location`, `r otm1_mem_bayesian_aov`.

## Discussion

We reproduced the procedure of @rydell_two_2006, using the original material and the first author of the original study approved the procedure.
Despite all efforts to keep the procedure as close as possible to the original procedure, we did not replicate the original finding.
In contrast to @rydell_two_2006, we observed that both implicit and explicit evaluations reflected the valence of the learned behavioral information.
The briefly presented USs did not lead to contradicting implicit evaluations compared to explicit evaluations.
In short, we found no evidence for an evaluative dissociation. 
Our findings mirror the results of the previous replication attempt by @heycke_two_2018.
Moreover, the observed results were consistent across three languages and countries indicating that neither inaccurate translations nor differences in sampled populations are likely to have caused the deviation of the results from the original findings.
Thus, our findings raise more doubts about the general replicability of the dissociative evaluative learning effect that was observed by @rydell_two_2006.

There is, however, one objection these findings cannot entirely dispel: The close physical recreation of the original procedure may not have faithfully reproduced the psychological conditions of the original learning task.
In the original study, US recognition accuracy was not significantly different from chance [@rydell_two_2006].
However, like @heycke_two_2018 we did observe better-than-chance US recognition accuracy.
We, therefore, have to assume that participants consciously perceived the briefly presented USs, which might have influenced our results.
Hence, it is possible that the conscious perception of briefly presented USs constitutes a critical departure from the to-be-reproduced learning conditions.
Although an exploratory analysis suggested that there was no relationship between US recognition accuracy and implicit evaluations (see SOM), we decided to repeat the experiment and reduced US visibility experimentally to more closely mimic the psychological conditions of the original learning task.

# Experiment 2

To address the concern that our previous replication may have been unsuccessful because USs were consciously perceived (as indicated by above-chance US recognition accuracy), we will conduct a second study and reduce the presentation duration of USs during the learning task.

## Visibility pilot study

```{r otm2pilot2f-analysis-preferences}
# Data location
raw_data_path <- "../otm2pilot2/results/data_raw_florida/"
processed_data_path <- "../otm2pilot2/results/data_processed_florida/"
```

```{r otm2pilot2f-load-data, cache = TRUE, dependson = "otm2pilot2f-analysis-preferences", warning = FALSE}
# Process raw data
if(process_rawdata) {

  # Merge raw data
  otm2p2f_eval <- batch_read(
    raw_data_path
    , pattern = "Eval"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm2p2f_mem <- batch_read(
    raw_data_path
    , pattern = "MemTest"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm2p2f_log <- batch_read(
    raw_data_path
    , pattern = "ScreenLog"
    , recursive = TRUE
    , read_fun = read.csv
    , header = FALSE
  )

  otm2p2f_demo <- batch_read(
    raw_data_path
    , pattern = "Demographics"
    , recursive = TRUE
    , read_fun = read.delim
    #, quote = "~" # Participants used " in their input
  ) %>%
    mutate(
        ParticipantNumber = factor(ParticipantNumber)
      , Sex = gsub("female|Female"
                   , "female"
                   , Gender
                   , ignore.case = TRUE) %>% tolower
      , Age = as.numeric(Age)
    )

  otm2p2f_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")

  otm2p2f_mem$ParticipantNumber <- as.integer(otm2p2f_mem$ParticipantNumber)
  #otm2p2_mem <- left_join(otm2p2_mem, otm2p2_demo, by = "ParticipantNumber")

  otm2p2f_mem <- otm2p2f_mem %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime - posPrime", "posPrime - negPrime") %>% factor
      , Block = factor(Block)
      , Accuracy = as.integer(NumbercorrectIdent) / 20
    )

    # Save processed data
  saveRDS(otm2p2f_eval, paste0(processed_data_path, "otm2p2f_eval.rds"))
  saveRDS(otm2p2f_mem, paste0(processed_data_path, "otm2p2f_memory.rds"))
} else {
  otm2p2f_eval <- readRDS(paste0(processed_data_path, "otm2p2f_eval.rds"))
  otm2p2f_mem <- readRDS(paste0(processed_data_path, "otm2p2f_memory.rds"))
}
```

```{r otm2p2f-recognition}
otm2p2f_mem_ttest <- t.test(otm2p2f_mem$Accuracy, mu = 0.5
                          , alternative = "greater") %>%
  apa_print %$%
  full_result

otm2p2f_mem_ttest_two_sided <- t.test(otm2p2f_mem$Accuracy, mu = 0.5) %>%
  apa_print %$%
  estimate

otm2p2f_mem_ttestBF <- ttestBF(otm2p2f_mem$Accuracy - 0.5
                             , mu = 0, rscale = "medium"
                             , nullInterval = c(0, Inf))[1] %>%
  apa_print(gt1 = FALSE) %$%
  full_result %>%
  gsub("\\.0", ".5", .) %>%
  gsub("\\$ ", "$, ", .)
```

To identify a presentation duration that replicates the psychological conditions of the original learning task (i.e., at-chance recognition accuracy for briefly presented USs), we ran a pilot study with a reduced US presentation duration of 13 ms (one frame on a 75 Hz CRT monitor) [^pilots].
Because all subsequent studies will be conducted in English, the pilot study used the English material and instructions and was conducted at the University of Florida.
Except for the shorter US presentation the methods were the same as in Experiment 1.
For the pilot study, we recruited `r nrow(otm2p2f_demo)` participants (aged `r paste(range(otm2p2f_demo$Age), collapse = "-")` years, $M = `r mean(otm2p2f_demo$Age)`$; `r sum(grepl("female", otm2p2f_demo$Sex)) / nrow(otm2p2f_demo) * 100`% female).

```{r rydell-recognition-effect, results = "hide"}
rydell_mem_ci <- ci.sm(ncp = -1.58, N = 50) %>% 
  lapply(function(x) x* 0.09 + 0.5)
rydell_mem_ci_res <- paste0(
  "$M = ", printnum(rydell_mem_ci$Standardized.Mean, gt1 = FALSE)
  , "$, 95% CI $[", printnum(rydell_mem_ci$Lower.Conf.Limit.Standardized.Mean, gt1 = FALSE)
  , "$, $", printnum(rydell_mem_ci$Upper.Conf.Limit.Standardized.Mean, gt1 = FALSE), "]$"
)

rydell_mem_bf <- paste0(
  "$\text{BF}_{01} = "
  , printnum(1/ttest.tstat(t = -1.58, n1 = 50, simple = TRUE))
  , "$"
)
```

The US identification performance was not significantly better than chance, `r otm2p2f_mem_ttest`, however the data provide no evidence for at-chance accuracy `r otm2p2f_mem_ttestBF`. 
Although these results do not formally confirm that the shortened presentation duration yielded at-chance US visibility, the estimates of US memory accuracy are very similar to those from @rydell_two_2006 (`r rydell_mem_ci_res`).
Further reduction of the presentation duration may eventually yield conclusive evidence for at-chance visibility, but it could inadvertently cause stimuli to become practically invisible.
We will, therefore, conduct the final studies using a US presentation duration of 13 ms.

[^pilots]:
We ran a series of pilot studies in Dutch, which also yielded above-chance US memory.
These pilot studies employed a shortened procedure, used Dutch material, or were conducted immediately after an unrelated priming study, which also used briefly presented words.
We, therefore, decided a posteriori, that above-chance performance in these studies may not be informative for our subsequent replication attempt, as we will use only English materials in the next studies.

## Method

### Participants

We will run the experiment in Florida, Indiana, and Hong Kong.
As in Experiment 1, 50 students will participate at each of three locations, yielding a total of $N = 150$ participants.
All participants who sign up for the study before the intended $n = 50$ has been reached will be allowed to participate; hence, the final sample size could be slightly larger.
We will exclude any participants from the analysis who abort the experiment or who ask us to remove their data (e.g., because they did not pay attention or did not follow the instructions).
We will recruit additional participants to replace those excluded.
<!--Participants will be compensated with xxxx.-->

### Material & Procedure

We will employ the same material and procedure as in Experiment 1 but use the shortened US presentation duration of 13 ms.
Furthermore, all labs will use the same python script to collect the data and only the English material will be used to match the official language at all three locations.
All materials are available at https://osf.io/8m3xb/.

### Data analysis

The new data[^pilot2data] from all locations will be jointly submitted to the same analyses as in Experiment 1.
We will, again, perform the analyses reported in the original study, supplement the ANOVA analysis of IAT scores by a linear mixed model analysis, and assess the replication success by performing Bayesian model comparisons.
All data and analysis code will be made available in the OSF repository and linked to in the manuscript.

[^pilot2data]:
To ensure representative results, the pilot study for Experiment 2 employed the complete experimental procedure, that is, we also collected evaluative ratings and IAT responses.
As of now, only the US identification performance was analyzed; we have not looked at the explicit and implicit evaluation data.
Once the data of the second, preregistered experiment are in, we will add the data from the pilot study to our final analyses.

\newpage

# References

```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parskip}{0pt}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-10-31 analysis_and_paper/prediction_plots.Rmd
add analysis and paper folder

```{r}
library("msm")
library("spatialfil")
```

```{r prediction-setup, cache = TRUE}
sd0 <- 0.6
kern <- convKernel(sigma = 8, k = "gaussian")

nrmlz <- function(mat) {
	tot <- sum(mat)
	mat/tot
}

thetaCons <- seq(-1.5, 1.5, .02)
thetaLib <- seq(-1.5, 1.5, .02)

combiThetas <- expand.grid(
  Liberals = thetaLib
  , Conservatives = thetaCons
  , figType = c("Model", "Prediction")
  , Model = c("No effect", "One mind", "Two minds", "Any effect")
)
combiThetas$Density <- NA

combiThetasRaw <- expand.grid(
  Liberals = thetaLib
  , Conservatives = thetaCons
)

makeTeamBPlot <- function(z, dat, ylab, xlab, breaks, strip = FALSE){
  graycols <- gray.colors(100, max(.0, .6 - 100 * max(dat$Density))
                          , max(.7, 1 - 50 * max(dat$Density)))
  ggplot(
    mapping = aes(y = Liberals, x = Conservatives, z = eval(parse(text = z)), fill = ..level..)
    , data = dat
  ) +
  stat_contour(geom = "polygon", bins = 20) +
  geom_hline(yintercept = 0, color = "grey70", size = .3, alpha = .3) +
  geom_vline(xintercept = 0, color = "grey70", size = .3, alpha = .3) +
  scale_fill_gradientn(colors = rev(graycols)) +
  xlim(c(min(combiThetas$Conservatives), max(combiThetas$Conservatives))) +
  ylim(c(min(combiThetas$Liberals), max(combiThetas$Liberals))) +
  coord_fixed() +
  labs(x = xlab, y = ylab) +
  facet_grid(Model ~ figType) + 
  theme(
    legend.position = "none"
    , axis.title.x = if(xlab == "") element_blank() else element_text()
    , axis.text.x = if(xlab == "") element_blank() else element_text()
    , axis.ticks.x = if(xlab == "") element_blank() else element_line()
    , strip.text.x = if(!strip) element_blank() else element_text()
    , panel.border = element_rect(color = "black", fill = NA)
    , panel.spacing = unit(rel(10), "points")
    , strip.text.y = ggplot2::element_text(margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
  )
}
```

```{r null-model-predicitons, warning = FALSE}
nullTruth <- function(theta, sd){
  dnorm(theta[1], 0, sd) * dnorm(theta[2], 0, sd)
}

modelDensityNull <- apply(combiThetasRaw
                                              , 1
                                              , nullTruth
                                              , sd = .01)

modelDensityNull <- nrmlz(modelDensityNull)

mat <- matrix(modelDensityNull, nrow = length(thetaLib), ncol = length(thetaCons))
predmat <- nrmlz(applyFilter(mat, kern))
predictionDensityNull <- as.vector(predmat) * 100

combiThetas[combiThetas$figType == "Model" & combiThetas$Model == "No effect", "Density"] <- modelDensityNull
combiThetas[combiThetas$figType == "Prediction" & combiThetas$Model == "No effect", "Density"] <- predictionDensityNull

nullmod <- data.frame(x = 0, y = 0, figType = "Model")
```

```{r one-mind-predictions, cache = TRUE, dependson = "prediction-setup"}
#Prior Model 
same_direction <- function(theta, Sigma){
  dtnorm(theta[2], 0, Sigma, lower = 0) * dtnorm(theta[1], 0, Sigma, lower = 0)}

model_same_direction  <- apply(combiThetasRaw
                                                    , 1
                                                    , same_direction
                                                    , Sigma = sd0)
model_same_direction <- nrmlz(model_same_direction)

mat <- matrix(model_same_direction
              , nrow = length(thetaCons)
              , ncol = length(thetaCons))
predmat <- nrmlz(applyFilter(mat, kern))
prediction_same_direction <- as.vector(predmat)

combiThetas[combiThetas$figType == "Model" & combiThetas$Model == "One mind", "Density"] <- model_same_direction
combiThetas[combiThetas$figType == "Prediction" & combiThetas$Model == "One mind", "Density"] <- prediction_same_direction
```

```{r two-mind-predictions, cache = TRUE, dependson = "prediction-setup"}
#Prior Model 
opposite_direction <- function(theta, Sigma){
  dtnorm(theta[2], 0, Sigma, lower = 0) * dtnorm(theta[1], 0, Sigma, upper = 0)}

model_opposite_direction  <- apply(combiThetasRaw
                                                    , 1
                                                    , opposite_direction
                                                    , Sigma = sd0)
model_opposite_direction <- nrmlz(model_opposite_direction)

mat <- matrix(model_opposite_direction
              , nrow = length(thetaCons)
              , ncol = length(thetaCons))
predmat <- nrmlz(applyFilter(mat, kern))
prediction_opposite_direction <- as.vector(predmat)

combiThetas[combiThetas$figType == "Model" & combiThetas$Model == "Two minds", "Density"] <- model_opposite_direction
combiThetas[combiThetas$figType == "Prediction" & combiThetas$Model == "Two minds", "Density"] <- prediction_opposite_direction
```

```{r unconstrained-predictions, cache = TRUE, dependson = "prediction-setup"}
# Prior Model
genTruth <- function(theta, sd){
  dnorm(theta[1], 0, sd) * dnorm(theta[2], 0, sd)
}

modelDensityGeneral <- apply(combiThetasRaw
                                              , 1
                                              , genTruth
                                              , sd = sd0)
modelDensityGeneral <- nrmlz(modelDensityGeneral)

# Model Predictions
mat <- matrix(modelDensityGeneral
              , nrow = length(thetaCons)
              , ncol = length(thetaCons))
predmat <- nrmlz(applyFilter(mat, kern))
predictionDensityGeneral <- as.vector(predmat)

combiThetas[combiThetas$figType == "Model" & combiThetas$Model == "Any effect", "Density"] <- modelDensityGeneral
combiThetas[combiThetas$figType == "Prediction" & combiThetas$Model == "Any effect", "Density"] <- predictionDensityGeneral
```

```{r model-plots, fig.width = 4.5, fig.height = 5.4, eval = FALSE}
# plot_labels <- data.frame(
#   Liberals = 1.25
#   , Conservatives = -0.725
#   , Model = c("One mind", "Two minds")
#   , label = c("One mind", "Two minds")
# )

otm1_models <- subset(combiThetas, figType == "Model") %>%
  mutate(Model = factor(Model, levels = c("One mind", "Two minds", "No effect", "Any effect"))) %>%
  group_by(Model) %>%
  do(mutate(., Density = exp(log(Density) - max(log(Density))))) %>%
  ggplot(
    mapping = aes(
      y = Liberals
      , x = Conservatives
    )
  ) +
  stat_contour(geom = "polygon", aes(z = Density, fill = ..level..)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  # scale_fill_gradient(low = bg_col, high = "#385E49") +
  geom_point(data = data.frame(Liberals = 0, Conservatives = 0, Model = "No effect"), color = "#385E49", size = 3) +
  # geom_text(data = plot_labels, aes(label = label)) +
  coord_fixed() +
  labs(
    x = expression(alpha)
    , y = expression(beta)
  ) +
  facet_wrap(~ Model, ncol = 2) +
  theme(
    legend.position = "none"
    , axis.text.x = element_blank()
    , axis.text.y = element_blank()
    , axis.ticks.x = element_blank()
    , axis.ticks.y = element_blank()
    , panel.border = element_rect(color = "black", fill = NA)
    , panel.spacing = unit(rel(10), "points")
    , strip.text.y = ggplot2::element_text(margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
  )
```

```{r prediction-plots}
otm1_prediction_plot <- subset(combiThetas, figType == "Prediction") %>%
  mutate(Model = factor(Model, levels = c("One mind", "Two minds", "No effect", "Any effect"))) %>%
  group_by(Model) %>%
  do(mutate(., Density = exp(log(Density) - max(log(Density))))) %>%
  ggplot(
    plot_data
    , mapping = aes(
      y = Liberals
      , x = Conservatives
      , z = Density
      , fill = ..level..
    )
  ) +
  stat_contour(geom = "polygon") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_fill_gradient(low = "white", high = "grey30") +
  coord_fixed() +
  labs(
    x = expression("Rating score difference"~group("[", Delta~italic(z)~score, "]"))
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  facet_wrap(~ Model, ncol = 2) +
  theme(
    legend.position = "none"
    , axis.text.x = element_blank()
    , axis.text.y = element_blank()
    , axis.ticks.x = element_blank()
    , axis.ticks.y = element_blank()
    , panel.border = element_rect(color = "black", fill = NA)
    , panel.spacing = unit(rel(10), "points")
    , plot.title = element_text(hjust = 0.5)
    , strip.text.x = element_text(margin = margin(b = rel(8)))
    , strip.text.y = element_text(margin = margin(0, 0, 0, rel(12)))
  )
```

### 2019-10-31 analysis_and_paper/supplements.Rmd
add analysis and paper folder

---
title           : |
  Supplementary online material for

  *Of Two Minds: A registered replication*

shorttitle      : "Replication of Rydell et al."

author: 
  - name          : Tobias Heycke
    affiliation   : 1, 2
    corresponding : yes    
    address       : "P.O. 122155, 68072 Mannheim, Germany"
    email         : "tobias.heycke@gesis.org"
  - name        : Frederik Aust
    affiliation : 1
  - name        : Mahzarin R. Banaji
    affiliation : 3
  - name        : John G. Conway
    affiliation : 4
  - name        : Pieter Van Dessel
    affiliation : 5
  - name        : Xiaoqing Hu
    affiliation : 6    
  - name        : Congjiao Jiang
    affiliation : 4    
  - name        : Benedek Kurdi
    affiliation : 3    
  - name        : Robert Rydell
    affiliation : 7
  - name        : Lisa Spitzer
    affiliation : 1
  - name        : Christoph Stahl
    affiliation : 1
  - name        : Christine A. Vitiello
    affiliation : 4
  - name        : Jan De Houwer
    affiliation : 5

affiliation:
  - id          : 1
    institution : University of Cologne
  - id          : 2
    institution : GESIS - Leibniz Institute for the Social Sciences
  - id          : 3
    institution : Harvard University 
  - id          : 4
    institution : University of Florida 
  - id          : 5
    institution : Ghent University 
  - id          : 6
    institution : The University of Hong Kong 
  - id          : 7
    institution : Indiana University

bibliography      : ["references.bib", "r-references.bib"]
#appendix          : "appendix.Rmd"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "doc"
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE, warning=FALSE}
library("magrittr")
library("tidyr")
library("dplyr")
library("assertthat")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("afex")
library("emmeans")
library("BayesFactor")

source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")
```

```{r analysis-preferences}
# Data location
raw_data_path <- "../ml-otm1/results/data_raw/"
processed_data_path <- "../ml-otm1/results/data_processed/"

# Set seed for random number generator
set.seed(315054738)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Use multivariate models for emmeans contrasts and post-hoc tests
afex_options(emmeans_model = "multivariate")

# Configure df approximation for mixed model contrasts and post-hoc tests
emm_options(
  lmer.df = "satterthwaite"
  , lmerTest.limit = 22384
)

# Default ggplot theme
theme_set(theme_apa())

## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
# assignInNamespace("theme_nothing", function() {
#     theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
# }, "cowplot")

# Number of MCMC samples for Bayesian analysis
otm1_n_mcmc_samples <- 1e6
```

```{r cache-preferences}
# Automatically manage cache dependencies
knitr::opts_chunk$set(autodep = TRUE)
knitr::dep_auto()

# Ignore changes to comments in cached chunks
knitr::opts_chunk$set(cache.comments = FALSE)

# Discard cache if random seed changes
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load-data}
otm1_attitudes <- readRDS(paste0(processed_data_path, "otm1_attitudes_cleaned.rds"))
otm1_iat <- readRDS(paste0(processed_data_path, "otm1_iat_trial_data_cleaned.rds"))
otm1_mem <- readRDS(paste0(processed_data_path, "otm1_memory_cleaned.rds"))
```

\newpage

# Experiment 1

In the following we report additional analyses and provide details for the model specification used for the Bayesian model comparisons.
We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between US recognition accuracy and associative learning.
Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.

(ref:otm1-participant-table) Participant demographics by location.

(ref:otm1-participant-table-note) Mean age is given with range in brackets.

```{r otm1-participant-table, results = "asis"}
otm1_mem %>% 
  group_by(Location) %>% 
  summarize(
    age_mean = mean(Age, na.rm = T)
    , age_min = min(Age)
    , age_max = max(Age)
    , "Female (\\%)" = printnum(sum(grepl("female", Sex)) / length(Accuracy) * 100)
    , "$n$" = length(Accuracy)
  ) %>%
  mutate(Age = paste0(printnum(age_mean), " [", age_min, ", ", age_max, "]")) %>%
  select(Location, Age, "Female (\\%)", "$n$") %>%
  apa_table(
    caption = "(ref:otm1-participant-table)"
    , note = "(ref:otm1-participant-table-note)"
    , align = "lccc"
    , escape = FALSE
    , placement = "h"
  )
```

## Mixed model analysis

The ANOVA of IAT scores reported in the main text ignores potential systematic trial-to-trial variability in IAT response latencies due to stimuli.
Any such systematic but unaccounted-for variance can inflate test statistics and yield underestimated $p$ values as well as underestimated confidence intervals.
We, therefore, also conducted a linear mixed model analysis of response times with crossed random effects for participants and items to ensure that our conclusion are not contingent on inadvertent stimulus effects [for details see @wolsiefer_modeling_2017].
For this analysis we excluded participants with error rates across all blocks larger than 50% or who responded faster than 300 ms on at least 10% of all trials.
We additionally discarded trials in which responses were faster than 400 ms or slower than 10 s.
These exclusion criteria are the same as those used by @wolsiefer_modeling_2017.

```{r otm1-lmer-exclusion, cache = TRUE}
lme_error_exclusion <- otm1_iat %>%
  group_by(ParticipantNumber) %>%
  summarize(Correct = mean(Correct), fast_rate = mean(RT < 0.3)) %>%
  filter(Correct < 0.5 & fast_rate > 0.1) %$% ParticipantNumber

if(length(lme_error_exclusion) > 0) {
  otm1_iat <- otm1_iat %>%
    filter(!ParticipantNumber %in% otm1_lme_exclusion)
}

otm1_iat <- otm1_iat %>%
  # Wolsiefer et al. (2017, p. 1196; doi: 10.3758/s13428-016-0779-0)
  filter(RT > 0.4 & RT < 10) %>%
  # Wolsiefer et al. (2017, p. 1198; doi: 10.3758/s13428-016-0779-0)
  group_by(ParticipantNumber, Block) %>%
  mutate(RTD = RT / sd(RT)) %>%
  ungroup
```

We analyzed standardized response latencies, that is, the time that elapsed between stimulus presentation and *correct* response divided by the standard deviation of all response latencies in a given block, Figure\ \@ref(fig:otm1-iat-plot).
To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
Hence, larger values represent more favorable implicit evaluations.

(ref:otm1-iat-plot) Standardized IAT response latencies across learning blocks.
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples.

```{r otm1-iat-plot, fig.cap = "(ref:otm1-iat-plot)"}
otm1_results_legend <- guide_legend(
    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
    title = expression(atop("Valence order", atop(scriptstyle("Learned behaviors"), scriptstyle("(Briefly presented USs)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
    , keyheight = 2
  )

my_labeller <- function(x, ...) label_both(x, sep = " ", ...)

otm1_iat %>%
  mutate(ValenceBlock = ifelse(ValenceBlock == "Positive-negative", " Positive-negative\n(Negative-positive)", " Negative-positive\n(Positive-negative)")) %>%
  ggplot(aes(x = Congruent, y = RTD, group = ValenceBlock, color = ValenceBlock, shape = ValenceBlock, fill = ValenceBlock)) +
  stat_summary(fun.y = mean, geom = "line", position = position_dodge(0.1)) +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23), guide = otm1_results_legend) +
  labs(x = "Response mapping", y = "Standardized response time") +
  facet_grid(~ Block, labeller = my_labeller) +
  theme(
    legend.position = c(0.4, 0.75)
    , strip.background = element_blank()
  )
```

```{r otm1-lmer, cache = TRUE, warning = FALSE}
# Wolsiefer et al. (2017, Erratum; doi: 10.3758/s13428-017-0897-3)
otm1_iat_lmer_formula <- RTD ~ Congruent * Block * ValenceBlock *
  (Category + wordType + imageType) +
  (Congruent * Block | ParticipantNumber) +
  (Congruent * Block * ValenceBlock | translatedStimulus)

otm1_iat_lmerTest <- lmerTest::lmer(
  otm1_iat_lmer_formula
  , data = otm1_iat
  , control = lmerControl(
    optCtrl = list(maxfun = 10 * 143^2)
  )
)

otm1_iat_lmerTest_summary <- summary(otm1_iat_lmerTest)
```

(ref:otm1-lmer-fixed-effects-caption) Fixed effect estimates of the linear mixed model analysis of standardized IAT response times.

(ref:otm1-lmer-fixed-effects-note) The model additionally included random participant and item effects with random intercepts and random slopes for all manipulations during the learning procedure and their interactions.

```{r otm1-lmer-table-fixed-effects, results = "asis"}
otm1_iat_lmerTest_summary$coefficients %>%
  as.data.frame %>%
  rename(
    "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$df$" = "df"
    , "$t$" = "t value"
    , "$p$" = "Pr(>|t|)"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
    , Effect = gsub("1", "", Effect)
    , Effect = gsub("\\bBlock", "Learning block", Effect)
    , Effect = gsub("ValenceBlock", "Valence order", Effect)
    , Effect = gsub("Block", " block", Effect)
    , Effect = gsub("Type", " type", Effect)
    , Effect = gsub("Congruent", " Response mapping", Effect)
  ) %>%
  printnum(
    digits = c(2, 2, 2, 2, 3, 0)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$t$`, `$df$`, `$p$`) %>%
  apa_table(
    caption = "(ref:otm1-lmer-fixed-effects-caption)"
    , note = "(ref:otm1-lmer-fixed-effects-note)"
    , align = "lrrrrr"
    , midrules = c(7, 19, 29)
    , escape = FALSE
    , landscape = TRUE
  )
```

(ref:otm1-lmer-random-effects-caption) Random effect estimates and correlations of the linear mixed model analysis of standardized IAT response times.

(ref:otm1-lmer-random-effects-note) We report the estimated standard deviations in the main diagonals and the correlations in the off-diagnoals. The percentages of variance for the random effects were calculated by dividing each variance component by the total random variance, i.e., the sum of the random-effect variances.

```{r otm1-lmer-table-random-effects, results = "asis"}
fix_term_names <- function(x) {
  fixed_table <- attr(x, "correlation")

  term_names <- x %>%
    colnames %>%
    papaja:::prettify_terms(.) %>%
    gsub("1", "", .) %>% 
    gsub("\\bBlock", "Learning block", .) %>% 
    gsub("ValenceBlock", "Valence order", .) %>% 
    gsub("Block", " block", .) %>% 
    gsub("Type", " type", .) %>% 
    gsub("Congruent", " Response mapping", .)

  diag(fixed_table) <- attr(x, "stddev")

  fixed_table <- as.data.frame(fixed_table) %>%
    printnum

  fixed_table[lower.tri(fixed_table)] <- ""

  dimnames(fixed_table) <- list(
    paste0(1:length(term_names), ". ", term_names)
    , paste0(1:length(term_names), ". ")
  )

  fixed_table
}

random_effect_tables <- lapply(otm1_iat_lmerTest_summary$varcor, fix_term_names)
names(random_effect_tables) <- c("Participant", "Stimulus")

stimulus_effect_names <- colnames(random_effect_tables$Stimulus)

random_variances <- lapply(otm1_iat_lmerTest_summary$varcor, diag) %>%
  unlist %>%
  unname

variance_explained <- (random_variances / sum(random_variances)) %>%
  printnum(gt1 = FALSE)

random_effect_tables$Participant <- cbind(
  "\\% of variance" = variance_explained[1:nrow(random_effect_tables$Participant)]
  , random_effect_tables$Participant
)

random_effect_tables$Stimulus <- cbind(
  "\\% of variance" = variance_explained[1:nrow(random_effect_tables$Stimulus) + nrow(random_effect_tables$Participant)]
  , random_effect_tables$Stimulus
)

random_effect_tables$Participant[, stimulus_effect_names[!stimulus_effect_names %in% colnames(random_effect_tables$Participant)]] <- ""

apa_table(
  random_effect_tables
  , caption = "(ref:otm1-lmer-random-effects-caption)"
  , note = "(ref:otm1-lmer-random-effects-note)"
  , align = "lcrrrrr"
  , midrules = 5
  , escape = FALSE
  , landscape = TRUE
  , font_size = "small"
)
```

In line with the ANOVA results, we found the expected three-way interaction between *Response mapping*, *Valence order*, and *Learning block*; the interaction was moderated by the type of stimulus that participants responded to (pictures of Bob and non-Bobs vs. positive and negative words; *Category*), Table\ \@ref(tab:otm1-lmer-table-fixed-effects) and \@ref(tab:otm1-lmer-table-random-effects).
The three-way interaction prompted us to test the differences between response mapping effects in the first and second learning block for each valence order.

```{r otm1-lmer-emm, cache = TRUE, message = FALSE, warning = FALSE}
otm1_iat_lmer <- lme4::lmer(
  otm1_iat_lmer_formula
  , data = otm1_iat
  , control = lmerControl(
    optCtrl = list(maxfun = 10 * 143^2)
  )
)

otm1_iat_lmer_emm <- emmeans(
  otm1_iat_lmer
  , ~ Congruent * Block * ValenceBlock
)
```

<!-- (ref:otm1-iat-lmer-contrasts) Planned contrasts of changes in congruency effects across learning blocks for the linear mixed model analysis of standardized IAT response times. -->

```{r otm1-lmer-emm-2, cache = TRUE, results = "asis"}
otm1_iat_lmer_contrasts <- contrast(
  otm1_iat_lmer_emm
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
) %>%
  apa_print

# otm1_iat_lmer_contrasts %$%
#   table %>%
#   rename("Valence order" = contrast) %>%
#   apa_table(
#     caption = "(ref:otm1-iat-lmer-contrasts)"
#     , escape = FALSE
#     , row.names = FALSE
#   )
```

In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the learned behaviors were first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
Vice versa, response time differences suggested more favorable evaluations after the second than after the first block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
Again, these results indicate that the explicit evaluations and IAT scores were consistent.

Due to the significant four-way interaction, we additionally explored these contrasts separately for responses to pictures of Bob vs. non-Bobs and positive vs. negative words, Table \ \@ref(tab:otm1-lmer-emm-3-table).
We found consistent changes in response mapping effects for both pictures and words, albeit the effects were larger for words.

```{r otm1-lmer-emm-3, cache = TRUE, warning = FALSE}
otm1_iat_lmer_emm2 <- emmeans(
  otm1_iat_lmer
  , ~ Congruent * Block * ValenceBlock | Category
)

otm1_iat_lmer_contrasts2 <- contrast(
  otm1_iat_lmer_emm2
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
  , adjust = "Tukey"
) %>%
  apa_print

variable_label(otm1_iat_lmer_contrasts2$table$contrast) <- "Valence order"
```

(ref:otm1-iat-lmer-contrasts2) Post-hoc tests of changes in response mapping effects across blocks separately for pictures and words for standardized IAT response times.

(ref:otm1-iat-lmer-contrasts2-note) $p$ values were Tukey-corrected for two comparisons.

```{r otm1-lmer-emm-3-table}
otm1_iat_lmer_contrasts2 %$%
  table %>%
  select(-matches("Category|df|statistic|p.value"), statistic, df, p.value) %>%
  apa_table(
    caption = "(ref:otm1-iat-lmer-contrasts2)"
    , note = "(ref:otm1-iat-lmer-contrasts2-note)"
    , align = "lrcrrr"
    , stub_indents = list("Pictures" = 1:2, "Words" = 3:4)
    , midrule = 3
    , escape = FALSE
    , row.names = FALSE
  )
```

# Bayesian model comparison

We implemented the unconstrained model as a hierarchical linear model that encompasses each of the other models as special cases:

$$
\begin{aligned}
\hat y_{ijk} = & \mu + \nu_i + \eta_l x_{1il} + \\
          & (\alpha + \tau_l x_{1il}) x_{2j} x_{3k} + \\
          & (\beta + \upsilon_l x_{1il}) (1 -  x_{2j}) x_{3k}
\end{aligned}
$$

The model predicts the $i$th participant's response to evaluation measure $j$ in the experimental block $k$.
Responses are predicted as a combination of a grand mean $\mu$, random participant intercepts $\nu_i$ (i.e., habitually higher or lower evaluations), a main effect of the labs $\eta_l$, and simple effects of learning block for rating scores ($\alpha$) and IAT score ($\beta$).
Additionally, we allowed the simple effects to be moderated by the labs ($\tau_l$ and $\upsilon_l$ represent the lab-specific deviations from the overall simple effects).
The model does not include a main effect of evaluative measure because any mean differences between evaluative measures were leveled by the by-measure $z$ standardization.
$x_{1il}$ represents $l$ effect coded variables that indicate which lab participant $i$ belongs to; $x_{2j}$ indicates the evaluative measure (1 for rating score and 0 for IAT score), such that $\alpha + \tau_l$ is only relevant for rating scores and $\beta + \upsilon_l$ is only relevant for IAT scores; $x_{3k}$ is an effect coded variable that is set to 0.5 for block 1 and -0.5 for block 2.

This model allowed us to place priors on the simple effects (in units of standardized mean differences $d$) for each evaluative measure and implement the theoretically motivated order constraints:

$$
\begin{aligned}
\mathcal{M}_\textrm{No effect}:~ & \delta_\alpha = 0 \\ & \delta_\beta = 0 \\
\mathcal{M}_\textrm{One mind}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{M}_\textrm{Two minds}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Negative-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{M}_\textrm{Any effect}:~ & \delta_\alpha \sim \textrm{Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Cauchy}(r = \sqrt2/2)
\end{aligned}
$$

Additionally, we placed default multivariate Cauchy priors ($r = \sqrt2/2$) on lab main effects $\eta_l$ as well as on lab effects on evaluative differences between blocks for rating scores ($\tau_l$) and IAT scores ($\upsilon_l$).

To formally assess whether the data from all labs exhibited consistent effects we added another model that enforced the order constraint of $\mathcal{M}_\textrm{One mind}$ and $\mathcal{M}_\textrm{Two minds}$ not only for the average block effects ($\alpha$ and $\beta$) but for each lab individually (i.e., $\alpha_l = \alpha + \tau_l$ and $\beta_l = \beta + \upsilon_l$; $\mathcal{M}_\textrm{One mind everywhere}$ and $\mathcal{M}_\textrm{Two minds everywhere}$).

For the analyses we drew 1 million samples to estimate the postrior distribtution of model parameters.
Because the draws from the posterior distribution are used to estimate the Bayes factors for model comparisons that involve order constraints [@klugkist_inequality_2005], the number of draws implies upper and lower bounds on some of the reported Bayes factors.
Most notably, as a direct consequence of the number MCMC samples the $\textrm{BF}_{\mathcal{M}_\textrm{One mind}/\mathcal{M}_\textrm{Two minds}} \in [\frac{1}{1 \times 10^6}, 1 \times 10^6]$.

### Prior sensitivity analysis

Bayesian model comparison by Bayes factors are by definition sensitive to the specified prior distributions.
To ensure that our inference is not contigent on our choice of piors we conducted prior sensitivity analyses for our key results.

#### Explicit and implicit measures

Our choice of piors for the simple effects of learning block for rating scores ($\alpha$) and IAT score ($\beta$) could be viewed as either overly optimistic or pessimistic.
The prior on simple rating score effects places considerable probability mass on effects $d$ < 0.707 although the previously reported effects were very large.
Similarly, placing the same prior on the simple effects for rating and IAT scores could be criticized because the previously reported IAT score effects were considerably smaller than those of rating scores.

```{r load-data-and-design-matrices}
tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-restructure_", recursive = TRUE)[1]))
tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-design-matrix_", recursive = TRUE)[1]))

otm1_n <- as.integer(nlevels(otm1_attitudes_collapsed$ParticipantNumber))
```

```{r otm1-prior-sensitivity-replication, cache = TRUE, warning=FALSE}
replication_rscales <- expand.grid(
  iat = seq(0.5, 1, length.out = 3)
  , rating = seq(sqrt(2)/2, 2, length.out = 3)
) %>% 
  filter(iat <= rating) %>%
  as.matrix %>% 
  `/`(., sqrt(2)) %>% # Rescale to ANOVA specification (see https://forum.cogsci.nl/discussion/3746/bayesfactor-scale-of-cauchy-prior-in-t-tests-and-anova)
  as.data.frame

replication_rscales$bf_one_mind_two_minds <- NA
replication_rscales$bf_one_mind_any_effect <- NA

for(i in 1:nrow(replication_rscales)) {
  i_rscales <- c(
    eta = 0.5
    , alpha = unname(replication_rscales[i, "rating"])
    , tau = 0.5
    , beta = unname(replication_rscales[i, "iat"])
    , upsilon = 0.5
  )

  # No effect model
  otm1_no_effect <- nWayAOV(
    y = otm1_attitudes_collapsed$Attitude
    , X = otm1_null_model_matrix
    , gMap = c(
      eta = rep(0, 2)
      , nu = rep(1, otm1_n)
    )
    , rscale = c(fixed = 0.5, random = 1)
    , iterations = otm1_n_mcmc_samples
  )

  # Fixed effect model
  otm1_unconstrained <- nWayAOV(
    y = otm1_attitudes_collapsed$Attitude
    , X = otm1_unconstrained_model_matrix
    , gMap = c(
      eta = rep(0, 2)
      , alpha = 1, tau = rep(2, 2)
      , beta = 3, upsilon = rep(4, 2)
      , nu = rep(5, otm1_n)
    )
    , rscale = c(fixed = i_rscales, random = 1)
    , iterations = otm1_n_mcmc_samples
  )
  otm1_unconstrained_bf <- exp(otm1_unconstrained$bf - otm1_no_effect$bf)

  # Fixed effect model
  otm1_unconstrained_samples <- nWayAOV(
    y = otm1_attitudes_collapsed$Attitude
    , X = otm1_unconstrained_model_matrix
    , gMap = c(
      eta = rep(0, 2)
      , alpha = 1, tau = rep(2, 2)
      , beta = 3, upsilon = rep(4, 2)
      , nu = rep(5, otm1_n)
    )
    , rscale = c(fixed = i_rscales, random = 1)
    , posterior = TRUE
    , iterations = otm1_n_mcmc_samples
  )
  colnames(otm1_unconstrained_samples)[1:ncol(otm1_fixed_effects_matrix) + 1] <- colnames(otm1_fixed_effects_matrix)

  ## Same direction
  otm1_same_direction_boost <- 4 * (
    (sum(
      otm1_unconstrained_samples[, "alpha"] > 0 &
      otm1_unconstrained_samples[, "beta"] > 0
    ) + 1) / (nrow(otm1_unconstrained_samples) + 2)
  )
  otm1_same_direction_bf <- otm1_unconstrained_bf * otm1_same_direction_boost

  ## Opposite direction
  otm1_opposite_direction_boost <- 4 * (
    (sum(
      otm1_unconstrained_samples[, "alpha"] > 0 &
      otm1_unconstrained_samples[, "beta"] < 0
    ) + 1) / (nrow(otm1_unconstrained_samples) + 2)
  )
  otm1_opposite_direction_bf <- otm1_unconstrained_bf * otm1_opposite_direction_boost

  rm("otm1_unconstrained_samples") # Go easy on GitHub

  replication_rscales$bf_one_mind_two_minds[i] <- otm1_same_direction_bf / otm1_opposite_direction_bf
  replication_rscales$bf_one_mind_any_effect[i] <- otm1_same_direction_bf / otm1_unconstrained_bf
}
```

We, therefore, varied the scale for the Cauchy priors on the simple effects in the ranges of $`r min(replication_rscales$rating)` < r_\alpha < `r max(replication_rscales$rating)`$ and $`r min(replication_rscales$iat)` < r_\beta < `r max(replication_rscales$iat)`$ for rating and IAT scores, respectively.
Considering results previous studies, we limited our reanalysis to combinations where the prior scale was larger for rating than for IAT effects.
The results of the prior sensitvity analysis reassure us that our inference is robust to a wide range and combination of scales of the default Cauchy priors, see Table\ \@ref(tab:otm1-prior-sensitivity-replication-table).
The Bayes factors were not affected by the scale of the priors to any meaningful degree.
This is because our data are informative enough to overwhelm the priors and because these Bayes factors primarily depend on the shape and location of the posterior distribution, not the prior distributions [@klugkist_bayesian_2005].

(ref:otm1-prior-sensitivity-replication-table) Results of the prior sensitivity analysis for the Bayesian model comparisons of primary interest.

(ref:otm1-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$ (see footnote 1 in the main article).
$r_\alpha$ and $r_\beta$ denote the scale for the Cauchy prior on the simple effects of learning block for rating scores ($\alpha$) and IAT scores ($\beta$), respectively (in units of standard deviations).

```{r otm1-prior-sensitivity-replication-table}
replication_rscales <- replication_rscales %>%
  printnum(format = c("f", "f", "e", "f")) %>%
  mutate(
    bf_one_mind_two_minds = papaja:::typeset_scientific(bf_one_mind_two_minds)
    , bf_one_mind_two_minds = paste0("$", bf_one_mind_two_minds, "$")
  ) %>%
  select(rating, everything())

variable_labels(replication_rscales) <- c(
  "rating" = "$r_\\alpha$"
  , "iat" = "$r_\\beta$"
  , "bf_one_mind_two_minds" = "$\\textrm{BF}_{\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Two minds}}$"
  , "bf_one_mind_any_effect" = "$\\textrm{BF}_{\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Any effect}}$"
)

apa_table(
  replication_rscales
  , caption = "(ref:otm1-prior-sensitivity-replication-table)"
  , note = "(ref:otm1-prior-sensitivity-replication-table-note)"
  , align = "c"
  , escape = FALSE
)
```

#### Recognition task

```{r otm1-prior-sensitivity-recognition}
rec_rscales <- seq(from = 0.5, to = 1, length.out = 2)

rec_bfs <- sapply(
  , X = rec_rscales
  , FUN = function(i, ...) { as.vector(ttestBF(otm1_mem$Accuracy - 0.5, mu = 0, rscale = i, nullInterval = c(0, Inf))[1]) }
)

rec_bfs_res <- rec_bfs %>%
  printnum(digits = 2, format = "e") %>%
  papaja:::typeset_scientific()
```

To test the robustness of our inference regarding participants recognition accuracy we varied the scale $r$ of the Cauchy prior in a wide interval of $[`r min(rec_rscales)`, `r max(rec_rscales)`]$.
The resulting Bayes factors were $`r rec_bfs_res[2]`< \textrm{BF}_{10} < `r rec_bfs_res[1]`$ and thus varied by a factor of `r rec_bfs[1] / rec_bfs[2]`.
These results again reassure that our inference is robust to a wide range of scales of the default Cauchy prior.

## Prime recogniton and implicit evaluations

(ref:otm1-rydell-recognition-plot) Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples.
Small points represent individual participants' accuracy.
Violins represent kernel density estimates of sample distributions.

```{r otm1-rydell-recognition-plot, fig.cap = "(ref:otm1-rydell-recognition-plot)", fig.width = 3.5, fig.height = 2.5}
otm1_mem %>%
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Location"
    , y = "US recognition accuracy"
  ) +
  theme(legend.position = "none")
```

In contrast to the original results reported by @rydell_two_2006, US recognition accuracy in this study was above chance, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
Memory for USs may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
We, therefore, performed an exploratory regression analysis of US recognition and the IAT score difference between blocks used in the Bayesian analysis above.
Positive values represent a more favorable evaluation after the block in which Bob was paired with positive learned behaviors and briefly presented negative USs.
Conversely, negative IAT score difference between blocks indicate that the IAT effects reflect the valence of the briefly presented USs.
If US recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between US recognition accuracy and IAT score differences between blocks:
When US recognition is high, IAT score differences should reflect the valence of the learned behaviors but not with the US valence.
We would expect to observe smaller and eventually negative IAT score differences as US recognition accuracy declines and associative learning takes over.

(ref:prime-recognition-iat-difference) Scatterplot of prime recognition accuracy and evaluative differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.

```{r prime-recognition-iat-difference, fig.cap = "(ref:prime-recognition-iat-difference)", message = FALSE}
tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-effects-plot_", recursive = TRUE)[1]))

otm1_iat_delta <- full_join(otm1_attitudes_delta, select(otm1_mem, ParticipantNumber, Accuracy)) %>% 
  filter(Measure == "IATscore")

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  labs(
    x = "US recognition accuracy"
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  theme_apa()
```

```{r prime-recognition-iat-difference-regression, results = "asis"}
otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  as.data.frame %>%
  lmBF(delta ~ Accuracy, data = .) %>%
  apa_print

otm1_iat_delta_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  lm(delta ~ Accuracy, data = .) %>% 
  apa_print
```

However, we were unable to detect any relationship between US recognition accuracy and IAT score differences between blocks, `r otm1_iat_delta_lm_res$full_result$Accuracy`; the data even provide some evidence against such a relationship, `r otm1_recognition_iat_lm_bf$statistic`.
We centered US recognition at .5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance US recognition accuracy, `r otm1_iat_delta_lm_res$full_result$Intercept`.
Hence, even for participants who exhibited no memory for briefly presented USs, IAT score differences reflected the valence of the learned behaviors, see Figure\ \@ref(fig:prime-recognition-iat-difference).
These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance US recognition accuracy in this study.

<!--
#### Prime valence memory

TODO TH: Is this supposed to be in the paper? 
TH: No - maybe not even online supplement?

```{r listPrimes, echo = FALSE, eval=FALSE}

# correct names of primes
eng_pos <- c("Flower",
            "Friend",
            "Gift",
            "Happy",
            "Puppy",
            "Pretty",
            "Party",
            "Kiss",
            "Kitten",
            "Smile")

eng_neg <- c("Corpse",
            "Death",
            "Hell",
            "Pain",
            "War",
            "Hurt",
            "Spider",
            "Stink",
            "Trash",
            "Ugly")

nl_pos <- c("Bloem",
            "Vriend",
            "Geschenk",
            "Blij",
            "Puppy",
            "Mooi",
            "Feest",
            "Kus",
            "Katje",
            "Glimlach")

nl_neg <- c("Lijk",
            "Dood",
            "Hel",
            "Pijn",
            "Oorlog",
            "Letsel",
            "Spin",
            "Stank",
            "Afval",
            "Lelijk")

ger_pos <- c("Blume",
            "Freund",
            "Geschenk",
            "Glücklich",
            "Welpe",
            "Hübsch",
            "Party",
            "Kuss",
            "Kätzchen",
            "Lächeln")

ger_neg <- c("Leiche",
            "Tod",
            "Hölle",
            "Schmerz",
            "Krieg",
            "Verletzung",
            "Spinne",
            "Gestank",
            "Abfall",
            "Hässlich")

# prep data frame to correspond with correct names

otm1_mem$chosenItems <- gsub("\\r", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("u'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("\\", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("ï»¿", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("[", "", otm1_mem$chosenItems, fixed = TRUE) 
otm1_mem$chosenItems <- gsub("]", "", otm1_mem$chosenItems, fixed = TRUE)

otm1_mem$chosenItems <- gsub("xfc", "ü", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xe4", "ä", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xf6", "ö", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xdf", "ß", otm1_mem$chosenItems)

otm1_mem <- separate(otm1_mem, 
                     col = "chosenItems", 
                     into = paste0("chosen", 1:20), 
                     sep = ", ")

pos <- c(eng_pos, nl_pos, ger_pos)
neg <- c(eng_neg, nl_neg, ger_neg)
otm1_mem$poscor <- 0
otm1_mem$negcor <- 0

for(i in 1:20){
  otm1_mem$poscor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% pos, otm1_mem$poscor + 1, otm1_mem$poscor + 0)
  otm1_mem$negcor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% neg, otm1_mem$negcor + 1, otm1_mem$negcor + 0)
}

aggregate(negcor ~ Location, data = otm1_mem, FUN = mean)
aggregate(poscor ~ Location, data = otm1_mem, FUN = mean)

t.test(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)

t.test(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)

t.test(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)

```
-->

\newpage

# References

\begingroup
\setlength{\parskip}{0pt}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-10-31 analysis_and_paper/modal_frame_rate.R

@@ -1,0 +1,15 @@
+#' Calculate per Person Frame Rate
+#'
+#' @param data.frame. Experimental log data
+#'
+#' @export
+
+modal_frame_rate <- function(x) {
+  rounded_frame_rate <- apply(x, 1, function(y) round(1 / y))
+  
+  apply(
+    rounded_frame_rate
+    , 2
+    , function(z) names(sort(-table(z)))[1]
+  )
+}

### 2019-10-31 otm1/preregistration/PreRegOTM_word_version.Rmd
add all materials

---
title           : "Of Two Minds: a registered replication"
shorttitle      : "Replication of Rydell et al."

author: 
  - name        : Tobias Heycke
    affiliation : 1
  - name        : Frederik Aust
    affiliation : 1
  - name        : Mahzarin R. Banaji
    affiliation : 2
  - name        : John G. Conway
    affiliation : 3
  - name        : Pieter Van Dessel
    affiliation : 4
  - name        : Xiaoqing Hu
    affiliation : 5    
  - name        : Congjiao Jiang
    affiliation : 3    
  - name        : Benedek Kurdi
    affiliation : 2    
  - name        : Robert Rydell
    affiliation : 6
  - name        : Lisa Spitzer
    affiliation : 1
  - name        : Christoph Stahl
    affiliation : 1
  - name        : Christine A. Vitiello
    affiliation : 3
  - name        : Jan De Houwer
    affiliation : 4

affiliation:
  - id          : 1
    institution : University of Cologne
  - id          : 2
    institution : Hardvard University 
  - id          : 3
    institution : University of Florida 
  - id          : 4
    institution : Ghent University 
  - id          : 5
    institution : The University of Hong Kong 
  - id          : 6
    institution : Indiana University

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
keeptex           : yes

bibliography:
  - OTM.bib

lang              : "english"
class             : doc
output            : papaja::apa6_pdf
---

# Study Information

## Title
`r rmarkdown::metadata$title`

## Note
Note that parts of this registration are copied from a previous registration by Heycke et al.: https://osf.io/cm2sj/ and the corresponding paper: https://osf.io/tsvkd/

## Research questions

One possible way of acquiring preferences is through evaluative conditioning (EC). 
In general, the EC-effect is defined as a change in evaluation, that is due to the pairing of a negative or positive valenced stimulus (called unconditioned stimulus, US) with a target object (referred to as conditioned stimulus, CS) [@deHouwer2007conceptual].

Multiple models have been proposed in an effort to answer the question of the underlying mechanisms in evaluative conditioning effects.
These models can be allocated to one of two conceptually different assumptions. 
On the one hand, single propositional process theories claim that there is only one path that leads to preference acquisition. 
The propositional assumption states that evaluative conditioning works through the conscious formation of a proposition about the relation between a CS-US pair. 
Therefore, contingency awareness of the connection between the CS and US would be necessary to establish an EC-Effect [e.g. @mitchell_propositional_2009].

Dual-process theories, on the other hand, propose two distinct systems that leads to preference acquisition. 
Apart from the conscious, propositional system, they describe a second associative system, where a link between the stimuli is formed automatically without contingency awareness.
Thus, in contrast to the single propositional view, an EC effect could occur through an associative system even when participants have no contingency awareness for the link between CS and US.
An influential example for such a theoretical account is the associative-propositional evaluation (APE) model, developed by @gawronski_associative_2006. 
Along the division between propositional and associative processes, they distinguish between implicit and explicit attitudes. 
Thereby, associations as CS-US pairings have a direct effect on implicit evaluations, whereas propositions form the basis for explicit attitude change [@gawronski_associativepropositional_2011].

One testable difference between dual-and single-process theories is the question of contingency awareness as a necessity for an EC effect to occur.
One way to experimentally assess the effect of contingency awareness on EC is subliminal conditioning:
If one stimulus is presented subliminally, contingency awareness between CS and US can be ruled out.
Following the APE model, it should be possible to form an unconscious association between CS and US through repeated pairing, since awareness of the relationship between stimuli is not needed for association formation. 
These pairings would ultimately result in an EC-effect, which one should be able to detect with implicit evaluation measures [@gawronski_associativepropositional_2011].
Finding an EC effect after a subliminal conditioning procedure would be a strong argument for dual-process theories of conditioning. 
If no EC occurred after subliminal conditioning, it would be an argument for propositional single-process theories [@mitchell_propositional_2009].

In fact, there are several studies that found evidence for subliminal EC-effects [e.g. @de_houwer_verbal_1994; @de_houwer_evaluative_1997; @field_dissociating_2005; @fulcher_when_2001]. 
Most of these studies however, can be criticized for methodological issues [see @sweldens_role_2014 for an overview]. 
Therefore, some authors still hold the opinion that an automatic link formation is not possible [@lovibond_role_2002; @pleyers_aware_2007; @stahl_respective_2009].
Certainly, finding an EC-effect in a well executed subliminal conditioning procedure would be a valuable contribution to the ongoing controversy, providing evidence against the necessity of contingency awareness.

One study showing a selective influence of subliminally presented USs is the study of @rydell_two_2006.
In this experiment, the CS was a picture of a character named “Bob”. 
On each trial, after a fixation cross, the picture of Bob was preceded by a prime word of either positive or negative valence that was presented subliminally. Then, participants saw the picture of Bob, and a few moments later behavioral information about Bob was presented alongside the image. 
This information was again either positive or negative. 
The participants were then asked to judge whether this behavior was characteristic of Bob or not. 
They subsequently received feedback about whether their judgment was correct or false. 
The experiment consisted of two experimental blocks with 100 trials in each block:
If the primes in the first block were negative, Bob was characterized by positive behavior and vice versa. 
Moreover, if the primes in the first block were negative, then they were positive in the second block and Bob was described by negative behavior.
The participants therefore received deviating implicit and explicit information in each experimental block. 
After each block, participants' implicit and explicit attitudes with regard to “Bob” were assessed.

The main finding of the study is that explicit attitudes were affected by behavioral information, whereas implicit attitudes reflected the valence of subliminal primes.
In line with the behavioral feedback information, there was a significant difference between the explicit attitudes measured after block one compared to the results of the explicit attitude measure after the second block. 
Independently, in line with the valence of subliminally presented primes, there was a significant difference between the two implicit attitude measures. 
@rydell_two_2006 conclude that their participants simultaneously held opposite implicit and explicit attitudes at the same time.

In a recent replication attempt the results of Rydell and colleagues could not be replicated [@heycke_two_inpress].
Even though the same stimulus material was used in this replication attempt, differences between the procedure by Heycke et al. (in press) and the original study might be the reason why the original result could not be replicated:
Specifically in Experiment 1 the stimulus material was translated to German and small changes to some words were made and in Experiment 2 the original material was used but the presentation time of the primes was reduced (16 ms compared to 25 ms in the original study).

Therefore, it seems necessary to conduct a replication of the original study which reproduces the original method as close as possible.
If the original results can be reproduced further studies could investigate why Heycke et al. (in press) were unable to reproduce the results (e.g., investigate the question whether the prime words were presented truly subliminally).

## Hypotheses

### Explicit Evaluation

Under both single-propositional and dual-process theories we would expect a more favorable rating of the target stimulus (i.e., Bob) when positive behavior is characteristic of Bob, than when negative behavior is characteristic of him [@rydell_two_2006]. 
We thus expect a significant difference between the results of the explicit attitude measure at time 1 compared to time 2, in the direction described above.

### IAT effect

Based on the findings by @rydell_two_2006 we would expect an IAT effect based on the valence of primes. 
We would therefore expect a significant difference between the results of the implicit attitude measure at time 1 compared to time 2. 
This result corresponds to the assumptions of a dual-process account.
According to such an account, we would thus expect that the implicit measure contradicts the explicit measure in each experimental block.

Based on the findings by Heycke and colleagues (in press) we would expect that the IAT effect reflects the supraliminal behavioral information of Bob, as does the explicit rating.

# Sampling Plan
<!-- Please describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study. -->

## Existing data
<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact the Center for Open Science if you have questions about how to answer this questions (prereg@cos.io). -->

**Registration prior to creation of data**. As of the date of submission of this research plan for preregistration, the data have not yet been collected, created, or realized.

## Data collection procedures
<!-- Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that don't include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use. -->

We plan to conduct our study at Ghent University (Belgium), Harvard University (USA), and the University of Cologne (Germany). 
Participants will receive 8 € or partial course credit for their participation. 
At each location participants will be seated behind a computer as the entire task is computerized.

If participants already took part in a previous replication attempt of this study, they are not allowed to participate in the study.

## Sample size
<!-- Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis? -->

We will collect the data of 50 participants in each lab.
Participants who signed up for the study are always allowed to participate, even when *N* = 50 has been reached before, which could result in a slightly larger sample size.

## Sample size rationale
<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel. -->

We will collect the same number of participants as used in the original study (N = 50) in each lab.
An a priori power analysis with the smallest effect ($f = 0.32$) from the original study and $\alpha = \beta = .05$ yielded a required sample of 34 participants. 
Pooling the data from all three labs (N = 150) would allow us to detect effects as small as $d_z$ = 0.27 (with $\alpha = \beta = .05$).

## Stopping rule
<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection. -->
We will collect the data of 50 participants in each lab.
When participants are excluded we will continue the data collection until 50 valid data sets are collected. 
Participants who signed up for the study are always allowed to participate, even when *N* = 50 has been reached before, which could result in a slightly larger sample size.

# Variables
<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. -->

## Manipulated variables
<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable. For observational studies and meta-analyses, simply state that this is not applicable. -->

Our main variable of interest is the valence of the primes and the valence of the (characteristic) behaviors.
Depending on whether participants receive positive explicit and negative implicit information first or vice versa, we should observe different responses of the measurement of implicit and explicit attitudes at time 1 and at time 2 (see Hypotheses).

We additionally manipulate the order of dependent measures to ensure that those are not responsible for any effects.
Half of the participants first respond to the implicit measure followed by the explicit attitudes measures, with the other half of participants having the opposite order.
As in the original study, we counterbalanced the order of the critical IAT blocks over participants (Combination 1: "Bob" or negative; "not Bob" or positive and Combination 2: "Bob" or positive; "not Bob" or negative).
Additionally, it is counterbalanced over participants whether in the IAT positive words have to be reacted to with the left or right key (and negative words with the other key).
As in the original study, we use different images for the target person.
Specifically, one out of six images is randomly assign to represent Bob and the other five images are used in the IAT as "Not Bob".

## Measured variables
<!-- Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study. -->
### Explicit Attitude

The explicit attitude toward the target person will be measures after the first and after the second learning block. 
We will use the same measures as in the original study, which will be administered on a computer and not (as in the original study) with a paper and pencil task:

In the Explicit Attitude Measure participants are asked to judge how likable the target person is, on a 9-point Likert scale, ranging from 1 (very unlikable) to 9 (very likable). 
After the participant indicated his/her response, five 9-point semantic differential scales, are presented together on a computer screen and participants are asked to judge the target person. These scales are as follows:

1. good - bad
2. pleasant – mean
3. agreeable – disagreeable
4. caring – uncaring
5. kind – cruel

Subsequently the participants are requested to evaluate the target person on a feeling thermometer that ranges from 0° to 100°, with higher values indicating a more positive evaluation of Bob.

### Implicit Attitude

We additionally measure the implicit attitude, by means of reaction times in an IAT, at time 1 and time 2. 
As in @rydell_two_2006, we used a modified IAT version reported by @mcconnell_relations_2001 consisting of seven 20-trial blocks.
Participants had to press the left key ("d") or right key ("k") as part of a classification task.
In the first block, images of the target character as well as images of other persons had to be categorized as depicting the target character or other persons (counterbalanced over participants whether the target character was on the left or the right key).
The target character name and "not" plus the target character name were displayed on the left or right bottom of the screen as category labels.
As in the original study we selected one image---out of the six images in the original material at random, for each participant anew, to represent the target character (in the learning phase and in the IAT). 
The remaining five other images were then used in the IAT to represent other individuals that were not the target character.
In the second block, positive and negative words had to be categorized as positive or negative (with the position of the corresponding key for positive/negative counterbalanced across participants).
Now the labels "positive" and "negative" were displayed on the left and right bottom of the screen.
In the third and fourth block, the first and second block were combined:
Half of the participants had the target character together with negative words on one key and all other images and positive words on the other key (Combination 1), while the other half of participants classified the target character together with positive words on one key and all other images and negative words on the other key (Combination 2).
The category labels from block 1 and block 2 were combined in this block (i.e., Bob + positive).
In the fifth block, a classification of the target character vs. other persons was again performed, but the location of the key for classifying the target character (vs. other persons) was switched compared to block 1 and block 3/4.
In the final two blocks (i.e., blocks six and seven), participants again worked on a combined classification task (i.e., a combination of blocks 2 and 5):
Participants who worked on Combination 1 in blocks 3 and 4 now worked on Combination 2 (and vice versa).
The order of trials in the critical blocks 3/4 and 6/7 was randomized for each participant anew, controlling that there were no more than 5 repetition trials (same key pressed as in previous trial) and controlling that there were approximately the same amount of response-switch (switching between the d and k key) and response-repetition trials.

During the learning phase we additionally measure the reaction time when judging a behavior to be characteristic or uncharacteristic of the target person.
We also measure the amount of correct primes identified in the memory task and ask demographic questions (Age, Study/Job, Gender, Suspected goal of study, Comments).

## Indices
<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section. -->

### Explicit Evaluation
In the original study, seven items were used to assess participants' attitudes towards Bob. After the items are z-standardized, an average score will be calculated for each participant at each of the two measurements.

### Implicit Evaluation
An IAT effect is calculated by subtracting the mean log RT of the block in which the target character and positive words (Combination 2) were presented from the mean log RT of the block in which the target character and negative words (Combination 1) were presented. The IAT effect is then z-standardized (across both IAT measures and all participants). Therefore a larger IAT effect indicates a more positive evaluation of the target character.

# Design Plan
<!-- In this section, you will be asked to describe the overall design of your study. Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration. -->

## Study type

**Experiment**. A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.

## Blinding
<!-- Blinding describes who is aware of the experimental manipulations within a study. Mark all that apply. -->

Participants are not informed about the experimental manipulation.

## Study design
<!-- Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies. -->

As Rydell et al. (2006) we will conduct a modified version of an attitude-learning paradigm developed by @kerpelman_partial_1971.

Participants will be seated at a computer and receive the instructions that they are going to learn something about a person, who is called Bob. 
Each trial starts with a blank screen for 1000 ms. 
Afterwards a fixation cross is displayed in the middle of the screen for 200 ms, which is replaced by either a positive or negative word (depending on the condition and block, see above) in white font on a black background, which is presented for 23.5 ms (Harvard) or 26.6 ms (Ghent and Cologne).
There are 10 positive and 10 negative primes, each presented 10 times, resulting in 200 trials altogether. 
Half of the participant will receive 10 $\times$ 10 positive Primes in the first block and 10 $\times$ 10 negative Primes in the second block. 
The other half will receive negative primes first and positives primes in the second block.
The prime is immediately followed by an image of the target person, which is shown without any information for 247 ms (Harvard) or 253 ms (Ghent and Cologne). 
Then negative or positive behavior written in white font appears underneath the image, until the participant presses either the "c" key or the "u" key to indicate whether he/she thinks that the behavior is characteristic or uncharacteristic for the target person.
In the first block of the learning phase, 50 positive behaviors and 50 negative behaviors are randomly drawn out of a list of 100 positive and 100 negative behaviors respectively, and presented in random order for each participant. 
In the second block, the remaining 50 positive and 50 negative behaviors are presented.
The valence of the primes is always opposite to the valence of the characteristic behaviors. 
The order of the 100 primes within each block is random for each participant.
After the judgment whether the behavior is characteristic of the target person or not, the participant receives feedback for 5000 ms about whether their judgment was correct or incorrect, by presenting the corresponding word on the screen.
After the first block, participants perform the first attitude measure consisting of explicit evaluations of the target person and an IAT. 
The order of these measures is counterbalanced across participants, with the same order after block 1 and block 2.

To assess implicit associations that the participants may hold towards Bob, an IAT is administered.
As @rydell_two_2006 we used a modified IAT version of the task by @mcconnell_relations_2001. 
As in those studies, we counterbalance which side is associated with positive/negative words and also counterbalance the order of critical blocks.

After the second experimental block and the second measure of dependent variables, a recognition memory test of the subliminally presented primes is administered. 
40 words are presented in a random order on the computer screen simultaneously. 20 of them are original primes, the other 20 are words were not used as primes.
Participants are asked to select 20 words from which they think that they occurred during the learning phase.

## Randomization
<!-- If you are doing a randomized study, how will you randomize, and at what level? -->

See above.

# Analysis Plan
<!-- For some studies, you may only want to preregister a single confirmatory analysis. For others, there may be multiple sets of confirmatory analyses you wish to register. If you wish to register more than one analysis set, you may do so. If subsequent analyses are very similar to previous ones, you may copy their content and then edit accordingly. Remember, all analyses specified in this section must be reported in the final article, and analyses not specified in this section that are reported in the paper must be clearly labeled as exploratory.
To help you keep track of multiple analyses, you may label each for your reference. -->

## Statistical models and hypotheses
<!-- What statistical model(s) will you use to test your hypothesis(ses)? Please include the type of model (e.g. ANOVA, regression, SEM, etc.) as well as the specification of the model (i.e. what variables will be included). Refer to the *variables* section and include the manipulated or measured variables in the description of the predictors, outcomes, and relevant covariates for the analysis. -->

How to evaluate the success of a replication attempt statistically is subject of current debate [e.g., @fabrigar_conceptualizing_2016; @simonsohn_small_2015-1; @verhagen_bayesian_2014]. Whether a pattern of results has been reproduced is especially difficult to diagnose if the to-be-replicated pattern consists of more than two cells of a factorial design.

It is, however, possible to instantiate specific patterns of mean differences, predicted by a theory or observed in a study, as a statistical model and evaluate the predictive accuracy of this model based on the results observed in the study [e.g., @rouder_2017_theories_models_predictions].

In this project we have two competing predictions:

(1) @rydell_two_2006 report that across both measurement times explicit ratings are congruent with behavioral descriptions of Bob. In contrast, IAT scores were incongruent with behavioral descriptions.

(2) In their replication, Heycke et al. (in press) observed the same pattern for explicit ratings but the opposite for IAT scores. Like explicit ratings, IAT scores were congruent with behavioral descriptions.

In a replication we could, thus, expect that the manipulation influences ratings and IAT scores in the same direction ($\mathcal{H}_\textrm{same direction}$), or in opposite directions ($\mathcal{H}_\textrm{opposite directions}$). In a Bayesian analysis we would directly compare which of the two patterns is a better a priori-description of the replication outcome. Hence, the analysis would directly inform the question which of the two patterns was replicated.

Additionally, it is advisable to add two theoretically less interesting exploratory models to the analysis: one model that assumes no effect of the manipulation ($\mathcal{H}_\textrm{no effect}$) and one model that is compatible with any pattern ($\mathcal{H}_\textrm{unconstrained effect}$). If the latter model provides the best a priori-description of the data, the observed data would be inconsistent with both previously reported outcomes.

$$
\begin{aligned}
\mathcal{H}_\textrm{no effect}:~ & \delta_\textrm{rating} = 0 \\ & \delta_\textrm{IAT} = 0 \\
\mathcal{H}_\textrm{same direction}:~ & \delta_\textrm{rating} \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\textrm{IAT} \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{H}_\textrm{opposite directions}:~ & \delta_\textrm{rating} \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\textrm{IAT} \sim \textrm{Negative-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{H}_\textrm{unconstrained effect}:~ & \delta_\textrm{rating} \sim \textrm{Cauchy}(r = \sqrt2/2) \\ & \delta_\textrm{IAT} \sim \textrm{Cauchy}(r = \sqrt2/2)
\end{aligned}
$$
We will analyse target evaluations using Bayesian ANOVA with default (multivariate) Cauchy prior [$r = \sqrt2/2$; @rouder_default_2012] and recognition memory performance using a one-tailed Bayesian $t$ test with default Cauchy prior [$r = \sqrt2/2$; @rouder_2009_bayesian_t_tests].

$$
\begin{aligned}
\mathcal{H}_\textrm{guessing}:~ & \delta_\textrm{recognition} = 0 \\
\mathcal{H}_\textrm{memory}:~ & \delta_\textrm{recognition} \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2)
\end{aligned}
$$

Furthermore, we will replicate the traditional frequentist ANOVA analyses as described by @rydell_two_2006.
However, this traditional ANOVA approach ignores systematic trial-to-trial variability in IAT response latencies due to stimuli, which can lead to inflated test statistics and underestimated confidence intervals.
Hence, we will supplement the ANOVA analysis of IAT scores by a mixed model analysis to ensure that our conclusion are not affected by stimulus effects [@wolsiefer_modeling_2017].

## Transformations
<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process. -->

We will transform the data as described in the original paper (see Indices).

## Follow-up analyses
<!-- If not specified previously, will you be conducting any confirmatory analyses to follow up on effects in your statistical model, such as subgroup analyses, pairwise or complex contrasts, or follow-up tests from interactions. Remember that any analyses not specified in this research plan must be noted as exploratory. -->

We will check if there are any differences in the results depending in the location of data collection.

## Inference criteria
<!-- What criteria will you use to make inferences? Please describe the information you'll use (e.g. p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this? -->

For the frequentist analysis we use $p$-values $p<.05$ as inference criteria. 
For the Bayesian analyses we will use Bayes factors.
We consider a Bayes factor $>10$ or $< 1/10$ to be convincing evidence for an effect, or the absence of an effect, respectively.
$\mathit{BF}_{10}$ or $\mathit{BF}_{01}$ smaller than 3 will only be considered to be anecdotal evidence [@schonbrodt_sequential_2015].

## Data exclusion
<!-- How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? -->

If participants already took part in a previous replication attempt of this study, they are not allowed to participate in the study. 
Data from participants who abort the study before completing it will be excluded. 
Additionally, data will be excluded if participants let us know that they did not follow the instructions properly.

## Missing data
<!-- How will you deal with incomplete or missing data? -->

If we encounter incomplete or missing data, the participant will be excluded from any analyses.

# Other
<!-- If there is any additional information that you feel needs to be included in your preregistration, please enter it here. -->

## Differences to the original study by Rydell et al. (2006)

We aimed to replicate the study of Rydell et al. (2006) as close as possible, but the following changes were made in accordance with the first author of the original study:

We translated all instructions and materials to German / Dutch for the experiment in Cologne/ Ghent to ensure that valent primes carry the intended affect for the participants and to ensure that participants understood all parts of the study.
For efficiency reasons, we decided to conduct the experiment solely at the computer and therefore computerized the paper-pencil tasks (i.e., the explicit evaluation and the memory test). 
Additionally, we will present the subliminal prime for 23.5 ms / 26.6 ms instead of 25 ms, due to a slight difference in CRT monitors (i.e., 75/ 85 Hz instead of 80 Hz in the original study).

# References

### 2019-10-31 otm1/results/analysis1.Rmd
add all materials

---
title             : "Analysis of ML-OTM1"
author            : "Frederik Aust"
date              : "`r format(Sys.time(), '%d %B, %Y')`"

output:
  bookdown::html_document2:
    theme         : "spacelab"
    df_print      : "kable"
    code_folding  : "hide"
    toc           : true
    toc_float     : true
---

```{r init, include = FALSE}
library("magrittr")
library("tidyr")
library("dplyr")
library("assertthat")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("afex")
library("emmeans")
library("BayesFactor")

source("https://gist.githubusercontent.com/crsh/bd4d1f62d300462ea0c0f44b9ad38616/raw/edd9c74e24b68f42433c2526cafc888509b1b8bc/batch_download_github.R")
source("https://gist.githubusercontent.com/crsh/357458c41fd3d554fb24/raw/f7725d5c4894a055a1b2e461dc5c39f3db23b2b8/batch_read.R")

source("../../R/modal_frame_rate.R")

# Set seed for random number generator
set.seed(315054738)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Use multivariate models for emmeans contrasts and post-hoc tests
afex_options(emmeans_model = "multivariate")

# Configure df approximation for mixed model contrasts and post-hoc tests
emm_options(
  lmer.df = "satterthwaite"
  , lmerTest.limit = 22384
)
```

```{r otm1-analysis-preferences, cache = TRUE}
# Data wrangling
process_rawdata <- TRUE
download_bornopen_data <- FALSE

# Data location
raw_data_path <- "data_raw/"
processed_data_path <- "data_processed/"

# Default ggplot theme
theme_set(theme_apa())

## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
assignInNamespace("theme_nothing", function() {
    theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
}, "cowplot")

# Number of MCMC samples for Bayesian analysis
otm1_n_mcmc_samples <- 1e6
```

```{r otm1-load-data, cache = TRUE, dependson = "otm1-analysis-preferences", warning = FALSE}
# Process raw data
if(process_rawdata) {

  # Born-open data from Cologne
  if(download_bornopen_data) {
    batch_download_github(
      "https://github.com/methexp/rawdata/tree/master/OTM"
      , pattern = "\\.dat"
      , paste0(raw_data_path, "cologne/")
    ) %>%
      is.null %>%
      assert_that(msg = "Download of born-open data failed.")
  }

  # Merge raw data
  otm1_eval <- batch_read(
    raw_data_path
    , pattern = "Eval"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm1_iat <- batch_read(
    raw_data_path
    , pattern = "IAT"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm1_mem <- batch_read(
    raw_data_path
    , pattern = "MemTest"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm1_demo <- batch_read(
    raw_data_path
    , pattern = "Demographics"
    , recursive = TRUE
    , read_fun = read.delim
    , quote = "~" # Participants used " in their input
  )

  otm1_log <- batch_read(
    raw_data_path
    , pattern = "ScreenLog"
    , recursive = TRUE
    , read_fun = read.csv
    , header = FALSE
  )

  # Recode, calculate indices, and filter data
  otm1_eval <- otm1_eval %>%
    mutate_at(vars(starts_with("Eval")), scale) %>%
    select(starts_with("Eval")) %>%
    rowwise %>%
    do(data.frame(Eval = sum(unlist(.)))) %>% 
    bind_cols(otm1_eval, .) %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
    )

  otm1_iat <- otm1_iat %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
      , IATBlock = factor(paste0("Block", IATBlock))

      # Wolsiefer et al. (2017, p. 1198; doi: 10.3758/s13428-016-0779-0)
      , imageType = ifelse(Category == "Image", ifelse(Type == "Bob", 1, -1), 0)
      , wordType = ifelse(Category == "Text", ifelse(Type == "neg", 1, -1), 0)
    ) %>%
    filter(IATBlock %in% c("Block34", "Block67")) %>%
    mutate(
      Correct = ifelse(Correct == "correct", 1, 0)
      , RT = ifelse(Correct == 1, RT, RTafterError)
      , cleanRT = ifelse(RT < 0.3, 0.3, RT)
      , cleanRT = ifelse(cleanRT > 3, 3, cleanRT)
      , logCleanRT = log(cleanRT)

      # Wolsiefer et al. (2017, p. 1198; doi: 10.3758/s13428-016-0779-0)
      # Combination 1: Combination 1 (Bob = negative) in Block 3 & 4
      # Combination 2: Combination 1 (Bob = negative) in Block 6 & 7
      , Congruent = ifelse(
        # Bob = negative
        (Combination == 1 & IATBlock == "Block34") |
        (Combination == 2 & IATBlock == "Block67")
        # (Combination == 1 & IATBlock == "Block34" & Block == 1 & ValenceBlock == "Negative-positive") |
        # (Combination == 1 & IATBlock == "Block34" & Block == 2 & ValenceBlock == "Positive-negative") |
        # (Combination == 2 & IATBlock == "Block67" & Block == 1 & ValenceBlock == "Negative-positive") |
        # (Combination == 2 & IATBlock == "Block67" & Block == 2 & ValenceBlock == "Positive-negative") |
        # # Bob = positive
        # (Combination == 1 & IATBlock == "Block67" & Block == 1 & ValenceBlock == "Positive-negative") |
        # (Combination == 1 & IATBlock == "Block67" & Block == 2 & ValenceBlock == "Negative-positive") |
        # (Combination == 2 & IATBlock == "Block34" & Block == 2 & ValenceBlock == "Negative-positive") |
        # (Combination == 2 & IATBlock == "Block34" & Block == 1 & ValenceBlock == "Positive-negative")
        , "Bob & negative" # -1
        , "Bob & positive" # 1
      ) %>% factor(levels = c("Bob & negative", "Bob & positive"))
      #   , "Congruent" # -1
      #   , "Incongruent" # 1
      # ) %>% factor(levels = c("Incongruent", "Congruent"))
    )

  otm1_stimulus_translations <- read.delim("IAT_word_translations.tab", header = FALSE)[-1, ] %>%
    set_colnames(c("German", "Dutch", "English"))

  german_iat_words <- match(otm1_iat$Stimulus, otm1_stimulus_translations$German)
  dutch_iat_words <- match(otm1_iat$Stimulus, otm1_stimulus_translations$Dutch)

  otm1_iat$translatedStimulus <- otm1_iat$Stimulus
  otm1_iat$translatedStimulus[!is.na(german_iat_words)] <- otm1_stimulus_translations$English[
    na.omit(german_iat_words)
  ]
  otm1_iat$translatedStimulus[!is.na(dutch_iat_words)] <- otm1_stimulus_translations$English[
    na.omit(dutch_iat_words)
  ]

  otm1_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")

  otm1_attitudes <- otm1_iat %>%
    group_by(ParticipantNumber, Location, MeasureOrder, Block, IATBlock, Combination, ValenceBlock) %>%
    summarize(meanRT = mean(logCleanRT), nRT = length(logCleanRT)) %>%
    ungroup %>%
    spread(IATBlock, meanRT) %>%
    # Combination 1: Combination 1 (Bob = negative) in Block 3 & 4
    # Combination 2: Combination 1 (Bob = negative) in Block 6 & 7
    mutate(IATscore = ifelse(Combination == 1, Block34 - Block67, Block67 - Block34)) %>%
    select(c(otm1_analysis_factors, "IATscore")) %>%
    left_join(
      select(otm1_eval, c(otm1_analysis_factors, "Eval"))
      , by = otm1_analysis_factors
    ) # %>%
    # mutate(
    #   Eval = scale(Eval) %>% as.vector
    #   , IATscore = scale(IATscore) %>% as.vector
    # )

  otm1_demo$frameRate <- modal_frame_rate(otm1_log)
  otm1_mem <- left_join(otm1_mem, otm1_demo, by = "ParticipantNumber")

  otm1_mem <- otm1_mem %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
      , Accuracy = NumbercorrectIdent / 20
    )

  rm("otm1_log", "otm1_demo")

  # Save processed data
  saveRDS(otm1_attitudes, paste0(processed_data_path, "otm1_attitudes.rds"))
  saveRDS(otm1_iat, paste0(processed_data_path, "otm1_iat_trial_data.rds"))
  saveRDS(otm1_mem, paste0(processed_data_path, "otm1_memory.rds"))
} else {
  otm1_attitudes <- readRDS(paste0(processed_data_path, "otm1_attitudes.rds"))
  otm1_iat <- readRDS(paste0(processed_data_path, "otm1_iat_trial_data.rds"))
  otm1_mem <- readRDS(paste0(processed_data_path, "otm1_memory.rds"))
}
```

# Participants

```{r otm1-check-data-integrity, cache = TRUE, dependson = "otm1-load-data"}
# Exclude participants due to technical failures
otm1_technical_failure <- c("345", "347")
otm1_technical_failure_expression <- expression(!as.character(ParticipantNumber) %in% otm1_technical_failure)

otm1_attitudes <- filter(otm1_attitudes, eval(otm1_technical_failure_expression)) %>%
  mutate(ParticipantNumber = factor(ParticipantNumber))
otm1_iat <- filter(otm1_iat, eval(otm1_technical_failure_expression)) %>% droplevels
otm1_mem <- filter(otm1_mem, eval(otm1_technical_failure_expression)) %>% droplevels

# Check for incomplete data
otm1_n_trials <- aggregate(Eval ~ ParticipantNumber, otm1_attitudes, length) %>%
  full_join(
    aggregate(RT ~ ParticipantNumber, otm1_iat, length)
    , by = "ParticipantNumber"
    ) %>%
  full_join(
    aggregate(NumbercorrectIdent ~ ParticipantNumber, otm1_mem, length)
    , by = "ParticipantNumber"
  )

otm1_incomplete_data <- otm1_n_trials$ParticipantNumber[
  with(
    otm1_n_trials
    , Eval != 2 ||
      RT != 160 ||
      NumbercorrectIdent != 1
  )
]

if(length(otm1_incomplete_data) > 0) warning(
  "Incomplete datasets: "
  , paste(otm1_incomplete_data, collapse = ", ")
)

# Check frame rate
otm1_frame_rate <- otm1_mem$ParticipantNumber[
  with(
    otm1_mem
    , (Location == "Cologne" & frameRate != 75) ||
      (Location == "Ghent" & frameRate != 75) ||
      (Location == "Harvard" & frameRate != 85)
  )
]

if(length(otm1_frame_rate) > 0) warning(
  "Incorrect frame rates: "
  , paste(otm1_frame_rate, collapse = ", ")
)
```

```{r otm1-exclusion, cache = TRUE, dependson = "otm1-check-data-integrity"}
otm1_noncompliance <- c()
otm1_exclude <- c(otm1_incomplete_data, otm1_frame_rate) %>%
  unique

otm1_n_excluded <- as.integer(length(c(otm1_exclude, otm1_technical_failure)))

otm1_exclusion_expression <- expression(!ParticipantNumber %in% otm1_exclude)

otm1_attitudes <- filter(otm1_attitudes, eval(otm1_exclusion_expression)) %>% droplevels
otm1_iat <- filter(otm1_iat, eval(otm1_exclusion_expression)) %>% droplevels
otm1_mem <- filter(otm1_mem, eval(otm1_exclusion_expression)) %>% droplevels

otm1_n <- as.integer(nlevels(otm1_attitudes$ParticipantNumber))
```

We recruited `r otm1_n + otm1_n_excluded` participants; `r printnum(otm1_n_excluded, numerals = otm1_n_excluded < 10)` participants were excluded due to technical failure or noncompliance with instructions.
Hence, the following results are based on data of `r otm1_n` participants.

(ref:otm1-participant-table)
Demographics by location.

(ref:otm1-participant-table-note)
Mean age is given with range in brackets.

```{r otm1-participant-table, results = "asis"}
otm1_mem %>% 
  mutate(
    Gender = gsub("^w|weiblich|v|vrouw|woman|f$", "female", Gender, ignore.case = TRUE) %>%
      tolower
    , Age = as.numeric(gsub("\\W", "", Age))
  ) %>%
  group_by(Location) %>% 
  summarize(
    age_mean = mean(Age, na.rm = T)
    , age_min = min(Age)
    , age_max = max(Age)
    , "Female (%)" = printnum(sum(grepl("female", Gender)) / length(Accuracy) * 100)
    , "$n$" = length(Accuracy)
  ) %>%
  mutate(Age = paste0(printnum(age_mean), " [", age_min, ", ", age_max, "]")) %>%
  select(Location, Age, "Female (%)", "$n$") %>%
  apa_table(
    caption = "(ref:otm1-participant-table)"
    , note = "(ref:otm1-participant-table-note)"
    , escape = FALSE
  )
```

# Results

In the following "Valence block" and "Valence order" both refer to the joint valence order of the explicit description of Bob and briefly presented primes.
When we refer to one valence order (e.g. positive-negative) we specify the order of the explicit descriptions of Bob; the briefly presented primes in that condition were of the opposite valence.

<!-- (ref:omt1-rating-plot) -->
<!-- Black-rimmed points represent means, error bars represent 95% bootstrap confidence intervals, small points represent individual participants' responses, and violins represent kernel density estiamtes of smaple distributions. -->

```{r otm1-rating-plot, fig.cap = "(ref:omt1-rating-plot)", warning = FALSE}
otm1_results_legend <- guide_legend(
    title = "Order of valent descriptions of Bob"
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
  )

otm1_rating_plot <- otm1_attitudes %>%
  ggplot(aes(x = Block, y = Eval, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
  geom_violin(position = position_dodge(0.1), alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(position = position_dodge(0.1), maxwidth = 0.2, alpha = 0.5, size = 0.5) +
  stat_summary(fun.y = mean, aes(group = ValenceBlock, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23), guide = otm1_results_legend) +
  labs(
    x = "Block"
    , y = " \nExplicit attitude score"
  ) +
  guides(linetype = otm1_results_legend) +
  facet_wrap(~ Location) +
  theme(
    legend.position = "top"
    , legend.justification = "center"
  )
```

<!-- (ref:omt1-iatscore-plot) -->
<!-- Black-rimmed points represent means, error bars represent 95% bootstrap confidence intervals, small points represent individual participants' responses, and violins represent kernel density estiamtes of smaple distributions. -->

```{r otm1-iatscore-plot, fig.cap = "(ref:omt1-iatscore-plot)", warning = FALSE}
otm1_iatscore_plot <- otm1_attitudes %>%
  ggplot(aes(x = Block, y = IATscore, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
  geom_violin(position = position_dodge(0.1), alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(position = position_dodge(0.1), maxwidth = 0.2, alpha = 0.5, size = 0.5) +
  stat_summary(fun.y = mean, aes(group = ValenceBlock, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  labs(
    x = "Block"
    , y = "IAT response time\ndifference [log(s)]"
  ) +
  facet_wrap(~ Location) +
  theme(legend.position = "none")
```

(ref:otm1-results-plot)
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participants' responses, and violins represent kernel density estimates of sample distributions.

```{r otm1-results-plot, fig.cap = "(ref:otm1-results-plot)", fig.height = 7, fig.width = 6.5, warning = FALSE}
plot_grid(
  otm1_rating_plot +
    theme(
      axis.title.x = element_blank()
      , axis.ticks.x = element_blank()
      , axis.text.x = element_blank()
      , axis.title.y = element_text(lineheight = 1.7)
      , strip.background = element_blank()
    )
  , NULL
  , otm1_iatscore_plot + 
    theme(strip.text.x = element_blank())
  , ncol = 1
  , rel_heights = c(1, 0.05, 0.8)
)
```

## Frequentist analysis

(ref:otm1-rydell-analysis-overall)
Results of the combined ANOVA of $z$ standardized attitude ratings and IAT scores.

```{r otm1-rydell-analysis-overall, results = "asis"}
otm1_attitudes %>%
  mutate(
    Eval = scale(Eval) %>% as.numeric
    , IATscore = scale(IATscore) %>% as.numeric
  ) %>%
  gather("Measure", "Attitude", Eval, IATscore) %>%
  mutate(Measure = factor(Measure)) %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Attitude"
    , within = c("Block", "Measure")
    # , between = "ValenceBlock"
    , between = c("ValenceBlock", "Location")
    , data = .
  ) %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm1-rydell-analysis-overall)"
    , escape = FALSE
  )
```

We found the expected three-way interaction between valence order, block, and attitude measure.
Moreover, we found that the three-way interaction differed between labs.
Visual inspection of the data suggested that labs differed with respect to magnitude of the differences in the valence order $\times$ block interaction between attitude measures---the direction of the interaction was the same for both measures in all labs.
We will return to this point below.
As in the original analysis we followed the significant three-way interaction up with separate analysis of each attitude measure.

### Explicit attitudes

(ref:otm1-rydell-analysis-explicit)
ANOVA results for attitude ratings.

```{r otm1-rydell-analysis-explicit, results = "asis"}
otm1_explicit_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "Eval"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Location")
  , data = otm1_attitudes
)

otm1_explicit_aov %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm1-rydell-analysis-explicit)"
    , escape = FALSE
  )
```

We found the expected two-way interaction between valence order and block.
Moreover, we found that the two-way interaction differed between labs.
The three-way interaction prompted us to test the differences between attitude ratings in Block 1 and 2 for each valence order of description of Bob in each lab.

(ref:otm1-rydell-analysis-explicit-contrasts)
Planned contrasts (Block 2 - Block 1) for the ANOVA of attitude ratings.

```{r otm1-rydell-analysis-explicit2, results = "asis"}
emmeans(otm1_explicit_aov, ~ Block | ValenceBlock * Location) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  ) %>%
  apa_print %$%
  table %>%
  select(-contrast) %>%
  rename("Valence order" = ValenceBlock) %>%
  apa_table(
    caption = "(ref:otm1-rydell-analysis-explicit-contrasts)"
    , escape = FALSE
    , row.names = FALSE
  )
```

As expected, in all labs ratings of Bob were more favorable after the first than after the second block when descriptions of Bob were first positive and later negative.
Vice versa, in all labs ratings of Bob were more favorable after the second than after the first block when descriptions of Bob were first negative and later positive.
Hence, the expected differences were consistently detectable in all labs but differed somewhat in magnitude as indicated by the three-way interaction.

### Implicit attitudes

(ref:otm1-rydell-analysis-implicit)
ANOVA results for IAT scores.

```{r otm1-rydell-analysis-implicit, results = "asis"}
otm1_iat_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "IATscore"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Location")
  , data = otm1_attitudes
)
otm1_iat_aov %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm1-rydell-analysis-implicit)"
    , escape = FALSE
  )
```

For IAT scores, we found the expected two-way interaction between valence order and block; in this case we detected no differences between labs.
Again, the significant two-way interaction prompted us to test the differences between IAT scores in Block 1 and 2 for each valence order of descriptions of Bob.

(ref:otm1-rydell-analysis-implicit-contrasts)
Planned contrasts (Block 2 - Block 1) for the ANOVA of IAT scores.

```{r otm1-rydell-analysis-implicit2, results = "asis"}
emmeans(otm1_iat_aov, ~ Block | ValenceBlock) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  ) %>%
  apa_print %$%
  table %>%
  select(-contrast) %>%
  rename("Valence order" = ValenceBlock) %>%
  apa_table(
    caption = "(ref:otm1-rydell-analysis-implicit-contrasts)"
    , escape = FALSE
    , row.names = FALSE
  )
```

IAT scores for Bob were more favorable after the first than after the second block when descriptions of Bob were first positive and later negative.
Vice versa, IAT scores for Bob were more favorable after the second than after the first block when descriptions of Bob were first negative and later positive.
The pattern is the same pattern as reported by Heycke et al. (2018) and the opposite of that reported by Rydell et al. (2006).
These results indicate that the attitudes assessed with explicit ratings and IAT scores did not dissociate.

#### Mixed model analysis of IAT

```{r otm1-lmer-exclusion, cache = TRUE, dependson = "otm1-exclusion"}
lme_error_exclusion <- otm1_iat %>%
  group_by(ParticipantNumber) %>%
  summarize(Correct = mean(Correct), fast_rate = mean(RT < 0.3)) %>%
  filter(Correct < 0.5 & fast_rate > 0.1) %$% ParticipantNumber

if(length(lme_error_exclusion) > 0) {
  otm1_iat <- otm1_iat %>%
    filter(!ParticipantNumber %in% otm1_lme_exclusion)
}

otm1_iat <- otm1_iat %>%
  # Wolsiefer et al. (2017, p. 1196; doi: 10.3758/s13428-016-0779-0)
  filter(RT > 0.4 & RT < 10) %>%
  # Wolsiefer et al. (2017, p. 1198; doi: 10.3758/s13428-016-0779-0)
  group_by(ParticipantNumber, Block) %>%
  mutate(RTD = RT / sd(RT)) %>%
  ungroup

# Wolsiefer et al. (2017, Erratum; doi: 10.3758/s13428-017-0897-3)
otm1_iat_lmer_formula <- RTD ~ Congruent * Block * ValenceBlock *
  (Category + wordType + imageType) +
  # (Congruent * Block | Location/ParticipantNumber) +
  (Congruent * Block | ParticipantNumber) +
  (Congruent * Block * ValenceBlock | translatedStimulus)
  # (1 | translatedStimulus) +
  # (0 + Congruent * Block * ValenceBlock | translatedStimulus)
```

We supplemented the ANOVA analysis of IAT scores by a mixed model analysis to ensure that our conclusion are
not affected by systematic stimulus effects.
We discarded trials in which responses were faster than 400 ms or slower than 10 s and analyzed standardized response latencies (Wolsiefer et al., 2017).
The following plot visualizes the analyzed standardized response latencies.

(ref:otm1-iat-plot)
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples.

```{r otm1-iat-plot, fig.cap = "(ref:otm1-iat-plot)"}
otm1_results_legend <- guide_legend(
    title = "Order of valent\ndescriptions of Bob"
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
  )

my_labeller <- function(x, ...) label_both(x, sep = " ", ...)

otm1_iat %>%
  ggplot(aes(x = Congruent, y = RTD, group = ValenceBlock, color = ValenceBlock, shape = ValenceBlock, fill = ValenceBlock)) +
  stat_summary(fun.y = mean, geom = "line", position = position_dodge(0.1)) +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23), guide = otm1_results_legend) +
  ylab("Standardized response time") +
  facet_grid(~ Block, labeller = my_labeller) +
  theme(
    legend.position = c(0.1, 0.85)
    , strip.background = element_blank()
  )
```

```{r eval = FALSE, echo = FALSE}
otm1_iat %>%
  ggplot(aes(x = Congruent, y = logCleanRT, group = ValenceBlock, color = ValenceBlock, shape = ValenceBlock, fill = ValenceBlock)) +
  stat_summary(fun.y = mean, geom = "line", position = position_dodge(0.1)) +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 5000)) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  ylab("Response time [log(s)]") +
  facet_grid(~ Block, labeller = label_both)
```

To assess the reversal of the congruency effect, we treated a common response mapping of Bob and negative words as congruent but Bob and positive words as incongruent.
Hence, larger values represent more favorable attitudes.

```{r otm1-lmer, cache = TRUE, dependson = "otm1-lmer-exclusion"}
otm1_iat_lmerTest <- lmerTest::lmer(
  otm1_iat_lmer_formula
  , data = otm1_iat
  , control = lmerControl(
    optCtrl = list(maxfun = 10 * 143^2)
  )
)

otm1_iat_lmerTest_summary <- summary(otm1_iat_lmerTest)
```

(ref:otm1-lmer-caption)
Results of the fixed effects in the linear mixed model analysis of standardized IAT response times.

(ref:otm1-lmer-note)
The model additionally included random participant and item effects with random intercepts and random slopes for all manipulations during the learning procedure and their interactions.

```{r otm1-lmer-table, results = "asis"}
otm1_iat_lmerTest_summary$coefficients %>%
  as.data.frame %>%
  rename(
    "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$df$" = "df"
    , "$t$" = "t value"
    , "$p$" = "Pr(>|t|)"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
    , Effect = gsub("1", "", Effect)
  ) %>%
  printnum(
    digits = c(2, 2, 2, 2, 3, 0)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`:`$p$`) %>%
  apa_table(
    caption = "(ref:otm1-lmer-caption)"
    , note = "(ref:otm1-lmer-note)"
    , escape = FALSE
  )
```

<br />

We found the expected three-way interaction between congruency, valence order, and block; the interaction was moderated by the type of stimulus that participants responded to (pictures of Bob and non-Bobs vs. positive and negative words; *Category*).
The three-way interaction prompted us to test the differences congruency effects in Block 1 and 2 for each valence order of descriptions of Bob.

```{r otm1-lmer-emm, cache = TRUE, dependson = "otm1-lmer-exclusion", message = FALSE}
otm1_iat_lmer <- lme4::lmer(
  otm1_iat_lmer_formula
  , data = otm1_iat
  , control = lmerControl(
    optCtrl = list(maxfun = 10 * 143^2)
  )
)

otm1_iat_lmer_emm <- emmeans(
  otm1_iat_lmer
  , ~ Congruent * Block * ValenceBlock
)
```

(ref:otm1-iat-lmer-contrasts)
Planned contrasts of changes in congruency effects across blocks for the linear mixed model analysis of standardized IAT response times.

```{r otm1-lmer-emm-2, cache = TRUE, dependson = "otm1-lmer-emm", results = "asis"}
contrast(
  otm1_iat_lmer_emm
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
) %>%
  apa_print %$%
  table %>%
  rename("Valence order" = contrast) %>%
  apa_table(
    caption = "(ref:otm1-iat-lmer-contrasts)"
    , escape = FALSE
    , row.names = FALSE
  )
```

In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable attitudes towards Bob after the first than after the second block when descriptions of Bob were first positive and later negative.
Vice versa, response time differences suggested more favorable attitudes after the second than after the first block when descriptions of Bob were first negative and later positive.
Again, these results indicate that the attitudes assessed with explicit ratings and IAT scores were consistent.

In light of the four-way interaction, we additionally explored these contrasts separately for responses to pictures of Bob vs. non-Bobs and positive vs. negative words.

(ref:otm1-iat-lmer-contrasts2)
Planned contrasts of changes in congruency effects across blocks for the linear mixed model analysis of standardized IAT response times.

```{r otm1-lmer-emm-3, cache = TRUE, dependson = "otm1-lmer-emm", results = "asis"}
otm1_iat_lmer_emm <- emmeans(
  otm1_iat_lmer
  , ~ Congruent * Block * ValenceBlock | Category
)

contrast(
  otm1_iat_lmer_emm
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
  , adjust = "bonferroni"
) %>%
  apa_print %$%
  table %>%
  rename("Valence order" = contrast) %>%
  apa_table(
    caption = "(ref:otm1-iat-lmer-contrasts2)"
    , escape = FALSE
    , row.names = FALSE
  )
```

The analysis indicated consistent changes in congruency effects albeit the effects were larger for words than for pictures ($p$ values Bonferroni-corrected for two comparisons).

```{r otm1-lmer-random-effects-plot-participants, cache = TRUE, dependson = "otm1-lmer-emm", eval = FALSE}
ranef_plots <- lattice::dotplot(ranef(otm1_iat_lmer))

ranef_plots$ParticipantNumber
```

```{r otm1-lmer-random-effects-plot-items, cache = TRUE, dependson = "otm1-lmer-emm", fig.width = 10, fig.height = 10, eval = FALSE}
ranef_plots$translatedStimulus
```

### Differences between implicit and explicit attitudes

As in the original study, we compared participants' $z$ standardized attitude toward Bob assessed by ratings and IAT scores.

(ref:otm1-rydell-attitude-differences)
Results of follow-up analysis comparing differences between attitude ratings and IAT scores in all experimental conditions.

```{r otm1-rydell-attitude-differences, results = "asis"}
otm1_attitudes %>%
  mutate(
    Eval = scale(Eval) %>% as.vector
    , IATscore = scale(IATscore) %>% as.vector
  ) %>%
  gather(dv, value, IATscore, Eval) %>%
  group_by(ValenceBlock, Block) %>%
  do(
    attitude_differences = t.test(value ~ dv, data = ., paired = TRUE) %>%
      broom::tidy()
  ) %>%
  unnest %>%
  mutate(
    p.value = printp(p.value)
    , ci = apply(data.frame(conf.low, conf.high), 1, papaja:::print_confint)
    , parameter = as.integer(parameter)
  ) %>%
  select(ValenceBlock, Block, estimate, ci, statistic, parameter, p.value) %>%
  printnum %>%
  rename(
    "Valence order" = ValenceBlock
    , "$\\Delta M$" = estimate
    , "95\\% CI" = ci
    , "$t$" = statistic
    , "$df$" = parameter
    , "$p$" = p.value
  ) %>%
  apa_table(
    caption = "(ref:otm1-rydell-attitude-differences)"
    , escape = FALSE
  )
```

We found differences between the attitudes assessed by ratings and IAT scores in all conditions.
Given that the assessed attitudes were consistent across measures, these differences indicate that the attitudes expressed in ratings were more extreme than those assessed in IAT scores.

### Recognition task

Finally, we tested participants recognition memory for the primes presented during the learning procedure.

(ref:otm1-rydell-recognition-plot)
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participants' responses, and violins represent kernel density estimates of sample distributions.

```{r otm1-rydell-recognition-plot, fig.cap = "(ref:otm1-rydell-recognition-plot)", fig.width = 3.5, fig.height = 3}
otm1_results_legend2 <- guide_legend(
    title.position = "top"
    , title.hjust = 0.5
  )

otm1_mem %>%
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  guides(shape = otm1_results_legend2) +
  labs(
    x = "Location"
    , y = "Prime recognition accuracy"
  ) +
  theme(
    legend.position = "top"
    , legend.justification = "center"
  )
```

(ref:otm1-rydell-recognition)
ANOVA results of prime recognition accuracy.

```{r otm1-rydell-recognition, results = "asis"}
otm1_mem_ttest <- t.test(otm1_mem$Accuracy, mu = 0.5, alternative = "greater") %>%
  apa_print %$%
  full_result

otm1_mem %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  droplevels %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Accuracy"
    , between = "Location"
    , data = .
    , anova_table = list(intercept = TRUE)
  ) %>%
  apa_print(intercept = TRUE) %$%
  table %>%
  apa_table(
    escape = FALSE
    , caption = "(ref:otm1-rydell-recognition)"
  )
```

Participants' recognition accuracy was better than chance, `r otm1_mem_ttest`---we detected no differences in recognition accuracy between labs.

## Bayesian analysis

The following analyses are targeted hypothesis tests that compare models that instantiate the patterns of mean differences observed by Rydell et al. (2006) and Heycke et al. (2018).
For simplicity we collapsed data across valence orders by reversing the coding of the blocks when Bob was first presented with negative and subsequently with positive descriptions.
Hence, in the following analysis the first block represents responses following trials in which Bob was presented with positive descriptions.
For both attitude measures we contrasted the first with the second block, such that positive values represent a more favorable attitude after the block in which Bob was presented with positive descriptions.

The first model of interest posits that the experimental manipulation has the same effect on attitude ratings and IAT scores, that is the direction of the effect is the same for both measures ($\mathcal{H}_\textrm{same direction}$; see Heycke et al., 2018).
The competing model of interest predicts effects in opposite directions ($\mathcal{H}_\textrm{opposite directions}$; see Rydell et al., 2006).
The following analysis assesses which of the two patterns is a better a priori-description of our findings.

We considered two additional control models: one model assumes no effect of the manipulation ($\mathcal{H}_\textrm{no effect}$), the other model is unconstrained and is compatible with any outcome ($\mathcal{H}_\textrm{unconstrained effect}$).
If the latter model provides the best a priori-description of the data, the results are inconsistent with both previously reported outcomes.

We implemented the unconstrained model as a hierarchical linear model that encompasses each of the other models as special cases:

$$
\begin{aligned}
\hat y_{ijk} = & \mu + \nu_i + \eta_l x_{1il} + \\
          & (\alpha + \tau_l x_{1il}) x_{2j} x_{3k} + \\
          & (\beta + \upsilon_l x_{1il}) (1 -  x_{2j}) x_{3k}
\end{aligned}
$$

The model predicts the $i$th participant's response to measure $j$ in the experimental block $k$.
Responses are predicted as a combination of a grand mean $\mu$, random participant intercepts $\nu_i$ (i.e., habitually higher or lower attitudes), a main effect of the labs $\eta_l$, and simple effects of experimental block for attitude ratings ($\alpha$) and IAT score ($\beta$).
Additionally, we allowed the simple effects to be moderated by the labs ($\tau_l$ and $\upsilon_l$ represent the lab-specific deviations from the overall simple effects).
The model does not include a main effect of attitude measure because any mean differences between attitude measures were leveled by the $z$ standardization.
$x_{1il}$ represents $l$ effect coded variables that indicate which lab participant $i$ belongs to; $x_{2j}$ indicates the attitude measure (1 for explicit attitude rating and 0 for IAT score), such that $\alpha + \tau_l$ is only relevant for attitude ratings and $\beta + \upsilon_l$ is only relevant for IAT scores; $x_{3k}$ is an effect coded variable that is set to 0.5 for block 1 and -0.5 for block 2.

This model allowed us to place priors on the simple effects (in units of $d$) for each attitude measure and implement the theoretically motivated order constraints:

$$
\begin{aligned}
\mathcal{H}_\textrm{no effect}:~ & \delta_\alpha = 0 \\ & \delta_\beta = 0 \\
\mathcal{H}_\textrm{same direction}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{H}_\textrm{opposite directions}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Negative-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{H}_\textrm{unconstrained effect}:~ & \delta_\alpha \sim \textrm{Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Cauchy}(r = \sqrt2/2)
\end{aligned}
$$

Additionally, placed default multivariate Cauchy priors ($r = \sqrt2/2$) on lab main effects $\eta_l$ and lab effects on attitude differences between blocks for attitude ratings ($\tau_l$) and IAT score ($\upsilon_l$).

```{r otm1-bayesian-replication-restructure, cache = TRUE, dependson = "otm1-exclusion"}
# Collapse across ValcenceOrder
otm1_attitudes_collapsed <- otm1_attitudes %>% 
  mutate(
    Block = ifelse(ValenceBlock == "Negative-positive", 3 - as.numeric(as.character(Block)), Block) %>% factor
  ) %>%
  select(-ValenceBlock) %>%
  mutate(Eval = scale(Eval) %>% as.vector, IATscore = scale(IATscore) %>% as.vector) %>%
  gather("Measure", "Attitude", Eval, IATscore)
```

```{r otm1-bayesian-replication-design-matrix, cache = TRUE, dependson = "otm1-bayesian-replication-restructure"}
# Participant random intercepts
otm1_random_participant_intercept_matrix <- BayesFactor:::oneDesignMatrix(
  trm = "ParticipantNumber"
  , data = otm1_attitudes_collapsed
  , dataTypes = c("ParticipantNumber" = "random")
) %>% as.matrix

# Fixed effects
## No main effect of attitude measure due to z standardization
unconstrained_effect_model <- function(x, a, b = NULL) {
  coding <- c(
    eta1 = 0, eta2 = 0
    , alpha = 0, tau1 = 0, tau2 = 0
    , beta = 0, upsilon1 = 0, upsilon2 = 0
  )

  # Main effect Location
  if(!is.null(b)) {
    switch(
      x["Location"]
      , Cologne = coding[c("eta1", "eta2")] <- b[1, ]
      , Ghent = coding[c("eta1", "eta2")] <- b[2, ]
      , Harvard = coding[c("eta1", "eta2")] <- b[3, ]
    )
  } else {
    coding <- coding[, c("alpha", "beta")]
  }

  # Simple block effects
  if(x["Measure"] == "Eval") {

    # alpha = Simple block effect for ratings
    if(x["Block"] == "1") {
      coding["alpha"] <- a[2, 1]
    } else {
      coding["alpha"] <- a[1, 1]
    }

    # tau = Interaction of alpha with location location
    if(!is.null(b)) {
      coding[c("tau1", "tau2")] <- coding[c("eta1", "eta2")] * coding["alpha"]
    }

  } else {

    # beta = Simple block effect for IATscore
    if(x["Block"] == "1") {
      coding["beta"] <- a[2, 1]
    } else {
      coding["beta"] <- a[1, 1]
    }

    # upsilon = Interaction of beta with location location
    if(!is.null(b)) {
      coding[c("upsilon1", "upsilon2")] <- coding[c("eta1", "eta2")] * coding["beta"]
    }
  }

  coding
}

a <- BayesFactor:::fixedFromRandomProjection(nlevels(otm1_attitudes_collapsed$Block))
b <- BayesFactor:::fixedFromRandomProjection(nlevels(otm1_attitudes_collapsed$Location))

otm1_fixed_effects_matrix <- t(apply(
  otm1_attitudes_collapsed
  , 1
  , unconstrained_effect_model
  , a = a
  , b = b
))

otm1_unconstrained_model_matrix <- cbind(
  otm1_fixed_effects_matrix
  , otm1_random_participant_intercept_matrix
)

otm1_no_lab_effect_model_matrix <- otm1_unconstrained_model_matrix[, -which(colnames(otm1_unconstrained_model_matrix) %in% c("tau1", "tau2", "upsilon1", "upsilon2"))]

otm1_null_model_matrix <- otm1_unconstrained_model_matrix[, -which(colnames(otm1_unconstrained_model_matrix) %in% c("alpha", "tau1", "tau2", "beta", "upsilon1", "upsilon2"))]
```

```{r otm1-bayesian-replication-analysis, cache = TRUE, dependson = "otm1-bayesian-replication-analysis-design-matrix"}
# No effect model
otm1_no_effect <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_null_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , nu = rep(1, otm1_n)
  )
  , rscale = c(fixed = 0.5, random = 1)
  , iterations = otm1_n_mcmc_samples
)

# Fixed effect model
otm1_unconstrained <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_unconstrained_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1, tau = rep(2, 2)
    , beta = 3, upsilon = rep(4, 2)
    , nu = rep(5, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , iterations = otm1_n_mcmc_samples
)
otm1_unconstrained_bf <- exp(otm1_unconstrained$bf - otm1_no_effect$bf)

# otm1_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_unconstrained_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{unconstrained effect}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )

# No lab effects model
otm1_no_lab_effect <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_no_lab_effect_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1
    , beta = 2
    , nu = rep(3, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 3), random = 1)
  , iterations = otm1_n_mcmc_samples
)
otm1_no_lab_effect_bf <- exp(otm1_no_lab_effect$bf - otm1_no_effect$bf)

# otm1_no_lab_effect_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_no_lab_effect_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{no lab effects}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm1-bayesian-replication-analysis-samples, cache = TRUE, dependson = "otm1-bayesian-replication-analysis-unconstrained"}
# Fixed effect model
otm1_unconstrained_samples <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_unconstrained_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1, tau = rep(2, 2)
    , beta = 3, upsilon = rep(4, 2)
    , nu = rep(5, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , posterior = TRUE
  , iterations = otm1_n_mcmc_samples
)
colnames(otm1_unconstrained_samples)[1:ncol(otm1_unconstrained_model_matrix) + 1] <- colnames(otm1_unconstrained_model_matrix)

otm1_unconstrained_samples <- otm1_unconstrained_samples %>%
  as.data.frame %>%
  mutate(
    alpha_cologne = alpha + tau1
    , alpha_ghent =  alpha + tau1 - tau2
    , alpha_harvard = alpha - tau1 - tau2
    , beta_cologne = beta + upsilon1
    , beta_ghent = beta + upsilon1 - upsilon2
    , beta_harvard = beta - upsilon1 - upsilon2
  ) %>%
  as.matrix
```

```{r otm1-bayesian-replication-analysis-same}
# Fixed effect model
otm1_same_direction_boost <- 4 * (
  sum(
    otm1_unconstrained_samples[, "alpha"] > 0 &
    otm1_unconstrained_samples[, "beta"] > 0
  ) / nrow(otm1_unconstrained_samples)
)
otm1_same_direction_bf <- otm1_unconstrained_bf * otm1_same_direction_boost

otm1_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_same_direction_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{no effect}"
  , escape = FALSE
)

## Same direction in all labs
otm1_all_labs_same_direction_boost <- 12 * (
  sum(
    otm1_unconstrained_samples[, "alpha_cologne"] > 0 &
    otm1_unconstrained_samples[, "beta_cologne"] > 0 &
    otm1_unconstrained_samples[, "alpha_ghent"] > 0 &
    otm1_unconstrained_samples[, "beta_ghent"] > 0 &
    otm1_unconstrained_samples[, "alpha_harvard"] > 0 &
    otm1_unconstrained_samples[, "beta_harvard"] > 0
  ) / nrow(otm1_unconstrained_samples)
)
otm1_all_labs_same_direction_bf <- otm1_unconstrained_bf * otm1_all_labs_same_direction_boost

# otm1_all_labs_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_all_labs_same_direction_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm1-bayesian-replication-analysis-opposite}
# Fixed effect model
otm1_opposite_direction_boost <- 4 * (
  sum(
    otm1_unconstrained_samples[, "alpha"] > 0 &
    otm1_unconstrained_samples[, "beta"] < 0
  ) / nrow(otm1_unconstrained_samples)
)
otm1_opposite_direction_bf <- otm1_unconstrained_bf * otm1_opposite_direction_boost

# otm1_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_opposite_direction_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{opposite direction}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
#   , auto_invert = FALSE
# )

## Opposite direction in all locations
# otm1_all_labs_opposite_direction_boost <- 12 * (
#   sum(
#     otm1_unconstrained_samples[, "alpha_cologne"] > 0 &
#     otm1_unconstrained_samples[, "beta_cologne"] < 0 &
#     otm1_unconstrained_samples[, "alpha_ghent"] > 0 &
#     otm1_unconstrained_samples[, "beta_ghent"] < 0 &
#     otm1_unconstrained_samples[, "alpha_harvard"] > 0 &
#     otm1_unconstrained_samples[, "beta_harvard"] < 0
#   ) / nrow(otm1_unconstrained_samples)
# )
# otm1_all_labs_opposite_direction_bf <- otm1_unconstrained_bf * otm1_all_labs_opposite_direction_boost
# 
# otm1_all_labs_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm1_all_opposite_direction_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{opposite direction}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm1-bayesian-replication-analysis-targeted-comparisons}
otm1_same_vs_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_same_direction_bf / otm1_opposite_direction_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{opposite direction}"
  , escape = FALSE
)

otm1_same_direction_vs_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_same_direction_bf / otm1_unconstrained_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{unconstrained effect}"
  , escape = FALSE
)

# In all labs
otm1_all_labs_same_direction_vs_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_all_labs_same_direction_bf / otm1_unconstrained_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{all same direction}/\\mathcal{H}_\\textrm{unconstrained effect}"
  , escape = FALSE
)

otm1_all_labs_same_vs_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_all_labs_same_direction_bf / otm1_same_direction_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{all same direction}/\\mathcal{H}_\\textrm{same effect}"
  , escape = FALSE
)

otm1_no_lab_effect_bf_res <- papaja:::apa_print_bf.numeric(
  otm1_no_lab_effect_bf / otm1_unconstrained_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{no lab effect}/\\mathcal{H}_\\textrm{unconstrained effect}"
  , escape = FALSE
)
```

(ref:bayesian-replication-analysis-plot)
Black-rimmed points represent means of observed attitude differences between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions. Ellipses represent 95% Bayesian credible intervals based on the unconstrained model.

```{r otm1-bayesian-replication-analysis-plot, fig.cap = "(ref:bayesian-replication-analysis-plot)", cache = TRUE}
otm1_unconstrained_pp <- otm1_unconstrained_samples %>%
  as.data.frame %>%
  select(alpha:upsilon2) %>%
  mutate(
    Eval_Cologne =   a[2, 1] * alpha + b[1, 1] * a[2, 1] * tau1 + b[1, 2] * a[2, 1] * tau2 -
                    (a[1, 1] * alpha + b[1, 1] * a[1, 1] * tau1 + b[1, 2] * a[1, 1] * tau2)
    , Eval_Ghent =   a[2, 1] * alpha + b[2, 1] * a[2, 1] * tau1 + b[2, 2] * a[2, 1] * tau2 -
                    (a[1, 1] * alpha + b[2, 1] * a[1, 1] * tau1 + b[2, 2] * a[1, 1] * tau2)
    , Eval_Harvard = a[2, 1] * alpha + b[3, 1] * a[2, 1] * tau1 + b[3, 2] * a[2, 1] * tau2 -
                    (a[1, 1] * alpha + b[3, 1] * a[1, 1] * tau1 + b[3, 2] * a[1, 1] * tau2)

    , IATscore_Cologne =  a[2, 1] * beta  + b[1, 1] * a[2, 1] * upsilon1 + b[1, 2] * a[2, 1] * upsilon2 -
                         (a[1, 1] * beta  + b[1, 1] * a[1, 1] * upsilon1 + b[1, 2] * a[1, 1] * upsilon2)
    , IATscore_Ghent =    a[2, 1] * beta  + b[2, 1] * a[2, 1] * upsilon1 + b[2, 2] * a[2, 1] * upsilon2 -
                         (a[1, 1] * beta  + b[2, 1] * a[1, 1] * upsilon1 + b[2, 2] * a[1, 1] * upsilon2)
    , IATscore_Harvard =  a[2, 1] * beta  + b[3, 1] * a[2, 1] * upsilon1 + b[3, 2] * a[2, 1] * upsilon2 -
                         (a[1, 1] * beta  + b[3, 1] * a[1, 1] * upsilon1 + b[3, 2] * a[1, 1] * upsilon2)

    , Eval_Overall =     a[2, 1] * alpha - (a[1, 1] * alpha)
    , IATscore_Overall = a[2, 1] * beta  - (a[1, 1] * beta)
  ) %>%
  select(-c(alpha:upsilon2)) %>%
  gather(effect, value) %>%
  mutate(iteration = rep(1:nrow(otm1_unconstrained_samples), 8)) %>%
  separate(effect, c("Measure", "Location")) %>%
  spread(Measure, value)

otm1_attitudes_delta <- otm1_attitudes_collapsed %>%
  spread(Block, Attitude) %>%
  mutate(delta = `1` - `2`) %>%
  select(-`1`, -`2`)

otm1_attitudes_delta_summary <- otm1_attitudes_delta %>%
  group_by(Measure) %>%
  summarize(delta = mean(delta)) %>%
  ungroup %>%
  spread(Measure, delta)

otm1_attitudes_delta_summary <- otm1_attitudes_delta %>%
  group_by(Measure, Location) %>%
  summarize(delta = mean(delta)) %>%
  ungroup %>%
  spread(Measure, delta) %>%
  rbind(cbind(Location = "Overall", otm1_attitudes_delta_summary))

otm1_attitudes_delta_summary %>%
  ggplot(aes(x = Eval, y = IATscore, color = Location, fill = Location, shape = Location)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  # stat_density_2d(
  #   data = otm1_unconstrained_effect_fixed_pp
  #   , aes(x = alpha, y = beta, color = Location)
  #   , bins = 5
  #   , inherit.aes = FALSE
  # ) +
  stat_ellipse(
    data = otm1_unconstrained_pp
    , type = "norm"
    , level = 0.95
  ) +
  geom_point(size = 3, color = "black") +
  # geom_point(
  #   data = otm1_unconstrained_effect_fixed_pp %>%
  #     summarize(alpha = median(alpha), beta = median(beta))
  #   , aes(x = alpha, y = beta)
  #   , color = "black"
  #   , inherit.aes = FALSE
  # ) +
  annotate(geom = "text", x = 1.1, y = c(0, -0.275) + 2, label = c("Of~one~mind", "(\U1D4D7[same~direction])"), parse = TRUE, hjust = 0.5) +
  annotate(geom = "text", x = 1.1, y = c(0.28, 0) - 2, label = c("Of~two~minds", "(\U1D4D7[opposite~direction])"), parse = TRUE, hjust = 0.5) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_shape_manual(values = c(21, 23, 24, 22)) +
  labs(
    x = expression(paste("Standardized rating effect [", Delta[Block], "]"))
    , y = expression(paste("Standardized IAT effect [", Delta[Block], "]"))
  ) +
  coord_fixed(xlim = c(-2.15, 2.15), ylim = c(-2.15, 2.15)) +
  theme_apa(box = TRUE) + 
  theme(
    legend.justification = c(0, 1)
    , legend.position = c(0.02, 0.99)
  )
```

The direct comparison of the prior predictive accuracy of the previously reported result patterns indicated that our data were overall most consistent with the results reported by Heycke et al. (2018), `r otm1_same_vs_opposite_direction_bf_res` (the Bayes factor is estimated as infinitely large due to numerical imprecision of the MCMC sampling approach).
Additional comparisons with the control models confirmed that our experimental manipulations were effective (`r otm1_same_direction_bf_res`) and did not produce an unexpected result pattern (`r otm1_same_direction_vs_unconstrained_bf_res`, range $[0, 4]$[^bf_range]).

[^bf_range]:
The comparison of these models is asymmetric.
If, as in this case, the data are perfectly consistent with $\mathcal{M}_\textrm{same direction}$, they are also consistent with $\mathcal{M}_\textrm{unconstrained}$.
The order restriction enforced by $\mathcal{M}_\textrm{same direction}$ limits the prediction of the model to 1/4 of the outcome space predicted by $\mathcal{M}_\textrm{unconstrained}$ (i.e. the upper right quadrant of Figure \ \@ref(fig:otm1-bayesian-replication-analysis-plot)).
This four-fold greater parsimony of $\mathcal{M}_\textrm{same direction}$ constitutes the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{same direction}/\mathcal{M}_\textrm{unconstrained}}$ (assuming all regions of the outcome space are equally likely a priori).
Hence, for this model comparison we could not have obtained stronger evidence (notwithstanding numerical imprecision of the MCMC sampling approach).
Conversely, if the data had fallen outside the predicted outcome space of $\mathcal{M}_\textrm{same direction}$ there is no upper bound to the evidence in favor of $\mathcal{M}_\textrm{unconstrained}$.

To formally assess whether the data from all labs homogeneously exhibited effects in the same direction we added another model that enforced the order constrained of the $\mathcal{M}_\textrm{same direction}$ not only on the average block effects ($\alpha$ and $\beta$) but on each labs block effect ($\alpha + \tau_l$ and $\beta + \upsilon_l$, $\mathcal{H}_\textrm{all same direction}$).
The data provide evidence in favor of homogeneous result patterns in all labs, `r otm1_all_labs_same_vs_same_direction_bf_res` (range $[0, 3]$) and `r otm1_all_labs_same_direction_vs_unconstrained_bf_res` (range $[0, 12]$[^bf_range2]).

[^bf_range2]:
The additional order constraints enforced by $\mathcal{M}_\textrm{all same direction}$ limits the prediction of the model to 1/12 of the outcome space predicted by the unconstrained model.
Hence, for this model comparison the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{all same direction}/\mathcal{M}_\textrm{unconstrained}}$ is 12 (assuming all regions of the outcome space are equally likely a priori).
Baring the transitivity of Bayes factors in mind this implies that the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{all same direction}/\mathcal{M}_\textrm{same direction}}$ is 3.
Hence, in both model comparisons we could not have obtained much stronger evidence in favor of $\mathcal{M}_\textrm{all same direction}$.

<!-- - Does the size of the effects differ between labs? -->

<!-- `r otm1_no_lab_effect_bf_res` -->

<!-- Do we need to try different priors for $\alpha$ and $\beta$, or $\tau$ and $\upsilon$? -->

### Recognition task

We tested participants recognition memory for the primes presented during the learning procedure using a one-tailed Bayesian $t$ test with default Cauchy prior ($r = \sqrt2/2$).

```{r otm1-bayesian-recognition, warning = FALSE, message = FALSE}
otm1_mem_accuracy_res <- ttestBF(otm1_mem$Accuracy - 0.5, mu = 0, nullInterval = c(0, Inf))[1] %>%
  apa_print %$%
  full_result

otm1_mem_accuracy_lab_res <- otm1_mem %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  droplevels %>%
  anovaBF(
    Accuracy ~ Location
    , data = .
  ) %>%
  apa_print %$%
  statistic
```

The data strongly support the conclusion that participants' recognition accuracy was better than chance, `r otm1_mem_accuracy_res`.
We performed a Bayesian ANOVA to test whether prime recognition accuracy differed between labs but the result was inconclusive, `r otm1_mem_accuracy_lab_res`.

## Prime recogniton and implicit attitudes

In contrast to the original results reported by Rydell et al. (2006), prime recognition accuracy in this study was above chance.
Memory for primes may, thus, have interfered with the associative learning process and hence may have obscured the reversal of the implicit attitudes.
We therefore performed an exploratory regression analysis of prime recognition and the IAT score difference between blocks used in the Bayesian analysis above where positive values represent a more favorable attitude after the block in which Bob was presented with positive explicit descriptions. 
A negative value of the IAT score difference between blocks would therefore indicate that the IAT effects were in line with the prime valence.
If prime recognition indeed obstructed the formation of associations, we would expect to observe a positive relationship between prime recognition accuracy and IAT score differences between blocks:
When prime recognition is high we would expect IAT differences in line with the valence of the explicit descriptions of Bob but not with the prime valence; we would expect to observe smaller and eventually negative IAT differences as prime recognition memory declines and associative learning takes over.

(ref:prime-recognition-iat-difference)
Scatterplot of prime recognition accuracy and attitude differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.

```{r prime-recognition-iat-difference, fig.cap = "(ref:prime-recognition-iat-difference)", message = FALSE}
otm1_iat_delta <- full_join(otm1_attitudes_delta, select(otm1_mem, ParticipantNumber, Accuracy)) %>% 
  filter(Measure == "IATscore")

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  labs(
    x = "Prime recognition accuracy"
    , y = expression(paste("Standardized IAT effect [", Delta[Block], "]"))
  ) +
  theme_apa()

```

(ref:prime-recognition-iat-difference-regression)
Results of linear regression predicting attitude differences in IAT scores between blocks with prime recognition accuracy.

```{r prime-recognition-iat-difference-regression, results = "asis"}
otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  as.data.frame %>%
  lmBF(delta ~ Accuracy, data = .) %>%
  apa_print

otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  lm(delta ~ Accuracy, data = .) %>% 
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:prime-recognition-iat-difference-regression)"
    , escape = FALSE
  )
```

We were unable to detect a relationship between prime recognition and IAT score differences between blocks and even found some evidence against such a relationship, `r otm1_recognition_iat_lm_bf$statistic`.
Moreover, we centered prime recognition at 0.5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance prime recognition.
Hence, even for participants who exhibited no memory for prime attitudes assessed with the IAT were in line with the explicit descriptions of Bob.
These results provide no indication that the deviation of our findings from those reported by Rydell et al. (2006) are attributable to the above-chance prime recognition accuracy in this study.

## Exploratory Analysis: Prime valence memory

```{r listPrimes, echo = FALSE, eval=FALSE}

# correct names of primes
eng_pos <- c("Flower",
            "Friend",
            "Gift",
            "Happy",
            "Puppy",
            "Pretty",
            "Party",
            "Kiss",
            "Kitten",
            "Smile")

eng_neg <- c("Corpse",
            "Death",
            "Hell",
            "Pain",
            "War",
            "Hurt",
            "Spider",
            "Stink",
            "Trash",
            "Ugly")

nl_pos <- c("Bloem",
            "Vriend",
            "Geschenk",
            "Blij",
            "Puppy",
            "Mooi",
            "Feest",
            "Kus",
            "Katje",
            "Glimlach")

nl_neg <- c("Lijk",
            "Dood",
            "Hel",
            "Pijn",
            "Oorlog",
            "Letsel",
            "Spin",
            "Stank",
            "Afval",
            "Lelijk")

ger_pos <- c("Blume",
            "Freund",
            "Geschenk",
            "Glücklich",
            "Welpe",
            "Hübsch",
            "Party",
            "Kuss",
            "Kätzchen",
            "Lächeln")

ger_neg <- c("Leiche",
            "Tod",
            "Hölle",
            "Schmerz",
            "Krieg",
            "Verletzung",
            "Spinne",
            "Gestank",
            "Abfall",
            "Hässlich")

# prep data frame to correspond with correct names

otm1_mem$chosenItems <- gsub("\\r", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("u'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("\\", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("ï»¿", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("[", "", otm1_mem$chosenItems, fixed = TRUE) 
otm1_mem$chosenItems <- gsub("]", "", otm1_mem$chosenItems, fixed = TRUE)

otm1_mem$chosenItems <- gsub("xfc", "ü", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xe4", "ä", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xf6", "ö", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xdf", "ß", otm1_mem$chosenItems)

otm1_mem <- separate(otm1_mem, 
                     col = "chosenItems", 
                     into = paste0("chosen", 1:20), 
                     sep = ", ")

pos <- c(eng_pos, nl_pos, ger_pos)
neg <- c(eng_neg, nl_neg, ger_neg)
otm1_mem$poscor <- 0
otm1_mem$negcor <- 0

for(i in 1:20){
  otm1_mem$poscor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% pos, otm1_mem$poscor + 1, otm1_mem$poscor + 0)
  otm1_mem$negcor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% neg, otm1_mem$negcor + 1, otm1_mem$negcor + 0)
}

aggregate(negcor ~ Location, data = otm1_mem, FUN = mean)
aggregate(poscor ~ Location, data = otm1_mem, FUN = mean)

t.test(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)

t.test(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)

t.test(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)

```

### 2019-10-31 otm2pilot/results/analysis2pilot.Rmd
add all materials

---
title             : "Analysis of OTM 2 pilot"
author            : "Frederik Aust & Tobias Heycke"
date              : "`r format(Sys.time(), '%d %B, %Y')`"

output:
  bookdown::html_document2:
    theme         : "spacelab"
    df_print      : "kable"
    code_folding  : "hide"
    toc           : true
    toc_float     : true
---

```{r init, include = FALSE}
library("magrittr")
library("tidyr")
library("dplyr")
library("assertthat")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("afex")
library("emmeans")
library("BayesFactor")

source("https://gist.githubusercontent.com/crsh/bd4d1f62d300462ea0c0f44b9ad38616/raw/edd9c74e24b68f42433c2526cafc888509b1b8bc/batch_download_github.R")
source("https://gist.githubusercontent.com/crsh/357458c41fd3d554fb24/raw/f7725d5c4894a055a1b2e461dc5c39f3db23b2b8/batch_read.R")

source("../../analysis_and_paper/modal_frame_rate.R")

# Set seed for random number generator
set.seed(315054738)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Use multivariate models for emmeans contrasts and post-hoc tests
afex_options(emmeans_model = "multivariate")

# Configure df approximation for mixed model contrasts and post-hoc tests
emm_options(
  lmer.df = "satterthwaite"
  , lmerTest.limit = 22384
)

#t test print function
printBFt <- function(BF, HStyle = 0, index = 1, OutputSize = 99999.99 , postit = 1000000, N = FALSE){
  if(as.vector(BF[index]) < 1 & HStyle == 0){
    b <- 1/as.vector(BF[index])
    num <- "01"
  }else{
    b <- as.vector(BF[index])
    num <- "10"
  }
  s <- " "
  if(N == TRUE) s <- paste0('(', nrow(BF@data), ') ') 
  if(as.character(class(BF@numerator[[names(BF@numerator)[index]]])) == "BFoneSample"){
    rBF <- BayesFactor::ttestBF(BF@data[,1], mu = BF@numerator[[names(BF@numerator)[index]]]@prior$mu, rscale = BF@numerator[[names(BF@numerator)[index]]]@prior$rscale)
  }
  if(as.character(class(BF@numerator[[names(BF@numerator)[1]]])) == "BFindepSample"){
      rBF <- BayesFactor::ttestBF(subset(BF@data, BF@data[,2] == "x")[,1] , subset(BF@data, BF@data[,2] == "y")[,1], rscale = BF@numerator[[names(BF@numerator)[index]]]@prior$rscale, paired = FALSE)
    }
  post <- BayesFactor::posterior(rBF, index = index, iterations = postit)
  d <- median(post[, "delta"])
  HDI <- coda::HPDinterval(post[, "delta"])
  ifelse(b > OutputSize, paste0('$\\mathit{BF}_{', num, '}', s, '= ', as.scientific(b), '$', ', ', '$d = ', printnum(d), '$', ', ', '95% HDI [', printnum(HDI[1]), ', ', printnum(HDI[2]), ']'), paste0('$\\mathit{BF}_{', num, '}', s, '= ', printnum(b), '$', ', ', '$d = ', printnum(d), '$', ', ', '95% HDI [', printnum(HDI[1]), ', ', printnum(HDI[2]), ']'))
}
```

```{r otm2pilot-analysis-preferences, cache = TRUE}
# Data wrangling
process_rawdata <- TRUE

# Data location
raw_data_path <- "data_raw/p1ghent/"
processed_data_path <- "data_processed/p1ghent/"

# Default ggplot theme
theme_set(theme_apa())

## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
assignInNamespace("theme_nothing", function() {
    theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
}, "cowplot")

# Number of MCMC samples for Bayesian analysis
otm2_n_mcmc_samples <- 1e6
```

# Introduction

As prime recognition was above chance in study 1, we planned to run a pilot study with a reduced presentation time.
As previous studies using this paradigm had used a presentation time of 17 ms and found no above-chance memory, we intended to run a pilot with a presentation time of 17 ms (1 frame at 60 Hz).
Due to a mistake with the monitor settings, we accidentally ran a first pilot study with prime presentation at 13 ms (75 Hz) and then collected data with the monitors set to 60 Hz (i.e., 17 ms prime presentation).
Screen refresh rates were saved by the experimental scripts confirming these settings.

# Method

The aim of the pilot was to keep the learning phase as similar to the actual experiment as possible, while keeping the pilot as short as possible.
We collected the data in Ghent, using the previously used Dutch version of the experiment.
We therefore had participants either complete 100 trials with positive primes (10 primes presented 10 times each) or 100 trials with negative primes.
After the learning phase an evaluation of Bob - as collected in study 1 - was administered, to erase any prime knowledge from working memory.
Afterwards the ten positive (or negative) primes and ten positive (or negative) new words were presented on the screen.
If participants had no prime memory, we would therefore expect five correct identifications by chance.
Participants were instructed to select ten words, that might have appeared during the learning phase. 
All instructions were as in the original study, the only difference was that participants were instructed to select 10 instead of 20 words and the IAT was not administered.

# 75 Hz Condition

```{r otm2pilot-load-data, cache = TRUE, dependson = "otm2pilot-analysis-preferences", warning = FALSE}
# Process raw data
if(process_rawdata) {

  # Merge raw data
  otm2p_eval <- batch_read(
    raw_data_path
    , pattern = "Eval"
    , recursive = TRUE
    , read_fun = read.delim
  )

  # change second entry of pp108  to participant number = 208
  otm2p_eval <- subset(otm2p_eval, ParticipantNumber != "ParticipantNumber")
  otm2p_eval[otm2p_eval$timeStamp == "2018-10-16_16.05.10.218000", 1] <- 208

  otm2p_mem <- batch_read(
    raw_data_path
    , pattern = "MemTest"
    , recursive = TRUE
    , read_fun = read.delim
  )

  # change second entry of pp108  to participant number = 208
  otm2p_mem <- subset(otm2p_mem, ParticipantNumber != "ParticipantNumber")
  otm2p_mem[otm2p_mem$timeStamp == "2018-10-16_16.05.10.218000", 1] <- 208

  otm2p_log <- batch_read(
    raw_data_path
    , pattern = "ScreenLog"
    , recursive = TRUE
    , read_fun = read.csv
    , header = FALSE
  )

  #pp108 is causing problems reading in the data as 2 participants were collected 
  #with this number (and an enter is missing after the entry of the first participant)

  p108 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_108.dat"))
  p108[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p108[2])
  p108[3] <- gsub("108", "208", p108[3]) # rename the second participants with 108 to 208

  #read all other files and remove participant 108
  f <- list.files(raw_data_path, pattern = "Demographics", recursive = TRUE)[-8]

  #add data to a data frame
  otm2p_demo <- lapply(paste0(raw_data_path, f), read.delim)
  otm2p_demo <- do.call("rbind", otm2p_demo)

  #add data of participants with number 108 to data file
  otm2p_demo <- rbind(otm2p_demo, read.delim(textConnection(paste(p108, collapse = "\n"))))

    # Recode, calculate indices, and filter data 
    # Needs to be changed as is currently not adapted to this data set
  # otm2p_eval <- otm2p_eval %>%
  #   mutate_at(vars(starts_with("Eval")), scale) %>%
  #   select(starts_with("Eval")) %>%
  #   rowwise %>%
  #   do(data.frame(Eval = sum(unlist(.)))) %>% 
  #   bind_cols(otm1_eval, .) %>%
  #   mutate(
  #     ParticipantNumber = factor(ParticipantNumber)
  #     , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
  #     , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
  #     , Block = factor(Block)
  #   )
  #

  otm2p_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")

  #otm2p_demo$frameRate <- modal_frame_rate(otm2p_log) #Todo FA

  otm2p_mem$ParticipantNumber <- as.integer(otm2p_mem$ParticipantNumber)
  otm2p_mem <- left_join(otm2p_mem, otm2p_demo, by = "ParticipantNumber")

  otm2p_mem <- otm2p_mem %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime", "posPrime") %>% factor
      , Block = factor(Block)
      , Accuracy = as.integer(NumbercorrectIdent) / 10
    )

  rm("otm2p_demo", "p108", "f")

  # Save processed data
  saveRDS(otm2p_eval, paste0(processed_data_path, "otm2p_eval.rds"))
  saveRDS(otm2p_mem, paste0(processed_data_path, "otm2p_memory.rds"))
} else {
  otm2p_eval <- readRDS(paste0(processed_data_path, "otm2p_eval.rds"))
  otm2p_mem <- readRDS(paste0(processed_data_path, "otm2p_memory.rds"))
}
```

## General information

The monitors were accidentally set to 75 Hz and the primes where therefore presented for about 13 ms (instead of the planned 17 ms).

```{r otm2p-recognition, results = "asis"}
otm2p_mem_ttest <- t.test(otm2p_mem$Accuracy, mu = 0.5
                          , alternative = "greater") %>%
  apa_print %$%
  full_result

otm2p_mem_ttestBF <- ttestBF(otm2p_mem$Accuracy - 0.5
                             , mu = 0, rscale = "medium"
                             , nullInterval = c(0, Inf))[1] %>%
  printBFt

```

## Memory in recognition task

The frequentist analysis (one sided *t* test) suggests, that prime recognition was above chance `r otm2p_mem_ttest`. 
The Bayesian analysis (also one sided *t* test) is not completely compelling but is also indicating that prime memory was above chance `r otm2p_mem_ttestBF`.

### positive vs. negative primes

```{r pos-neg-otm2p}
otm2p_pos_neg <- t.test(otm2p_mem$Accuracy ~ otm2p_mem$ValenceBlock) %>%
  apa_print %$%
  full_result

otm2p_pos_negBF <- ttestBF(subset(otm2p_mem, ValenceBlock == "negPrime")$Accuracy
                          ,subset(otm2p_mem, ValenceBlock == "posPrime")$Accuracy
                          ,rscale = "medium") %>%
  printBFt

```

Descriptively there appeared to be a decently sized difference between positive and negative words, which was supported by the frequentist analysis `r otm2p_pos_neg`, but not by a Bayesian test `r otm2p_pos_negBF`. 
It is important to mention, that we had only about 10 participants per group and we do not know whether the positive words are easier to see, remembered better, or whether participants merely selected more positive words in the memory task.

```{r visualize-pos-neg-otm2p}
apa_beeplot(otm2p_mem
            , id = "ParticipantNumber"
            , factors = "ValenceBlock"
            , dv = "Accuracy"
            , args_points = list(bg = "lightblue", col = "#045a8d", cex = 1.5)
            , args_swarm = list(cex = 1.4)
            , ylim = c(0, 1)
  )
abline(h = 0.5, col = "darkblue", lty = 5)
```

<!--
## Response in demographics on goal of study

```{r goalResponse, results = "asis"}
apa_table(otm2p_mem[, c("ParticipantNumber", "Goal")]
          , caption = "Reponse of all participants on the question what they think the experiment was about")
```

Based on their response, the following participants were maybe aware of the primes during the learning phase: 103, 108, 116, 119, 120, 208.
Interestingly, looking at their scores on the visibility test, three out of six participants had an accuracy on chance level. 
Of course these small numbers should not be over interpreted, but these numbers could indicate that the memory test is not suited to measure visibility and we might largely underestimate actual visibility. Participants might be aware of the primes and remember that they were generally positive/negative but might not remember the actual words.

```{r visScoresomt2p, results = "asis"}
otm2p_adler <- c(103, 108, 116, 119, 120, 208)

apa_table(otm2p_mem[otm2p_mem$ParticipantNumber %in% otm2p_adler
         , c("ParticipantNumber", "Accuracy")]
         , caption = "Accuracy scores of participants who might have known the goal of the study (chance = 0.5)")

```
-->

# 60 Hz Condition

We ran the exact same study with the monitors set to 60 Hz before the data of the first pilot were analyzed.

```{r initp2, cache = TRUE}
raw_data_path <- "data_raw/p2ghent/"
processed_data_path <- "data_processed/p2ghent/"

```

```{r otm2pilot2-load-data, cache = TRUE, dependson = "initp2", warning = FALSE}
# Process raw data
if(process_rawdata) {

  # Merge raw data
  otm2p2_eval <- batch_read(
    raw_data_path
    , pattern = "Eval"
    , recursive = TRUE
    , read_fun = read.delim
  )

   # change second entry of pp 4 to participant number = 104
   otm2p2_eval <- subset(otm2p2_eval, ParticipantNumber != "ParticipantNumber")
   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-26_13.28.11.484000", 1] <- 104

   # change secodn entry pf participant 6 to 106 and third entry to 206
   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-30_17.51.56.687000", 1] <- 106
   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-30_18.41.18.078000", 1] <- 206

  otm2p2_mem <- batch_read(
    raw_data_path
    , pattern = "MemTest"
    , recursive = TRUE
    , read_fun = read.delim
  )

   # change participant numbers (see above)
   otm2p2_mem <- subset(otm2p2_mem, ParticipantNumber != "ParticipantNumber")
   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-26_13.28.11.484000", 1] <- 104
   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-30_17.51.56.687000", 1] <- 106
   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-30_18.41.18.078000", 1] <- 206

  otm2p2_log <- batch_read(
    raw_data_path
    , pattern = "ScreenLog"
    , recursive = TRUE
    , read_fun = read.csv
    , header = FALSE
  )

  # pp 4 and 6 are causing problems as multiple participants were collected 
  # with this number
  p4 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_4.dat"))
  p4[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p4[2])
  p4[3] <- gsub("!9", "19", p4[3]) # I am making the assumption that the participant intended to enter 19 not !9
  p4[3] <- gsub("4", "104", p4[3])

  # repeat as above with participant number 6
  p6 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_6.dat"))
  p6[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p6[2])
  p6[3] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p6[3])
  p6[3] <- gsub("6", "106", p6[3])
  p6[4] <- gsub("6", "206", p6[4])

  #read all other files and remove participant 4, 5(no data collected), 6
  f2 <- list.files(raw_data_path, pattern = "Demographics", recursive = TRUE)[-c(15, 16, 17)]

  #add data to a data frame
  otm2p2_demo <- lapply(paste0(raw_data_path, f2), read.delim)
  otm2p2_demo <- do.call("rbind", otm2p2_demo)

  #add data of participants with number 4, 104, 6, 106, and 206 to data file
  otm2p2_demo <- rbind(otm2p2_demo, read.delim(textConnection(paste(p4, collapse = "\n"))))
  otm2p2_demo <- rbind(otm2p2_demo, read.delim(textConnection(paste(p6, collapse = "\n"))))

    # Recode, calculate indices, and filter data
    # Needs to be changed as is currently not adapted to this data set
  # otm2p_eval <- otm2p_eval %>%
  #   mutate_at(vars(starts_with("Eval")), scale) %>%
  #   select(starts_with("Eval")) %>%
  #   rowwise %>%
  #   do(data.frame(Eval = sum(unlist(.)))) %>%
  #   bind_cols(otm1_eval, .) %>%
  #   mutate(
  #     ParticipantNumber = factor(ParticipantNumber)
  #     , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
  #     , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
  #     , Block = factor(Block)
  #   )
  #

  otm2p_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")

  #otm2p_demo$frameRate <- modal_frame_rate(otm2p_log) #Todo FA

  otm2p2_mem$ParticipantNumber <- as.integer(otm2p2_mem$ParticipantNumber)
  otm2p2_mem <- left_join(otm2p2_mem, otm2p2_demo, by = "ParticipantNumber")

  otm2p2_mem <- otm2p2_mem %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime", "posPrime") %>% factor
      , Block = factor(Block)
      , Accuracy = as.integer(NumbercorrectIdent) / 10
    )

  rm("otm2p2_demo", "p4", "p6", "f2")

  # Save processed data
  saveRDS(otm2p2_eval, paste0(processed_data_path, "otm2p2_eval.rds"))
  saveRDS(otm2p2_mem, paste0(processed_data_path, "otm2p2_memory.rds"))
} else {
  otm2p2_eval <- readRDS(paste0(processed_data_path, "otm2p2_eval.rds"))
  otm2p2_mem <- readRDS(paste0(processed_data_path, "otm2p2_memory.rds"))
}
```

```{r otm2p2-recognition, results = "asis"}
otm2p2_mem_ttest <- t.test(otm2p2_mem$Accuracy, mu = 0.5
                          , alternative = "greater") %>%
  apa_print %$%
  full_result

otm2p2_mem_ttestBF <- ttestBF(otm2p2_mem$Accuracy - 0.5
                             , mu = 0, rscale = "medium"
                             , nullInterval = c(0, Inf))[1] %>%
  printBFt

```

## Memory in recognition task (60 Hz)

Interestingly, the frequentist analysis (one sided *t* test) suggested, that prime recognition was not above chance `r otm2p2_mem_ttest`. 
In this study, the Bayesian analysis (also one sided *t* test) was in line with the frequentist analysis `r otm2p2_mem_ttestBF`.

### positive vs. negative primes (60 Hz)

```{r pos-neg-otm2p2}
otm2p2_pos_neg <- t.test(otm2p2_mem$Accuracy ~ otm2p2_mem$ValenceBlock) %>%
  apa_print %$%
  full_result

otm2p2_pos_negBF <- ttestBF(subset(otm2p2_mem, ValenceBlock == "negPrime")$Accuracy
                          ,subset(otm2p2_mem, ValenceBlock == "posPrime")$Accuracy
                          ,rscale = "medium") %>%
  printBFt

```

We again looked at the difference between positive and negative prime identification. 
As in the 75 Hz condition, there appeared to be a decently sized difference between positive and negative words, which in this case is supported by both the frequentist analysis `r otm2p2_pos_neg`, and by the Bayesian *t* test `r otm2p2_pos_negBF`.

```{r visualize-pos-neg-otm2p2}
apa_beeplot(otm2p2_mem
            , id = "ParticipantNumber"
            , factors = "ValenceBlock"
            , dv = "Accuracy"
            , args_points = list(bg = "lightblue", col = "#045a8d", cex = 1.5)
            , args_swarm = list(cex = 1.4)
            , ylim = c(0, 1)
  )
abline(h = 0.5, col = "darkblue", lty = 5)
```

<!--
## Response in demographics on goal of study (60 Hz)

```{r goalResponse2, results = "asis"}
apa_table(otm2p2_mem[, c("ParticipantNumber", "Goal")]
          , caption = "Reponse of all participants on the question what they think the experiment was about")
```
-->

# Comparing 60 and 75 Hz

```{r otm2p-compare-60-75}
otm2p_6075 <- t.test(x = otm2p_mem$Accuracy, y = otm2p2_mem$Accuracy) %>%
  apa_print %$%
  full_result

otm2p_6075BF <- ttestBF(otm2p_mem$Accuracy
                          ,otm2p2_mem$Accuracy
                          ,rscale = "medium") %>%
  printBFt

```

The overall difference in accuracy (chance = 0.5) between the 75 Hz condition (*M* = `r round(mean(otm2p_mem$Accuracy), 2)`) and the 60 Hz condition (*M* = `r round(mean(otm2p2_mem$Accuracy), 2)`), was statistically significant, `r otm2p_6075`, but the Bayesfactor was not convincing `r otm2p_6075BF` (two sided *t* tests).

# Discussion

It seems odd, that recognition was above chance in the 75 Hz condition but at chance in the 60 Hz condition.
This could of course be a coincidence or a mistake was made somewhere.
However, the results might be plausible for the following reason:
Viewing stimuli on a 60 Hz CRT monitor is very uncomfortable as the screen is flickering, which is not the case when the screen running with 75 Hz. 
This could decrease actual visibility in the 60 Hz condition, compared to the 75 Hz condition.
It is, of course, possible that participants merely do not look at the screen closely as it is uncomfortable in the 60 Hz condition, which artificially reduces visibility of the primes.

Additionally, there appeared to be a robust difference between positive and negative prime word recognition (i.e., more correct identifications of positive than negative primes). 
Looking at the results of the memory test from Study 1, there appeared to be a difference in prime recognition of positive/negative words only in the data collected in Ghent and not in the data collected in Harvard or Cologne.
Therefore, this issue might not be as important for the studies collecting data with an English version of the experiment.

### 2019-10-31 otm2pilot2/results/analysis2pilot2_florida.Rmd
add all materials

--- 2019-10-31 otm2pilot/results/analysis2pilot.Rmd
@@
 ---
-title             : "Analysis of OTM 2 pilot"
+title             : "Analysis of OTM 2 pilot 2: Florida"
 author            : "Frederik Aust & Tobias Heycke"
@@
 
-```{r otm2pilot-analysis-preferences, cache = TRUE}
+```{r otm2pilot2f-analysis-preferences, cache = TRUE}
 # Data wrangling
@@
 # Data location
-raw_data_path <- "data_raw/p1ghent/"
-processed_data_path <- "data_processed/p1ghent/"
+raw_data_path <- "data_raw_florida/"
+processed_data_path <- "data_processed_florida/"
 
@@
 
-# Introduction
-
-As prime recognition was above chance in study 1, we planned to run a pilot study with a reduced presentation time.
-As previous studies using this paradigm had used a presentation time of 17 ms and found no above-chance memory, we intended to run a pilot with a presentation time of 17 ms (1 frame at 60 Hz).
-Due to a mistake with the monitor settings, we accidentally ran a first pilot study with prime presentation at 13 ms (75 Hz) and then collected data with the monitors set to 60 Hz (i.e., 17 ms prime presentation).
-Screen refresh rates were saved by the experimental scripts confirming these settings.
-
-# Method
-
-The aim of the pilot was to keep the learning phase as similar to the actual experiment as possible, while keeping the pilot as short as possible.
-We collected the data in Ghent, using the previously used Dutch version of the experiment.
-We therefore had participants either complete 100 trials with positive primes (10 primes presented 10 times each) or 100 trials with negative primes.
-After the learning phase an evaluation of Bob - as collected in study 1 - was administered, to erase any prime knowledge from working memory.
-Afterwards the ten positive (or negative) primes and ten positive (or negative) new words were presented on the screen.
-If participants had no prime memory, we would therefore expect five correct identifications by chance.
-Participants were instructed to select ten words, that might have appeared during the learning phase. 
-All instructions were as in the original study, the only difference was that participants were instructed to select 10 instead of 20 words and the IAT was not administered.
-
-# 75 Hz Condition
-
-```{r otm2pilot-load-data, cache = TRUE, dependson = "otm2pilot-analysis-preferences", warning = FALSE}
+```{r otm2pilot2f-load-data, cache = TRUE, dependson = "otm2pilot2f-analysis-preferences", warning = FALSE}
 # Process raw data
@@
   # Merge raw data
-  otm2p_eval <- batch_read(
+  otm2p2f_eval <- batch_read(
     raw_data_path
@@
 
-  # change second entry of pp108  to participant number = 208
-  otm2p_eval <- subset(otm2p_eval, ParticipantNumber != "ParticipantNumber")
-  otm2p_eval[otm2p_eval$timeStamp == "2018-10-16_16.05.10.218000", 1] <- 208
-
-  otm2p_mem <- batch_read(
+  otm2p2f_mem <- batch_read(
     raw_data_path
@@
 
-  # change second entry of pp108  to participant number = 208
-  otm2p_mem <- subset(otm2p_mem, ParticipantNumber != "ParticipantNumber")
-  otm2p_mem[otm2p_mem$timeStamp == "2018-10-16_16.05.10.218000", 1] <- 208
-
-  otm2p_log <- batch_read(
+  otm2p2f_log <- batch_read(
     raw_data_path
@@
 
-  #pp108 is causing problems reading in the data as 2 participants were collected 
-  #with this number (and an enter is missing after the entry of the first participant)
+  otm2p2f_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")
 
-  p108 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_108.dat"))
-  p108[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p108[2])
-  p108[3] <- gsub("108", "208", p108[3]) # rename the second participants with 108 to 208
+  otm2p2f_mem$ParticipantNumber <- as.integer(otm2p2f_mem$ParticipantNumber)
+  #otm2p2_mem <- left_join(otm2p2_mem, otm2p2_demo, by = "ParticipantNumber")
 
-  #read all other files and remove participant 108
-  f <- list.files(raw_data_path, pattern = "Demographics", recursive = TRUE)[-8]
-
-  #add data to a data frame
-  otm2p_demo <- lapply(paste0(raw_data_path, f), read.delim)
-  otm2p_demo <- do.call("rbind", otm2p_demo)
-
-  #add data of participants with number 108 to data file
-  otm2p_demo <- rbind(otm2p_demo, read.delim(textConnection(paste(p108, collapse = "\n"))))
-
-    # Recode, calculate indices, and filter data 
-    # Needs to be changed as is currently not adapted to this data set
-  # otm2p_eval <- otm2p_eval %>%
-  #   mutate_at(vars(starts_with("Eval")), scale) %>%
-  #   select(starts_with("Eval")) %>%
-  #   rowwise %>%
-  #   do(data.frame(Eval = sum(unlist(.)))) %>% 
-  #   bind_cols(otm1_eval, .) %>%
-  #   mutate(
-  #     ParticipantNumber = factor(ParticipantNumber)
-  #     , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
-  #     , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
-  #     , Block = factor(Block)
-  #   )
-  #
-
-  otm2p_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")
-
-  #otm2p_demo$frameRate <- modal_frame_rate(otm2p_log) #Todo FA
-
-  otm2p_mem$ParticipantNumber <- as.integer(otm2p_mem$ParticipantNumber)
-  otm2p_mem <- left_join(otm2p_mem, otm2p_demo, by = "ParticipantNumber")
-
-  otm2p_mem <- otm2p_mem %>%
+  otm2p2f_mem <- otm2p2f_mem %>%
     mutate(
       ParticipantNumber = factor(ParticipantNumber)
-      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime", "posPrime") %>% factor
+      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime - posPrime", "posPrime - negPrime") %>% factor
       , Block = factor(Block)
-      , Accuracy = as.integer(NumbercorrectIdent) / 10
+      , Accuracy = as.integer(NumbercorrectIdent) / 20
     )
 
-  rm("otm2p_demo", "p108", "f")
-
     # Save processed data
-  saveRDS(otm2p_eval, paste0(processed_data_path, "otm2p_eval.rds"))
-  saveRDS(otm2p_mem, paste0(processed_data_path, "otm2p_memory.rds"))
+  saveRDS(otm2p2f_eval, paste0(processed_data_path, "otm2p2f_eval.rds"))
+  saveRDS(otm2p2f_mem, paste0(processed_data_path, "otm2p2f_memory.rds"))
 } else {
-  otm2p_eval <- readRDS(paste0(processed_data_path, "otm2p_eval.rds"))
-  otm2p_mem <- readRDS(paste0(processed_data_path, "otm2p_memory.rds"))
+  otm2p2f_eval <- readRDS(paste0(processed_data_path, "otm2p2f_eval.rds"))
+  otm2p2f_mem <- readRDS(paste0(processed_data_path, "otm2p2f_memory.rds"))
 }
@@
 
-## General information
-
-The monitors were accidentally set to 75 Hz and the primes where therefore presented for about 13 ms (instead of the planned 17 ms).
-
-```{r otm2p-recognition, results = "asis"}
-otm2p_mem_ttest <- t.test(otm2p_mem$Accuracy, mu = 0.5
+```{r otm2p2f-recognition, results = "asis"}
+otm2p2f_mem_ttest <- t.test(otm2p2f_mem$Accuracy, mu = 0.5
                           , alternative = "greater") %>%
@@
 
-otm2p_mem_ttestBF <- ttestBF(otm2p_mem$Accuracy - 0.5
+otm2p2f_mem_ttestBF <- ttestBF(otm2p2f_mem$Accuracy - 0.5
                              , mu = 0, rscale = "medium"
@@
 
-## Memory in recognition task
+# Results
 
-The frequentist analysis (one sided *t* test) suggests, that prime recognition was above chance `r otm2p_mem_ttest`. 
-The Bayesian analysis (also one sided *t* test) is not completely compelling but is also indicating that prime memory was above chance `r otm2p_mem_ttestBF`.
+The identification performance was not significantly better than chance, `r otm2p2f_mem_ttest`, however the Bayes Factor was inconclusive `r otm2p2f_mem_ttestBF`.
 
-### positive vs. negative primes
-
-```{r pos-neg-otm2p}
-otm2p_pos_neg <- t.test(otm2p_mem$Accuracy ~ otm2p_mem$ValenceBlock) %>%
-  apa_print %$%
-  full_result
-
-otm2p_pos_negBF <- ttestBF(subset(otm2p_mem, ValenceBlock == "negPrime")$Accuracy
-                          ,subset(otm2p_mem, ValenceBlock == "posPrime")$Accuracy
-                          ,rscale = "medium") %>%
-  printBFt
-
+```{r otm2p2f-recognition-viz, fig.width = 3, fig.height = 4, fig.align = "center"}
+ggplot(otm2p2f_mem, aes(x = 1, y = Accuracy)) +
+  geom_violin() +
+  geom_hline(yintercept = 0.5, color = grey(0.7), linetype = "22") +
+  geom_sina() +
+  stat_summary(fun.data = mean_cl_boot) +
+  theme(
+    axis.text.x = element_blank()
+    , axis.title.x = element_blank()
+    , axis.ticks.x = element_blank()
+  )
 ```
-
-Descriptively there appeared to be a decently sized difference between positive and negative words, which was supported by the frequentist analysis `r otm2p_pos_neg`, but not by a Bayesian test `r otm2p_pos_negBF`.
-It is important to mention, that we had only about 10 participants per group and we do not know whether the positive words are easier to see, remembered better, or whether participants merely selected more positive words in the memory task.
-
-```{r visualize-pos-neg-otm2p}
-apa_beeplot(otm2p_mem
-            , id = "ParticipantNumber"
-            , factors = "ValenceBlock"
-            , dv = "Accuracy"
-            , args_points = list(bg = "lightblue", col = "#045a8d", cex = 1.5)
-            , args_swarm = list(cex = 1.4)
-            , ylim = c(0, 1)
-  )
-abline(h = 0.5, col = "darkblue", lty = 5)
-```
-
-<!--
-## Response in demographics on goal of study
-
-```{r goalResponse, results = "asis"}
-apa_table(otm2p_mem[, c("ParticipantNumber", "Goal")]
-          , caption = "Reponse of all participants on the question what they think the experiment was about")
-```
-
-Based on their response, the following participants were maybe aware of the primes during the learning phase: 103, 108, 116, 119, 120, 208.
-Interestingly, looking at their scores on the visibility test, three out of six participants had an accuracy on chance level. 
-Of course these small numbers should not be over interpreted, but these numbers could indicate that the memory test is not suited to measure visibility and we might largely underestimate actual visibility.
-Participants might be aware of the primes and remember that they were generally positive/negative but might not remember the actual words.
-
-```{r visScoresomt2p, results = "asis"}
-otm2p_adler <- c(103, 108, 116, 119, 120, 208)
-
-apa_table(otm2p_mem[otm2p_mem$ParticipantNumber %in% otm2p_adler
-         , c("ParticipantNumber", "Accuracy")]
-         , caption = "Accuracy scores of participants who might have known the goal of the study (chance = 0.5)")
-
-```
--->
-
-# 60 Hz Condition
-
-We ran the exact same study with the monitors set to 60 Hz before the data of the first pilot were analyzed.
-
-```{r initp2, cache = TRUE}
-raw_data_path <- "data_raw/p2ghent/"
-processed_data_path <- "data_processed/p2ghent/"
-
-```
-
-```{r otm2pilot2-load-data, cache = TRUE, dependson = "initp2", warning = FALSE}
-# Process raw data
-if(process_rawdata) {
-
-  # Merge raw data
-  otm2p2_eval <- batch_read(
-    raw_data_path
-    , pattern = "Eval"
-    , recursive = TRUE
-    , read_fun = read.delim
-  )
-
-   # change second entry of pp 4 to participant number = 104
-   otm2p2_eval <- subset(otm2p2_eval, ParticipantNumber != "ParticipantNumber")
-   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-26_13.28.11.484000", 1] <- 104
-
-   # change secodn entry pf participant 6 to 106 and third entry to 206
-   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-30_17.51.56.687000", 1] <- 106
-   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-30_18.41.18.078000", 1] <- 206
-
-  otm2p2_mem <- batch_read(
-    raw_data_path
-    , pattern = "MemTest"
-    , recursive = TRUE
-    , read_fun = read.delim
-  )
-
-   # change participant numbers (see above)
-   otm2p2_mem <- subset(otm2p2_mem, ParticipantNumber != "ParticipantNumber")
-   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-26_13.28.11.484000", 1] <- 104
-   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-30_17.51.56.687000", 1] <- 106
-   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-30_18.41.18.078000", 1] <- 206
-
-  otm2p2_log <- batch_read(
-    raw_data_path
-    , pattern = "ScreenLog"
-    , recursive = TRUE
-    , read_fun = read.csv
-    , header = FALSE
-  )
-
-  # pp 4 and 6 are causing problems as multiple participants were collected 
-  # with this number
-  p4 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_4.dat"))
-  p4[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p4[2])
-  p4[3] <- gsub("!9", "19", p4[3]) # I am making the assumption that the participant intended to enter 19 not !9
-  p4[3] <- gsub("4", "104", p4[3])
-
-  # repeat as above with participant number 6
-  p6 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_6.dat"))
-  p6[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p6[2])
-  p6[3] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p6[3])
-  p6[3] <- gsub("6", "106", p6[3])
-  p6[4] <- gsub("6", "206", p6[4])
-
-  #read all other files and remove participant 4, 5(no data collected), 6
-  f2 <- list.files(raw_data_path, pattern = "Demographics", recursive = TRUE)[-c(15, 16, 17)]
-
-  #add data to a data frame
-  otm2p2_demo <- lapply(paste0(raw_data_path, f2), read.delim)
-  otm2p2_demo <- do.call("rbind", otm2p2_demo)
-
-  #add data of participants with number 4, 104, 6, 106, and 206 to data file
-  otm2p2_demo <- rbind(otm2p2_demo, read.delim(textConnection(paste(p4, collapse = "\n"))))
-  otm2p2_demo <- rbind(otm2p2_demo, read.delim(textConnection(paste(p6, collapse = "\n"))))
-
-    # Recode, calculate indices, and filter data
-    # Needs to be changed as is currently not adapted to this data set
-  # otm2p_eval <- otm2p_eval %>%
-  #   mutate_at(vars(starts_with("Eval")), scale) %>%
-  #   select(starts_with("Eval")) %>%
-  #   rowwise %>%
-  #   do(data.frame(Eval = sum(unlist(.)))) %>%
-  #   bind_cols(otm1_eval, .) %>%
-  #   mutate(
-  #     ParticipantNumber = factor(ParticipantNumber)
-  #     , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
-  #     , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
-  #     , Block = factor(Block)
-  #   )
-  #
-
-  otm2p_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")
-
-  #otm2p_demo$frameRate <- modal_frame_rate(otm2p_log) #Todo FA
-
-  otm2p2_mem$ParticipantNumber <- as.integer(otm2p2_mem$ParticipantNumber)
-  otm2p2_mem <- left_join(otm2p2_mem, otm2p2_demo, by = "ParticipantNumber")
-
-  otm2p2_mem <- otm2p2_mem %>%
-    mutate(
-      ParticipantNumber = factor(ParticipantNumber)
-      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime", "posPrime") %>% factor
-      , Block = factor(Block)
-      , Accuracy = as.integer(NumbercorrectIdent) / 10
-    )
-
-  rm("otm2p2_demo", "p4", "p6", "f2")
-
-  # Save processed data
-  saveRDS(otm2p2_eval, paste0(processed_data_path, "otm2p2_eval.rds"))
-  saveRDS(otm2p2_mem, paste0(processed_data_path, "otm2p2_memory.rds"))
-} else {
-  otm2p2_eval <- readRDS(paste0(processed_data_path, "otm2p2_eval.rds"))
-  otm2p2_mem <- readRDS(paste0(processed_data_path, "otm2p2_memory.rds"))
-}
-```
-
-```{r otm2p2-recognition, results = "asis"}
-otm2p2_mem_ttest <- t.test(otm2p2_mem$Accuracy, mu = 0.5
-                          , alternative = "greater") %>%
-  apa_print %$%
-  full_result
-
-otm2p2_mem_ttestBF <- ttestBF(otm2p2_mem$Accuracy - 0.5
-                             , mu = 0, rscale = "medium"
-                             , nullInterval = c(0, Inf))[1] %>%
-  printBFt
-
-```
-
-## Memory in recognition task (60 Hz)
-
-Interestingly, the frequentist analysis (one sided *t* test) suggested, that prime recognition was not above chance `r otm2p2_mem_ttest`. 
-In this study, the Bayesian analysis (also one sided *t* test) was in line with the frequentist analysis `r otm2p2_mem_ttestBF`.
-
-### positive vs. negative primes (60 Hz)
-
-```{r pos-neg-otm2p2}
-otm2p2_pos_neg <- t.test(otm2p2_mem$Accuracy ~ otm2p2_mem$ValenceBlock) %>%
-  apa_print %$%
-  full_result
-
-otm2p2_pos_negBF <- ttestBF(subset(otm2p2_mem, ValenceBlock == "negPrime")$Accuracy
-                          ,subset(otm2p2_mem, ValenceBlock == "posPrime")$Accuracy
-                          ,rscale = "medium") %>%
-  printBFt
-
-```
-
-We again looked at the difference between positive and negative prime identification. 
-As in the 75 Hz condition, there appeared to be a decently sized difference between positive and negative words, which in this case is supported by both the frequentist analysis `r otm2p2_pos_neg`, and by the Bayesian *t* test `r otm2p2_pos_negBF`.
-
-```{r visualize-pos-neg-otm2p2}
-apa_beeplot(otm2p2_mem
-            , id = "ParticipantNumber"
-            , factors = "ValenceBlock"
-            , dv = "Accuracy"
-            , args_points = list(bg = "lightblue", col = "#045a8d", cex = 1.5)
-            , args_swarm = list(cex = 1.4)
-            , ylim = c(0, 1)
-  )
-abline(h = 0.5, col = "darkblue", lty = 5)
-```
-
-<!--
-## Response in demographics on goal of study (60 Hz)
-
-```{r goalResponse2, results = "asis"}
-apa_table(otm2p2_mem[, c("ParticipantNumber", "Goal")]
-          , caption = "Reponse of all participants on the question what they think the experiment was about")
-```
--->
-
-# Comparing 60 and 75 Hz
-
-```{r otm2p-compare-60-75}
-otm2p_6075 <- t.test(x = otm2p_mem$Accuracy, y = otm2p2_mem$Accuracy) %>%
-  apa_print %$%
-  full_result
-
-otm2p_6075BF <- ttestBF(otm2p_mem$Accuracy
-                          ,otm2p2_mem$Accuracy
-                          ,rscale = "medium") %>%
-  printBFt
-
-```
-
-The overall difference in accuracy (chance = 0.5) between the 75 Hz condition (*M* = `r round(mean(otm2p_mem$Accuracy), 2)`) and the 60 Hz condition (*M* = `r round(mean(otm2p2_mem$Accuracy), 2)`), was statistically significant, `r otm2p_6075`, but the Bayesfactor was not convincing `r otm2p_6075BF` (two sided *t* tests).
-
-# Discussion
-
-It seems odd, that recognition was above chance in the 75 Hz condition but at chance in the 60 Hz condition.
-This could of course be a coincidence or a mistake was made somewhere.
-However, the results might be plausible for the following reason:
-Viewing stimuli on a 60 Hz CRT monitor is very uncomfortable as the screen is flickering, which is not the case when the screen running with 75 Hz. 
-This could decrease actual visibility in the 60 Hz condition, compared to the 75 Hz condition.
-It is, of course, possible that participants merely do not look at the screen closely as it is uncomfortable in the 60 Hz condition, which artificially reduces visibility of the primes.
-
-Additionally, there appeared to be a robust difference between positive and negative prime word recognition (i.e., more correct identifications of positive than negative primes). 
-Looking at the results of the memory test from Study 1, there appeared to be a difference in prime recognition of positive/negative words only in the data collected in Ghent and not in the data collected in Harvard or Cologne.
-Therefore, this issue might not be as important for the studies collecting data with an English version of the experiment.

### 2019-10-31 otm2pilot2/results/analysis2pilot2_ghent.Rmd
add all materials

--- 2019-10-31 otm2pilot/results/analysis2pilot.Rmd
@@
 ---
-title             : "Analysis of OTM 2 pilot"
+title             : "Analysis of OTM 2 pilot 2"
 author            : "Frederik Aust & Tobias Heycke"
@@
 ---
+
+# Set up analysis
 
@@
 
-```{r otm2pilot-analysis-preferences, cache = TRUE}
+```{r otm2pilot2-analysis-preferences, cache = TRUE}
 # Data wrangling
@@
 # Data location
-raw_data_path <- "data_raw/p1ghent/"
-processed_data_path <- "data_processed/p1ghent/"
+raw_data_path <- "data_raw_ghent/"
+processed_data_path <- "data_processed_ghent/"
 
@@
 
-# Introduction
+# Load the Data
 
-As prime recognition was above chance in study 1, we planned to run a pilot study with a reduced presentation time.
-As previous studies using this paradigm had used a presentation time of 17 ms and found no above-chance memory, we intended to run a pilot with a presentation time of 17 ms (1 frame at 60 Hz).
-Due to a mistake with the monitor settings, we accidentally ran a first pilot study with prime presentation at 13 ms (75 Hz) and then collected data with the monitors set to 60 Hz (i.e., 17 ms prime presentation).
-Screen refresh rates were saved by the experimental scripts confirming these settings.
-
-# Method
-
-The aim of the pilot was to keep the learning phase as similar to the actual experiment as possible, while keeping the pilot as short as possible.
-We collected the data in Ghent, using the previously used Dutch version of the experiment.
-We therefore had participants either complete 100 trials with positive primes (10 primes presented 10 times each) or 100 trials with negative primes.
-After the learning phase an evaluation of Bob - as collected in study 1 - was administered, to erase any prime knowledge from working memory.
-Afterwards the ten positive (or negative) primes and ten positive (or negative) new words were presented on the screen.
-If participants had no prime memory, we would therefore expect five correct identifications by chance.
-Participants were instructed to select ten words, that might have appeared during the learning phase. 
-All instructions were as in the original study, the only difference was that participants were instructed to select 10 instead of 20 words and the IAT was not administered.
-
-# 75 Hz Condition
-
-```{r otm2pilot-load-data, cache = TRUE, dependson = "otm2pilot-analysis-preferences", warning = FALSE}
-# Process raw data
-if(process_rawdata) {
-
-  # Merge raw data
-  otm2p_eval <- batch_read(
-    raw_data_path
-    , pattern = "Eval"
-    , recursive = TRUE
-    , read_fun = read.delim
-  )
-
-  # change second entry of pp108  to participant number = 208
-  otm2p_eval <- subset(otm2p_eval, ParticipantNumber != "ParticipantNumber")
-  otm2p_eval[otm2p_eval$timeStamp == "2018-10-16_16.05.10.218000", 1] <- 208
-
-  otm2p_mem <- batch_read(
-    raw_data_path
-    , pattern = "MemTest"
-    , recursive = TRUE
-    , read_fun = read.delim
-  )
-
-  # change second entry of pp108  to participant number = 208
-  otm2p_mem <- subset(otm2p_mem, ParticipantNumber != "ParticipantNumber")
-  otm2p_mem[otm2p_mem$timeStamp == "2018-10-16_16.05.10.218000", 1] <- 208
-
-  otm2p_log <- batch_read(
-    raw_data_path
-    , pattern = "ScreenLog"
-    , recursive = TRUE
-    , read_fun = read.csv
-    , header = FALSE
-  )
-
-  #pp108 is causing problems reading in the data as 2 participants were collected 
-  #with this number (and an enter is missing after the entry of the first participant)
-
-  p108 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_108.dat"))
-  p108[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p108[2])
-  p108[3] <- gsub("108", "208", p108[3]) # rename the second participants with 108 to 208
-
-  #read all other files and remove participant 108
-  f <- list.files(raw_data_path, pattern = "Demographics", recursive = TRUE)[-8]
-
-  #add data to a data frame
-  otm2p_demo <- lapply(paste0(raw_data_path, f), read.delim)
-  otm2p_demo <- do.call("rbind", otm2p_demo)
-
-  #add data of participants with number 108 to data file
-  otm2p_demo <- rbind(otm2p_demo, read.delim(textConnection(paste(p108, collapse = "\n"))))
-
-    # Recode, calculate indices, and filter data 
-    # Needs to be changed as is currently not adapted to this data set
-  # otm2p_eval <- otm2p_eval %>%
-  #   mutate_at(vars(starts_with("Eval")), scale) %>%
-  #   select(starts_with("Eval")) %>%
-  #   rowwise %>%
-  #   do(data.frame(Eval = sum(unlist(.)))) %>% 
-  #   bind_cols(otm1_eval, .) %>%
-  #   mutate(
-  #     ParticipantNumber = factor(ParticipantNumber)
-  #     , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
-  #     , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
-  #     , Block = factor(Block)
-  #   )
-  #
-
-  otm2p_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")
-
-  #otm2p_demo$frameRate <- modal_frame_rate(otm2p_log) #Todo FA
-
-  otm2p_mem$ParticipantNumber <- as.integer(otm2p_mem$ParticipantNumber)
-  otm2p_mem <- left_join(otm2p_mem, otm2p_demo, by = "ParticipantNumber")
-
-  otm2p_mem <- otm2p_mem %>%
-    mutate(
-      ParticipantNumber = factor(ParticipantNumber)
-      , ValenceBlock = ifelse(ValenceBlock == 1, "negPrime", "posPrime") %>% factor
-      , Block = factor(Block)
-      , Accuracy = as.integer(NumbercorrectIdent) / 10
-    )
-
-  rm("otm2p_demo", "p108", "f")
-
-  # Save processed data
-  saveRDS(otm2p_eval, paste0(processed_data_path, "otm2p_eval.rds"))
-  saveRDS(otm2p_mem, paste0(processed_data_path, "otm2p_memory.rds"))
-} else {
-  otm2p_eval <- readRDS(paste0(processed_data_path, "otm2p_eval.rds"))
-  otm2p_mem <- readRDS(paste0(processed_data_path, "otm2p_memory.rds"))
-}
-```
-
-## General information
-
-The monitors were accidentally set to 75 Hz and the primes where therefore presented for about 13 ms (instead of the planned 17 ms).
-
-```{r otm2p-recognition, results = "asis"}
-otm2p_mem_ttest <- t.test(otm2p_mem$Accuracy, mu = 0.5
-                          , alternative = "greater") %>%
-  apa_print %$%
-  full_result
-
-otm2p_mem_ttestBF <- ttestBF(otm2p_mem$Accuracy - 0.5
-                             , mu = 0, rscale = "medium"
-                             , nullInterval = c(0, Inf))[1] %>%
-  printBFt
-
-```
-
-## Memory in recognition task
-
-The frequentist analysis (one sided *t* test) suggests, that prime recognition was above chance `r otm2p_mem_ttest`. 
-The Bayesian analysis (also one sided *t* test) is not completely compelling but is also indicating that prime memory was above chance `r otm2p_mem_ttestBF`.
-
-### positive vs. negative primes
-
-```{r pos-neg-otm2p}
-otm2p_pos_neg <- t.test(otm2p_mem$Accuracy ~ otm2p_mem$ValenceBlock) %>%
-  apa_print %$%
-  full_result
-
-otm2p_pos_negBF <- ttestBF(subset(otm2p_mem, ValenceBlock == "negPrime")$Accuracy
-                          ,subset(otm2p_mem, ValenceBlock == "posPrime")$Accuracy
-                          ,rscale = "medium") %>%
-  printBFt
-
-```
-
-Descriptively there appeared to be a decently sized difference between positive and negative words, which was supported by the frequentist analysis `r otm2p_pos_neg`, but not by a Bayesian test `r otm2p_pos_negBF`.
-It is important to mention, that we had only about 10 participants per group and we do not know whether the positive words are easier to see, remembered better, or whether participants merely selected more positive words in the memory task.
-
-```{r visualize-pos-neg-otm2p}
-apa_beeplot(otm2p_mem
-            , id = "ParticipantNumber"
-            , factors = "ValenceBlock"
-            , dv = "Accuracy"
-            , args_points = list(bg = "lightblue", col = "#045a8d", cex = 1.5)
-            , args_swarm = list(cex = 1.4)
-            , ylim = c(0, 1)
-  )
-abline(h = 0.5, col = "darkblue", lty = 5)
-```
-
-<!--
-## Response in demographics on goal of study
-
-```{r goalResponse, results = "asis"}
-apa_table(otm2p_mem[, c("ParticipantNumber", "Goal")]
-          , caption = "Reponse of all participants on the question what they think the experiment was about")
-```
-
-Based on their response, the following participants were maybe aware of the primes during the learning phase: 103, 108, 116, 119, 120, 208.
-Interestingly, looking at their scores on the visibility test, three out of six participants had an accuracy on chance level. 
-Of course these small numbers should not be over interpreted, but these numbers could indicate that the memory test is not suited to measure visibility and we might largely underestimate actual visibility.
-Participants might be aware of the primes and remember that they were generally positive/negative but might not remember the actual words.
-
-```{r visScoresomt2p, results = "asis"}
-otm2p_adler <- c(103, 108, 116, 119, 120, 208)
-
-apa_table(otm2p_mem[otm2p_mem$ParticipantNumber %in% otm2p_adler
-         , c("ParticipantNumber", "Accuracy")]
-         , caption = "Accuracy scores of participants who might have known the goal of the study (chance = 0.5)")
-
-```
--->
-
-# 60 Hz Condition
-
-We ran the exact same study with the monitors set to 60 Hz before the data of the first pilot were analyzed.
-
-```{r initp2, cache = TRUE}
-raw_data_path <- "data_raw/p2ghent/"
-processed_data_path <- "data_processed/p2ghent/"
-
-```
-
-```{r otm2pilot2-load-data, cache = TRUE, dependson = "initp2", warning = FALSE}
+```{r otm2pilot2-load-data, cache = TRUE, dependson = "otm2pilot-analysis-preferences", warning = FALSE}
 # Process raw data
@@
 
-   # change second entry of pp 4 to participant number = 104
-   otm2p2_eval <- subset(otm2p2_eval, ParticipantNumber != "ParticipantNumber")
-   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-26_13.28.11.484000", 1] <- 104
-
-   # change secodn entry pf participant 6 to 106 and third entry to 206
-   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-30_17.51.56.687000", 1] <- 106
-   otm2p2_eval[otm2p2_eval$timeStamp == "2018-10-30_18.41.18.078000", 1] <- 206
-
   otm2p2_mem <- batch_read(
@@
   )
-
-   # change participant numbers (see above)
-   otm2p2_mem <- subset(otm2p2_mem, ParticipantNumber != "ParticipantNumber")
-   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-26_13.28.11.484000", 1] <- 104
-   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-30_17.51.56.687000", 1] <- 106
-   otm2p2_mem[otm2p2_mem$timeStamp == "2018-10-30_18.41.18.078000", 1] <- 206
 
@@
 
-  # pp 4 and 6 are causing problems as multiple participants were collected 
-  # with this number
-  p4 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_4.dat"))
-  p4[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p4[2])
-  p4[3] <- gsub("!9", "19", p4[3]) # I am making the assumption that the participant intended to enter 19 not !9
-  p4[3] <- gsub("4", "104", p4[3])
-
-  # repeat as above with participant number 6
-  p6 <- readLines(paste0(raw_data_path,"Data_Demographics_OTMPilot_Ghent_6.dat"))
-  p6[2] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p6[2])
-  p6[3] <- gsub("ParticipantNumber\tAge\tStudy\tGender\tGoal\tComment", "", p6[3])
-  p6[3] <- gsub("6", "106", p6[3])
-  p6[4] <- gsub("6", "206", p6[4])
-
-  #read all other files and remove participant 4, 5(no data collected), 6
-  f2 <- list.files(raw_data_path, pattern = "Demographics", recursive = TRUE)[-c(15, 16, 17)]
-
-  #add data to a data frame
-  otm2p2_demo <- lapply(paste0(raw_data_path, f2), read.delim)
-  otm2p2_demo <- do.call("rbind", otm2p2_demo)
-
-  #add data of participants with number 4, 104, 6, 106, and 206 to data file
-  otm2p2_demo <- rbind(otm2p2_demo, read.delim(textConnection(paste(p4, collapse = "\n"))))
-  otm2p2_demo <- rbind(otm2p2_demo, read.delim(textConnection(paste(p6, collapse = "\n"))))
-
-    # Recode, calculate indices, and filter data
-    # Needs to be changed as is currently not adapted to this data set
-  # otm2p_eval <- otm2p_eval %>%
-  #   mutate_at(vars(starts_with("Eval")), scale) %>%
-  #   select(starts_with("Eval")) %>%
-  #   rowwise %>%
-  #   do(data.frame(Eval = sum(unlist(.)))) %>%
-  #   bind_cols(otm1_eval, .) %>%
-  #   mutate(
-  #     ParticipantNumber = factor(ParticipantNumber)
-  #     , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
-  #     , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
-  #     , Block = factor(Block)
-  #   )
-  #
-
-  otm2p_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")
-
-  #otm2p_demo$frameRate <- modal_frame_rate(otm2p_log) #Todo FA
+  otm2p2_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")
 
   otm2p2_mem$ParticipantNumber <- as.integer(otm2p2_mem$ParticipantNumber)
-  otm2p2_mem <- left_join(otm2p2_mem, otm2p2_demo, by = "ParticipantNumber")
+  #otm2p2_mem <- left_join(otm2p2_mem, otm2p2_demo, by = "ParticipantNumber")
 
@@
       , Block = factor(Block)
-      , Accuracy = as.integer(NumbercorrectIdent) / 10
+      , Accuracy = as.integer(NumbercorrectIdent) / 20
     )
-
-  rm("otm2p2_demo", "p4", "p6", "f2")
 
@@
 ```
+
+# Analyze memory scores
 
@@
 
-## Memory in recognition task (60 Hz)
+Frequentists analysis: `r otm2p2_mem_ttest`
 
-Interestingly, the frequentist analysis (one sided *t* test) suggested, that prime recognition was not above chance `r otm2p2_mem_ttest`. 
-In this study, the Bayesian analysis (also one sided *t* test) was in line with the frequentist analysis `r otm2p2_mem_ttestBF`.
-
-### positive vs. negative primes (60 Hz)
-
-```{r pos-neg-otm2p2}
-otm2p2_pos_neg <- t.test(otm2p2_mem$Accuracy ~ otm2p2_mem$ValenceBlock) %>%
-  apa_print %$%
-  full_result
-
-otm2p2_pos_negBF <- ttestBF(subset(otm2p2_mem, ValenceBlock == "negPrime")$Accuracy
-                          ,subset(otm2p2_mem, ValenceBlock == "posPrime")$Accuracy
-                          ,rscale = "medium") %>%
-  printBFt
-
-```
-
-We again looked at the difference between positive and negative prime identification. 
-As in the 75 Hz condition, there appeared to be a decently sized difference between positive and negative words, which in this case is supported by both the frequentist analysis `r otm2p2_pos_neg`, and by the Bayesian *t* test `r otm2p2_pos_negBF`.
-
-```{r visualize-pos-neg-otm2p2}
-apa_beeplot(otm2p2_mem
-            , id = "ParticipantNumber"
-            , factors = "ValenceBlock"
-            , dv = "Accuracy"
-            , args_points = list(bg = "lightblue", col = "#045a8d", cex = 1.5)
-            , args_swarm = list(cex = 1.4)
-            , ylim = c(0, 1)
-  )
-abline(h = 0.5, col = "darkblue", lty = 5)
-```
-
-<!--
-## Response in demographics on goal of study (60 Hz)
-
-```{r goalResponse2, results = "asis"}
-apa_table(otm2p2_mem[, c("ParticipantNumber", "Goal")]
-          , caption = "Reponse of all participants on the question what they think the experiment was about")
-```
--->
-
-# Comparing 60 and 75 Hz
-
-```{r otm2p-compare-60-75}
-otm2p_6075 <- t.test(x = otm2p_mem$Accuracy, y = otm2p2_mem$Accuracy) %>%
-  apa_print %$%
-  full_result
-
-otm2p_6075BF <- ttestBF(otm2p_mem$Accuracy
-                          ,otm2p2_mem$Accuracy
-                          ,rscale = "medium") %>%
-  printBFt
-
-```
-
-The overall difference in accuracy (chance = 0.5) between the 75 Hz condition (*M* = `r round(mean(otm2p_mem$Accuracy), 2)`) and the 60 Hz condition (*M* = `r round(mean(otm2p2_mem$Accuracy), 2)`), was statistically significant, `r otm2p_6075`, but the Bayesfactor was not convincing `r otm2p_6075BF` (two sided *t* tests).
-
-# Discussion
-
-It seems odd, that recognition was above chance in the 75 Hz condition but at chance in the 60 Hz condition.
-This could of course be a coincidence or a mistake was made somewhere.
-However, the results might be plausible for the following reason:
-Viewing stimuli on a 60 Hz CRT monitor is very uncomfortable as the screen is flickering, which is not the case when the screen running with 75 Hz. 
-This could decrease actual visibility in the 60 Hz condition, compared to the 75 Hz condition.
-It is, of course, possible that participants merely do not look at the screen closely as it is uncomfortable in the 60 Hz condition, which artificially reduces visibility of the primes.
-
-Additionally, there appeared to be a robust difference between positive and negative prime word recognition (i.e., more correct identifications of positive than negative primes). 
-Looking at the results of the memory test from Study 1, there appeared to be a difference in prime recognition of positive/negative words only in the data collected in Ghent and not in the data collected in Harvard or Cologne.
-Therefore, this issue might not be as important for the studies collecting data with an English version of the experiment.
+Bayesian Analysis: `r otm2p2_mem_ttestBF`

### 2019-10-31 otm1/material/Cologne/OTM_exp_script 1024x768 75Hz Cologne.py

@@ -1,0 +1,990 @@
+# -*- coding: utf-8 -*-
+
+#coded in PsychoPy v1.83.04
+#wrote for 75Hz monitors - in frames
+
+#import python functions
+from psychopy import visual, sound, core, gui, event, logging, __version__
+from random import shuffle
+from socket import gethostname
+import datetime
+import time
+import os
+import sys, platform
+import codecs
+
+# ###########################################################################################################################
+# Function definition
+# ###########################################################################################################################
+
+#Function that waits for space key to continue (used for the instruction amd demographic pages)
+def furtherFunction():
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'space')
+        if keyPress == ['space']:
+            further = False
+
+#Used for text presentation on last page, e must be pressed to finish experiment
+def LastPage(textOnPage):
+    instr = visual.TextStim(window, text= textOnPage, color = "white")
+    instr.draw()
+    window.flip()
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'e')
+        if keyPress == ['e']:
+            further = False
+
+# Function that helps getting a list from a txt file into a python list
+def getList (listname):
+    wordList = []
+    for eachLine in range(len(listname)) :
+        currentWord = listname[eachLine][:-1]
+        wordList.append(currentWord) 
+    return wordList
+
+# Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
+def ReadTxt(File, remove):
+    tL = []
+    with codecs.open(File, "r", encoding = "utf-8") as my_file:
+        lines = my_file.readlines()
+        tL.append(lines)
+    my_file.close()
+    l = []
+    for eachLine in range(len(tL[0])) :
+        currentWord = tL[0][eachLine][:remove]
+        l.append(currentWord) 
+    return(l)
+
[…]

### 2019-10-31 otm1/material/Gent/OTM_exp_script_1024x768 75Hz GHENT.py

@@ -1,0 +1,989 @@
+# -*- coding: utf-8 -*-
+
+#coded in PsychoPy v1.83.04
+#wrote for 75Hz monitors - in frames
+
+#import python functions
+from psychopy import visual, sound, core, gui, event, logging, __version__
+from random import shuffle
+from socket import gethostname
+import datetime
+import time
+import os
+import sys, platform
+import codecs
+
+# ###########################################################################################################################
+# Function definition
+# ###########################################################################################################################
+
+#Function that waits for space key to continue (used for the instruction amd demographic pages)
+def furtherFunction():
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'space')
+        if keyPress == ['space']:
+            further = False
+
+#Used for text presentation on last page, e must be pressed to finish experiment
+def LastPage(textOnPage):
+    instr = visual.TextStim(window, text= textOnPage, color = "white")
+    instr.draw()
+    window.flip()
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'e')
+        if keyPress == ['e']:
+            further = False
+
+# Function that helps getting a list from a txt file into a python list
+def getList (listname):
+    wordList = []
+    for eachLine in range(len(listname)) :
+        currentWord = listname[eachLine][:-1]
+        wordList.append(currentWord) 
+    return wordList
+
+# Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
+def ReadTxt(File, remove):
+    tL = []
+    with codecs.open(File, "r", encoding = "utf-8") as my_file:
+        lines = my_file.readlines()
+        tL.append(lines)
+    my_file.close()
+    l = []
+    for eachLine in range(len(tL[0])) :
+        currentWord = tL[0][eachLine][:remove]
+        l.append(currentWord) 
+    return(l)
+
[…]

### 2019-10-31 otm1/material/Harvard/OTM_exp_script 1024x768 85Hz HARVARD.py

@@ -1,0 +1,988 @@
+# -*- coding: utf-8 -*-
+
+#coded in PsychoPy v1.83.04
+#wrote for 85Hz monitors - in frames
+
+#import python functions
+from psychopy import visual, sound, core, gui, event, logging, __version__
+from random import shuffle
+from socket import gethostname
+import datetime
+import time
+import os
+import sys, platform
+import codecs
+
+# ###########################################################################################################################
+# Function definition
+# ###########################################################################################################################
+
+#Function that waits for space key to continue (used for the instruction amd demographic pages)
+def furtherFunction():
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'space')
+        if keyPress == ['space']:
+            further = False
+
+#Used for text presentation on last page, e must be pressed to finish experiment
+def LastPage(textOnPage):
+    instr = visual.TextStim(window, text= textOnPage, color = "white")
+    instr.draw()
+    window.flip()
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'e')
+        if keyPress == ['e']:
+            further = False
+
+# Function that helps getting a list from a txt file into a python list
+def getList (listname):
+    wordList = []
+    for eachLine in range(len(listname)) :
+        currentWord = listname[eachLine][:-1]
+        wordList.append(currentWord) 
+    return wordList
+
+# Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
+def ReadTxt(File, remove):
+    tL = []
+    with codecs.open(File, "r", encoding = "utf-8") as my_file:
+        lines = my_file.readlines()
+        tL.append(lines)
+    my_file.close()
+    l = []
+    for eachLine in range(len(tL[0])) :
+        currentWord = tL[0][eachLine][:remove]
+        l.append(currentWord) 
+    return(l)
+
+#function used for instruction: disyplays text on a page and continues when space is pressed
[…]

### 2019-10-31 otm2/material/OTM_exp_script_1280_1024_75Hz.py

@@ -1,0 +1,989 @@
+# -*- coding: utf-8 -*-
+
+#coded in PsychoPy v1.83.04
+#written for 75Hz monitors - in frames
+
+#import python functions
+from psychopy import visual, sound, core, gui, event, logging, __version__
+from random import shuffle
+from socket import gethostname
+import datetime
+import time
+import os
+import sys, platform
+import codecs
+
+# ###########################################################################################################################
+# Function definition
+# ###########################################################################################################################
+
+#Function that waits for space key to continue (used for the instruction amd demographic pages)
+def furtherFunction():
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'space')
+        if keyPress == ['space']:
+            further = False
+
+#Used for text presentation on last page, e must be pressed to finish experiment
+def LastPage(textOnPage):
+    instr = visual.TextStim(window, text= textOnPage, color = "white")
+    instr.draw()
+    window.flip()
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'e')
+        if keyPress == ['e']:
+            further = False
+
+# Function that helps getting a list from a txt file into a python list
+def getList (listname):
+    wordList = []
+    for eachLine in range(len(listname)) :
+        currentWord = listname[eachLine][:-1]
+        wordList.append(currentWord) 
+    return wordList
+
+# Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
+def ReadTxt(File, remove):
+    tL = []
+    with codecs.open(File, "r", encoding = "utf-8") as my_file:
+        lines = my_file.readlines()
+        tL.append(lines)
+    my_file.close()
+    l = []
+    for eachLine in range(len(tL[0])) :
+        currentWord = tL[0][eachLine][:remove]
+        l.append(currentWord) 
+    return(l)
+
+#function used for instruction: disyplays text on a page and continues when space is pressed
[…]

### 2019-10-31 otm2pilot/material/OTM_exp_script_1024x768 60Hz GHENT.py

@@ -1,0 +1,735 @@
+# -*- coding: utf-8 -*-
+
+#coded in PsychoPy v1.83.04
+#wrote for 60Hz monitors - in frames
+
+#import python functions
+from psychopy import visual, sound, core, gui, event, logging, __version__
+from random import shuffle
+from socket import gethostname
+import datetime
+import time
+import os
+import sys, platform
+import codecs
+
+# ###########################################################################################################################
+# Function definition
+# ###########################################################################################################################
+
+#Function that waits for space key to continue (used for the instruction amd demographic pages)
+def furtherFunction():
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'space')
+        if keyPress == ['space']:
+            further = False
+
+#Used for text presentation on last page, e must be pressed to finish experiment
+def LastPage(textOnPage):
+    instr = visual.TextStim(window, text= textOnPage, color = "white")
+    instr.draw()
+    window.flip()
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'e')
+        if keyPress == ['e']:
+            further = False
+
+# Function that helps getting a list from a txt file into a python list
+def getList (listname):
+    wordList = []
+    for eachLine in range(len(listname)) :
+        currentWord = listname[eachLine][:-1]
+        wordList.append(currentWord) 
+    return wordList
+
+# Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
+def ReadTxt(File, remove):
+    tL = []
+    with codecs.open(File, "r", encoding = "utf-8") as my_file:
+        lines = my_file.readlines()
+        tL.append(lines)
+    my_file.close()
+    l = []
+    for eachLine in range(len(tL[0])) :
+        currentWord = tL[0][eachLine][:remove]
+        l.append(currentWord) 
+    return(l)
+
[…]

### 2019-10-31 otm2pilot2/material/Ghent/OTM_exp_script_1024x768_75Hz_13ms.py

@@ -1,0 +1,990 @@
+# -*- coding: utf-8 -*-
+
+#coded in PsychoPy v1.83.04
+#wrote for 75Hz monitors - in frames
+#prime will be presented for 13 ms (i.e., 1 frame)
+
+#import python functions
+from psychopy import visual, sound, core, gui, event, logging, __version__
+from random import shuffle
+from socket import gethostname
+import datetime
+import time
+import os
+import sys, platform
+import codecs
+
+# ###########################################################################################################################
+# Function definition
+# ###########################################################################################################################
+
+#Function that waits for space key to continue (used for the instruction amd demographic pages)
+def furtherFunction():
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'space')
+        if keyPress == ['space']:
+            further = False
+
+#Used for text presentation on last page, e must be pressed to finish experiment
+def LastPage(textOnPage):
+    instr = visual.TextStim(window, text= textOnPage, color = "white")
+    instr.draw()
+    window.flip()
+    further = True
+    keyPress = ""
+    while further:
+        keyPress = event.waitKeys(keyList = 'e')
+        if keyPress == ['e']:
+            further = False
+
+# Function that helps getting a list from a txt file into a python list
+def getList (listname):
+    wordList = []
+    for eachLine in range(len(listname)) :
+        currentWord = listname[eachLine][:-1]
+        wordList.append(currentWord) 
+    return wordList
+
+# Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
+def ReadTxt(File, remove):
+    tL = []
+    with codecs.open(File, "r", encoding = "utf-8") as my_file:
+        lines = my_file.readlines()
+        tL.append(lines)
+    my_file.close()
+    l = []
+    for eachLine in range(len(tL[0])) :
+        currentWord = tL[0][eachLine][:remove]
+        l.append(currentWord) 
+    return(l)
+
[…]

### 2019-11-07 otm1/results/analysis1.Rmd
Corrects some paths and knitts analysis for experiment 1 and supplements.

@@
 
-source("../../R/modal_frame_rate.R")
+source("../../analysis_and_paper/modal_frame_rate.R")
 
@@
 
+colnames(otm1_random_participant_intercept_matrix) <- paste0("ParticipantNumber", levels(otm1_attitudes_collapsed$ParticipantNumber))
+
 # Fixed effects
@@
 
-```{r otm1-bayesian-replication-analysis, cache = TRUE, dependson = "otm1-bayesian-replication-analysis-design-matrix"}
+```{r otm1-bayesian-replication-analysis, cache = TRUE, dependson = "otm1-bayesian-replication-design-matrix"}
 # No effect model
@@
 
-```{r otm1-bayesian-replication-analysis-samples, cache = TRUE, dependson = "otm1-bayesian-replication-analysis-unconstrained"}
+```{r otm1-bayesian-replication-analysis-samples, cache = TRUE, dependson = "otm1-bayesian-replication-analysis"}
 # Fixed effect model
@@
 colnames(otm1_unconstrained_samples)[1:ncol(otm1_unconstrained_model_matrix) + 1] <- colnames(otm1_unconstrained_model_matrix)
-
+```
+
+```{r}
 otm1_unconstrained_samples <- otm1_unconstrained_samples %>%
@@
 
-## Exploratory Analysis: Prime valence memory
-
+<!-- ## Exploratory Analysis: Prime valence memory -->
 ```{r listPrimes, echo = FALSE, eval=FALSE}

### 2020-06-15 analysis_and_paper/effect_sizes.R
Added via the Open Science Framework

@@ -1,0 +1,22 @@
+pes_to_dz <- function(pes, n, n_groups = 2) {
+  # I *think* sqrt(n_groups) is needed because of the between subject factor
+  # either way I validate that the results for pes, f, and dz are correct
+  sqrt(((1 - n) * pes)/(n * (pes - 1))) * sqrt(n_groups)
+}
+
+dz_to_f <- function(dz, rho) {
+  0.5 * dz * sqrt(2 * (1 - rho))
+}
+
+pes_to_f <- function(pes, n, rho) {
+  dz <- pes_to_dz(pes, n)
+  dz_to_f(dz, rho)
+}
+
+f_to_dz <- function(f, rho) {
+  (sqrt(2) * f) / sqrt(1 - rho)
+}
+
+dz_to_pes <- function(dz, n, n_groups = 2) {
+  (dz^2 * n)/(dz^2 * n + n*n_groups - n_groups)
+}

### 2020-06-15 analysis_and_paper/supplements.Rmd
Corrects some paths and knitts analysis for experiment 1 and supplements.
Updated via the Open Science Framework

@@
   - name          : Tobias Heycke
-    affiliation   : 1, 2
+    affiliation   : "1,2"
     corresponding : yes    
@@
   - name          : Frederik Aust
-    affiliation : 1
+    affiliation   : "1"
   - name          : Mahzarin R. Banaji
     affiliation   : 3
-  - name        : John G. Conway
-    affiliation : 4
+  - name          : Jeremy Cone
+    affiliation   : 9
   - name          : Pieter Van Dessel
     affiliation   : 5
+  - name          : Melissa J. Ferguson
+    affiliation   : 8
   - name          : Xiaoqing Hu
@@
   - name          : Benedek Kurdi
-    affiliation : 3    
+    affiliation   : "3,8"
   - name          : Robert Rydell
@@
     affiliation   : 1
-  - name        : Christine A. Vitiello
+  - name          : Christine Vitiello
     affiliation   : 4
@@
     institution   : Indiana University
+  - id            : 8
+    institution   : Cornell University
+  - id            : 9
+    institution   : Williams College
 
 bibliography      : ["references.bib", "r-references.bib"]
-#appendix          : "appendix.Rmd"
 
@@
 
+# devtools::install_github("arcaldwell49/Superpower")
+library("Superpower")
+
 source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")
+source("error_in_variables.R")
+source("effect_sizes.R")
 ```
@@
 # Data location
-raw_data_path <- "../ml-otm1/results/data_raw/"
-processed_data_path <- "../ml-otm1/results/data_processed/"
+raw_data_path <- "../otm1/results/data_raw/"
+processed_data_path <- "../otm1/results/data_processed/"
 
@@
 
-## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
-# assignInNamespace("theme_nothing", function() {
-#     theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
-# }, "cowplot")
-
 # Number of MCMC samples for Bayesian analysis
@@
 
-In the following we report additional analyses and provide details for the model specification used for the Bayesian model comparisons.
-We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between US recognition accuracy and associative learning.
+In the following we report details on our power analysis, the model specification used for the Bayesian model comparisons, and additional secondary analyses.
+We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between the recognition accuracy of briefly flashed words and associative learning.
 Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.
@@
 
+## Power analysis
+
+The prediction, which is supported by all previous empirical reports, is a crossed disordinal interaction between the factor *learning block* and the control factor *valence order*.
+Therefore, our power analyses focuses on this interaction and the theoretically relevant simple effects of *learning block*.
+We estimate the sensitivity of our design using the R-package *Superpower* [@R-Superpower] for the contrast analyes using the R-package *emmeans* [@R-emmeans].
+
+```{r rydell-effects, cache = TRUE}
+rydell_pes <- 0.1
+rydell_f <- 4.78
+rydell_n <- 50
+rydell_dz <- pes_to_dz(rydell_pes, rydell_n, n_groups = 2)
+
+heycke_t <- c(2.54, 1.45)
+heycke_n <- c(28, 26)
+heycke_dz <- heycke_t / sqrt(heycke_n)
+heycke_pes <- dz_to_pes(heycke_dz, heycke_n, n_groups = 1)
+```
+
+```{r otm1-power, cache = TRUE}
+otm1_power <- function(f, rm_cor, n = 76, alpha = 0.05) {
+  contrast_code <- tibble::tibble(
+    a = rep(contr.sum(2), 2)
+    , b = rep(contr.sum(2), each = 2)
+    , x = a*b * -1
+  )
+
+  mu <- with(
+    contrast_code
+    , f * x +
+      - 0.25 * a
+  )
+
+  cor_mat <- diag(4)
+  triangular <- c(0, 1, 0, 0, 1, 0)
+  cor_mat[upper.tri(cor_mat)] <- triangular * rm_cor
+  cor_mat[lower.tri(cor_mat)] <- triangular * rm_cor
+
+  string <- "2w*2b"
+  labelnames <- c("block", "1", "2", "order", "n-p", "p-n")
+
+  design_result <- ANOVA_design(
+    design = string
+    , n = n
+    , mu = mu
+    , sd = 1
+    , r = cor_mat
+    , labelnames = labelnames
+  )
+
+  otm1_power <- ANOVA_exact(
+    design_result
+    , alpha_level = alpha
+    , emm = TRUE
+    , verbose = FALSE
+    , contrast_type = "pairwise"
+    , emm_comp = "block | order"
+  )
+
+  otm1_power
+}
+
+otm1_n <- 76
+
+# 95% power
+otm1_pes <- 0.08068
+otm1_dz <- pes_to_dz(otm1_pes, otm1_n, n_groups = 2)
+# rho <- 0.5
+# f <- dz_to_f(otm1_dz, rho)
+# 
+# otm1_contrast_power <- otm1_power(f = f, n = otm1_n, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm1_contrast_power
+
+# 80% power
+otm1_pes2 <- 0.050336
+otm1_dz2 <- pes_to_dz(otm1_pes2, otm1_n, n_groups = 2)
+# f <- dz_to_f(otm1_dz2, rho)
+# 
+# otm1_contrast_power2 <- otm1_power(f = f, n = otm1_n, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm1_contrast_power2
+```
+
+@rydell_two_2006 found the smallest learning block difference for IAT scores, $\hat\eta_p^2 = `r printp(rydell_pes)`$, $d_z \approx `r rydell_dz`$.
+The learning block differences reported by @heycke_two_2018 were of similar magnitude but with an opposite sign.
+Across all labs ($N = 152$), our design has 95% power to detect effects as small as $\eta^2_p = `r printp(otm1_pes)`$ ($\delta_z = `r otm1_dz`$) and 80% power to detect effects as small as $\eta^2_p = `r printp(otm1_pes2)`$ ($\delta_z = `r otm1_dz2`$) in two-sided tests.
+Thus, our design is sufficiently sensitive to detect (or rule out) differences `r round((1 - otm1_dz/rydell_dz) * 100)`% smaller than the smallest learning block difference reported by @rydell_two_2006.
+Figure\ \@ref(fig:otm1-power-curve) illustrates the implied sensitivity in units of Cohen's $\delta$ depending on the assumed repeated-measures correlation $\rho$.
+
+(ref:otm1-power-curve) Sensitivity curves for learning block contrasts in Experiment 1 depending on the assumed repeated measures correlation.
+The grey dashed line at the top represents the smallest estimate of the learning block difference reported by Rydell et al. [$d_z = `r rydell_dz`$; -@rydell_two_2006].
+
+```{r otm1-power-curve, fig.width = 5.75, fig.height = 4, fig.cap = "(ref:otm1-power-curve)"}
+rydell_power_curve <- tibble(
+  rho = seq(-1, 1, length.out = 100)
+  , delta = c(
+    dz_to_f(rydell_dz, unique(rho)) * 2
+  )
+  , power = NA
+)
+
+otm1_power_curve <- tibble(
+  rho = rep(seq(-1, 1, length.out = 100), 2)
+  , delta = c(
+    dz_to_f(otm1_dz, unique(rho)) * 2
+    , dz_to_f(otm1_dz2, unique(rho)) * 2
+  )
+  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
+)
+
+otm1_power_curve %>% 
+  mutate(
+    power = relevel(factor(power), "0.95")
+  ) %>% 
+  ggplot(aes(x = rho, y = delta, group = power, linetype = power)) +
+  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
+  geom_line() +
+  ylim(c(0, 1)) +
+  scale_linetype_discrete(
+    labels = c(
+      bquote(.(unique(otm1_power_curve$power)[1])~~(delta[z] == .(printnum(otm1_dz))))
+      , bquote(.(unique(otm1_power_curve$power)[2])~~(delta[z] == .(printnum(otm1_dz2))))
+    )
+  ) +
+  labs(
+    x = bquote("Correlation between learning blocks ["*rho*"]")
+    , y = bquote("Learning block difference [Cohen's"~delta*"]")
+    , color = "Contrast"
+    , linetype = bquote("Power"~"["*1 - beta*"]")
+  ) +
+  ggtitle("", subtitle = bquote(list(alpha ==~".05", italic(N) == .(otm1_n*2)))) +
+  theme_apa(box = TRUE) + 
+  theme(
+    panel.grid.major.x = element_line()
+    , panel.grid.major.y = element_line()
+    , panel.grid.minor.x = element_line()
+    , panel.grid.minor.y = element_line()
+    , legend.justification = "top"
+  )
+```
+
+```{r otm1-power-curves, eval = FALSE}
+otm1_power_curve <- expand.grid(
+  n = 76
+  , rho = seq(-0.9, 0.9, length.out = 10)
+  , alpha = 0.05
+  , d = seq(0, 0.9, length.out = 96)
+) %>%
+  as_tibble %>% 
+  mutate(
+    f = d/2
+    , generalized_eta_squared = f^2 / (1 + f^2)
+    , interaction = NULL
+    , contrast = NULL
+  )
+
+otm1_power_curve[, c("interaction", "contrast")] <- t(apply(
+  otm1_power_curve
+  , 1
+  , function(x) {
+    power <- otm1_power(n = x["n"], f = x["f"], rm_cor = x["rho"], alpha = x["alpha"])
+
+    c(
+      power_int = power$main_result["order:block", "power"] / 100
+      , power_contrast = emmeans_power(power$emmeans$contrasts, alpha_level = x["alpha"])[1, "power"] / 100
+    )
+  }
+))
+```
+
+```{r otm1-power-curves-plot, fig.width = 7, fig.height = 4.5, eval = FALSE}
+otm1_annotations <- data.frame(
+  label = c(
+    paste0("list(italic(N) ==", unique(otm1_power_curve$n)*2, ", alpha == 0.05, epsilon == 1)")
+    , paste0("list(italic(n) ==", unique(otm1_power_curve$n), ", alpha == 0.05)")
+  )
+  , test = factor(
+      c("interaction", "contrast")
+      , levels = c("interaction", "contrast")
+      , labels = c("italic('Learning block')%*%italic('Valence order')", "atop(italic('Learning block')*'-contrasts', 'by'~italic('Valence order'))")
+    )
+  )
+
+pivot_longer(
+  otm1_power_curve
+  , cols = c("interaction", "contrast")
+  , names_to = "test"
+  , values_to = "power"
+) %>% 
+  mutate(
+    test = factor(
+      test
+      , levels = c("interaction", "contrast")
+      , labels = c("italic('Learning block')%*%italic('Valence order')", "atop(italic('Learning block')*'-contrasts', 'by'~italic('Valence order'))")
+    )
+  ) %>% 
+  filter(power <= 0.99) %>% 
+  ggplot(aes(x = d, y = power, color = rho, group = rho)) +
+    geom_hline(yintercept = c(0.8, 0.95), linetype = "solid", color = grey(0.75), size = 0.25) +
+    geom_line(linetype = "solid") +
+    geom_text(data = otm1_annotations, aes(x = 0.87, y = 0.09, label = label), inherit.aes = FALSE, parse = TRUE, hjust = 0, vjust = 1) +
+    scale_x_continuous(
+      name = bquote("Cohen's"~delta)
+      , position = "top"
+      , breaks = function(x) seq(0, x[2], 0.1)
+      , sec.axis = sec_axis(trans = ~ .^2 / (4 + .^2), name = bquote(eta[G]^2), breaks = function(x) { b <- seq(0, (2*sqrt(x[2]))/sqrt(1 - x[2]), 0.1); b^2 / (4 + b^2) }, labels = printp)
+    ) +
+    scale_y_continuous(
+      name = bquote(1 - beta)
+      , breaks = function(x) seq(0.05, 0.95, 0.15)
+      , labels = function(...) printp(..., digits = 2)
+    ) +
+    scale_color_viridis_c(
+      name = bquote(rho)
+      , end = 0.9
+      , guide = guide_colorbar(title.position = "top", title.hjust = 0.5, direction = "vertical", barheight = unit(75, "pt"), barwidth = unit(12, "pt"), reverse = TRUE)
+      , limits = c(-1, 1)
+    ) +
+    facet_grid(~ test, labeller = label_parsed) +
+    guides(linetype = FALSE) +
+    coord_flip(ylim = c(0.05, 1)) +
+    papaja::theme_apa(box = TRUE) +
+    theme(
+      legend.position = c(0, 0.88)
+      , legend.justification = c(0, 1)
+      , legend.background = element_blank()
+      , plot.title = element_text(margin = margin(b = rel(5)))
+      , strip.text.x = element_text(margin = margin(b = rel(10)))
+      , panel.grid.major.y = element_line(linetype = "22")
+    )
+```
+
 ## Mixed model analysis
@@
 To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
-Hence, larger values represent more favorable implicit evaluations.
+Hence, larger values represent more favorable indirect evaluations.
 
@@
 otm1_results_legend <- guide_legend(
-    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
-    title = expression(atop("Valence order", atop(scriptstyle("Learned behaviors"), scriptstyle("(Briefly presented USs)"))))
+    title = expression(atop("Valence order", atop(scriptstyle("Behavioral information"), scriptstyle("(Briefly flashed words)"))))
     , title.position = "top"
@@
 
+```{r explore-salience-asymmetry, eval = FALSE}
+# Main effect of response mapping is significant for both image types
+otm1_iat_lmerTest %>%
+  emmeans(specs = ~ Congruent | imageType, at = list(imageType = c(-1, 1))) %>%
+  pairs()
+```
+
 (ref:otm1-lmer-random-effects-caption) Random effect estimates and correlations of the linear mixed model analysis of standardized IAT response times.
@@
 
-<!-- (ref:otm1-iat-lmer-contrasts) Planned contrasts of changes in congruency effects across learning blocks for the linear mixed model analysis of standardized IAT response times. -->
-
 ```{r otm1-lmer-emm-2, cache = TRUE, results = "asis"}
@@
   apa_print
-
-# otm1_iat_lmer_contrasts %$%
-#   table %>%
-#   rename("Valence order" = contrast) %>%
-#   apa_table(
-#     caption = "(ref:otm1-iat-lmer-contrasts)"
-#     , escape = FALSE
-#     , row.names = FALSE
-#   )
-```
-
-In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the learned behaviors were first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
+```
+
+In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the behavioral information was first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
 Vice versa, response time differences suggested more favorable evaluations after the second than after the first block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
-Again, these results indicate that the explicit evaluations and IAT scores were consistent.
+Again, these results indicate that the self-reported evaluations and IAT scores were consistent.
 
@@
 
-# Bayesian model comparison
+## Bayesian model comparison
 
@@
 
-#### Explicit and implicit measures
+#### Direct and indirect evaluations
 
@@
 
-```{r load-data-and-design-matrices}
-tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-restructure_", recursive = TRUE)[1]))
-tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-design-matrix_", recursive = TRUE)[1]))
-
+```{r otm1-prior-sensitivity-replication, cache = TRUE, warning = FALSE}
+manuscript_cache <- "manuscript_cache/latex/"
+
+otm1_attitudes_collapsed <- knitr::load_cache(label = "otm1-bayesian-replication-restructure", object = "otm1_attitudes_collapsed", path = manuscript_cache)
 otm1_n <- as.integer(nlevels(otm1_attitudes_collapsed$ParticipantNumber))
-```
-
-```{r otm1-prior-sensitivity-replication, cache = TRUE, warning=FALSE}
+
+otm1_null_model_matrix <- knitr::load_cache(label = "otm1-bayesian-replication-design-matrix", object = "otm1_null_model_matrix", path = manuscript_cache)
+otm1_unconstrained_model_matrix <- knitr::load_cache(label = "otm1-bayesian-replication-design-matrix", object = "otm1_unconstrained_model_matrix", path = manuscript_cache)
+
 replication_rscales <- expand.grid(
@@
 
-## Prime recogniton and implicit evaluations
+## Word recogniton and indirect evaluations
 
@@
   geom_violin(alpha = 0.3) +
-  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
   geom_sina(alpha = 0.5, size = 1) +
-  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
   stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
-  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
-  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
   scale_shape_manual(values = c(21, 23, 24)) +
@@
     x = "Location"
-    , y = "US recognition accuracy"
+    , y = "Recognition accuracy"
   ) +
@@
 
-In contrast to the original results reported by @rydell_two_2006, US recognition accuracy in this study was above chance, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
-Memory for USs may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
-We, therefore, performed an exploratory regression analysis of US recognition and the IAT score difference between blocks used in the Bayesian analysis above.
-Positive values represent a more favorable evaluation after the block in which Bob was paired with positive learned behaviors and briefly presented negative USs.
-Conversely, negative IAT score difference between blocks indicate that the IAT effects reflect the valence of the briefly presented USs.
-If US recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between US recognition accuracy and IAT score differences between blocks:
-When US recognition is high, IAT score differences should reflect the valence of the learned behaviors but not with the US valence.
-We would expect to observe smaller and eventually negative IAT score differences as US recognition accuracy declines and associative learning takes over.
-
-(ref:prime-recognition-iat-difference) Scatterplot of prime recognition accuracy and evaluative differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
+In contrast to the original results reported by @rydell_two_2006, the recognition accuracy of briefly flashed words was above chance  in this study, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
+Memory for these words may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
+We, therefore, performed an exploratory regression analysis of the recognition accuracy of briefly flashed words and the IAT score difference between blocks used in the Bayesian analysis above.
+Positive IAT score differences represent a more favorable evaluation after the block in which Bob was paired with positive behavioral information and briefly flashed negative words.
+Conversely, negative IAT score differences between blocks indicate that the IAT effects reflect the valence of the briefly flashed words.
+If word recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between the recognition accuracy and IAT score differences between blocks:
+When the recognition for briefly flashed words is high, IAT score differences should reflect the valence of the behavioral information but not with the word valence.
+We would expect to observe smaller and eventually negative IAT score differences as the recognition accuracy declines and associative learning takes over.
+To account for measurement error in the recognition accuracy of briefy flashed words we fit an errors-in-variable regression model [@Klauer_Draine_Greenwald_1998].
+Because the model assumes that predictor values are sampled from a Gaussian distribution truncated at 0, we probit-transformed the recognition accuracy.^[A standard linear regression analysis yielded the same results.]
+
+(ref:prime-recognition-iat-difference) Scatterplot of the recognition accuracy of briefly flashed words (on probit scale) and evaluative differences in IAT scores between learning blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
+The regression line and confidence band represents predictions of the errors-in-variables model [@Klauer_Draine_Greenwald_1998].
 
@@
   ggplot(aes(x = Accuracy, y = delta)) +
-  geom_hline(yintercept = 0, linetype = "dotted") +
-  geom_vline(xintercept = 0.5, linetype = "dotted") +
+  geom_hline(yintercept = 0, linetype = "22") +
+  geom_vline(xintercept = 0.5, linetype = "22") +
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", color = "black") +
+  geom_smooth(method = "eiv_lm", color = "black") +
   labs(
-    x = "US recognition accuracy"
+    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
     , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
   ) +
+  scale_x_continuous(trans = "probit") +
   theme_apa()
@@
 ```{r prime-recognition-iat-difference-regression, results = "asis"}
-otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
+otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
   filter(Measure == "IATscore") %>%
-  mutate(Accuracy = Accuracy - 0.5) %>%
-  as.data.frame %>%
-  lmBF(delta ~ Accuracy, data = .) %>%
+  mutate(Accuracy = qnorm(Accuracy)) %>%
+  eiv_lm(delta ~ Accuracy, data = ., n.optim = 10) %>% 
   apa_print
-
-otm1_iat_delta_lm_res <- otm1_iat_delta %>%
-  filter(Measure == "IATscore") %>%
-  mutate(Accuracy = Accuracy - 0.5) %>%
-  lm(delta ~ Accuracy, data = .) %>% 
-  apa_print
-```
-
-However, we were unable to detect any relationship between US recognition accuracy and IAT score differences between blocks, `r otm1_iat_delta_lm_res$full_result$Accuracy`; the data even provide some evidence against such a relationship, `r otm1_recognition_iat_lm_bf$statistic`.
-We centered US recognition at .5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance US recognition accuracy, `r otm1_iat_delta_lm_res$full_result$Intercept`.
-Hence, even for participants who exhibited no memory for briefly presented USs, IAT score differences reflected the valence of the learned behaviors, see Figure\ \@ref(fig:prime-recognition-iat-difference).
-These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance US recognition accuracy in this study.
-
-<!--
-#### Prime valence memory
-
-TODO TH: Is this supposed to be in the paper? 
-TH: No - maybe not even online supplement?
-
-```{r listPrimes, echo = FALSE, eval=FALSE}
-
-# correct names of primes
-eng_pos <- c("Flower",
-            "Friend",
-            "Gift",
-            "Happy",
-            "Puppy",
-            "Pretty",
-            "Party",
-            "Kiss",
-            "Kitten",
-            "Smile")
-
-eng_neg <- c("Corpse",
-            "Death",
-            "Hell",
-            "Pain",
-            "War",
-            "Hurt",
-            "Spider",
-            "Stink",
-            "Trash",
-            "Ugly")
-
-nl_pos <- c("Bloem",
-            "Vriend",
-            "Geschenk",
-            "Blij",
-            "Puppy",
-            "Mooi",
-            "Feest",
-            "Kus",
-            "Katje",
-            "Glimlach")
-
-nl_neg <- c("Lijk",
-            "Dood",
-            "Hel",
-            "Pijn",
-            "Oorlog",
-            "Letsel",
-            "Spin",
-            "Stank",
-            "Afval",
-            "Lelijk")
-
-ger_pos <- c("Blume",
-            "Freund",
-            "Geschenk",
-            "Glücklich",
-            "Welpe",
-            "Hübsch",
-            "Party",
-            "Kuss",
-            "Kätzchen",
-            "Lächeln")
-
-ger_neg <- c("Leiche",
-            "Tod",
-            "Hölle",
-            "Schmerz",
-            "Krieg",
-            "Verletzung",
-            "Spinne",
-            "Gestank",
-            "Abfall",
-            "Hässlich")
-
-# prep data frame to correspond with correct names
-
-otm1_mem$chosenItems <- gsub("\\r", "", otm1_mem$chosenItems, fixed = TRUE)
-otm1_mem$chosenItems <- gsub("u'", "", otm1_mem$chosenItems) 
-otm1_mem$chosenItems <- gsub("'", "", otm1_mem$chosenItems) 
-otm1_mem$chosenItems <- gsub("\\", "", otm1_mem$chosenItems, fixed = TRUE)
-otm1_mem$chosenItems <- gsub("ï»¿", "", otm1_mem$chosenItems) 
-otm1_mem$chosenItems <- gsub("[", "", otm1_mem$chosenItems, fixed = TRUE) 
-otm1_mem$chosenItems <- gsub("]", "", otm1_mem$chosenItems, fixed = TRUE)
-
-otm1_mem$chosenItems <- gsub("xfc", "ü", otm1_mem$chosenItems) 
-otm1_mem$chosenItems <- gsub("xe4", "ä", otm1_mem$chosenItems) 
-otm1_mem$chosenItems <- gsub("xf6", "ö", otm1_mem$chosenItems) 
-otm1_mem$chosenItems <- gsub("xdf", "ß", otm1_mem$chosenItems)
-
-otm1_mem <- separate(otm1_mem, 
-                     col = "chosenItems", 
-                     into = paste0("chosen", 1:20), 
-                     sep = ", ")
-
-pos <- c(eng_pos, nl_pos, ger_pos)
-neg <- c(eng_neg, nl_neg, ger_neg)
-otm1_mem$poscor <- 0
-otm1_mem$negcor <- 0
-
-for(i in 1:20){
-  otm1_mem$poscor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% pos, otm1_mem$poscor + 1, otm1_mem$poscor + 0)
-  otm1_mem$negcor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% neg, otm1_mem$negcor + 1, otm1_mem$negcor + 0)
+```
+
+We did not detect a relationship between the recognition accuracy of briefly preseted words and IAT score differences between learning blocks, `r otm1_iat_delta_eiv_lm_res$full_result$Accuracy`.
+Moreover, the positive intercept of the regression line indicates a positive IAT score difference despite at-chance word recognition accuracy, `r otm1_iat_delta_eiv_lm_res$full_result$Intercept`.
+Hence, even for participants who exhibited no memory for briefly flashed words, IAT score differences reflected the valence of the behavioral information, see Figure\ \@ref(fig:prime-recognition-iat-difference).
+These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance recognition of briefly flashed words in this study.
+
+# Experiment 2
+
+In the following we report the details of our a priori power analysis, provide details for the model specification used for the Bayesian model comparisons, and additional secondary analyses.
+
+## Power analysis
+
+As for Experiment 1, our power analyses focuses on this interaction and the theoretically relevant simple effects of *learning block*.
+We estimate the sensitivity of our design using the R-package *Superpower* [@R-Superpower] for the contrast analyes using the R-package *emmeans* [@R-emmeans].
+@rydell_two_2006 found the smallest learning block difference for IAT scores, $\hat\eta_p^2 = `r printp(rydell_pes)`$, $d_z \approx `r rydell_dz`$.
+The learning block differences reported by @heycke_two_2018 were of similar magnitude but with an opposite sign.
+
+```{r otm2-omnibus-power, cache = TRUE}
+# Main effect block and three-way interaction
+otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
+  contrast_codes <- tibble::tibble(
+    time = rep(contr.treatment(2), 4)
+    , order = rep(rep(contr.sum(2), each = 2), 2)
+    , block = rep(contr.sum(2), each = 4)
+    , time_block = time * block
+    , time_order = time * order
+    , block_order = block * order
+    , time_block_order = time * block * order
+  )
+
+  mu <- with(
+    contrast_codes
+    , -block_order * f +
+      -block * 0.5 * f +
+      time_block_order * f
+  )
+
+  string <- "2w*2b*2b"
+  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")
+
+  design_result <- ANOVA_design(
+    design = string
+    , n = n
+    , mu = mu
+    , sd = 1
+    , r = rm_cor
+    , labelnames = labelnames
+  )
+
+  ANOVA_exact(
+    design_result
+    , alpha_level = alpha_level
+    , emm = FALSE
+    , verbose = FALSE
+  )
 }
 
-aggregate(negcor ~ Location, data = otm1_mem, FUN = mean)
-aggregate(poscor ~ Location, data = otm1_mem, FUN = mean)
-
-t.test(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)
-ttestBF(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)
-
-t.test(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)
-ttestBF(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)
-
-t.test(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)
-ttestBF(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)
-
-```
--->
+otm2_n <- 320/4
+
+# 95% power
+otm2_pes <- 0.03973071
+otm2_dz <- pes_to_dz(otm2_pes, otm2_n, n_groups = 4)
+rho <- 0.5
+f <- dz_to_f(otm2_dz, rho)
+
+# otm2_time_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho, alpha = 0.05)
+# otm2_time_power$main_result
+
+otm2_dz_block <- f_to_dz(0.5*f, rho = rho)
+otm2_pes_block <- dz_to_pes(otm2_dz_block, otm2_n, n_groups = 4)
+
+otm2_dz_int <- f_to_dz(f, rho = rho)
+otm2_pes_int <- dz_to_pes(otm2_dz_int, otm2_n, n_groups = 4)
+```
+
+```{r otm2-contrast-power, cache = TRUE}
+otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
+  contrast_codes <- tibble::tibble(
+    time = rep(contr.treatment(2), 4)
+    , order = rep(rep(contr.sum(2), each = 2), 2)
+    , block = rep(contr.sum(2), each = 4)
+    , time_block = time * block
+    , time_order = time * order
+    , block_order = block * order
+    , time_block_order = time * block * order
+  )
+
+  mu <- with(
+    contrast_codes
+    , -order * 0.25*f +
+      -block_order * f
+  )
+
+  string <- "2w*2b*2b"
+  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")
+
+  design_result <- ANOVA_design(
+    design = string
+    , n = n
+    , mu = mu
+    , sd = 1
+    , r = rm_cor
+    , labelnames = labelnames
+  )
+
+  ANOVA_exact(
+    design_result
+    , alpha_level = alpha_level
+    , emm = TRUE
+    , verbose = FALSE
+    , contrast_type = "pairwise"
+    , emm_comp = "block | time * order"
+  )
+}
+
+# Learning block contrasts
+
+## Simple contrasts
+### 95% power
+otm2_pes <- 0.03973071
+otm2_dz <- pes_to_dz(otm2_pes, otm2_n, n_groups = 4)
+# rho <- 0.5
+# f <- dz_to_f(otm2_dz, rho)
+# 
+# otm2_contrast_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_contrast_power
+
+### 80% power
+otm2_pes2 <- 0.0243813
+otm2_dz2 <- pes_to_dz(otm2_pes2, otm2_n, n_groups = 4)
+# f <- dz_to_f(otm2_dz2, rho)
+# 
+# otm2_contrast_power2 <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_contrast_power2
+
+## Collapsed once
+### 95% power
+otm2_dz_between_collapsed <- f_to_dz(dz_to_f(otm2_dz, rho) / sqrt(2), rho)
+otm2_pes_between_collapsed <- dz_to_pes(otm2_dz_between_collapsed, otm2_n, n_groups = 4)
+# f <- dz_to_f(otm2_dz_between_collapsed, rho)
+# 
+# otm2_time_collapsed_contrast_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block | order) %>%
+#   pairs %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_time_collapsed_contrast_power
+
+### 80% power
+otm2_dz2_between_collapsed <- f_to_dz(dz_to_f(otm2_dz2, rho) / sqrt(2), rho)
+otm2_pes2_between_collapsed <- dz_to_pes(otm2_dz2_between_collapsed, otm2_n, n_groups = 4)
+# f <- dz_to_f(otm2_dz2_between_collapsed, rho)
+# 
+# otm2_time_collapsed_contrast_power2 <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block | order) %>%
+#   pairs %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_time_collapsed_contrast_power2
+
+## Collapsed twice
+### 95% power
+otm2_dz_collapsed <- f_to_dz(dz_to_f(otm2_dz, rho) / sqrt(4), rho)
+otm2_pes_collapsed <- dz_to_pes(otm2_dz_collapsed, otm2_n, n_groups = 4)
+# f <- dz_to_f(otm2_dz_collapsed, rho)
+# 
+# otm2_collapsed_contrast_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block * order) %>%
+#   contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>%
+#   emmeans_power(alpha_level = 0.05)
+# otm2_collapsed_contrast_power
+
+### 80% power
+otm2_dz2_collapsed <- f_to_dz(dz_to_f(otm2_dz2, rho) / sqrt(4), rho)
+otm2_pes2_collapsed <- dz_to_pes(otm2_dz2_collapsed, otm2_n, n_groups = 4)
+# f <- dz_to_f(otm2_dz2_collapsed, rho)
+# 
+# otm2_collapsed_contrast_power2 <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block * order) %>%
+#   contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>%
+#   emmeans_power(alpha_level = 0.05)
+# otm2_collapsed_contrast_power2
+```
+
+Across all locations we will recruit N = 320 participants (not including participants from the pilot study).
+To maximize the power of the planned contrasts, we will test whether valence order moderates the learning block contrasts by testing the main effect of learning block ($\alpha = \beta = .05$ for $\delta_z = `r otm2_dz_block`$ and $N = 320$).
+If we detect no main effect of learning block, we will pool participants across valence orders by reversing the learning block coding in one group (as in the Bayesian model comparison of Experiment 1).
+Similarly, if the different prime presentation durations do not moderate the learning block contrasts, we will pool participants across presentation durations ($\alpha = \beta = .05$ for $\delta_z = `r otm2_dz_int`$ and $N = 320$).
+This analysis plan results in four possible contrast analyses of the learning blocks: (1) 4 learning block contrasts by valence order and presentation duration, (2) 2 learning block contrasts collapsed across valence orders but separate for presentation durations, (3) 2 learning block contrasts collapsed across presentation durations but separate for valence orders, and (4) 1 learning block contrasts collapsed across valence orders and presentation durations.
+
+The data from all locations (N = 320, not including participants from the pilot study) provides 95% power to detect learning block differences as small as $\eta^2_p = `r printp(otm2_pes)`$ ($\delta_z = `r otm2_dz`$) or as small as $\eta^2_p = `r printp(otm2_pes_between_collapsed)`$ ($\delta_z = `r otm2_dz_between_collapsed`$) and $\eta^2_p = `r printp(otm2_pes_collapsed)`$ ($\delta_z = `r otm2_dz_collapsed`$) when pooling participants across one or both between-participant factors ($\alpha = .05$).
+Thus, our design is sufficiently sensitive to detect (or rule out) differences `r round((1 - otm2_dz/rydell_dz) * 100)`% smaller (`r round((1 - otm2_dz_between_collapsed/rydell_dz) * 100)`% or `r round((1 - otm2_dz_collapsed/rydell_dz) * 100)`% when pooling participants across one or both between-participant factors, respectively) than the smallest learning block difference reported by @rydell_two_2006.
+Figure\ \@ref(fig:otm2-power-curves) illustrates the implied sensitivity in units of Cohen's $\delta$ depending on the assumed repeated-measures correlation $\rho$.
+
+(ref:otm2-power-curves) Sensitivity curves for learning block contrasts in Experiment 2 depending on the assumed repeated measures correlation.
+Simple contrast are estimated within each *flashed word presentation duration*-*valence order* combination (not adjusted for multiple comparisons).
+Collapsed contrasts pool participants across one or both  of the between subject factors (i.e., *flashed word presentation duration* and *valence order*).
+$\delta_z$-values in the legend correspond to 95% and 80% power.
+The grey dashed line at the top represents the smallest estimate of the learning block difference reported by Rydell et al. [$d_z = 0.47$; -@rydell_two_2006].
+
+```{r otm2-power-curves, fig.width = 7, fig.height = 4, fig.cap = "(ref:otm2-power-curves)"}
+rydell_power_curve <- tibble(
+  rho = seq(-1, 1, length.out = 100)
+  , delta = c(
+    dz_to_f(rydell_dz, unique(rho)) * 2
+  )
+  , power = NA
+)
+
+otm1_power_curve <- tibble(
+  rho = rep(seq(-1, 1, length.out = 100), 2)
+  , delta = c(
+    dz_to_f(otm1_dz, unique(rho)) * 2
+    , dz_to_f(otm1_dz2, unique(rho)) * 2
+  )
+  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
+)
+
+tibble(
+  rho = rep(seq(-1, 1, length.out = 100), 2)
+  , otm2_delta_simple = c(
+    dz_to_f(otm2_dz, unique(rho)) * 2
+    , dz_to_f(otm2_dz2, unique(rho)) * 2
+  )
+  , otm2_delta_between_collapsed = c(
+    dz_to_f(otm2_dz_between_collapsed, unique(rho)) * 2
+    , dz_to_f(otm2_dz2_between_collapsed, unique(rho)) * 2
+  )
+  , otm2_delta_collapsed = c(
+    dz_to_f(otm2_dz_collapsed, unique(rho)) * 2
+    , dz_to_f(otm2_dz2_collapsed, unique(rho)) * 2
+  )
+  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
+) %>% 
+  pivot_longer(cols = matches("otm"), names_to = "contrast", values_to = "delta") %>%
+  mutate(
+    power = relevel(factor(power), "0.95")
+    , contrast = gsub("otm2_delta_", "", contrast)
+    , contrast = gsub("_", " ", contrast)
+    , contrast = factor(contrast, levels = c("simple", "between collapsed", "collapsed"))
+  ) %>% 
+  ggplot(aes(x = rho, y = delta, color = contrast, group = interaction(power, contrast), linetype = power)) +
+  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
+  geom_line() +
+  scale_color_viridis_d(
+    end = 0.8
+    , labels = c(
+      bquote("Simple                 "~delta[z] %in% "{"*.(printnum(otm2_dz))*", "*.(printnum(otm2_dz2))*"}")
+      , bquote("Collapsed once   "~delta[z] %in% "{"*.(printnum(otm2_dz_between_collapsed))*", "*.(printnum(otm2_dz2_between_collapsed))*"}")
+      , bquote("Collapsed twice   "~delta[z] %in% "{"*.(printnum(otm2_dz_collapsed))*", "*.(printnum(otm2_dz2_collapsed))*"}")
+    )
+  ) +
+  ylim(c(0, 1)) +
+  labs(
+    x = bquote("Correlation between learning blocks ["*rho*"]")
+    , y = bquote("Learning block difference [Cohen's"~delta*"]")
+    , color = "Contrast"
+    , linetype = bquote("Power"~"["*1 - beta*"]")
+  ) +
+  ggtitle("", subtitle = bquote(list(alpha ==~".05", italic(N) == .(otm2_n*4)))) +
+  theme_apa(box = TRUE) + 
+  theme(
+    panel.grid.major.x = element_line()
+    , panel.grid.major.y = element_line()
+    , panel.grid.minor.x = element_line()
+    , panel.grid.minor.y = element_line()
+    , legend.justification = "top"
+  )
+```
+
+```{r create_r-references}
+r_refs(file = "r-references.bib")
+```
 

### 2020-06-15 analysis_and_paper/error_in_variables.R
Added via the Open Science Framework

@@ -1,0 +1,338 @@
+################################################################################
+###
+### Klauer, K. C., Draine, S. C., & Greenwald, A. G. (1998).
+### An unbiased errors-in-variables approach to detecting unconscious cognition.
+### British Journal of Mathematical and Statistical Psychology, 51(2), 253–267.
+### doi:10.1111/j.2044-8317.1998.tb00680.x
+###
+### R code: Daniel W. Heck (heck@uni-mannheim.de)
+### Contact: Simone Malejka (s.malejka@ucl.ac.uk)
+###
+################################################################################
+
+## regression correction
+## usage: fit(data)
+## data: data frame with variables x (predictor) and y (criterion)
+## (cs)
+
+
+# library("minqa")
+# library("numDeriv")
+
+## only needed for simulations:
+#library("parallel")
+
+### Log-likelihood function on p. 258
+eiv_loglik <- function(par, dv, iv, const=1e20) {
+  mu <- par[1]
+  sigma <- par[2]
+  sx <- par[3]
+  sy <- par[4]
+  beta <- par[5]
+  alpha <- par[6]
+  
+  x <- iv
+  y <- dv
+  
+  nu <- (sy * sigma)^2 + (beta * sx * sigma)^2 + (sx * sy)^2
+  xi <- 1/sqrt(nu) * (x * sy/sx * sigma + beta * (y - alpha) * sx/sy * sigma +
+                        mu * sx * sy / sigma)
+  gamma <- x^2 / sx^2 + (y - alpha)^2 / sy^2 + mu^2 / sigma^2
+  
+  f <- 1/(2*pi*sqrt(nu)) * exp(-1/2 * (gamma - xi^2)) * (1 - pnorm(-xi)) +
+    1/(2*pi * sx * sy) * exp(-1/2 * (gamma - (mu/sigma)^2)) * pnorm(-mu / sigma)
+  
+  ll <- - sum(log(f))
+  if(ll == Inf || is.na(ll))
+    ll <- const
+  ll
+}
+
+### Maximum-likelihood estimation
+eiv_lm <- function(formula, data, start=NULL, n.optim=3, ...) {
+  vars <- all.vars(formula)
+  
+  data <- model.frame(formula, data, ...)
+  
+  if (missing(start) || is.null(start))
+    start <- runif(6, c(-1, 0, 0, 0, -.2, -.2), c(1, 3, 3, 3, .2, .2))
[…]

### 2020-12-03 analysis_and_paper/manuscript.Rmd
Corrects some paths and knitts analysis for experiment 1 and supplements.
Adds updated files following IPA at PS.

@@
   - name          : Tobias Heycke
-    affiliation   : 1, 2
+    affiliation   : "1,2"
     corresponding : yes    
     address       : "P.O. 122155, 68072 Mannheim, Germany"
-    email         : "tobias.heycke@gesis.org"
+    email         : "tobias.heycke@gmail.com"
+    equal_contrib : yes
   - name          : Frederik Aust
-    affiliation   : 1
+    affiliation   : "1,9"
+    equal_contrib : yes
   - name          : Mahzarin R. Banaji
     affiliation   : 3
+  - name          : Jeremy Cone
+    affiliation   : 8
   - name          : Pieter Van Dessel
     affiliation   : 5
+  - name          : Melissa J. Ferguson
+    affiliation   : 10
   - name          : Xiaoqing Hu
@@
   - name          : Benedek Kurdi
-    affiliation   : 3    
+    affiliation   : "3,10"
   - name          : Robert Rydell
@@
     institution   : Indiana University
-
-abstract: |
-  Findings of dissociations between implicit (i.e., automatic) and explicit (i.e., non-automatic) evaluations that are based on distinct associative (i.e., co-occurrence based) and propositional (i.e., rule-based) learning procedures have fueled the dominance of dual-process theories of evaluative learning for decades.
-Arguably the most influential evidence has been found in a study by Rydell, McConnell, Mackie, and Strain (2006) in which participants learned about a person named Bob.
-It was observed that implicit evaluations reflected the valence of brief pairings of valenced words with the image of Bob whereas explicit evaluations reflected the (opposite) valence of the behavioral statements that were instructed to be characteristic of Bob.
-A recent study by Heycke and colleagues (2018) was unable to reproduce this data pattern independently.
-Given the theoretical importance of the findings by Rydell and colleagues, we present a series of additional replication attempts conducted by an international collective of researchers including the first author of the original finding.
+  - id            : 8
+    institution   : Williams College
+  - id            : 9
+    institution   : University of Amsterdam
+  - id            : 10
+    institution   : Yale University
+
+abstract: "(ref:abstract)"
 
 authornote: |
-  All data, analysis scripts and materials can be found at https://osf.io/8m3xb/
-
-keywords          : "evaluative conditioning, subliminal influence, implicit learning, replication"
+  All data, analysis scripts and materials are available at https://osf.io/8m3xb/; the supplementary online material (SOM) is available at https://osf.io/8w9bd/.
+
+note: |
+  \clearpage
+
+keywords          : "evaluative learning, subliminal influence, implicit learning, replication"
 #wordcount         : "X"
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 draft             : no
+quote_labels      : yes
+
+link-citations    : yes
+linkcolor         : blue
+urlcolor          : blue
 
@@
 library("MBESS")
+library("effectsize")
+library("Superpower")
 
@@
 source("modal_frame_rate.R")
+source("effect_sizes.R")
+source("apa_print_ps.R")
 ```
@@
 
-<!--
-Guideline:
-Authors of a PDR must make a convincing case that the replication will make a valuable contribution to understanding a phenomenon and/or theory of broad current interest to psychologists.
-As with all Psychological Science submissions, the primary criterion is general theoretical significance.
-Direct replications should reproduce the original methods and procedures as closely as possible, with the goal of measuring the same effect under essentially (but not necessarily superficially) the same conditions as in the original study
-
-Word limit: 
-Intro + Discussion + notes + acknowledgements + appendices = 1500
-
-Max Figures/tables:
-3
-
-Max references:
-30
--->
-
-Evaluative conditioning (EC) refers to the robust finding of a change in liking of a stimulus, referred to as conditioned stimulus (CS), that is due to its pairing with a stimulus of positive or negative valence, referred to as unconditioned stimulus (US) [@dehouwerConceptualTheoreticalAnalysis2007; @hofmannEvaluativeConditioningHumans2010].
-Dual-process theories postulate that EC can depend both on a mechanism via which co-occurrences between stimuli result in the automatic formation of mental associations as well as a second mechanism via which propositional beliefs are formed [e.g., @gawronskiAssociativePropositionalProcesses2006; @rydellUnderstandingImplicitExplicit2006].
-Though dual-process theories have had a huge impact, it has been argued that there is actually little evidence for automatic association formation as a distinct mechanism for EC [see @corneilleAssociativeAttitudeLearning2018a].
-This conclusion is in line with propositional single-process views [e.g., @mitchellPropositionalNatureHuman2009] which postulate that all associative (evaluative) learning (including EC) is based on propositional processes.
-
-One finding, however, is particularly difficult to reconcile with propositional single-process accounts: 
-@rydell_two_2006 reported that participants exhibited conflicting explicit and implicit evaluations (e.g., positive explicit and negative implicit evaluations) of a single target person after the presentation of rapid stimulus-stimulus pairings and behavioral statements that implied the opposite valence.
-In this study, participants engaged in a learning task about a person named Bob in which they determined whether Bob was a good or bad person by guessing whether positive and negative behavioral statements were characteristic of Bob.
-They received feedback about the accuracy of each of their guesses.
-Unbeknownst to the participants, on each trial, a valent word (US) was presented briefly (25 ms) prior to the presentation of a picture of Bob and the behavioral statement. 
-Critically, the valence of the US words was always opposite to the behavioral information (e.g., USs were always positive when negative behavioral statements were characteristic of Bob).
-Following the learning task, explicit evaluations of Bob, assessed with a trait rating task, reflected the valence of the learned behavioral information, while implicit evaluations, assessed with an Implicit Association Test [IAT: @greenwaldMeasuringIndividualDifferences1998] reflected the valence of the USs.
-These results were conceptually replicated by the original authors using similar methods [@rydellConsequencesDiscrepantExplicit2008; @rydellUnderstandingImplicitExplicit2006].
-The @rydell_two_2006 article has been referred to as providing strong evidence for numerous dual-process theories [@gawronskiAssociativePropositionalEvaluation2011; @rydellUnderstandingImplicitExplicit2006] and has been cited more than 320 times overall (Google Scholar, 10.15.2019).
-
-Judging from its impact, the reported effect is generally assumed to be robust and replicable.
-A recent study, composed of two experiments, however, could not replicate the dissociative effect [@heycke_two_2018].
-Instead, both implicit and explicit evaluations consistently reflected the valence of the learned behavioral information.
-At present, it remains unclear whether these unsuccessful attempts call into question the replicability of the original study or point towards boundary conditions.
-This ambiguity is due to the modifications made to the original materials and procedure in the replication studies: First, some words were replaced to ensure that no words presented in the learning phase served as distractors in the US memory assessment at the end of the study [see @heycke_two_2018].
-Second, one experiment used German translations of the verbal material (rather than the original English material).
-Third, the other experiment, while using the original material, was conducted with a modified procedure: Because  a subset of participants correctly identified USs after the learning task in the first experiment, the presentation duration of USs was reduced from 25 ms to 16 ms to ensure at-chance post-learning US recognition.
-
-In the current study we will rigorously test the replicability of the original findings reported by @rydell_two_2006 by closely adhering to the original procedure.
-To ensure its informativeness, the current replication attempt was a joint effort that involved researchers from different labs that all have expertise in studying evaluative conditioning and implicit measures.
-Moreover, both the first author of the original study and authors of the unsuccessful replication attempts collaborated on the studies presented here.
-To explore the generality of our results, data were collected in multiple countries and languages.
-In a first, already concluded,  experiment we have conducted a close replication in three different locations. 
-In a second experiment, for which the data has not been collected yet, we will use the knowledge gained from the first experiment to adjust the procedure to closely replicate the psychological conditions of the original study.
+```{r load-sample-sizes}
+man_cache <- "manuscript_cache/latex/"
+otm1_n <- knitr::load_cache(label = "otm1-exclusion", object = "otm1_n", path = man_cache)
+otm2_n <- knitr::load_cache(label = "otm2-exclusion", object = "otm2_n", notfound = "TBD", path = man_cache)
+```
+
+(ref:abstract) Several dual-process theories of evaluative learning posit two distinct implicit (or automatic) and explicit (or controlled) evaluative learning processes.
+As such, one may like a person explicitly but simultaneously dislike them implicitly.
+Dissociations between direct measures (e.g., Likert scales), reflecting explicit evaluations, and indirect measures (e.g., Implicit Association Test), reflecting implicit evaluations, support this claim.
+Rydell et al.
+(2006) found a striking dissociation when they brief flashed either positive or negative words prior to presenting a photograph of a person was with behavioral information of the opposite valence was presented: IAT scores reflected the valence of the flashed words whereas rating scores reflected the opposite valence of the behavioral information.
+A recent study, however, suggests that this finding may not be replicable.
+Given its theoretical importance, we report two new replication attempts ($n = `r otm1_n`$ recruited in Belgium, Germany and the USA; $n = `r otm2_n`$ recruited in Hong Kong and the USA).
+
+<@~{#intro-paragraph}
+
+Are our explicit and implicit evaluations of an object or person always consistent with one another?
+Or is it possible that we like a person explicitly but simultaneously dislike them implicitly?
+One way to investigate this question is to compare two families of evaluative measures: direct measures (e.g., Likert scales) that assumedly elicit relatively more explicit, conscious, effortful, and controllable evaluations (hereafter explicit evaluations), on the one hand, and indirect measures [such as the Implicit Association Test [IAT]; @greenwald_measuring_1998] that assumedly elicit relatively more implicit, unconscious, effortless, and uncontrollable evaluations (hereafter implicit evaluations), on the other hand.
+Indeed, several studies have shown dissociations between direct and indirect measures [see  @harmon-jones_what_2019]. 
+Such evidence has been critical in supporting dual-process theories positing that explicit and implicit evaluations reflect different sets of attitudes that are acquired via two distinct processes.[^attitude_definition]
+
+[^attitude_definition]:
+By *attitude* we mean latent knowledge representations that underlie the behavioral expression of *evaluations* on direct and indirect measures [@cunningham_attitudes_2007].
+
+~@>
+
+An influential dual-process theory is the Systems of Evaluation Model [SEM; @mcconnell_systems_2014; @mcconnell_forming_2008; @rydellUnderstandingImplicitExplicit2006]. 
+This theory assumes that implicit evaluations emerge from mental associations that develop without conscious awareness or control, from the co-occurrence of stimuli with valenced events.
+For example, positive associations may develop simply because a person repeatedly wears a shirt in one’s favorite color.
+In contrast, explicit evaluations are thought to reflect propositional representations that emerge from conscious, attention-demanding reasoning processes.
+For example, negative propositions may develop as a result of learning that the person holds political opinions that clash with one’s own views.
+Hence, under this theory, a double dissociation between direct and indirect measures of evaluation is expected, with the former reflecting only consciously formed propositions and the latter reflecting only unconsciously formed associations.
+
+As a test of this model, @rydell_two_2006 contrasted two different learning pathways experimentally.
+In the experiment, participants learned about an unfamiliar person called Bob.
+Each trial started with a brief (25 ms) flash of a positive or negative word, not intended to be consciously registered by participants.
+Then a photograph of Bob was presented alone for 250 ms before a positive or negative behavioral statement was added to the display.
+The statement was clearly visible until participants made a guess as to whether the behavior was characteristic or uncharacteristic of Bob.
+Participants immediately received feedback, which implied that Bob was a good or bad person.
+Crucially, this behavioral information was always opposite in valence to the briefly flashed word.
+In line with the predictions of the SEM, explicit evaluations of Bob, measured via self-report, reflected predominantly the valence of the behavioral information.
+More intriguingly, implicit evaluations, measured via the IAT, reflected predominantly the valence of the words that had been briefly flashed prior to the photograph of Bob.
+
+This finding has been influential in support of the SEM and other dual-process theories [e.g., @gawronskiAssociativePropositionalEvaluation2011]. 
+However, beyond this prominent result, empirical evidence for dual evaluative learning processes remains weak overall [@corneilleAssociativeAttitudeLearning2018a]. 
+The absence of compelling evidence that implicit evaluations emerge from unconsciously formed associations has allowed for a different, more parsimonious, account to be popularized: that both implicit and explicit evaluations reflect propositional knowledge [e.g., @de_houwer_propositional_2018].
+Crucially, many prominent single-process propositional theories assume that propositional learning requires conscious awareness [@mitchellPropositionalNatureHuman2009]. 
+As such, the result reported by @rydell_two_2006, where implicit evaluations reflected predominantly unconsciously formed associations, is particularly difficult to reconcile with these accounts.
+Under most propositional theories, both direct (self-report) measures and indirect measures (such as the IAT) should reflect propositional knowledge that emerges from conscious, attention-demanding reasoning processes.
+
+Given the theoretical issues at stake, a replication of the double dissociation reported by  @rydell_two_2006 is critical. 
+If the double dissociation is replicated, such a result would lend credence to strong forms of dual-process theories positing that implicit and explicit evaluations reflect different types of (associative and propositional) representations that are acquired via different learning pathways.
+Moreover, such a finding would provide evidence in favor of subliminal associative learning, a phenomenon for which current evidence is weak at best [@corneilleAssociativeAttitudeLearning2018a]. 
+On the other hand, if the finding by @rydell_two_2006 does not replicate, and both direct and indirect measures are found to reflect the valence of the consciously processed behavioral information, such a result would strengthen confidence in single-process propositional theories of evaluation.
+After all, these theories argue that both implicit and explicit evaluations largely reflect the same consciously formed propositions.
+
+In two recent experiments, the double dissociation reported by @rydell_two_2006 did not replicate [@heycke_two_2018]. 
+Instead, both direct and indirect measures consistently reflected the valence of the behavioral information.
+At present, it is unclear whether these results point towards boundary conditions or call into question the replicability of the original study more generally.
+This ambiguity is due to the fact that materials were translated into German and stimuli were presented for a duration different from the original study.
+Here, we rigorously test the replicability of the double dissociation by closely adhering to the original procedure.
+To ensure its informativeness, the current replication attempt was conducted jointly by an international collective of experts on evaluative learning and implicit measures.
+Among the collaborators were the first author of the original study and authors of the previous replication attempts.
+To explore the generality of our results, we collected data in multiple countries and languages.
+A first, already concluded, experiment was conducted in Belgium, Germany and the USA.
+In a second experiment, for which the data is yet to be collected, we will use the insights from the first experiment to adjust the procedure to closely replicate the psychological conditions of the original study.
 
@@
     rowwise %>%
-    do(data.frame(Eval = sum(unlist(.)))) %>% 
+    do(data.frame(Eval = mean(unlist(.)))) %>% 
     bind_cols(otm1_eval, .) %>%
@@
 
-As the results reported by @heycke_two_2018 could have been the result of the modifications to the experimental procedure, we conducted a replication study using the unmodified experimental procedure of the original study.
+Because the procedural modifications made by @heycke_two_2018 may have caused the diverging results, we conducted a replication study using the unmodified experimental procedure of the original study.
 
@@
 
-Materials and procedure were inspected by the first author of the original study to ensure that they closely corresponded to the original.
-The experiment was preregistered (https://osf.io/xe8au/) and data were collected in Germany, Belgium, and the United States.
-All data files, materials and analysis files are available at https://osf.io/8m3xb/.
+The first author of the original study verified that our materials and procedure faithfully reproduced the original.
+The experiment was preregistered (https://osf.io/xe8au/) and data were collected at the University of Cologne (Germany), Ghent University (Belgium), and Harvard University (USA).
+All data files, materials, and analysis scripts are available at https://osf.io/8m3xb/.
+To give a vivid impression of the experimental procedure, an examplary video recording is available at https://osf.io/hmcfg/.
 
@@
 
-The experimental procedure consisted of three components: learning task, evaluation task, and US recognition task.
+The experimental procedure consisted of three components: a learning task, evaluation task, and recognition task.
 
 As in the original study, the learning task was a modified version of the evaluative learning paradigm by @kerpelmanPartialReinforcementEffects1971. 
-We briefly presented a US followed by a longer presentation of a picture of Bob together with a statement that described the behavior of Bob.
-Presentation durations differed across labs due to the availability of different refresh rates of the CRT monitors (85 Hz in the United States and 75 Hz in Belgium and Germany).
+We briefly flashed a valent word followed by a longer presentation of a photograph of Bob together with a behavioral statement.
+Presentation durations differed across labs due to the availability of different refresh rates of the CRT monitors (85 Hz at Harvard and 75 Hz at Ghent and Cologne).
 In the following we will describe the setup of a trial with the presentation durations at a 75 Hz-refresh rate; deviating durations for a 85 Hz-refresh rate are given in brackets.
 
-On each trial, a central fixation cross was displayed for 200 ms followed by a US displayed for 27 ms (24 ms; 2 frames).
-USs were immediately replaced by the picture of Bob, which served as a backward mask.
-The picture of Bob was presented in the center of the screen for 253 ms (247 ms) before the behavioral information was added underneath.
-The screen background was black and text was colored white and set in Times New Roman font. 
-Participants’ task was to press the "c" (= "characteristic") or "u" (= "uncharacteristic") key to judge whether the behavioral information was characteristic or uncharacteristic of Bob, which was displayed on the screen during the judgment phase.
-After every judgment, the image of Bob, the behavioral statement, and the key labels were replaced with either the word "Correct" displayed in green letters or the word "False" in red letters, displayed for 5000 ms.
+On each trial, a central fixation cross was displayed for 200 ms followed by a valent word flashed for 27 ms (24 ms; 2 frames).
+The screen background was black and text was white and set in Times New Roman font. 
+The briefly flashed word was immediately replaced by the photograph of Bob, which served as a backward mask.
+Next, we provided behavioral information about Bob consisting of a behavioral statement and the additional information whether this behavior was characteristic or uncharacteristic of Bob.
+The photograph of Bob was presented in the center of the screen for 253 ms (247 ms) before a behavioral statement was added underneath.
+Participants’ task was to press the "c" (= "characteristic") or "u" (= "uncharacteristic") key to guess whether the behavioral statement was characteristic or uncharacteristic of Bob. 
+After every guess, the photograph of Bob, the behavioral statement, and the key labels were replaced with either the word "Correct" displayed in green letters or the word "False" in red letters, displayed for 5000 ms.
 Each trial ended with a blank screen presented for 1000 ms.
 
-As US valence was manipulated within participants, they completed two 100-trial-blocks of the learning task.
-Each block consisted of trials with either only positive or negative USs and the order of USs was randomized. 
-In blocks with positive USs, positive behavioral information was always uncharacteristic of Bob and negative information was characteristic. 
-These contingencies were reversed in the blocks with negative USs. 
-We used 10 positive and 10 negative words as USs each of which was presented 10 times. 
-For behavioral information, we used 100 positive and 100 negative statements. 
-50 positive and 50 negative statements were randomly selected for the first block, the remaining statements were assigned to the second block. 
-The order of USs and behavioral information was randomized for each participant anew, whereas the order of blocks was counterbalanced across participants. 
-A different picture of Bob was randomly selected from six pictures of white males for each participant. 
-The remaining five images were used in the implicit evaluation measure (see below). 
-All materials were taken from the original study, with the sole exception that US words, behavioral information, and instructions were translated to German and Dutch for use in Germany and Belgium.
-
-After each block, participants completed implicit and explicit evaluation measures. 
+As the valence of briefly flashed words was manipulated within participants, they completed two 100-trial-blocks of the learning task.
+Each block consisted of trials with either only positive or negative words and the order of the blocks was randomized.
+The valence of the behavioral information was always opposite to the valence of the briefly flashed word.
+In blocks with positive words, positive behavioral statements were uncharacteristic of Bob and negative statements were characteristic.
+These contingencies were reversed in the blocks with negative words. 
+We used 10 positive and 10 negative words; each of which was presented 10 times. 
+For behavioral statements, we used 100 positive and 100 negative statements; 50 positive and 50 negative statements were randomly selected for the first block, the remaining statements were assigned to the second block.
+The order of briefly flashed words and behavioral information was randomized for each participant anew, whereas the order of blocks was counterbalanced across participants. 
+A different photograph of Bob was randomly selected from six photographs of white males for each participant. 
+The remaining five images were used in the implicit association test (see below). 
+All materials were taken from the original study[^discrpaper], with the sole exception that briefly flashed words, behavioral statements, and instructions were translated to German and Dutch for use in Germany and Belgium.
+
+[^discrpaper]:
+The original manuscript lists the words  "love", "party", "hate", and "death" as examples for briefly flashed words.
+The words "hate" and "love", however, were neither used as briefly flashed words in the original, nor our replication studies.
+
+After each block, we measured evaluations of Bob directly and indirectly using Likert-scale ratings and the IAT, respectively.
 As in the original study, the order of the measures was the same for both blocks but counterbalanced across participants.
 
-The explicit evaluation consisted of three parts, each presented on a single screen:
+As direct measure of evaluation, we used three rating scales:
 First, participants rated Bob's likableness on a 9-point slider with the anchors labelled *Very Unlikable* and *Very Likable*.
@@
 Finally, they judged Bob on a 'feeling thermometer' by entering a number between 0 (*Extremely unfavorable*) and 100 (*Extremely favorable*).
-Deviating from the original protocol, we collected explicit evaluations as part of the computer task rather than using a paper-pencil questionnaire.
-
-We assessed the implicit evaluations using the IAT described by @rydell_two_2006. 
+Deviating from the original protocol, we collected rating scale responses as part of the computer task rather than using a paper-pencil questionnaire.
+
+As indirect measure of evaluation, we used an IAT. 
 Participants initially completed two types of training blocks with 20 trials each to familiarize themselves with the task.
@@
 not-Bob with reversed key position and afterwards a second critical block with 40 trials with the reversed key mapping compared to the first critical block.
-It was counterbalanced whether participants completed the IAT with the key mappings described above or with key mappings in reversed order [for a detailed description see @heycke_two_2018, p. 1712].
-
-After completing the explicit and implicit evaluation measures, participants completed the second learning block and again completed implicit and explicit evaluations.
-Following the second set of evaluations, participants completed a surprise US recognition task.
+It was counterbalanced whether participants completed the IAT as described above or with key mappings in reversed order [for a detailed description see @heycke_two_2018, p. 1712].
+We instructed participants to respond quickly without making too many errors.
+In case of erroneous responses we displayed a red X as feedback and instructed participants to quickly correct their response to start the next trial.
+
+Following the first round of evaluations, participants completed the second learning block and again evaluated Bob directly and indirectly.
+After the second round of evaluations, participants completed a surprise recognition test for the briefly flashed words.
 We presented 40 words in random order on a computer screen.
-Half of the words were the briefly presented USs from the learning task, the other half were new distractor words.
-We informed participants that 20 words were presented briefly during the learning task, asked them to select the briefly presented words from the list, and encouraged them to guess if they did not know the correct answer.
+Half of the words were the briefly flashed words from the learning task, the other half were new distractor words.
+We informed participants that 20 words were flashed briefly during the learning task, asked them to select the briefly flashed words from the list, and encouraged them to guess if they did not know the correct answer.
 Participants could only proceed with the experiment once they had selected exactly 20 words.
@@
 The experiment ended with a demographic questionnaire (age, field of study/profession, gender, goal of the experiment, and comments).
-Our procedure was identical to the original procedure, with the exception that participants completed explicit evaluation and US recognition tasks at the computer rather than using paper and pencil.
+Our procedure was identical to the original procedure, with the exception that participants completed self-reported evaluations and the recognition task at the computer rather than using paper and pencil.
 In Belgium and Germany, we furthermore used Dutch and German translations of the original material.
 The procedure took approximately 50 minutes to complete.
+
+### Data analysis {#data-analysis1}
+
+<@~{#score-calculation}
+
+In keeping with the original analysis strategy, we calculated composite rating scores and IAT scores as direct and indirect measures of evaluation.
+Rating scores were the average of the three $z$-standardized Likert-scale responses.
+To calculate IAT scores we logarithmized all response times after winsorizing responses faster than 300 ms or slower than 3,000 ms.
+IAT scores were the difference of mean transformed response times for blocks which combined Bob and negative words and blocks which combined Bob and positive words.
+Thus, for rating and IAT scores larger values indicate a more positive evaluation of Bob.
+
+~@>
+
+How to statistically assess the success of a replication attempt is subject of current debate [e.g., @fabrigar_conceptualizing_2016; @simonsohn_small_2013; @verhagen_bayesian_2014]. 
+Whether a pattern of results has been replicated is challenging to measure directly if the to-be-replicated pattern consists of more than two cells of a factorial design.
+One elegant approach is to instantiate a pattern of mean differences (i.e., the rank order of means), predicted by a theory or observed in a previous study, as order constraints in a statistical model [e.g., @hoijtink_informative_2012; @rouder_theories_2018].
+With the model in hand, replication success can be quantified as predictive accuracy of this model relative to a competing model, such as a null model or an encompassing unconstrained model [e.g., @rouder_theories_2018].
+
+Based on previously reported results, there are two competing predictions for the current paradigm:
+(1) @rydell_two_2006 reported that across both learning blocks ratings scores were congruent with the behavioral information about Bob, whereas IAT scores were incongruent with the behavioral information ($\mathcal{H}_\textrm{Two minds}$).
+(2) In contrast, @heycke_two_2018 observed a consistent pattern for rating scores and IAT scores; both measures were congruent with the behavioral information ($\mathcal{H}_\textrm{One mind}$).
+We considered two additional predictions: no effect of the manipulation ($\mathcal{H}_\textrm{No effect}$) and the all-encompassing prediction of any outcome ($\mathcal{H}_\textrm{Any effect}$).
+If, of all predictions considered, our results are best described by the prediction of no effect, our experimental manipulations failed.
+The prediction of any effect reflects the possibility that we may observe an entirely unexpected outcome that is neither in line with the results reported by @rydell_two_2006 or @heycke_two_2018.
+
+We implemented all predictions as order (or null) constraints in an ANOVA model with default (multivariate) Cauchy priors [$r = 0.5$ for fixed effects and $r = 1$ for random participant effects, see SOM for details; @rouder_default_2012; @rouder_theories_2018].
+To simplify the presentation of the Bayesian model comparison results, we collapsed data across valence orders such that we always contrasted blocks where the behavioral information was positive with those where it was negative.
+Thus, for both rating and IAT scores positive difference indicate that evaluations are congruent with the valence of the behavioral information, whereas negative values indicate that evaluations are congruent with the valence of the briefly flashed words.
+We assessed the relative predictive accuracy of these models by Bayesian model comparisons using Bayes factors.
+Note that comparisons of models where one model is a special order-constrained case of the other are asymmetric.
+Consider the example of $\mathcal{H}_\textrm{One mind}$, which is a special case of $\mathcal{H}_\textrm{Any effect}$.
+If the data are perfectly consistent with $\mathcal{M}_\textrm{One mind}$, they are inevitably also perfectly consistent with $\mathcal{M}_\textrm{Any effect}$.
+In this case $\mathcal{M}_\textrm{One mind}$ will be favored by the Bayes factor because $\mathcal{M}_\textrm{One mind}$ makes a more specific prediction---it predicts that 3/4 of the outcomes predicted by $\mathcal{M}_\textrm{Any effect}$ are impossible, Figure \ \@ref(fig:otm1-bayesian-replication-analysis-plot)A.
+The degree to which the order-constrained model is more specific (more parsimonious) places an upper bound on the Bayes factor in its favor.
+On the other hand, there is no such bound on the Bayes factor in favor of the unconstrained model if the data are inconsistent with the order constraint---that is, the data fall outside of the predictive space deemd possible by the order-constrained model.
+It follows that $\mathrm{BF}_{\mathcal{M}_\textrm{One mind}/\mathcal{M}_\textrm{Any effect}} \in [0, 4]$ because $\mathcal{M}_\textrm{One mind}$ limits its predictions to 1/4 of those of $\mathcal{M}_\textrm{Any effect}$.
+To guide their interpretation, we report the theoretical bounds on the reported Bayes factors alongside our results where applicable.
+Finally, we tested whether recognition memory accuracy using a one-tailed Bayesian $t$ test with default Cauchy prior [$r = \sqrt2/2$; @rouder_bayesian_2009].
+
+To facilitate comparisons with previously reported statistics, we also conducted the frequentist analyses described by @rydell_two_2006.
+To ensure that our conclusions about indirectly measured evaluations are robust to stimulus effects, we supplemented the ANOVA analysis of IAT scores by a frequentist linear mixed model analysis, see SOM.
+We used `r cite_r("r-references.bib", pkgs = c("papaja", "afex", "emmeans", "BayesFactor"), withhold = FALSE)` for all our analyses.
 
@@
 
-We set out to collect $N = 50$ participants at each location [@rydell_two_2006].
-For each evaluation measure, the data from all three labs ($N = 150$) provides 95% power to observe two-way interaction effects as small as $f = 0.15$ ($d = 0.30$) and contrasts between blocks of the learning task as small as $d_z = 0.27$ [$\alpha = \beta = .05$, repeated-measures correlation $r = .5$, @nosek_implicit_2007].
-Our design was, thus, adequately powered to detect effects half the size of those reported by @rydell_two_2006.
-We recruited `r otm1_n + otm1_n_excluded` participants (aged `r paste(range(otm1_mem$Age), collapse = "-")` years, $M = `r mean(otm1_mem$Age)`$; `r sum(grepl("female", otm1_mem$Sex)) / nrow(otm1_mem) * 100`% female, `r printnum(sum(grepl("nonbinary", otm1_mem$Sex)) / nrow(otm1_mem) * 100)`% nonbinary; see supplementary online material (SOM) for details); `r printnum(otm1_n_excluded, numerals = otm1_n_excluded > 10, capitalize = TRUE)` participants were excluded due to technical failure<!-- or noncompliance with instructions-->.
-Hence, the following results are based on data from `r otm1_n` participants.
+We set out to collect $n = 50$ participants at each location (N = 150).
+We recruited `r otm1_n + otm1_n_excluded` participants (aged `r paste(range(otm1_mem$Age), collapse = "-")` years, $M = `r mean(otm1_mem$Age)`$; `r sum(grepl("female", otm1_mem$Sex)) / nrow(otm1_mem) * 100`% female, `r printnum(sum(grepl("nonbinary", otm1_mem$Sex)) / nrow(otm1_mem) * 100)`% nonbinary; see supplementary online material [SOM] for details); `r printnum(otm1_n_excluded, numerals = otm1_n_excluded > 10)` participants were excluded due to technical failures<!-- or noncompliance with instructions-->.
+Hence, the reported results are based on data from `r otm1_n` participants.
 We compensated all participants with either € 8/10 (Cologne/Ghent), or partial course credit (Cologne/Harvard).
 
-### Data analysis
-
-How to evaluate the success of a replication attempt statistically is subject of current debate [e.g., @fabrigar_conceptualizing_2016; @simonsohn_small_2013; @verhagen_bayesian_2014]. 
-Whether a pattern of results has been replicated is challenging to assess directly if the to-be-replicated pattern consists of more than two cells of a factorial design.
-One elegant approach is to instantiate a pattern of mean differences (i.e., the rank order of means), predicted by a theory or observed in a previous study, as order constraints in a statistical model [e.g., @hoijtink_informative_2012; @rouder_theories_2018].
-With the model in hand, replication success can be quantified as predictive accuracy of this model relative to a competing model, such as a null model or an encompassing unconstrained model [e.g., @rouder_theories_2018].
-
-Based on previously reported results, there are two competing predictions for the current paradigm:
-(1) @rydell_two_2006 found that across both measurement times explicit ratings were congruent with the learned behavioral information about Bob, whereas IAT scores were incongruent with learned behavioral information ($\mathcal{H}_\textrm{Two minds}$).
-(2) In contrast, @heycke_two_2018 observed the same pattern for explicit ratings and IAT scores; across both measurement times both measures were congruent with the learned behavioral information ($\mathcal{H}_\textrm{One mind}$).
-We considered two additional predictions: no effect of the manipulation ($\mathcal{H}_\textrm{No effect}$) and the all-encompassing prediction of any outcome ($\mathcal{H}_\textrm{Any effect}$).
-If, of all predictions considered, our results are best described by the prediction of no effect, our experimental manipulations did not succeed.
-The prediction of any effects serves as a control and reflects the possibility that we may observe an entirely unexpected outcome that is neither in line with the results reported by @rydell_two_2006 or @heycke_two_2018.
-
-We implemented all predictions as order (or null) constraints in an ANOVA model with default (multivariate) Cauchy priors [$r = 0.5$ for fixed effects and $r = 1$ for random participant effects, see SOM for details; @rouder_default_2012; @rouder_theories_2018].
-To evaluate the relative predictive accuracy of these models we performed Bayesian model comparison using Bayes factors.
-To test whether recognition memory performance was above chance we used a one-tailed Bayesian $t$ test with default Cauchy prior [$r = \sqrt2/2$; @rouder_bayesian_2009].
-We also report the results of the analyses described by @rydell_two_2006 to facilitate comparisons with previously reported statistics.
-
-For both analyses, we processed the IAT response times as described in the original study [for details see @rydell_two_2006; @heycke_two_2018].
-To ensure that our conclusions are robust to stimulus effects, we additionally supplemented the ANOVA analysis of IAT scores by a frequentist linear mixed model analysis, see SOM.
-To simplify the presentation of the Bayesian model comparison results, we collapsed data across valence orders by reversing the coding of the blocks when learned behaviors were first negative and subsequently positive.
-Thus, for both explicit and implicit evaluation measures we contrasted the first with the second block, such that positive values represent a more positive evaluation following the block in which learned behaviors were positive and USs negative.
-We used `r cite_r("r-references.bib", pkgs = c("papaja", "afex", "emmeans", "BayesFactor"), withhold = FALSE)` for all our analyses.
+### Statistical power
+
+```{r rydell-effects, cache = TRUE}
+rydell_pes <- 0.1
+rydell_f <- 4.78
+rydell_n <- 50
+rydell_dz <- pes_to_dz(rydell_pes, rydell_n, n_groups = 2)
+
+heycke_t <- c(2.54, 1.45)
+heycke_n <- c(28, 26)
+heycke_dz <- heycke_t / sqrt(heycke_n)
+heycke_pes <- dz_to_pes(heycke_dz, heycke_n, n_groups = 1)
+```
+
+```{r otm1-power, cache = TRUE}
+otm1_power <- function(f, rm_cor, n = 76, alpha = 0.05) {
+  contrast_code <- tibble::tibble(
+    a = rep(contr.sum(2), 2)
+    , b = rep(contr.sum(2), each = 2)
+    , x = a*b * -1
+  )
+
+  mu <- with(
+    contrast_code
+    , f * x +
+      - 0.25 * a
+  )
+
+  cor_mat <- diag(4)
+  triangular <- c(0, 1, 0, 0, 1, 0)
+  cor_mat[upper.tri(cor_mat)] <- triangular * rm_cor
+  cor_mat[lower.tri(cor_mat)] <- triangular * rm_cor
+
+  string <- "2w*2b"
+  labelnames <- c("block", "1", "2", "order", "n-p", "p-n")
+
+  design_result <- ANOVA_design(
+    design = string
+    , n = n
+    , mu = mu
+    , sd = 1
+    , r = cor_mat
+    , labelnames = labelnames
+  )
+
+  otm1_power <- ANOVA_exact(
+    design_result
+    , alpha_level = alpha
+    , emm = TRUE
+    , verbose = FALSE
+    , contrast_type = "pairwise"
+    , emm_comp = "block | order"
+  )
+
+  otm1_power
+}
+
+otm1_n_power <- 76
+
+# 95% power
+otm1_pes <- 0.08068
+otm1_dz <- pes_to_dz(otm1_pes, otm1_n_power, n_groups = 2)
+# rho <- 0.5
+# f <- dz_to_f(otm1_dz, rho)
+# 
+# otm1_contrast_power <- otm1_power(f = f, n = otm1_n_power, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm1_contrast_power
+
+# 80% power
+otm1_pes2 <- 0.050336
+otm1_dz2 <- pes_to_dz(otm1_pes2, otm1_n_power, n_groups = 2)
+# f <- dz_to_f(otm1_dz2, rho)
+# 
+# otm1_contrast_power2 <- otm1_power(f = f, n = otm1_n_power, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm1_contrast_power2
+```
+
+<@~{#power1}
+
+The prediction, which is supported by all previous empirical reports, is a crossed disordinal interaction between the factor *learning block* and the control factor *valence order*.
+Our assessment of the statistical senstivitiy of our design focused on the tests of simple *learning block* effects, because they are of primary theoretical interest and less sensitive than the test of the interaction.
+We estimate the sensitivity for the frequentist analyses described by @rydell_two_2006 using the R-package *Superpower* [@R-Superpower].
+The smallest simple effect of learning block reported by @rydell_two_2006 was $d_z \approx `r rydell_dz`$ ($\hat\eta_p^2 = `r printp(rydell_pes)`$) for IAT scores.[^compareheycke]
+Across all locations, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm1_dz`$[^impliedd] ($\eta_p^2 = `r printp(otm1_pes)`$; $N = `r otm1_n_power * 2`$, $\alpha = .05$, two-sided tests).
+Thus, our design is sufficiently sensitive to detect (or rule out) differences 11% smaller than the smallest learning block difference reported in the original study.
+
+[^compareheycke]: The learning block differences reported by Heycke et al. (2018) were of similar magnitude but with an opposite sign.
+
+[^impliedd]: We report the implied sensitivity in units of Cohen's $\delta$ depending on the assumed repeated-measures correlation $\rho$ in the supplementary material.
+
+~@>
 
@@
 
-In the following, *valence order* refers to the joint order of learned behaviors and briefly presented USs.
-Any time we refer to one valence order (e.g., positive-negative) we specify the order of the learned behavior; the corresponding briefly presented USs were always of the opposite valence.
+In the following, *valence order* refers to the joint order of briefly flashed words and behavioral information.
+Any time we refer to one valence order (e.g., positive-negative) we specify the order of the behavioral information; briefly flashed words were always of the opposite valence.
+
+<@~{#prediction-list}
+
+To reiterate, @rydell_two_2006 reported that across learning blocks ratings scores were congruent with the behavioral information about Bob, whereas IAT scores were incongruent with the behavioral information.
+This pattern of results implies (1) a three-way interaction of *measure of evaluation*, *valence order*, and *learning block* in a joint analysis of all evaluations, (2) two opposite crossed disordinal interactions of *valence order* and *learning block* for separate analyses of rating and IAT scores, (3) larger rating scores following learning blocks in which the behavioral information was positive compared to when it was negative, and, finally, (4) smaller IAT scores following learning blocks in which the behavioral information was positive compared to when it was negative.
+We first report the results of the frequentist analyses described by @rydell_two_2006.
+Busy readers interested in an integrative replicability assessment may wish to skip ahead to the [Bayesian model comparisons](#replicability-assessment1).
+
+~@>
 
@@
     # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
-    title = expression(atop("Valence order", atop(scriptstyle("Learned behaviors"), scriptstyle("(Briefly presented USs)"))))
+    title = expression(atop("Valence order", atop(scriptstyle("Behavioral information"), scriptstyle("(Briefly flashed words)"))))
     , title.position = "top"
@@
   ggplot(aes(x = Block, y = Eval, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
+  # geom_hline(yintercept = 0, color = grey(0.7)) +
   geom_violin(position = position_dodge(0.1), alpha = 0.3) +
@@
   stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000), geom = "pointrange", size = 0.6) +
-  scale_y_continuous(labels = scales::number_format(accuracy = 0.1)) +
+  scale_y_continuous(
+    labels = scales::number_format(accuracy = 0.1)
+    , sec.axis = sec_axis(~ scale(.), name = bquote(italic(z)~"score"))
+  ) +
   scale_color_viridis_d(option = "C", begin = 0.1, end = 0.9, guide = otm1_results_legend) +
@@
   ggplot(aes(x = Block, y = IATscore, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
+  # geom_hline(yintercept = 0, color = grey(0.7)) +
   geom_violin(position = position_dodge(0.1), alpha = 0.3) +
@@
   stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000), geom = "pointrange", size = 0.6) +
+  scale_y_continuous(sec.axis = sec_axis(~ scale(.), name = bquote(italic(z)~"score"))) +
   scale_color_viridis_d(option = "C", begin = 0.1, end = 0.9, guide = otm1_results_legend) +
@@
 
-(ref:otm1-factorial-results-plot) Evaluative rating and IAT scores for Experiments 1 (**A**) and Experiment 2 (**B**).
-Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participants' responses, and violins represent kernel density estimates of sample distributions.
+(ref:otm1-factorial-results-plot) Mean evaluative rating and IAT scores for Experiments 1 (**A**) and Experiment 2 (**B**) broken down by valence order, learning block, and lab location.
+Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participant scores, and violins represent kernel density estimates of sample distributions.
 
@@
 
+```{r eval = FALSE}
+print_mean_cl <- function(x) {
+  paste(printnum(x[1]), paste0("[", paste(printnum(x[2:3]), collapse = ", "), "]"))
+}
+
+otm1_descriptives <- otm1_attitudes %>% 
+  select(-ParticipantNumber) %>% 
+  group_by_if(is.factor) %>% 
+  do(
+    Eval = mean_cl_normal(.$Eval)
+    , IAT = mean_cl_normal(.$IATscore)
+  ) %>% 
+  mutate(
+    Eval = print_mean_cl(Eval)
+    , IAT = print_mean_cl(IAT)
+  ) %>% 
+  pivot_wider(names_from = "Block", values_from = c("Eval", "IAT")) %>% 
+  label_variables(
+    Eval_1 = "Learning block 1"
+    , Eval_2 = "Learning block 2"
+    , IAT_1 = "Learning block 1"
+    , IAT_2 = "Learning block 2"
+  )
+
+apa_table(
+  list(
+    Cologne = filter(otm1_descriptives, Location == "Cologne") %>% select(-Location)
+    , Ghent = filter(otm1_descriptives, Location == "Ghent") %>% select(-Location)
+    , Harvard = filter(otm1_descriptives, Location == "Harvard") %>% select(-Location)
+  )
+  , col_spanners = list("Rating score" = 2:3, "IAT score" = 4:5)
+  , caption = "(ref:otm1-descriptives)"
+  , align = c("lcccc")
+)
+```
+
 ```{r otm1-rydell-analysis-overall, results = "asis"}
@@
 
-otm1_attitudes_aov_res <- otm1_attitudes_aov %>%
-  apa_print
+otm1_attitudes_aov_res <- apa_print_ps(otm1_attitudes_aov)
+
+# otm1_attributes_aov_matrix <- expand.grid(
+#   contr.sum(2)
+#   , contr.sum(2)
+#   , contr.sum(2)
+# )[rep(1:8, 3), ]
+# 
+# otm1_attitudes_aov_grid <- otm1_attitudes_aov %>% 
+#   emmeans(specs = ~ Block * Measure * ValenceBlock * Location)
+# 
+# otm1_attitudes_aov_threeway_d <- otm1_attitudes_aov_grid %>% 
+#   contrast(
+#     list(
+#       three_way = mutate(otm1_attributes_aov_matrix, I = Var1 * Var2 * Var3) %>%
+#         {-.$I}
+#     )
+#   ) %>%
+#   {eff_size(
+#     .
+#     , sigma = (1/data.frame(.)$t * data.frame(.)$estimate) / sqrt(2 / (otm1_n/2))
+#     , edf = df.residual(otm1_attitudes_aov$lm)
+#     , method = "identity"
+#   )} %>% 
+#   apa_print(est_name = "d") %>% 
+#   {.$estimate$three_way}
+# 
+# otm1_attitudes_aov_twoway_d <- otm1_attitudes_aov_grid %>% 
+#   contrast(
+#     list(
+#       two_way = mutate(otm1_attributes_aov_matrix, I = Var2 * Var3) %>%
+#         {.$I}
+#     )
+#   ) %>%
+#   {eff_size(
+#     .
+#     , sigma = (1/data.frame(.)$t * data.frame(.)$estimate) / sqrt(2 / (otm1_n/2))
+#     , edf = df.residual(otm1_attitudes_aov$lm)
+#     , method = "identity"
+#   )} %>% 
+#   apa_print(est_name = "d") %>% 
+#   {.$estimate$two_way}
 
@@
   filter(`model term` == "ValenceBlock:Measure:Block")
-```
-
-In the joint analysis of implicit and explicit evaluations, we found the three-way interaction between valence order, learning block, and evaluation measure, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Block_Measure` previously reported by @rydell_two_2006 (Figure\ \@ref(fig:otm1-factorial-results-plot)).
-Moreover, we found that the three-way interaction was significant in each lab (all $F(`r unique(otm1_attitudes_location_aov$df1)`, `r unique(otm1_attitudes_location_aov$df2)`) > `r min(otm1_attitudes_location_aov$F.ratio)`$, $p `r printp(max(otm1_attitudes_location_aov$p.value))`$), but differed slightly in magnitude, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Location_Block_Measure`.
-The direction of the effect was consistent across labs.
-As in the original analysis we examined the significant three-way interaction with separate analyses of each evaluation measure.
-
-### Explicit evaluation
+
+# For reviewers:
+## Differences between valence orders in learning block 2
+otm1_order_contrast_summary <- otm1_attitudes_aov %>%
+  emmeans(~ ValenceBlock | Block * Measure) %>%
+  pairs %>% 
+  as.data.frame %>% 
+  {paste0(
+    "$t(", unique(.$df), ") > ", printnum(min(abs(.$t.ratio)))
+    , "$, $p < ", printp(max(.$p.value)), "$"
+  )}
+
+## Difference between valence orders in learning block 2 vs 1
+# otm1_attitudes_aov %>%
+#   emmeans(~ Block * ValenceBlock * Measure) %>%
+#   # emmeans(~ Block * ValenceBlock * Measure | Location) %>%
+#   contrast(
+#     list(
+#       eval = c(-0.5, -0.5, 0.5, 0.5, 0, 0, 0, 0)
+#       , iat = c(0, 0, 0, 0, -0.5, -0.5, 0.5, 0.5)
+#     )
+#   ) %>%
+#   # test(side = ">")
+#   joint_tests()
+```
+
+(ref:otm1-descriptives) Means and 95% confidence intervals of rating and IAT scores in Experiment 1 broken down by valence order, learning block, and lab location.
+
+```{r otm1-descriptives-table}
+print_mean_cl <- function(x) {
+  paste(printnum(x[1]), paste0("[", paste(printnum(x[2:3]), collapse = ", "), "]"))
+}
+
+# # z-standardized values we analyzed
+# emmeans(otm1_attitudes_aov, ~ Block * Measure * ValenceBlock * Location) %>%
+#   as_tibble %>%
+#   group_by_if(is.factor) %>%
+#   summarize(estimate = print_mean_cl(c(emmean, lower.CL, upper.CL))) %>%
+#   pivot_wider(names_from = c("Measure", "Block"), values_from = "estimate") %>%
+#   select(Location, everything()) %>%
+#   arrange(Location, ValenceBlock)
+
+otm1_eval_descriptives <- otm1_attitudes %>% aov_ez(
+    id = "ParticipantNumber"
+    , dv = "Eval"
+    , within = c("Block")
+    # , between = "ValenceBlock"
+    , between = c("ValenceBlock", "Location")
+    , data = .
+  ) %>% 
+    emmeans(., ~ Block * ValenceBlock * Location)
+
+otm1_iat_descriptives <- otm1_attitudes %>% aov_ez(
+    id = "ParticipantNumber"
+    , dv = "IATscore"
+    , within = c("Block")
+    # , between = "ValenceBlock"
+    , between = c("ValenceBlock", "Location")
+    , data = .
+  ) %>% 
+    emmeans(., ~ Block * ValenceBlock * Location)
+
+otm1_descriptives <- bind_rows(
+  Eval = as_tibble(otm1_eval_descriptives)
+  , IAT = as_tibble(otm1_iat_descriptives)
+  , .id = "Measure"
+) %>% 
+  mutate(Measure = factor(Measure)) %>% 
+  group_by_if(is.factor) %>%
+  summarize(estimate = print_mean_cl(c(emmean, lower.CL, upper.CL))) %>%
+  pivot_wider(names_from = c("Measure", "Block"), values_from = "estimate") %>% 
+  select(Location, everything()) %>% 
+  arrange(Location, ValenceBlock) %>% 
+  ungroup() %>% 
+  label_variables(
+    Eval_X1 = "Learning block 1"
+    , Eval_X2 = "Learning block 2"
+    , IAT_X1 = "Learning block 1"
+    , IAT_X2 = "Learning block 2"
+  )
+
+apa_table(
+  list(
+    Cologne = filter(otm1_descriptives, Location == "Cologne") %>% select(-Location)
+    , Ghent = filter(otm1_descriptives, Location == "Ghent") %>% select(-Location)
+    , Harvard = filter(otm1_descriptives, Location == "Harvard") %>% select(-Location)
+  )
+  , col_spanners = list("Rating score" = 2:3, "IAT score" = 4:5)
+  , caption = "(ref:otm1-descriptives)"
+  , align = c("lcccc")
+  , font_size = "small"
+)
+```
+
+### Joint analysis of rating and IAT scores
+
+For a joint analysis, we separately $z$-standardized directly and indirectly measured evaluations and submitted them to a four-way ANOVA with the factors *measure of evaluation* (direct vs.
+indirect), *valence order* (positive or negative behavioral information first), *learning block* (first or second learning block), and *lab location* (Cologne, Ghent, Harvard).
+Table\ \@ref(tab:otm1-descriptives-table) summarizes the condition means.
+We found a significant three-way interaction between valence order, learning block, and measure of evaluation, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Block_Measure`, Figure\ \@ref(fig:otm1-factorial-results-plot)[^fignalysis].
+Moreover, we observed a significant four-way interaction indicating that the three-way interaction differed between lab locations, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Location_Block_Measure`.
+Follow-up tests indicated that the three-way interaction was significant in each lab (all $F(`r unique(otm1_attitudes_location_aov$df1)`, `r unique(otm1_attitudes_location_aov$df2)`) > `r min(otm1_attitudes_location_aov$F.ratio)`$, $p `r printp(max(otm1_attitudes_location_aov$p.value))`$) and the direction of the effect was consistent across labs.
+In line with the original analysis, we next examined the interaction between valence order, learning block, and lab location in separate analyses of rating and IAT scores.
+
+[^fignalysis]:
+Figure\ \@ref(fig:otm1-factorial-results-plot) may give the impression that the difference between valence orders was of similar magnitude at learning block 1 and 2 in rating scores but differed in IAT scores.
+However, we found differences between valence orders at learning blocks 1 and 2 in both measures of evaluation (all `r otm1_order_contrast_summary`) and we did not find these differences between valence orders to vary between evaluative measures, `r otm1_attitudes_aov_res$full_result$ValenceBlock_Measure`.
+
+### Direct measure: Evaluative rating scores
 
@@
 
-otm1_explicit_aov_res <- otm1_explicit_aov %>%
-  apa_print
+otm1_explicit_aov_res <- apa_print_ps(otm1_explicit_aov)
 
@@
 ```{r otm1-rydell-analysis-explicit2, results = "asis"}
-otm1_explicit_contrasts <- emmeans(otm1_explicit_aov, ~ Block | ValenceBlock) %>%
-  contrast(
-    method = list("Block 2 - Block 1" = c(-1, 1))
-    , adjust = "none"
-  ) %>%
-  apa_print
+# otm1_explicit_contrasts <- emmeans(otm1_explicit_aov, ~ Block | ValenceBlock) %>%
+#   contrast(
+#     method = list("Block 2 - Block 1" = c(-1, 1))
+#     , adjust = "none"
+#   ) %>%
+#   apa_print
 
@@
 
-otm1_explicit_location_contrasts_res <- otm1_explicit_location_contrasts %>%
-  apa_print
+otm1_explicit_location_contrasts_res <- apa_print_ps(
+  otm1_explicit_location_contrasts
+  , otm1_explicit_aov$lm
+  , est_name = "d_z"
+)
 
@@
 
-As in the previous studies, we found a two-way interaction between valence order and learning block, `r otm1_explicit_aov_res$full_result$ValenceBlock_Block`.
-This interaction was significant in each lab (all $F(`r unique(otm1_explicit_location_aov$df1)`, `r unique(otm1_explicit_location_aov$df2)`) > `r min(otm1_explicit_location_aov$F.ratio)`$, $p `r printp(max(otm1_explicit_location_aov$p.value))`$), but also differed between labs, `r otm1_explicit_aov_res$full_result$ValenceBlock_Location_Block`.
-In all labs, ratings of Bob were more favorable after the first than after the second block when learned behaviors were first positive and later negative, 
+As in the previous studies, for rating scores we found a two-way interaction between valence order and learning block, `r otm1_explicit_aov_res$full_result$ValenceBlock_Block`.
+This interaction was significant in each lab (all $F(`r unique(otm1_explicit_location_aov$df1)`, `r unique(otm1_explicit_location_aov$df2)`) > `r min(otm1_explicit_location_aov$F.ratio)`$, $p `r printp(max(otm1_explicit_location_aov$p.value))`$), but also differed in magnitude, `r otm1_explicit_aov_res$full_result$ValenceBlock_Location_Block`.
+In all labs, rating scores corresponded to the valence of the behavioral information.
+Rating scores indicated *more* favorable evaluations after the first than after the second block when behavioral information was first positive and later negative, 
 Cologne: `r otm1_explicit_location_contrasts_res$estimate$Positive_negative_Cologne_Block2_Block1`; 
@@
 all $t(`r unique(otm1_explicit_location_pos_neg_contrasts$df)`) < `r max(otm1_explicit_location_pos_neg_contrasts$t.ratio)`$, $p$ `r printp(max(otm1_explicit_location_pos_neg_contrasts$p.value))`.
-Vice versa, in all labs, ratings of Bob were more favorable after the second than after the first block when learned behaviors were first negative and later positive, 
+Conversely, rating scores indicated *less* favorable evaluations after the first than after the second block when behavioral information was first negative and later positive, 
 Cologne: `r otm1_explicit_location_contrasts_res$estimate$Negative_positive_Cologne_Block2_Block1`; 
@@
 Harvard: `r otm1_explicit_location_contrasts_res$estimate$Negative_positive_Harvard_Block2_Block1`; 
-all $t(`r unique(otm1_explicit_location_neg_pos_contrasts$df)`) < `r max(otm1_explicit_location_neg_pos_contrasts$t.ratio)`$, $p$ `r printp(max(otm1_explicit_location_neg_pos_contrasts$p.value))`.
-Hence, the predicted differences were consistently detectable in all labs but differed in magnitude.
-No other effects were significant.
-
-### Implicit evaluation
+all $t(`r unique(otm1_explicit_location_neg_pos_contrasts$df)`) > `r min(otm1_explicit_location_neg_pos_contrasts$t.ratio)`$, $p$ `r printp(max(otm1_explicit_location_neg_pos_contrasts$p.value))`.
+Hence, in all labs directly measured evaluations corresponded to the valence of the behavioral information and were opposite to the valence of the briefly flashed words.
+
+### Indirect measure: IAT scores
 
@@
 
-otm1_iat_aov_res <- otm1_iat_aov %>%
-  apa_print
+otm1_iat_aov_res <- apa_print_ps(otm1_iat_aov)
 ```
@@
     , adjust = "none"
-  ) %>%
-  apa_print 
-```
-
-For IAT scores, we found a two-way interaction between valence order and learning block, `r otm1_iat_aov_res$full_result$ValenceBlock_Block`; in this case we detected no differences between labs, `r otm1_iat_aov_res$full_result$ValenceBlock_Location_Block`.
-IAT scores for Bob were larger, indicating a more favorable attitude, after the first than after the second block when learned behaviors were first positive and later negative, `r otm1_implicit_contrasts$full_result$Positive_negative_Block2_Block1`.
-Vice versa, IAT scores for Bob were larger after the second than after the first block when learned behaviors were first negative and later positive, `r otm1_implicit_contrasts$full_result$Negative_positive_Block2_Block1`.
-The results of the mixed model analysis were in line with the conclusions from the ANOVA analysis, see SOM.
-Hence, evaluations of Bob assessed with the IAT corresponded to the valence of the learned behaviors and contradicted the valence of the briefly presented USs.
-Explicit ratings and IAT scores did not dissociate.
-
-### Differences between implicit and explicit evaluations
-
-As in the original study, we additionally compared participants' $z$ standardized evaluations toward Bob assessed by ratings and IAT scores.
+  )
+
+otm1_implicit_contrasts <- apa_print_ps(
+  otm1_implicit_contrasts
+  , otm1_iat_aov$lm
+  , est_name = "d_z"
+)
+```
+
+For IAT scores, we found a two-way interaction between valence order and learning block, `r otm1_iat_aov_res$full_result$ValenceBlock_Block`; in this case we detected no differences across labs, `r otm1_iat_aov_res$full_result$ValenceBlock_Location_Block`.
+In all labs, IAT scores corresponded to the valence of the behavioral information.
+IAT scores indicated *more* favorable evaluations after the first than after the second block when behavioral information was first positive and later negative, `r otm1_implicit_contrasts$full_result$Positive_negative_Block2_Block1`.
+Conversely, IAT scores indicated *less* favorable evaluations after the first than after the second block when behavioral information was first negative and later positive, `r otm1_implicit_contrasts$full_result$Negative_positive_Block2_Block1`.
+The results of the mixed model analysis corroborated the conclusions from the ANOVA analysis, see SOM.
+Hence, in all labs indirectly measured evaluations corresponded to the valence of the behavioral information and were opposite to the valence of the briefly flashed words.
+Directly and indirectly measured evaluations did not dissociate.
+
+### Differences between rating and IAT scores
 
@@
   emmeans(~ Measure | ValenceBlock * Block) %>% 
-  pairs %>%
-  apa_print
-```
-
-Evaluations assessed by rating and IAT scores differed in all conditions.
-Ratings of Bob were more favorable than IAT scores in the first block, `r otm1_attitudes_measure_contrasts$full_result$Positive_negative_X1_Eval_IATscore`, but less favorable in the second block when learned behaviors were first positive and later negative, `r otm1_attitudes_measure_contrasts$full_result$Positive_negative_X2_Eval_IATscore`.
-Conversely, ratings of Bob were less favorable than IAT scores in the first block, `r otm1_attitudes_measure_contrasts$full_result$Negative_positive_X1_Eval_IATscore`, but more favorable in the second block when learned behaviors were first positive and later negative, `r otm1_attitudes_measure_contrasts$full_result$Negative_positive_X2_Eval_IATscore`.
-Given that evaluations were consistent in valence across measures, these differences indicate that evaluations assessed by ratings were more extreme than those assessed by IAT scores.
-
-### Bayesian model comparisons
+  pairs
+
+otm1_attitudes_measure_contrasts <- apa_print_ps(
+    otm1_attitudes_measure_contrasts
+    , otm1_attitudes_aov$lm
+    , est_name = "d_z"
+  )
+```
+
+In keeping with our preregisted analysis plan, we also compared $z$-standardized directly and indirectly measured evaluations---despite the consistent pattern of results---and found that they differed across measures in every condition.
+When behavioral information was first positive and later negative, rating scores indicated a more favorable evaluation than IAT scores in the first block, `r otm1_attitudes_measure_contrasts$full_result$Positive_negative_X1_Eval_IATscore`, but a less favorable evaluation in the second block, `r otm1_attitudes_measure_contrasts$full_result$Positive_negative_X2_Eval_IATscore`.
+Conversely, when behavioral information was first negative and later positive rating scores indicated a less evaluation than IAT scores in the first block, `r otm1_attitudes_measure_contrasts$full_result$Negative_positive_X1_Eval_IATscore`, but a more favorable evaluation in the second block, `r otm1_attitudes_measure_contrasts$full_result$Negative_positive_X2_Eval_IATscore`.
+These results, corroborate that directly and indirectly measured evaluations were consistent, but indicate that directly measured evaluations were more extreme than indirect measured evaluations.
+
+### Bayesian model comparisons {#replicability-assessment1}
 
@@
 (ref:bayesian-replication-analysis-plot) Predictions of the four models of primary interest (**A**) and results of Experiment 1 and Experiment 2 (**B**).
-Black-rimmed points represent means of observed attitude differences between learning blocks with positive and negative learned behaviors.
-Positive values indicate that attitudes correspond to the valence of learned behaviors and contradict the valence of the briefly presented USs.
+Black-rimmed points represent mean differences in evaluations between the two learning blocks.
+To simplify the presentation of the results, we collapsed data across valence orders such that we always contrasted blocks where the behavioral information was positive with those where it was negative.
+Thus, for both rating and IAT scores positive difference indicate that evaluations correspond to the valence of the behavioral information, whereas negative values indicate that evaluations correspond to the valence of the briefly flashed words.
 Ellipses represent 95% Bayesian credible intervals based on the unconstrained model $\mathcal{M}_\textrm{Any effect}$.
-
-```{r otm1-effects-plot, cache = TRUE, warning=FALSE}
+For comparison, the grey $\times$ represents the learning block differences reported in the original study.
+
+```{r otm1-effects-plot, cache = TRUE, warning = FALSE}
 otm1_unconstrained_pp <- otm1_unconstrained_samples %>%
@@
   rbind(cbind(Location = "Overall", otm1_attitudes_delta_summary))
+
+rydell_descriptives <- rbind(
+  cbind(read.csv2("rydell_explicit.csv", header = FALSE), Measure = "Eval")
+  , cbind(read.csv2("rydell_implicit.csv", header = FALSE), Measure = "IATscore")
+) %>% 
+  mutate(
+    valenceOrder = if_else(V1 < 3, "Positive-negative", "Negative-positive")
+    , Block = if_else((V1 < 1.5) | (V1 > 3 & V1 < 4.5), 1, 2)
+    , Block = if_else(valenceOrder == "Negative-positive", 3 - Block, Block)
+  ) %>% 
+  group_by(Measure, Block) %>% 
+  summarize(V2 = mean(V2)) %>% 
+  spread(Block, V2) %>% 
+  mutate(delta = `1` - `2`) %>% 
+  select(Measure, delta) %>% 
+  spread(Measure, delta) %>% 
+  mutate(Location = NA)
 
@@
   geom_point(size = 3, color = "black") +
+  geom_point(data = rydell_descriptives, shape = 4, color = grey(0.7), fill = NA, size = 3) +
   # geom_point(
@@
   annotate(geom = "text", x = 1.17, y = -2, label = "Two minds", hjust = 0.5, size = 4, color = "gray50") +
-  scale_color_viridis_d() +
-  scale_fill_viridis_d() +
+  scale_color_viridis_d(direction = -1) +
+  scale_fill_viridis_d(direction = -1) +
   scale_shape_manual(values = c(21, 23, 24, 22)) +
@@
 
-The direct comparison of predictive accuracy indicated that our data overwhelmingly favored the result patterns reported by @heycke_two_2018 over those reported by @rydell_two_2006, `r otm1_same_vs_opposite_direction_bf_res`, Table\ \@ref(tab:otm1-bayesian-replication-analysis-table).
-Additional comparisons with the control models confirmed that the experimental manipulations were effective (`r otm1_same_direction_bf_res`) and did not produce an unexpected result pattern (`r otm1_same_direction_vs_unconstrained_bf_res`, $\in [0, 4]$[^bf_range]).
-
-We additionally assessed whether all labs produced the same result pattern.
-We implemented a model that enforced the order constraint of $\mathcal{M}_\textrm{One mind}$ not only on the average block effects but on each lab's block effect.
-Our data provide strong evidence for consistent result patterns across labs relative to the less-constrained models, `r otm1_all_labs_same_vs_same_direction_bf_res` ($\in [0, 3]$) and `r otm1_all_labs_same_direction_vs_unconstrained_bf_res` ($\in [0, 12]$[^bf_range2]).
-Prior sensitivity analyses confirmed that the above results are robust to a wide range of priors, see SOM.
-
-[^bf_range]:
-The comparison of these models is asymmetric.
-If, as in this case, the data are perfectly consistent with $\mathcal{M}_\textrm{One mind}$, they are also consistent with $\mathcal{M}_\textrm{Any effect}$.
-The order restriction enforced by $\mathcal{M}_\textrm{One mind}$ limits the prediction of the model to 1/4 of the outcome space predicted by $\mathcal{M}_\textrm{Any effect}$ (i.e., the upper right quadrant of Figure \ \@ref(fig:otm1-bayesian-replication-analysis-plot)).
-This four-fold greater parsimony of $\mathcal{M}_\textrm{One mind}$ constitutes the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{One mind}/\mathcal{M}_\textrm{Any effect}}$ (assuming all regions of the outcome space are equally likely a priori).
-Hence, for this model comparison we could not have obtained stronger evidence (given numerical imprecision of the MCMC sampling approach).
-Conversely, if the data had fallen outside the predicted outcome space of $\mathcal{M}_\textrm{One mind}$ there is no upper bound to the evidence in favor of $\mathcal{M}_\textrm{Any effect}$.
-
-[^bf_range2]:
-The additional order constraints enforced by $\mathcal{M}_\textrm{One mind everywhere}$ limits the prediction of the model to 1/12 of the outcome space predicted by the unconstrained model.
-Hence, for this model comparison the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{One mind everywhere}/\mathcal{M}_\textrm{Any effect}}$ is 12 (assuming all regions of the outcome space are equally likely a priori).
-Baring the transitivity of Bayes factors in mind this implies that the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{One mind everywhere}/\mathcal{M}_\textrm{One mind}}$ is 3.
-Hence, in both model comparisons we could not have obtained much stronger evidence in favor of $\mathcal{M}_\textrm{One mind everywhere}$.
+The direct comparison of predictive accuracy indicated that our data overwhelmingly favored the qualitative pattern reported by @heycke_two_2018 over that reported by @rydell_two_2006, `r otm1_same_vs_opposite_direction_bf_res`, Table\ \@ref(tab:otm1-bayesian-replication-analysis-table).
+Additional comparisons with the control models confirmed that the experimental manipulations were effective (`r otm1_same_direction_bf_res`) and did not produce an unexpected result, `r otm1_same_direction_vs_unconstrained_bf_res` $\in [0, 4]$.
+
+We additionally assessed whether all labs consistently produced the same result pattern.
+We implemented a model that enforced the order-constraint of $\mathcal{M}_\textrm{One mind}$ not only on the average learning block effects but on each lab's learning block effect.
+Our data provide strong evidence for consistent result patterns across labs relative to the less-constrained models, `r otm1_all_labs_same_vs_same_direction_bf_res` $\in [0, 3]$ and `r otm1_all_labs_same_direction_vs_unconstrained_bf_res` $\in [0, 12]$.
+As noted in the [Data analysis](#data-analysis1) section, due to the upper bounds on the Bayes factors, we could not have obtained much stronger evidence in favor of $\mathcal{M}_\textrm{One mind everywhere}$.
+Prior sensitivity analyses confirmed that our results are robust to a wide range of priors, see SOM.
 
@@
 
-(ref:otm1-bayesian-replication-analysis-table-note) The Bayes factors (BF) in favor of $\mathcal{M}_\textrm{One mind}$ and $\mathcal{M}_\textrm{One mind everywhere}$ relative to $\mathcal{M}_\textrm{Any effect}$ are bounded within the range of $[0, 4]$^1^<!--[^bf_range]--> and $[0, 12]$^2^<!--[^bf_range2]-->, respectively.
+(ref:otm1-bayesian-replication-analysis-table-note) As noted in the [Data analysis](#data-analysis1) section, the Bayes factors (BF) in favor of $\mathcal{M}_\textrm{One mind}$ and $\mathcal{M}_\textrm{One mind everywhere}$ relative to $\mathcal{M}_\textrm{Any effect}$ are bounded within the range of $[0, 4]$ and $[0, 12]$, respectively.
 Hence, in both model comparisons we could not have obtained much stronger evidence against $\mathcal{M}_\textrm{Any effect}$.
@@
 
-### Recognition task
-
-```{r otm1-rydell-recognition, results = "asis"}
+### Recognition of briefly presented words
+
+```{r otm1-rydell-recognition, warning = FALSE, results = "asis"}
 otm1_mem_ttest <- t.test(otm1_mem$Accuracy, mu = 0.5, alternative = "greater", rscale = "medium") %>%
@@
   ) %>%
-  apa_print(intercept = TRUE) %$%
-  full_result
+  apa_print_ps(intercept = TRUE) %$%
+  full_result %>% 
+  setNames(c("Intercept", "Location"))
 ```
@@
 otm1_mem_bayesian_ttest <- ttestBF(otm1_mem$Accuracy - 0.5, mu = 0, rscale = "medium", nullInterval = c(0, Inf))[1] %>%
-  apa_print(gt1 = FALSE) %$%
-  full_result %>%
-  gsub("\\.0", ".5", .)
+  apa_print %$%
+  statistic
 
@@
 
-Finally, we examined participants' recognition memory for the words that we presented briefly as USs during the learning procedure.
+Finally, we examined participants' recognition memory for the briefly flashed words at the end of the study.
 Recognition accuracy was better than chance, `r otm1_mem_ttest`, `r otm1_mem_bayesian_ttest`.
-Hence, we cannot assume that the stimulus presentation was subliminal.
-It remained unclear, however, whether recognition accuracy differed between labs, `r otm1_mem_aov$Location`, `r otm1_mem_bayesian_aov`.
+Hence, we cannot assume that the stimulus presentation was outside of participants' conscious awareness.
+It remains unclear whether recognition accuracy differed between labs, `r otm1_mem_aov$Location`, `r otm1_mem_bayesian_aov` (see SOM for details).
 
@@
 
-We reproduced the procedure of @rydell_two_2006, using the original material and the first author of the original study approved the procedure.
-Despite all efforts to keep the procedure as close as possible to the original procedure, we did not replicate the original finding.
-In contrast to @rydell_two_2006, we observed that both implicit and explicit evaluations reflected the valence of the learned behavioral information.
-The briefly presented USs did not lead to contradicting implicit evaluations compared to explicit evaluations.
-In short, we found no evidence for an evaluative dissociation. 
+As confirmed by the first author of the original study, we faithfully reproduced the procedure of @rydell_two_2006, but the original results did not replicate.
+We observed that both directly and indirectly measured evaluations reflected the valence of the behavioral information; the briefly flashed words did not produce a reversal of the indirectly measured evaluations.
+In short, we found no dissociation between directly and indirectly measured evaluations. 
 Our findings mirror the results of the previous replication attempt by @heycke_two_2018.
-Moreover, the observed results were consistent across three languages and countries indicating that neither inaccurate translations nor differences in sampled populations are likely to have caused the deviation of the results from the original findings.
-Thus, our findings raise more doubts about the general replicability of the dissociative evaluative learning effect that was observed by @rydell_two_2006.
-
-There is, however, one objection these findings cannot entirely dispel: The close physical recreation of the original procedure may not have faithfully reproduced the psychological conditions of the original learning task.
-In the original study, US recognition accuracy was not significantly different from chance [@rydell_two_2006].
-However, like @heycke_two_2018 we did observe better-than-chance US recognition accuracy.
-We, therefore, have to assume that participants consciously perceived the briefly presented USs, which might have influenced our results.
-Hence, it is possible that the conscious perception of briefly presented USs constitutes a critical departure from the to-be-reproduced learning conditions.
-Although an exploratory analysis suggested that there was no relationship between US recognition accuracy and implicit evaluations (see SOM), we decided to repeat the experiment and reduced US visibility experimentally to more closely mimic the psychological conditions of the original learning task.
+Moreover, our results were consistent across three languages and countries indicating that neither inaccurate translations nor differences in sampled populations are likely to have caused the divergence from the original finding.
+Thus, our results raise more doubts about the replicability of the dissociative evaluative learning effect that was reported by @rydell_two_2006.
+
+There is, however, one objection our data cannot dispel: The close physical recreation of the original procedure does not guarantee a faithful reproduction of the psychological conditions of the original learning task.
+In the original study, recognition accuracy of the briefly flashed words was not significantly different from chance [@rydell_two_2006].
+Like @heycke_two_2018, however, we observed better-than-chance recognition accuracy.
+We have to assume that participants consciously perceived at least some of the briefly flashed words, which may have affected our results.
+Hence, it is possible that the conscious perception of briefly flashed words constitutes a critical departure from the to-be-reproduced learning conditions.
+Although an exploratory analysis suggested that there was no relationship between recognition accuracy and indirectly measured evaluations (see SOM), we decided to repeat the experiment and reduce the visibility of briefly flashed words to more closely mimic the psychological conditions of the original study.
 
@@
 
-To address the concern that our previous replication may have been unsuccessful because USs were consciously perceived (as indicated by above-chance US recognition accuracy), we will conduct a second study and reduce the presentation duration of USs during the learning task.
-
-## Visibility pilot study
+To address the concern that our previous replication may have been unsuccessful because briefly flashed words were consciously perceived, we will conduct a second study and reduce the presentation duration of the briefly flashed words during the learning task.
+
+## Pilot study
 
@@
 
-otm2p2f_mem_ttestBF <- ttestBF(otm2p2f_mem$Accuracy - 0.5
-                             , mu = 0, rscale = "medium"
-                             , nullInterval = c(0, Inf))[1] %>%
-  apa_print(gt1 = FALSE) %$%
-  full_result %>%
-  gsub("\\.0", ".5", .) %>%
-  gsub("\\$ ", "$, ", .)
-```
-
-To identify a presentation duration that replicates the psychological conditions of the original learning task (i.e., at-chance recognition accuracy for briefly presented USs), we ran a pilot study with a reduced US presentation duration of 13 ms (one frame on a 75 Hz CRT monitor) [^pilots].
-Because all subsequent studies will be conducted in English, the pilot study used the English material and instructions and was conducted at the University of Florida.
-Except for the shorter US presentation the methods were the same as in Experiment 1.
+otm2p2f_mem_ttest_nonsuperiority <- lm(Accuracy - 0.5 ~ 1, otm2p2f_mem) %>%
+  emmeans(~ 1) %>%
+  summary(side = "<", delta = 0.03, infer = TRUE) %>% 
+  apa_print %$%
+  statistic %$%
+  overall
+
+otm2p2f_mem_ttestBF <- ttestBF(
+  otm2p2f_mem$Accuracy - 0.5
+  , mu = 0
+  , rscale = "medium"
+  , nullInterval = c(0, Inf)
+)[1] %>%
+  apa_print() %$%
+  statistic
+```
+
+To identify a presentation duration that reproduces the psychological conditions of the original study (i.e., at-chance recognition accuracy for briefly flashed words), we ran a pilot study with a presentation duration reduced to 13 ms (one frame on a 75 Hz CRT monitor) [^pilots].
+Because all subsequent studies will be conducted in English, the pilot study used the English material and was conducted at the University of Florida.
+Except for the shorter presentation duration the methods were the same as in Experiment 1.
 For the pilot study, we recruited `r nrow(otm2p2f_demo)` participants (aged `r paste(range(otm2p2f_demo$Age), collapse = "-")` years, $M = `r mean(otm2p2f_demo$Age)`$; `r sum(grepl("female", otm2p2f_demo$Sex)) / nrow(otm2p2f_demo) * 100`% female).
@@
 
-The US identification performance was not significantly better than chance, `r otm2p2f_mem_ttest`, however the data provide no evidence for at-chance accuracy `r otm2p2f_mem_ttestBF`. 
-Although these results do not formally confirm that the shortened presentation duration yielded at-chance US visibility, the estimates of US memory accuracy are very similar to those from @rydell_two_2006 (`r rydell_mem_ci_res`).
-Further reduction of the presentation duration may eventually yield conclusive evidence for at-chance visibility, but it could inadvertently cause stimuli to become practically invisible.
-We will, therefore, conduct the final studies using a US presentation duration of 13 ms.
+Recognition accuracy for the briefly flashed words was not significantly better than chance, `r otm2p2f_mem_ttest`, but the Bayesian evidence for at-chance accuracy was inconclusive, `r otm2p2f_mem_ttestBF`.
+Based on these results we cannot rule out that, even with the shortened presentation duration, briefly flashed words were recognized above chance. 
+To confirm that the recognition accuracy was comparable to the original study, we performed a nonsuperiority test. 
+We compared the observed accuracy to the smallest deviation from at-chance accuracy that could have been detected in the original study, i.e., $M = 0.53$.
+The test confirmed that the recognition accuracy was comparable to that observed by @rydell_two_2006, , `r rydell_mem_ci_res`, `r otm2p2f_mem_ttest_nonsuperiority`. 
+Thus, we conclude that the visibility of words flashed for 13 ms is likely to be functionally comparable to that of the original study. 
+Of course the presentation duration could be reduced further to obtain conclusive evidence for at-chance visibility, but this runs the risk of inadvertently causing stimuli to become practically invisible.
+To safeguard against the possibility that the 13 ms presentation duration is already too brief, we will add a second presentation duration and flash words for for 20 ms in some locations[^alllocations].
+This means that across both studies, briefly flashed words will have been presented for 13 ms, 20 ms 24 ms, and 27 ms.
 
 [^pilots]:
-We ran a series of pilot studies in Dutch, which also yielded above-chance US memory.
-These pilot studies employed a shortened procedure, used Dutch material, or were conducted immediately after an unrelated priming study, which also used briefly presented words.
-We, therefore, decided a posteriori, that above-chance performance in these studies may not be informative for our subsequent replication attempt, as we will use only English materials in the next studies.
+We ran a series of pilot studies in Dutch, which also yielded above-chance recognition of briefly flashed words.
+These pilot studies employed a shortened procedure, used Dutch material, or were conducted immediately after an unrelated priming study, which also used briefly flashed words.
+We, therefore, decided a posteriori, that above-chance accuracy in these studies may not be informative for our subsequent replication attempt, as we will use only English materials in the next studies.
+
+[^alllocations]:
+In case we can collect data in all five locations, the following sentence will be added to the manuscript: 
+Three locations flashe words for 20 ms; only two locations flashed words for 13 ms because we also included the data of pilot study (N = `r nrow(otm2p2f_demo)`) in the overall analysis, which also used a 13 ms presentation duration.
 
@@
 
+### Material & Procedure
+
+We will use the same materials and procedure as in Experiment 1 but flash words for 13 ms or 20 ms.
+Furthermore, all labs will use the same Python script to collect the data and only the English material will be used to match the official language at all locations.
+
+### Data analysis
+
+<@~{#hongkong-exploration}
+
+The new data[^pilot2data] from all locations will be submitted to analyses analogous to those of Experiment 1. 
+We will, again, perform the analyses reported in the original study and assess replication success by performing Bayesian model comparisons. 
+In contrast to Experiment 1, all labs will use the same stimulus material and lab location will be partially confounded with the presentation duration of the briefly flashed words. 
+Thus, we will replace the lab location factor by presentation duration of the briefly flashed words in both analyses.
+Additionally, we will compare the data from Hong Kong to those from the American labs to explore whether our results are consistent across ethnicities and cultures.
+Given the consistent results in Experiment 1, we will omit the linear mixed model analysis of IAT response times.
+
+~@>
+
+To maximize the power of the planned contrasts in the frequentist ANOVA analyses, we will test whether valence order moderates the learning block contrasts by testing the main effect of learning block.
+If we detect no main effect of learning block, we will pool participants across valence orders by reversing the learning block coding in one group (as in the Bayesian model comparison of Experiment 1).
+Similarly, if the different presentation durations of flashed words do not moderate the learning block contrasts, we will pool participants across presentation durations.
+All data and analysis code will be made available in the OSF repository and linked to in the manuscript.
+
+[^pilot2data]: To ensure valid results, the pilot study for Experiment 2 employed the complete experimental procedure, that is, we also collected evaluative ratings and IAT responses.
+As of now, only the word recognition accuracy was analyzed; we have not looked at evaluative ratings and IAT responses.
+Once the data of the second, preregistered experiment are in, we will add the data from the pilot study to our final analyses.
+
 ### Participants
 
-We will run the experiment in Florida, Indiana, and Hong Kong.
-As in Experiment 1, 50 students will participate at each of three locations, yielding a total of $N = 150$ participants.
-All participants who sign up for the study before the intended $n = 50$ has been reached will be allowed to participate; hence, the final sample size could be slightly larger.
-We will exclude any participants from the analysis who abort the experiment or who ask us to remove their data (e.g., because they did not pay attention or did not follow the instructions).
-We will recruit additional participants to replace those excluded.
-<!--Participants will be compensated with xxxx.-->
-
-### Material & Procedure
-
-We will employ the same material and procedure as in Experiment 1 but use the shortened US presentation duration of 13 ms.
-Furthermore, all labs will use the same python script to collect the data and only the English material will be used to match the official language at all three locations.
-All materials are available at https://osf.io/8m3xb/.
-
-### Data analysis
-
-The new data[^pilot2data] from all locations will be jointly submitted to the same analyses as in Experiment 1.
-We will, again, perform the analyses reported in the original study, supplement the ANOVA analysis of IAT scores by a linear mixed model analysis, and assess the replication success by performing Bayesian model comparisons.
-All data and analysis code will be made available in the OSF repository and linked to in the manuscript.
-
-[^pilot2data]:
-To ensure representative results, the pilot study for Experiment 2 employed the complete experimental procedure, that is, we also collected evaluative ratings and IAT responses.
-As of now, only the US identification performance was analyzed; we have not looked at the explicit and implicit evaluation data.
-Once the data of the second, preregistered experiment are in, we will add the data from the pilot study to our final analyses.
+```{r otm2-omnibus-power, cache = TRUE}
+# Main effect block and three-way interaction
+otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
+  contrast_codes <- tibble::tibble(
+    time = rep(contr.treatment(2), 4)
+    , order = rep(rep(contr.sum(2), each = 2), 2)
+    , block = rep(contr.sum(2), each = 4)
+    , time_block = time * block
+    , time_order = time * order
+    , block_order = block * order
+    , time_block_order = time * block * order
+  )
+
+  mu <- with(
+    contrast_codes
+    , #-order * 0.25*f +
+      -block_order * f +
+      -block * 0.5 * f +
+      time_block_order * f
+  )
+
+  string <- "2w*2b*2b"
+  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")
+
+  design_result <- ANOVA_design(
+    design = string
+    , n = n
+    , mu = mu
+    , sd = 1
+    , r = rm_cor
+    , labelnames = labelnames
+  )
+
+  ANOVA_exact(
+    design_result
+    , alpha_level = alpha
+    , emm = FALSE
+    , verbose = FALSE
+  )
+}
+
+otm2_n_power <- 320/4
+
+# 95% power
+otm2_pes <- 0.039732
+otm2_dz <- pes_to_dz(otm2_pes, otm2_n_power, n_groups = 4)
+rho <- 0.5
+f <- dz_to_f(otm2_dz, rho)
+
+# otm2_time_power <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho, alpha = 0.05)
+# otm2_time_power$main_result
+
+# otm2_time_power$dataframe %>%
+#   mutate(
+#     order = ifelse(order == "order_n-p", "Negative-positive", "Positive-negative")
+#     , block = ifelse(block == "block_1", "1", "2")
+#     , time = ifelse(time == "time_13", "13 ms", "20 ms")
+#   ) %>%
+#   ggplot(aes(x = block, y = y, color = order, group = order)) +
+#   stat_summary(fun.y = mean, geom = "line") +
+#   stat_summary(fun.data = mean_cl_normal) +
+#   coord_cartesian(ylim = c(-0.6, 0.6)) +
+#   facet_grid(~ time) +
+#   guides(color = FALSE) +
+#   ggtitle("Assumed for power analysis") +
+#   labs(x = "Block", y = "Attitude") +
+#   theme_bw()
+
+otm2_dz_block <- f_to_dz(0.5*f, rho = rho)
+otm2_pes_block <- dz_to_pes(otm2_dz_block, otm2_n_power, n_groups = 4)
+
+otm2_dz_int <- f_to_dz(f, rho = rho)
+otm2_pes_int <- dz_to_pes(otm2_dz_int, otm2_n_power, n_groups = 4)
+```
+
+```{r otm2-contrast-power, cache = TRUE}
+otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
+  contrast_codes <- tibble::tibble(
+    time = rep(contr.treatment(2), 4)
+    , order = rep(rep(contr.sum(2), each = 2), 2)
+    , block = rep(contr.sum(2), each = 4)
+    , time_block = time * block
+    , time_order = time * order
+    , block_order = block * order
+    , time_block_order = time * block * order
+  )
+
+  mu <- with(
+    contrast_codes
+    , -order * 0.25*f +
+      -block_order * f
+  )
+
+  string <- "2w*2b*2b"
+  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")
+
+  design_result <- ANOVA_design(
+    design = string
+    , n = n
+    , mu = mu
+    , sd = 1
+    , r = rm_cor
+    , labelnames = labelnames
+  )
+
+  ANOVA_exact(
+    design_result
+    , alpha_level = alpha
+    , emm = TRUE
+    , verbose = FALSE
+    , contrast_type = "pairwise"
+    , emm_comp = "block | time * order"
+  )
+}
+
+# Learning block contrasts
+
+## Simple contrasts
+### 95% power
+otm2_pes <- 0.039732
+otm2_dz <- pes_to_dz(otm2_pes, otm2_n_power, n_groups = 4)
+# rho <- 0.5
+# f <- dz_to_f(otm2_dz, rho)
+# 
+# otm2_contrast_power <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_contrast_power
+
+### 80% power
+otm2_pes2 <- 0.0243813
+otm2_dz2 <- pes_to_dz(otm2_pes2, otm2_n_power, n_groups = 4)
+# f <- dz_to_f(otm2_dz2, rho)
+# 
+# otm2_contrast_power2 <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho)$emmeans$contrasts %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_contrast_power2
+
+## Collapsed once
+### 95% power
+otm2_dz_between_collapsed <- f_to_dz(dz_to_f(otm2_dz, rho) / sqrt(2), rho)
+otm2_pes_between_collapsed <- dz_to_pes(otm2_dz_between_collapsed, otm2_n_power, n_groups = 4)
+# f <- dz_to_f(otm2_dz_between_collapsed, rho)
+# 
+# otm2_time_collapsed_contrast_power <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block | order) %>%
+#   pairs %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_time_collapsed_contrast_power
+
+### 80% power
+otm2_dz2_between_collapsed <- f_to_dz(dz_to_f(otm2_dz2, rho) / sqrt(2), rho)
+otm2_pes2_between_collapsed <- dz_to_pes(otm2_dz2_between_collapsed, otm2_n_power, n_groups = 4)
+# f <- dz_to_f(otm2_dz2_between_collapsed, rho)
+# 
+# otm2_time_collapsed_contrast_power2 <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block | order) %>%
+#   pairs %>%
+#   emmeans_power(alpha = 0.05) %>%
+#   .[1, ]
+# otm2_time_collapsed_contrast_power2
+
+## Collapsed twice
+### 95% power
+otm2_dz_collapsed <- f_to_dz(dz_to_f(otm2_dz, rho) / sqrt(4), rho)
+otm2_pes_collapsed <- dz_to_pes(otm2_dz_collapsed, otm2_n_power, n_groups = 4)
+# f <- dz_to_f(otm2_dz_collapsed, rho)
+# 
+# otm2_collapsed_contrast_power <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block * order) %>%
+#   contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>%
+#   emmeans_power(alpha_level = 0.05)
+# otm2_collapsed_contrast_power
+
+### 80% power
+otm2_dz2_collapsed <- f_to_dz(dz_to_f(otm2_dz2, rho) / sqrt(4), rho)
+otm2_pes2_collapsed <- dz_to_pes(otm2_dz2_collapsed, otm2_n_power, n_groups = 4)
+# f <- dz_to_f(otm2_dz2_collapsed, rho)
+# 
+# otm2_collapsed_contrast_power2 <- otm2_power(f = f, n = otm2_n_power, rm_cor = rho)$emmeans$emmeans %>%
+#   emmeans(specs = ~ block * order) %>%
+#   contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>%
+#   emmeans_power(alpha_level = 0.05)
+# otm2_collapsed_contrast_power2
+```
+
+If the current SARS-CoV-2 pandemic premits, we will recruit `r otm2_n_power` participants at Yale University, the University of Florida, the University of Hong Kong, Indiana University Bloomington, and Williams College, but in no less than four of these locations.
+As in Experiment 1, all participants who sign up, before the planned sample size has been reached will be allowed to participate. 
+We will, again, recruit additional participants to replace those excluded, unless data removal is requested after completion of the data collection.
+
+### Statistical power
+
+<@~{#power2}
+
+As for Experiment 1, our assessment of the statistical senstivitiy of our design focused on the tests of simple *learning block* effects.
+Across the minimum of four locations, our planned contrasts will have 95% power to detect learning block effects as small as $\delta_z = `r otm2_dz`$ ($\eta_p^2 = `r printp(otm2_pes)`$) or as small as $\delta_z = `r otm2_dz_between_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_between_collapsed)`$) and $\delta_z = `r otm2_dz_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_collapsed)`$) when pooling participants across one or both between-participant factors ($N = `r otm2_n_power * 4`$, $\alpha = .05$, two-sided tests).[^impliedd]
+The tests of the main effect of learning block and the three-way interaction, on which we will base our decision to pool participants across the between-subject conditions, will have 95% power to detect effecs as small as  $\delta_z = `r otm2_dz_block`$ ($\eta_p^2 = `r printp(otm2_pes_block)`$) and
+$\delta_z = `r otm2_dz_int`$ ($\eta_p^2 = `r printp(otm2_pes_int)`$), respectively ($N = `r otm2_n_power * 4`$, $\alpha = .05$, two-sided tests).
+Thus, our design is sufficiently sensitive to detect (or rule out) differences 13% smaller (39% or 57% when pooling participants across one or both between-participant factors, respectively) than the smallest learning block difference reported by @rydell_two_2006.
+Note that these are conservative estimates as they do not take into account the additional `r nrow(otm2p2f_demo)` participants from our pilot study that we will include in the analysis and because we may collect data in five rather than four locations.
+
+~@>
 

### 2020-12-03 analysis_and_paper/supplements.Rmd
Adds updated files following IPA at PS.

--- 2019-10-31 analysis_and_paper/supplements.Rmd
@@
     email         : "tobias.heycke@gesis.org"
+    equal_contrib : yes
   - name          : Frederik Aust
-    affiliation : 1
+    affiliation   : "1,9"
+    equal_contrib : yes
   - name          : Mahzarin R. Banaji
     affiliation   : 3
-  - name        : John G. Conway
-    affiliation : 4
+  - name          : Jeremy Cone
+    affiliation   : 8
   - name          : Pieter Van Dessel
     affiliation   : 5
+  - name          : Melissa J. Ferguson
+    affiliation   : 10
   - name          : Xiaoqing Hu
@@
   - name          : Benedek Kurdi
-    affiliation : 3    
+    affiliation   : "3,10"
   - name          : Robert Rydell
@@
     institution   : Indiana University
+  - id            : 8
+    institution   : Williams College
+  - id            : 9
+    institution   : University of Amsterdam
+  - id            : 10
+    institution   : Yale University
 
 bibliography      : ["references.bib", "r-references.bib"]
-#appendix          : "appendix.Rmd"
 
@@
 theme_set(theme_apa())
-
-## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
-# assignInNamespace("theme_nothing", function() {
-#     theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
-# }, "cowplot")
 
@@
 
+In the following we report details on our power analyses, the model specifications used for the Bayesian model comparisons, and additional secondary analyses.
+
+# Sensitivity of our design
+
+```{r otm1-power-results}
+som_cache <- "manuscript_cache/latex/"
+rydell_pes <- knitr::load_cache(label = "rydell-effects", object = "rydell_pes", path = som_cache)
+rydell_dz <- knitr::load_cache(label = "rydell-effects", object = "rydell_dz", path = som_cache)
+otm1_n_power <- knitr::load_cache(label = "otm1-power", object = "otm1_n_power", path = som_cache) * 2
+otm1_pes <- knitr::load_cache(label = "otm1-power", object = "otm1_pes", path = som_cache)
+otm1_dz <- knitr::load_cache(label = "otm1-power", object = "otm1_dz", path = som_cache)
+
+otm2_n_power <- knitr::load_cache(label = "otm2-omnibus-power", object = "otm2_n_power", path = som_cache) * 4
+otm2_pes <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes", path = som_cache)
+otm2_dz <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz", path = som_cache)
+otm2_pes_between_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes_between_collapsed", path = som_cache)
+otm2_dz_between_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz_between_collapsed", path = som_cache)
+otm2_pes_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes_collapsed", path = som_cache)
+otm2_dz_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz_collapsed", path = som_cache)
+```
+
+As noted in the main text, our assessment of the statistical senstivitiy of our design focused the tests of simple *learning block* effects, because they are of primary theoretical interest and less sensitive than the test of the interaction.
+In Experiment 1, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm1_dz`$ ($\eta_p^2 = `r printp(otm1_pes)`$).
+In Experiment 2, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm2_dz`$ ($\eta_p^2 = `r printp(otm2_pes)`$) or as small as $\delta_z = `r otm2_dz_between_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_between_collapsed)`$) and $\delta_z = `r otm2_dz_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_collapsed)`$) when pooling participants across one or both between-participant factors ($N = `r otm2_n_power * 4`$, $\alpha = .05$, two-sided tests).
+Figure\ \@ref(fig:power-curve-plot) illustrates the implied sensitivity of our designs in units of Cohen's $\delta$ as a function of the assumed repeated-measures correlation $\rho$.
+Note that these are conservative estimates as they do not take into account the additional 60 participants from our pilot study that we included in the analysis.
+
+(ref:otm1-power-curve) Sensitivity curves for simple learning block effects in Experiment 1 (**A**) and Experiment 2 (**B**) as a function of the assumed repeated measures correlation.
+Simple contrast are estimated within each *flashed word presentation duration*-*valence order* combination (not adjusted for multiple comparisons).
+Collapsed contrasts pool participants across one or both  of the between subject factors (i.e., *flashed word presentation duration* and *valence order*).
+$\delta_z$-values in the legend correspond to 95% and 80% power.
+Note that these are conservative estimates as they do not take into account the additional 60 participants from our pilot study that we included in the analysis.
+The grey dashed line at the top represents the smallest learning block difference reported by Rydell et al. [$d_z = `r rydell_dz`$; -@rydell_two_2006].
+
+```{r power-curve-plot, fig.width = 7, fig.height = 8, fig.cap = "(ref:otm1-power-curve)"}
+rydell_power_curve <- tibble(
+  rho = seq(-1, 1, length.out = 100)
+  , delta = c(
+    dz_to_f(rydell_dz, unique(rho)) * 2
+    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
+  )
+  , power = NA
+)
+
+otm1_power_curve <- tibble(
+  rho = rep(seq(-1, 1, length.out = 100), 2)
+  , delta = c(
+    dz_to_f(otm1_dz, unique(rho)) * 2
+    , dz_to_f(otm1_dz2, unique(rho)) * 2
+  )
+  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
+)
+
+otm1_power_curve_plot <- otm1_power_curve %>% 
+  mutate(
+    power = relevel(factor(power), "0.95")
+  ) %>% 
+  ggplot(aes(x = rho, y = delta, group = power, linetype = power)) +
+  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
+  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
+  geom_line() +
+  # annotate("text", x = 1, y = 0.9, label = paste0("list(alpha ==~\".05\", italic(N) ==", otm1_n, ", epsilon == 1)"), parse = TRUE, hjust = 1, vjust = 0.5) +
+  ylim(c(0, 1)) +
+  scale_linetype_discrete(
+    labels = c(
+      bquote(.(unique(otm1_power_curve$power)[1])~~(delta[z] == .(printnum(otm1_dz))))
+      , bquote(.(unique(otm1_power_curve$power)[2])~~(delta[z] == .(printnum(otm1_dz2))))
+    )
+  ) +
+  labs(
+    x = bquote("Correlation between learning blocks ["*rho*"]")
+    , y = bquote("Learning block difference [Cohen's"~delta*"]")
+    , color = "Contrast"
+    , linetype = bquote("Power"~"["*1 - beta*"]")
+  ) +
+  ggtitle("", subtitle = bquote(list(italic(N) == .(otm1_n_power*2), alpha ==~".05", "two-sided"))) +
+  theme_apa(box = TRUE) + 
+  theme(
+    panel.grid.major.x = element_line()
+    , panel.grid.major.y = element_line()
+    , panel.grid.minor.x = element_line()
+    , panel.grid.minor.y = element_line()
+    # , legend.position = c(0.99, 0.99)
+    , legend.justification = "top"
+    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
+  )
+
+rydell_power_curve <- tibble(
+  rho = seq(-1, 1, length.out = 100)
+  , delta = c(
+    dz_to_f(rydell_dz, unique(rho)) * 2
+    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
+  )
+  , power = NA
+)
+
+otm1_power_curve <- tibble(
+  rho = rep(seq(-1, 1, length.out = 100), 2)
+  , delta = c(
+    dz_to_f(otm1_dz, unique(rho)) * 2
+    , dz_to_f(otm1_dz2, unique(rho)) * 2
+  )
+  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
+)
+
+otm2_power_curve_plot <- tibble(
+  rho = rep(seq(-1, 1, length.out = 100), 2)
+  , otm2_delta_simple = c(
+    dz_to_f(otm2_dz, unique(rho)) * 2
+    , dz_to_f(otm2_dz2, unique(rho)) * 2
+  )
+  , otm2_delta_between_collapsed = c(
+    dz_to_f(otm2_dz_between_collapsed, unique(rho)) * 2
+    , dz_to_f(otm2_dz2_between_collapsed, unique(rho)) * 2
+  )
+  , otm2_delta_collapsed = c(
+    dz_to_f(otm2_dz_collapsed, unique(rho)) * 2
+    , dz_to_f(otm2_dz2_collapsed, unique(rho)) * 2
+  )
+  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
+) %>% 
+  pivot_longer(cols = matches("otm"), names_to = "contrast", values_to = "delta") %>%
+  mutate(
+    power = relevel(factor(power), "0.95")
+    , contrast = gsub("otm2_delta_", "", contrast)
+    , contrast = gsub("_", " ", contrast)
+    , contrast = factor(contrast, levels = c("simple", "between collapsed", "collapsed"))
+  ) %>% 
+  ggplot(aes(x = rho, y = delta, color = contrast, group = interaction(power, contrast), linetype = power)) +
+  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
+  # geom_line(data = otm1_power_curve, aes(group = power, linetype = power, color = "simple"), alpha = 0.3) +
+  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
+  geom_line() +
+  scale_color_viridis_d(
+    end = 0.8
+    , labels = c(
+      bquote("Simple               "~delta[z] %in% "{"*.(printnum(otm2_dz))*", "*.(printnum(otm2_dz2))*"}")
+      , bquote("Collapsed once   "~delta[z] %in% "{"*.(printnum(otm2_dz_between_collapsed))*", "*.(printnum(otm2_dz2_between_collapsed))*"}")
+      , bquote("Collapsed twice   "~delta[z] %in% "{"*.(printnum(otm2_dz_collapsed))*", "*.(printnum(otm2_dz2_collapsed))*"}")
+    )
+  ) +
+  ylim(c(0, 1)) +
+  labs(
+    x = bquote("Correlation between learning blocks ["*rho*"]")
+    , y = bquote("Learning block difference [Cohen's"~delta*"]")
+    , color = "Contrast"
+    , linetype = bquote("Power"~"["*1 - beta*"]")
+  ) +
+  ggtitle("", subtitle = bquote(list(italic(N) == .(otm2_n_power*4), alpha ==~".05", "two-sided"))) +
+  theme_apa(box = TRUE) + 
+  theme(
+    panel.grid.major.x = element_line()
+    , panel.grid.major.y = element_line()
+    , panel.grid.minor.x = element_line()
+    , panel.grid.minor.y = element_line()
+    # , legend.position = c(0.99, 0.99)
+    , legend.justification = "top"
+    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
+  )
+
+plot_grid(
+  plot_grid(otm1_power_curve_plot, NULL, rel_widths = c(1, 1 - 5.65/7))
+  , otm2_power_curve_plot
+  , nrow = 2
+  , ncol = 1
+  , labels = "AUTO"
+)
+```
+
 # Experiment 1
 
-In the following we report additional analyses and provide details for the model specification used for the Bayesian model comparisons.
-We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between US recognition accuracy and associative learning.
+In the following we report details on our power analysis, the model specification used for the Bayesian model comparisons, and additional secondary analyses.
+We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between the recognition accuracy of briefly flashed words and indirectyl measured evaluations.
 Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.
@@
 The ANOVA of IAT scores reported in the main text ignores potential systematic trial-to-trial variability in IAT response latencies due to stimuli.
-Any such systematic but unaccounted-for variance can inflate test statistics and yield underestimated $p$ values as well as underestimated confidence intervals.
+Any such systematic but unaccounted-for variance can inflate test statistics and yield anticonservative $p$ values as well as underestimated confidence intervals.
 We, therefore, also conducted a linear mixed model analysis of response times with crossed random effects for participants and items to ensure that our conclusion are not contingent on inadvertent stimulus effects [for details see @wolsiefer_modeling_2017].
@@
 To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
-Hence, larger values represent more favorable implicit evaluations.
+Hence, larger values indicate more favorable evaluations.
 
@@
   )
+```
+
+```{r explore-salience-asymmetry, eval = FALSE}
+# Main effect of response mapping is significant for both image types
+otm1_iat_lmerTest %>%
+  emmeans(specs = ~ Congruent | imageType, at = list(imageType = c(-1, 1))) %>%
+  pairs()
 ```
@@
 
-In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the learned behaviors were first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
-Vice versa, response time differences suggested more favorable evaluations after the second than after the first block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
-Again, these results indicate that the explicit evaluations and IAT scores were consistent.
+Also in line with the ANOVA analysis, we found that response time differences indicated *more* favorable evaluations after the first than after the second block when the behavioral information was first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
+Vice versa, response time differences indicated *less* favorable evaluations after the first than after the second block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
+Again, these results indicate that the rating and IAT scores did not dissociate.
 
@@
 
-#### Explicit and implicit measures
+#### Directly and indirectly measured evaluations
 
@@
 
-```{r load-data-and-design-matrices}
-tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-restructure_", recursive = TRUE)[1]))
-tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-design-matrix_", recursive = TRUE)[1]))
+```{r otm1-prior-sensitivity-replication, cache = TRUE, warning = FALSE}
+manuscript_cache <- "manuscript_cache/latex/"
 
+otm1_attitudes_collapsed <- knitr::load_cache(label = "otm1-bayesian-replication-restructure", object = "otm1_attitudes_collapsed", path = manuscript_cache)
 otm1_n <- as.integer(nlevels(otm1_attitudes_collapsed$ParticipantNumber))
-```
 
-```{r otm1-prior-sensitivity-replication, cache = TRUE, warning=FALSE}
+otm1_null_model_matrix <- knitr::load_cache(label = "otm1-bayesian-replication-design-matrix", object = "otm1_null_model_matrix", path = manuscript_cache)
+otm1_unconstrained_model_matrix <- knitr::load_cache(label = "otm1-bayesian-replication-design-matrix", object = "otm1_unconstrained_model_matrix", path = manuscript_cache)
+
 replication_rscales <- expand.grid(
@@
 We, therefore, varied the scale for the Cauchy priors on the simple effects in the ranges of $`r min(replication_rscales$rating)` < r_\alpha < `r max(replication_rscales$rating)`$ and $`r min(replication_rscales$iat)` < r_\beta < `r max(replication_rscales$iat)`$ for rating and IAT scores, respectively.
-Considering results previous studies, we limited our reanalysis to combinations where the prior scale was larger for rating than for IAT effects.
+In light of the results from previous studies, we limited our analysis to combinations where the prior scale was larger for rating than for IAT effects.
 The results of the prior sensitvity analysis reassure us that our inference is robust to a wide range and combination of scales of the default Cauchy priors, see Table\ \@ref(tab:otm1-prior-sensitivity-replication-table).
 The Bayes factors were not affected by the scale of the priors to any meaningful degree.
-This is because our data are informative enough to overwhelm the priors and because these Bayes factors primarily depend on the shape and location of the posterior distribution, not the prior distributions [@klugkist_bayesian_2005].
+This is because our data are informative enough to overwhelm the priors and because these Bayes factors primarily depend on the shape and location of the joint posterior distribution [@klugkist_bayesian_2005].
 
@@
 
-(ref:otm1-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$ (see footnote 1 in the main article).
+(ref:otm1-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$.
 $r_\alpha$ and $r_\beta$ denote the scale for the Cauchy prior on the simple effects of learning block for rating scores ($\alpha$) and IAT scores ($\beta$), respectively (in units of standard deviations).
@@
     bf_one_mind_two_minds = papaja:::typeset_scientific(bf_one_mind_two_minds)
-    , bf_one_mind_two_minds = paste0("$", bf_one_mind_two_minds, "$")
+    # , bf_one_mind_two_minds = paste0("$", bf_one_mind_two_minds, "$")
   ) %>%
@@
   printnum(digits = 2, format = "e") %>%
-  papaja:::typeset_scientific()
+  papaja:::typeset_scientific() %>%
+  papaja:::strip_math_tags()
 ```
@@
 
-## Prime recogniton and implicit evaluations
+## Word recogniton and IAT score differences
 
@@
 
-In contrast to the original results reported by @rydell_two_2006, US recognition accuracy in this study was above chance, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
-Memory for USs may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
-We, therefore, performed an exploratory regression analysis of US recognition and the IAT score difference between blocks used in the Bayesian analysis above.
-Positive values represent a more favorable evaluation after the block in which Bob was paired with positive learned behaviors and briefly presented negative USs.
-Conversely, negative IAT score difference between blocks indicate that the IAT effects reflect the valence of the briefly presented USs.
-If US recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between US recognition accuracy and IAT score differences between blocks:
-When US recognition is high, IAT score differences should reflect the valence of the learned behaviors but not with the US valence.
-We would expect to observe smaller and eventually negative IAT score differences as US recognition accuracy declines and associative learning takes over.
+In contrast to the original results reported by @rydell_two_2006, the recognition accuracy of briefly flashed words was above chance in this study, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
+Memory for these words may, thus, have interfered with the associative learning process and prevented the predicted reversal of IAT score differences between learning blocks.
+We, therefore, performed an exploratory regression analysis of IAT score difference and recognition accuracy of briefly flashed words.
+Positive IAT score differences indicate a more favorable evaluation after the block in which we presented positive behavioral information and briefly flashed negative words.
+If word recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between the recognition accuracy and IAT score differences between blocks:
+When the recognition for briefly flashed words is high, IAT score differences should be positive, that is reflect the valence of the behavioral information.
+We would expect to observe smaller and eventually negative IAT score differences as the recognition accuracy declines and associative learning takes over.
+To account for measurement error in the recognition accuracy of briefy flashed words we fit an errors-in-variable regression model [@Klauer_Draine_Greenwald_1998].
+Because the model assumes that predictor values are sampled from a Gaussian distribution truncated at 0, we probit-transformed the recognition accuracy.^[A standard linear regression analysis yielded the same results.]
 
-(ref:prime-recognition-iat-difference) Scatterplot of prime recognition accuracy and evaluative differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
+(ref:prime-recognition-iat-difference) Scatterplot of the recognition accuracy of briefly flashed words (on probit scale) and evaluative differences in IAT scores between learning blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
+The regression line and confidence band represents predictions of the errors-in-variables model [@Klauer_Draine_Greenwald_1998].
 
@@
   ggplot(aes(x = Accuracy, y = delta)) +
-  geom_hline(yintercept = 0, linetype = "dotted") +
-  geom_vline(xintercept = 0.5, linetype = "dotted") +
+  geom_hline(yintercept = 0, linetype = "22") +
+  geom_vline(xintercept = 0.5, linetype = "22") +
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", color = "black") +
+  geom_smooth(method = "eiv_lm", color = "black") +
+  # geom_smooth(method = "lm", color = "black") +
   labs(
-    x = "US recognition accuracy"
+    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
     , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
   ) +
+  scale_x_continuous(trans = "probit") +
   theme_apa()
@@
 ```{r prime-recognition-iat-difference-regression, results = "asis"}
-otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
+# otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
+#   filter(Measure == "IATscore") %>%
+#   mutate(Accuracy = Accuracy - 0.5) %>%
+#   as.data.frame %>%
+#   lmBF(delta ~ Accuracy, data = .) %>%
+#   apa_print
+# 
+# otm1_iat_delta_lm_res <- otm1_iat_delta %>%
+#   filter(Measure == "IATscore") %>%
+#   mutate(Accuracy = Accuracy - 0.5) %>%
+#   lm(delta ~ Accuracy, data = .) %>% 
+#   apa_print
+
+otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
   filter(Measure == "IATscore") %>%
-  mutate(Accuracy = Accuracy - 0.5) %>%
-  as.data.frame %>%
-  lmBF(delta ~ Accuracy, data = .) %>%
-  apa_print
-
-otm1_iat_delta_lm_res <- otm1_iat_delta %>%
-  filter(Measure == "IATscore") %>%
-  mutate(Accuracy = Accuracy - 0.5) %>%
-  lm(delta ~ Accuracy, data = .) %>% 
+  mutate(Accuracy = qnorm(Accuracy)) %>%
+  eiv_lm(delta ~ Accuracy, data = ., n.optim = 10) %>% 
   apa_print
@@
 
-However, we were unable to detect any relationship between US recognition accuracy and IAT score differences between blocks, `r otm1_iat_delta_lm_res$full_result$Accuracy`; the data even provide some evidence against such a relationship, `r otm1_recognition_iat_lm_bf$statistic`.
-We centered US recognition at .5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance US recognition accuracy, `r otm1_iat_delta_lm_res$full_result$Intercept`.
-Hence, even for participants who exhibited no memory for briefly presented USs, IAT score differences reflected the valence of the learned behaviors, see Figure\ \@ref(fig:prime-recognition-iat-difference).
-These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance US recognition accuracy in this study.
+We did not detect a relationship between the recognition accuracy of briefly preseted words and IAT score differences between learning blocks, `r otm1_iat_delta_eiv_lm_res$full_result$Accuracy`.
+Moreover, the positive intercept of the regression line indicates a positive IAT score difference despite at-chance word recognition accuracy, `r otm1_iat_delta_eiv_lm_res$full_result$Intercept`.
+Hence, even for participants who did not recognize the briefly flashed words, IAT score differences reflected the valence of the behavioral information, see Figure\ \@ref(fig:prime-recognition-iat-difference).
+These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance recognition of briefly flashed words in this study.
 
@@
 
+```{r create_r-references}
+r_refs(file = "r-references.bib")
+```
+
 \newpage

### 2020-12-03 analysis_and_paper/error_in_variables.R

@@ -218,19 +218,19 @@ apa_print.eiv_lm <- function(
   
   ## Assemble regression table
   regression_table <- data.frame(tidy_x[, c("term", "estimate", "statistic", "p.value")], row.names = NULL)
-  regression_table$ci <- apply(
-    tidy_x[, utils::tail(names(tidy_x), 2)]
+  regression_table$conf.int <- apply(
+    ci
     , 1
     , function(y) do.call(function(...) papaja:::print_confint(x = y[utils::tail(names(y), 2)], ...), ellipsis) # Don't add "x% CI" to each line
   )
-  regression_table <- regression_table[, c("term", "estimate", "ci", "statistic", "p.value")] # Change order of columns
+  regression_table <- regression_table[, c("term", "estimate", "conf.int", "statistic", "p.value")] # Change order of columns
   regression_table$term <- papaja:::prettify_terms(regression_table$term, standardized = FALSE)
   
   regression_table$estimate <- do.call(function(...) papaja::printnum(regression_table$estimate, ...), ellipsis)
   regression_table$statistic <- papaja::printnum(regression_table$statistic, digits = 2)
   regression_table$p.value <- papaja::printp(regression_table$p.value)
   
-  colnames(regression_table) <- c("predictor", "estimate", "ci", "statistic", "p.value")
+  colnames(regression_table) <- c("term", "estimate", "conf.int", "statistic", "p.value")
   
   if(stat_name == "z") {
     test_statistic <- paste0("$", stat_name, "$")
@@ -239,9 +239,9 @@ apa_print.eiv_lm <- function(
   }
   
   papaja::variable_label(regression_table) <- c(
-    predictor = "Predictor"
+    term = "Predictor"
     , estimate = paste0("$", est_name, "$")
-    , ci = paste0(conf_level, "\\% CI")
+    , conf.int = paste0(conf_level, "\\% CI")
     , statistic = test_statistic
     , p.value = "$p$"
   )

### 2021-09-10 analysis_and_paper/manuscript.Rmd
Adds IPA-note to manuscript.
Preparations for Experiment 2 data collection

@@
 note: |
+  This manuscript has been accepted in-principle as a registered report at *Psychological Science*. Data for Experiment 2 will be collected when the SARS-CoV-2 pandemic permits.
   \clearpage
@@
 
-otm1_incomplete_data <- otm1_n_trials$ParticipantNumber[
-  with(
-    otm1_n_trials
-    , Eval != 2 ||
-      RT != 160 ||
-      NumbercorrectIdent != 1
-  )
-]
+otm1_incomplete_data <- otm1_n_trials %>% 
+  rowwise %>% 
+  mutate(
+    incomplete = (Eval != 2 || RT != 160 || NumbercorrectIdent != 1)
+  ) %>% 
+  filter(incomplete) %>% 
+  pull(ParticipantNumber)
 

### 2021-09-10 analysis_and_paper/supplements.Rmd
Preparations for Experiment 2 data collection

@@
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "eiv_lm", color = "black") +
+  geom_smooth(method = "eiv_lm", color = "black", method.args = list(n.optim = 50)) +
   # geom_smooth(method = "lm", color = "black") +
@@
   mutate(Accuracy = qnorm(Accuracy)) %>%
-  eiv_lm(delta ~ Accuracy, data = ., n.optim = 10) %>% 
+  eiv_lm(delta ~ Accuracy, data = ., n.optim = 50) %>% 
   apa_print

### 2021-09-10 otm2/preregistration/power_analyses.Rmd
Preparations for Experiment 2 data collection

---
title             : "Power analyses for OTM2"
author            : "Frederik Aust"
date              : "`r format(Sys.time(), '%d %B, %Y')`"

output:
  bookdown::html_document2:
    theme         : "spacelab"
    df_print      : "kable"
    code_folding  : "hide"
    toc           : true
    toc_float     : true
---

```{r setup, include = FALSE}
library("tidyr")
library("dplyr")
library("ggplot2")
library("cowplot")
library("papaja")

library("pwr")
library("emmeans")

# devtools::install_github("arcaldwell49/Superpower")
library("Superpower")

source("../../analysis_and_paper/effect_sizes.R")
```

Because it grants greater flexibility for ANOVA designs, I here used the in-development R package `Superpower`.
The make sure I'm doing this right, I first reproduced the power analyses done in G*Power for OTM1.

# OTM 1

The following gives the interaction power for the effect size estimated in the G*Power sensitivity analysis

```{r}
contrast_code <- tibble::tibble(
  a = rep(contr.sum(2), 2)
  , b = rep(contr.sum(2), each = 2)
  , x = a*b * -1
)$x

f <- 0.1481313
mu <- f * contrast_code
n <- 75
r <- 0.5
alpha_level <- 0.05

string <- "2w*2b"
labelnames <- c("block", "1", "2", "order", "n-p", "p-n")

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = r
  , labelnames = labelnames
)

otm1_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | order"
)

otm1_power$main_results
```

as well as the power for the block contrasts

```{r}
otm1_power$emm_results
```

However, this doesn't give the result for the desired contrast that collapses over the counterbalancing factor, nor for a directional test.
I contributed a pull request to `Superpower` to enable power analyses for contrasts specified with `emmeans`.
The following gives the result for the collapsed contrast

```{r}
custom_contrast <- contrast(
  emmeans(
    otm1_power$emmeans$emmeans
    , specs = ~ order * block
  )
  , list(block_effect = c(0.5, -0.5, -0.5, 0.5))
)

emmeans_power(custom_contrast, alpha_level = 0.05)
```

which is the same as doing a within-subject t-test in this case.

```{r}
pwr.t.test(n = 150, d = 2*f, sig.level = 0.05, type = "paired")
```

To get the power for the directional test, I can increase the alpha level as needed, which shows that this contrast is the same as the within-subject t-test collapsing data across groups.

```{r}
emmeans_power(custom_contrast, alpha_level = 0.1)
pwr.t.test(150, sig.level = 0.05, d = 2*f, type = "paired", alternative = "greater")
```

This now also allows me to get the power for the one-sided tests of the uncollapsed contrasts

```{r}
emmeans_power(otm1_power$emmeans$contrasts, alpha_level = 0.1)
```

Anyway, the following reproduces the G*Power sensitivity analysis for the collapsed contrast.

```{r}
pwr.t.test(150, sig.level = 0.05, power = 0.95, type = "paired", alternative = "greater")
```

<!--

```{r}
knitr::opts_chunk$set(eval = FALSE)
```

## More elaborate considerations of repeated-measure correlations

The following is a table of repeated measure correlations from OTM1 across locations.

```{r}
readRDS("../../otm1/results/data_processed/otm1_attitudes_cleaned.rds") %>%
  mutate(
      Eval = scale(Eval) %>% as.numeric
      , IATscore = scale(IATscore) %>% as.numeric
  ) %>%
  gather("Measure", "Attitude", Eval, IATscore) %>%
  mutate(Measure = factor(Measure)) %>%
  pivot_wider(names_from = c("Block", "Measure"), values_from = "Attitude") %>%
  select_if(is.numeric) %>%
  psych::corr.test()
```

```{r}
otm1_power <- function(f, rm_cor, n = 76, alpha = 0.05) {
  contrast_code <- tibble::tibble(
    a = rep(contr.sum(2), 2)
    , b = rep(contr.sum(2), each = 2)
    , x = a*b * -1
  )$x

  mu <- f * contrast_code

  cor_mat <- diag(4)
  triangular <- c(0, 1, 0, 0, 1, 0)
  cor_mat[upper.tri(cor_mat)] <- triangular * rm_cor
  cor_mat[lower.tri(cor_mat)] <- triangular * rm_cor

  string <- "2w*2b"
  labelnames <- c("block", "1", "2", "order", "n-p", "p-n")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = cor_mat
    , labelnames = labelnames
  )

  otm1_power <- ANOVA_exact(
    design_result
    , alpha_level = alpha
    , emm = TRUE
    , verbose = FALSE
    , contrast_type = "pairwise"
    , emm_comp = "block | order"
  )

  otm1_power
}
```

### Evaluative ratings

```{r}
eval_rm_cor <- -0.8
otm1_f_eval_anova <- 0.27918

otm1_power_eval_anova <- otm1_power(f = otm1_f_eval_anova, rm_cor = eval_rm_cor)
otm1_power_eval_anova_int <- otm1_power_eval_anova$main_result

otm1_power_eval_anova_int$generalized_eta_squared <- afex::aov_4(
  y ~ block * order + (block | subject)
  , data = otm1_power_eval_anova$dataframe
)$anova_table$ges
otm1_power_eval_anova_int
```

Without Bonferroni-correction for the order-wise two-sided contrasts

```{r}
otm1_f_eval_contrast <- 0.39482
emmeans_power(otm1_power(f = otm1_f_eval_contrast, rm_cor = eval_rm_cor)$emmeans$contrasts, alpha_level = 0.05)
```

For the collapsed two-sided contrasts

```{r}
otm1_power(f = 0.2543, rm_cor = eval_rm_cor)$emmeans$emmeans %>%
  emmeans(specs = ~ block * order) %>%
  contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>% 
  emmeans_power(alpha_level = 0.1)
```

### IAT scores

```{r}
iat_rm_cor <- -0.6 * sqrt(0.5^2)
otm1_f_iat_anova <- 0.23726

otm1_power_iat_anova <- otm1_power(f = otm1_f_iat_anova, rm_cor = iat_rm_cor)
otm1_power_iat_anova_int <- otm1_power_iat_anova$main_result

otm1_power_iat_anova_int$generalized_eta_squared <- afex::aov_4(
  y ~ block * order + (block | subject)
  , data = otm1_power_iat_anova$dataframe
)$anova_table$ges
otm1_power_iat_anova_int
```

Without Bonferroni-correction for the order-wise two-sided contrasts

```{r}
otm1_f_iat_contrast <- 0.335535
emmeans_power(otm1_power(f = otm1_f_iat_contrast, rm_cor = iat_rm_cor)$emmeans$contrasts, alpha_level = 0.05)
```

For the collapsed one-sided contrasts

```{r}
otm1_power(f = 0.21611, rm_cor = iat_rm_cor)$emmeans$emmeans %>%
  emmeans(specs = ~ block * order) %>%
  contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>% 
  emmeans_power(alpha_level = 0.1)
```

```{r eval = TRUE}
knitr::opts_chunk$set(eval = TRUE)
```

## Simplified again

-->

## With implicit repeated measures correlation

```{r}
rydell_pes <- 0.1
rydell_f <- 4.78
rydell_n <- 50
rydell_dz <- pes_to_dz(rydell_pes, rydell_n, n_groups = 2)

heycke_t <- c(2.54, 1.45)
heycke_n <- c(28, 26)
heycke_dz <- heycke_t / sqrt(heycke_n)
heycke_pes <- dz_to_pes(heycke_dz, heycke_n, n_groups = 1)
# heycke_pes <- (heycke_dz^2 * heycke_n) / (heycke_dz^2 * heycke_n + heycke_n - 1) # pes

# mean(c(heycke_dz, rydell_dz))
# mean(c(heycke_pes, rydell_pes))
```

To simplify this, I will focus on the power for what we'd expect to be the smallest effect: The *learning block* contrast within each *valence order* group in IAT scores.
Rydell et al. report the smallest contrast as $\eta_p^2 = `r rydell_pes`$ ($d_z \approx `r rydell_dz`$), which is comparable in magnitude (but not direction) to the corresponding effect sizes reported by Heycke et al.

```{r}
otm1_power <- function(f, rm_cor, n = 76, alpha = 0.05) {
  contrast_code <- tibble::tibble(
    a = rep(contr.sum(2), 2)
    , b = rep(contr.sum(2), each = 2)
    , x = a*b * -1
  )

  mu <- with(
    contrast_code
    , f * x +
      - 0.25 * a
  )

  cor_mat <- diag(4)
  triangular <- c(0, 1, 0, 0, 1, 0)
  cor_mat[upper.tri(cor_mat)] <- triangular * rm_cor
  cor_mat[lower.tri(cor_mat)] <- triangular * rm_cor

  string <- "2w*2b"
  labelnames <- c("block", "1", "2", "order", "n-p", "p-n")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = cor_mat
    , labelnames = labelnames
  )

  otm1_power <- ANOVA_exact(
    design_result
    , alpha_level = alpha
    , emm = TRUE
    , verbose = FALSE
    , contrast_type = "pairwise"
    , emm_comp = "block | order"
  )

  otm1_power
}
```

```{r}
otm1_n <- 76

# 95% power
otm1_pes <- 0.08068
otm1_dz <- pes_to_dz(otm1_pes, otm1_n, n_groups = 2)
# rho <- 0.5
# f <- dz_to_f(otm1_dz, rho)
# 
# otm1_contrast_power <- otm1_power(f = f, n = otm1_n, rm_cor = rho)$emmeans$contrasts %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm1_contrast_power

# 80% power
otm1_pes2 <- 0.050336
otm1_dz2 <- pes_to_dz(otm1_pes2, otm1_n, n_groups = 2)
# f <- dz_to_f(otm1_dz2, rho)
# 
# otm1_contrast_power2 <- otm1_power(f = f, n = otm1_n, rm_cor = rho)$emmeans$contrasts %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm1_contrast_power2
```

Across all labs, our experimental design has 95% power to detect effects as small as $\eta^2_p = `r printp(otm1_pes)`$ ($\delta_z = `r otm1_dz`$) and 80% power to detect effects as small as $\eta^2_p = `r printp(otm1_pes2)`$ ($\delta_z = `r otm1_dz2`$).
Figure\ \@ref(fig:pes-plot) illustrates the implied Cohen's $\delta$ depending on the assumed repeated-measures correlation $\rho$. 
That is, we have sufficient power to find (or rule out) effects approximately 20% smaller than the typical effects reported for the weakest contrast.

```{r pes-plot, fig.width = 5, fig.height = 4, fig.cap = "Sensitivity curve for OTM1"}
tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
) %>% 
  mutate(power = relevel(factor(power), "0.95")) %>% 
  ggplot(aes(x = rho, y = delta, color = power, group = power)) +
  geom_line() +
  scale_color_viridis_d(end = 0.8) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Cohen's"~delta)
    , color = bquote("Power"~"["*1 - beta*"]")
  ) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    , legend.position = c(0.99, 0.99)
    , legend.justification = c(1, 1)
    , legend.background = element_rect(fill = scales::alpha("white", 0.5))
  )
```

# OTM 2

<!--

```{r}
knitr::opts_chunk$set(eval = FALSE)
```

The following gives the senseitivity analyses for the three-way interaction.
Because `superpower` only allows for power analyses, I manually estimated the effect size that yields approximately 95% power.

```{r}
contrast_codes <- tibble::tibble(
  a = rep(contr.sum(2), 4)
  , b = rep(rep(contr.sum(2), each = 2), 2)
  , c = rep(contr.sum(2), each = 4)
  , x2 = a*c * -1
  , x3 = a*b*c * -1
)

f <- 0.0807625
mu <- contrast_codes$x3 * f
n <- 125
sd <- 1
r <- 0.5
alpha_level <- 0.05

string = "2w*2b*2b"
labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = r
  , labelnames = labelnames
)

otm2_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | time * order"
)

otm2_power$main_results
```

Thus, we have 95% power to detect a three-way interaction between *order*, *block*, and *presentation time* of $f = `r round(f, 2)`$ ($d = `r round(2*f, 2)`$).

The two-way interaction contrasts the same number of cells and participants and, thus, we have the same power here.

```{r}
f <- 0.0807625
mu <- contrast_codes$x2 * f

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = r
  , labelnames = labelnames
)

otm2_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | time"
)

otm2_power$main_results
```

For example, we have 95% power to detect a two-way interaction between *block*, and *presentation time* of $f = `r round(f, 2)`$ ($d = `r round(2*f, 2)`$).

If we want to test the *block* effects (collapsed across *order*) separately for each presentation time, we get different sensitivities depending on whether we perform correction for multiple comparisons.

```{r}
f <- 0.104169
mu <- contrast_codes$x2 * f

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = r
  , labelnames = labelnames
)

otm2_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | time"
)

emmeans_power(otm2_power$emmeans$contrasts, alpha_level = 0.1)
```

Without correction, we have 95% power to detect a block effect within *presentation times* of $f = `r round(f, 2)`$ ($d = `r round(2*f, 2)`$).

```{r}
f <- 0.1142145
mu <- contrast_codes$x2 * f

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = r
  , labelnames = labelnames
)

otm2_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | time"
)

emmeans_power(otm2_power$emmeans$contrasts, alpha_level = 0.05)
```

With bonferroni correction, we have 95% power to detect a block effect within *presentation times* of $f = `r round(f, 2)`$ ($d = `r round(2*f, 2)`$).

In case presentation time has no effect, we can collapse across presentation durations.

```{r}
f <- 0.0736605
mu <- contrast_codes$x2 * f

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = r
  , labelnames = labelnames
)

otm2_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | time"
)

custom_contrast <- contrast(
  emmeans(
      otm2_power$emmeans$emmeans
      , specs = ~ time * block
  )
  , list(block_effect = c(-0.5, 0.5, 0.5, -0.5))
)

emmeans_power(custom_contrast, alpha_level = 0.1)
```

Here, we have 95% power to detect a block effect of $f = `r round(f, 2)`$ ($d = `r round(2*f, 2)`$).

## Time x Measure x Block

Because `superpower` only allows for power analyses, I manually determined the sample size that yields approximately 95% power.
The following assumes that we are not interested in the effect of the counterbalancing factor *order*.

```{r fig.width = 7, fig.height = 7}
contrast_codes <- tibble::tibble(
  time = rep(contr.sum(2), 4)
  , block = rep(rep(contr.sum(2), each = 2), 2)
  , measure = rep(contr.sum(2), each = 4)
  , time_block = time * block
  , time_measure = time * measure
  , block_measure = block * measure
  , time_block_measure = time * block * measure
)

f <- 0.5
mu <- with(
  contrast_codes
  , block * f +
    block_measure * f + 
    -time_block * 0.25*f + 
    time_block_measure * 0.25*f
)
n <- 68
# r <- 0.5
alpha_level <- 0.05

eval_reliability <- 0.8
iat_reliability <- 0.5
measure_cor <- 0.8 * sqrt(eval_reliability * iat_reliability)

string <- "2w*2w*2b"
labelnames <- c("measure", "eval", "iat", "block", "1", "2", "time", "13", "20")

eval_cor_mat <- iat_cor_mat <- inter_cor_mat <- diag(4)
triangular <- c(0, 1, 0, 0, 1, 0)

eval_cor_mat[upper.tri(eval_cor_mat)] <- triangular * -eval_reliability
eval_cor_mat[lower.tri(eval_cor_mat)] <- triangular * -eval_reliability
iat_cor_mat[upper.tri(eval_cor_mat)] <- triangular * -iat_reliability
iat_cor_mat[lower.tri(eval_cor_mat)] <- triangular * -iat_reliability

inter_cor_mat <- inter_cor_mat * measure_cor
inter_cor_mat[upper.tri(eval_cor_mat)] <- triangular * -measure_cor
inter_cor_mat[lower.tri(eval_cor_mat)] <- triangular * -measure_cor

cor_mat <- rbind(cbind(eval_cor_mat, inter_cor_mat), cbind(inter_cor_mat, iat_cor_mat))

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = 0.5
  , labelnames = labelnames
)
dimnames(cor_mat) <- dimnames(design_result$cor_mat)

design_result <- ANOVA_design(
  design = string
  , n = n
  , mu = mu
  , sd = 1
  , r = cor_mat
  , labelnames = labelnames
)

otm2_power <- ANOVA_exact(
  design_result
  , alpha_level = alpha_level
  , emm = TRUE
  , verbose = FALSE
  , contrast_type = "pairwise"
  , emm_comp = "block | time * measure"
)

otm1_observed_plot <- readRDS("../../otm1/results/data_processed/otm1_attitudes_cleaned.rds") %>%
    mutate(
      Block = ifelse(ValenceBlock == "Negative-positive", 3 - as.numeric(as.character(Block)), Block) %>% factor
    ) %>%
    select(-ValenceBlock) %>%
    mutate(Rating = scale(Eval) %>% as.vector, `IAT score` = scale(IATscore) %>% as.vector) %>%
    gather("Measure", "Attitude", Rating, `IAT score`) %>% 
    mutate(Measure = factor(Measure)) %>%
    ggplot(aes(x = Block, y = Attitude)) +
      stat_summary(fun.data = mean_cl_normal) +
      facet_grid("" ~ Measure) +
      coord_cartesian(ylim = c(-1.25, 1.25)) +
      theme_bw() +
      ggtitle("Results of Experiment 1")

otm2_expected_plot <- otm2_power$dataframe %>% 
  mutate(
    measure = ifelse(measure == "measure_eval", "Rating", "IAT score")
    , block = ifelse(block == "block_1", "1", "2")
    , time = ifelse(time == "time_13", "13 ms", "20 ms")
  ) %>%
  ggplot(aes(x = block, y = y)) +
    stat_summary(fun.data = mean_cl_normal) +
    facet_grid(time ~ measure) +
    coord_cartesian(ylim = c(-1.25, 1.25)) +
    theme_bw() +
    ggtitle("Assumed for power analysis") +
    labs(x = "Block", y = "Attitude")

plot_grid(
  otm1_observed_plot
  , otm2_expected_plot
  , ncol = 1
  , rel_heights = c(1, 1.5)
)

otm2_power$main_results
```

Thus, we have 95% power to detect a three-way interaction between *measure*, *block*, and *presentation time* of $f = `r round(0.25*f, 2)`$ ($d = `r round(2*0.25*f, 2)`$) and more than 95% power to detect a two-way interaction between *measure*, *block* of $f = `r round(f, 2)`$ ($d = `r round(f, 2)`$) for $n = `r n`$ ($N = `r 2*n`$).
These results are, of course, contigent on the assumed reliabilities of the rating measure ($r = `r #round(eval_reliability, 2)`$), the IAT score ($r = `r #round(iat_reliability, 2)`$), and the correlation among the two measures ($r = `r #round(measure_cor, 2)`$; $r = 0.8$ unattenuated).

If we want to test the *block* effects (collapsed across *order*) separately for each presentation time and measure, we get different sensitivities depending on whether we perform correction for multiple comparisons.

Without Bonferroni-correction:

```{r}
otm2_power$emmeans$contrasts

emmeans_power(otm2_power$emmeans$contrasts, alpha_level = 0.1)
```

If we want 80% power for the IAT effect here, we would need $n = 75$ ($N = 150$).
For 95% we need $n = 131$ ($N = 262$).

With Bonferroni-correction

```{r}
emmeans_power(otm2_power$emmeans$contrasts, alpha_level = 0.05)
```

If we want 80% power for the IAT effect here, we would need $n = 96$ ($N = 192$).
For 95% we need $n = 157$ ($N = 314$).

In case presentation time has no effect, we can collapse across presentation times:

```{r}
custom_contrast <- contrast(
  emmeans(
      otm2_power$emmeans$emmeans
      , specs = ~ time * measure * block
  )
  , list(
      eval_block_effect = c(0.5, 0.5, 0, 0, -0.5, -0.5, 0, 0)
      , iat_block_effect = c(0, 0, -0.5, 0.5, 0, 0, 0.5, -0.5)
  )
)

emmeans_power(custom_contrast, alpha_level = 0.1)
```

## Time x Order x Block

```{r eval = TRUE}
knitr::opts_chunk$set(eval = TRUE)
```

-->

## By measure

Because `Superpower` only allows for power analyses, I manually determined the sample size that yields approximately 95% power.
The following assumes that we are not interested in the effect of the counterbalancing factor *order*.

```{r}
otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
  contrast_codes <- tibble::tibble(
    time = rep(contr.treatment(2), 4)
    , order = rep(rep(contr.sum(2), each = 2), 2)
    , block = rep(contr.sum(2), each = 4)
    , time_block = time * block
    , time_order = time * order
    , block_order = block * order
    , time_block_order = time * block * order
  )

  mu <- with(
    contrast_codes
    , -order * 0.25*f +
      -block_order * f
  )

  string <- "2w*2b*2b"
  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = rm_cor
    , labelnames = labelnames
  )

  ANOVA_exact(
    design_result
    , alpha_level = alpha_level
    , emm = TRUE
    , verbose = FALSE
    , contrast_type = "pairwise"
    , emm_comp = "block | time * order"
  )
}

otm2_n <- 320/4

# 95% power
otm2_pes <- 0.02027
otm2_dz <- pes_to_dz(otm2_pes, otm2_n, n_groups = 4)
rho <- 0.5
f <- dz_to_f(otm2_dz, rho)

otm2_int_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho, alpha = 0.05)

otm1_observed <- readRDS("../../otm1/results/data_processed/otm1_attitudes_cleaned.rds") %>%
    mutate(`IAT score` = scale(IATscore) %>% as.vector)

otm1_observed_iat_plot <- otm1_observed %>%
  ggplot(aes(x = Block, y = `IAT score`, color = ValenceBlock, group = ValenceBlock)) +
    stat_summary(fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_normal) +
    facet_grid(~ "24/27ms") +
    theme_bw() +
    ggtitle("Results of Experiment 1")

otm2_expected_plot <- otm2_int_power$dataframe %>%
  mutate(
    order = ifelse(order == "order_n-p", "Negative-positive", "Positive-negative")
    , block = ifelse(block == "block_1", "1", "2")
    , time = ifelse(time == "time_13", "13 ms", "20 ms")
  ) %>%
  ggplot(aes(x = block, y = y, color = order, group = order)) +
    stat_summary(fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_normal) +
    coord_cartesian(ylim = c(-0.6, 0.6)) +
    facet_grid(~ time) +
    guides(color = FALSE) +
    ggtitle("Assumed for power analysis") +
    labs(x = "Block", y = "Attitude") +
    theme_bw()

plot_grid(
  otm1_observed_iat_plot
  , otm2_expected_plot
  , ncol = 2
)
```

```{r}
# 95% power
otm2_pes <- 0.03973071
otm2_dz <- pes_to_dz(otm2_pes, otm2_n, n_groups = 4)
# rho <- 0.5
# f <- dz_to_f(otm2_dz, rho)
# 
# otm2_contrast_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$contrasts %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm2_contrast_power

# 80% power
otm2_pes2 <- 0.0243813
otm2_dz2 <- pes_to_dz(otm2_pes2, otm2_n, n_groups = 4)
# f <- dz_to_f(otm2_dz2, rho)
# 
# otm2_contrast_power2 <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$contrasts %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm2_contrast_power2
```

```{r}
# 95% power
otm2_dz_between_collapsed <- f_to_dz(dz_to_f(otm2_dz, rho) / sqrt(2), rho)
otm2_pes_between_collapsed <- dz_to_pes(otm2_dz_between_collapsed, otm2_n, n_groups = 4)
# f <- dz_to_f(otm2_dz_between_collapsed, rho)
# 
# otm2_time_collapsed_contrast_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
#   emmeans(specs = ~ block | order) %>%
#   pairs %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm2_time_collapsed_contrast_power

# 80% power
otm2_dz2_between_collapsed <- f_to_dz(dz_to_f(otm2_dz2, rho) / sqrt(2), rho)
otm2_pes2_between_collapsed <- dz_to_pes(otm2_dz2_between_collapsed, otm2_n, n_groups = 4)
# f <- dz_to_f(otm2_dz2_between_collapsed, rho)
# 
# otm2_time_collapsed_contrast_power2 <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
#   emmeans(specs = ~ block | order) %>%
#   pairs %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm2_time_collapsed_contrast_power2
```

```{r}
# (Same results apply to two-way and three-way interaction)

# 95% power
otm2_dz_collapsed <- f_to_dz(dz_to_f(otm2_dz, rho) / sqrt(4), rho)
otm2_pes_collapsed <- dz_to_pes(otm2_dz_collapsed, otm2_n, n_groups = 4)
# f <- dz_to_f(otm2_dz_collapsed, rho)
# 
# otm2_collapsed_contrast_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
#   emmeans(specs = ~ block * order) %>%
#   contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>%
#   emmeans_power(alpha_level = 0.05)
# otm2_collapsed_contrast_power

# 80% power
otm2_dz2_collapsed <- f_to_dz(dz_to_f(otm2_dz2, rho) / sqrt(4), rho)
otm2_pes2_collapsed <- dz_to_pes(otm2_dz2_collapsed, otm2_n, n_groups = 4)
# f <- dz_to_f(otm2_dz2_collapsed, rho)
# 
# otm2_collapsed_contrast_power2 <- otm2_power(f = f, n = otm2_n, rm_cor = rho)$emmeans$emmeans %>%
#   emmeans(specs = ~ block * order) %>%
#   contrast(method = list(collapsed = c(-0.5, 0.5, 0.5, -0.5))) %>%
#   emmeans_power(alpha_level = 0.05)
# otm2_collapsed_contrast_power2
```

(ref:otm2-pes-plot) Sensitivity curves for OTM2.
The simple contrast is the comparison of the two learning blocks within each *presentation duration*-*valence order* combination (not adjusted for multiple comparisons).
Collapsed sensitivity curves apply to contrasts where data are pooled across either *presentation duration* or *valence order* (valence orders are pooled by reverse coding one order).
$\eta^2_p$-values in the represent effect sizes corresponding to 95% and 80% power.
The grey dashed line at the top represents the smallest *learning block* difference reported by Rydell et al. (2006).
<!-- The power to detect a two-way or three-way interaction is the same as the collapsed once contrast. -->

```{r otm2-pes-plot, fig.width = 7, fig.height = 4, fig.cap = ""}
rydell_power_curve <- tibble(
  rho = seq(-1, 1, length.out = 100)
  , delta = c(
    dz_to_f(rydell_dz, unique(rho)) * 2
    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
  )
  , power = NA
)

otm1_power_curve <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
)

tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , otm2_delta_simple = c(
    dz_to_f(otm2_dz, unique(rho)) * 2
    , dz_to_f(otm2_dz2, unique(rho)) * 2
  )
  , otm2_delta_between_collapsed = c(
    dz_to_f(otm2_dz_between_collapsed, unique(rho)) * 2
    , dz_to_f(otm2_dz2_between_collapsed, unique(rho)) * 2
  )
  , otm2_delta_collapsed = c(
    dz_to_f(otm2_dz_collapsed, unique(rho)) * 2
    , dz_to_f(otm2_dz2_collapsed, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
) %>% 
  pivot_longer(cols = matches("otm"), names_to = "contrast", values_to = "delta") %>%
  mutate(
    power = relevel(factor(power), "0.95")
    , contrast = gsub("otm2_delta_", "", contrast)
    , contrast = gsub("_", " ", contrast)
    , contrast = factor(contrast, levels = c("simple", "between collapsed", "collapsed"))
  ) %>% 
  ggplot(aes(x = rho, y = delta, color = contrast, group = interaction(power, contrast), linetype = power)) +
  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
  # geom_line(data = otm1_power_curve, aes(group = power, linetype = power, color = "simple"), alpha = 0.3) +
  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
  geom_line() +
  scale_color_viridis_d(
    end = 0.8
    , labels = c(
      bquote("Simple                 "~delta[z] %in% "{"*.(printnum(otm2_dz))*", "*.(printnum(otm2_dz2))*"}")
      , bquote("Collapsed once   "~delta[z] %in% "{"*.(printnum(otm2_dz_between_collapsed))*", "*.(printnum(otm2_dz2_between_collapsed))*"}")
      , bquote("Collapsed twice   "~delta[z] %in% "{"*.(printnum(otm2_dz_collapsed))*", "*.(printnum(otm2_dz2_collapsed))*"}")
    )
  ) +
  ylim(c(0, 1)) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Learning block difference [Cohen's"~delta*"]")
    , color = "Contrast"
    , linetype = bquote("Power"~"["*1 - beta*"]")
  ) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    # , legend.position = c(0.99, 0.99)
    # , legend.justification = c(1, 1)
    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
  )
```

### Sensitivty for omnibus-tests

```{r}
# Main effect block and three-way interaction
otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
  contrast_codes <- tibble::tibble(
    time = rep(contr.treatment(2), 4)
    , order = rep(rep(contr.sum(2), each = 2), 2)
    , block = rep(contr.sum(2), each = 4)
    , time_block = time * block
    , time_order = time * order
    , block_order = block * order
    , time_block_order = time * block * order
  )

  mu <- with(
    contrast_codes
    , #-order * 0.25*f +
      -block_order * f +
      -block * 0.5 * f +
      time_block_order * f
  )

  string <- "2w*2b*2b"
  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = rm_cor
    , labelnames = labelnames
  )

  ANOVA_exact(
    design_result
    , alpha_level = alpha_level
    , emm = FALSE
    , verbose = FALSE
  )
}

otm2_n <- 320/4

# 95% power
otm2_pes <- 0.03973071
otm2_dz <- pes_to_dz(otm2_pes, otm2_n, n_groups = 4)
rho <- 0.5
f <- dz_to_f(otm2_dz, rho)

otm2_time_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho, alpha = 0.05)
otm2_time_power$main_result

# otm2_time_power$dataframe %>%
#   mutate(
#     order = ifelse(order == "order_n-p", "Negative-positive", "Positive-negative")
#     , block = ifelse(block == "block_1", "1", "2")
#     , time = ifelse(time == "time_13", "13 ms", "20 ms")
#   ) %>%
#   ggplot(aes(x = block, y = y, color = order, group = order)) +
#   stat_summary(fun.y = mean, geom = "line") +
#   stat_summary(fun.data = mean_cl_normal) +
#   coord_cartesian(ylim = c(-0.6, 0.6)) +
#   facet_grid(~ time) +
#   guides(color = FALSE) +
#   ggtitle("Assumed for power analysis") +
#   labs(x = "Block", y = "Attitude") +
#   theme_bw()

otm2_dz_block <- f_to_dz(0.5*f, rho = 0.5)
otm2_pes_block <- dz_to_pes(otm2_dz_block, otm2_n, n_groups = 4)

otm2_dz_int <- f_to_dz(f, rho = 0.5)
otm2_pes_int <- dz_to_pes(otm2_dz_int, otm2_n, n_groups = 4)
```

### 2021-09-10 analysis_and_paper/error_in_variables.R

@@ -20,7 +20,7 @@
 # library("numDeriv")
 
 ## only needed for simulations:
-#library("parallel")
+# library("parallel")
 
 ### Log-likelihood function on p. 258
 eiv_loglik <- function(par, dv, iv, const=1e20) {
@@ -288,19 +288,23 @@ gen <- function(n, par){
 }
 
 ### Replication function for simulation
-replication <- function(i){
+replication <- function(i) {
   sim <- gen(n, par)
-  mod <- eiv_lm(sim, par)
-  mod$estimate
+  eiv_mod <- eiv_lm(y ~ x, data = sim, start = par)
+  lm_mod <- lm(y ~ x, data = sim)
+  rbind(
+    cbind(mod = "eiv", i = i, summary(eiv_mod)[, c("term", "estimate", "p.value")])
+    , cbind(mod = "lm", i = i, broom::tidy(lm_mod)[, c("term", "estimate", "p.value")])
+  )
 }
 
-################################################################################
-# 
-# ### Example in Klauer (1998, Table 1)
+# ################################################################################
+# # 
+# # ### Example in Klauer (1998, Table 1)
 # n <- 1431
 # par <- c(mu=-.2, sigma=1.67, sx=.8, sy=.27, beta=.02, alpha=.000)
 # sim <- gen(n, par)
-
+# 
 # # Check summary statistics on p. 259
 # mean(sim$y)
 # sd(sim$y)
@@ -315,24 +319,44 @@ replication <- function(i){
 # mod <- eiv_lm(y ~ x, sim, par)
 # 
 # # Check Table 1
-# cbind(true=par, est=mod$est, se=mod$se,
-#       lm=c(NA, NA, NA, NA, coef(reg)))
-
-################################################################################
+# cbind(true=par, est=mod$est, se=mod$std.err,
+#       lm.est=c(NA, NA, NA, NA, coef(reg)), lm.se = c(NA, NA, NA, NA, summary(reg)$coefficients[, 2]))
+# 
+# ###############################################################################
 # 
 # ### Simulation in Klauer (1998, Table 2)
-# cl <- makeCluster(8)
-# tmp <- clusterEvalQ(cl, {library("minqa"); library("numDeriv")})
-# clusterExport(cl, c("fit", "gen", "eiv_loglik", "n", "par"))
[…]

### 2021-09-10 otm2/material/OTM_exp_script_florida_1280_1024_75Hz.py

@@ -43,7 +43,7 @@ def getList (listname):
     wordList = []
     for eachLine in range(len(listname)) :
         currentWord = listname[eachLine][:-1]
-        wordList.append(currentWord) 
+        wordList.append(currentWord)
     return wordList
 
 # Function reading txt files and saves each line as one element in list (able to use all utf 8 symbols)
@@ -56,7 +56,7 @@ def ReadTxt(File, remove):
     l = []
     for eachLine in range(len(tL[0])) :
         currentWord = tL[0][eachLine][:remove]
-        l.append(currentWord) 
+        l.append(currentWord)
     return(l)
 
 #function used for instruction: disyplays text on a page and continues when space is pressed
@@ -111,7 +111,7 @@ def trial(prime, bob, bobName, behavior, Valence):
     instruction_key_d.draw()
     instruction_key_k.draw()
     window.flip()
-    timer.reset() 
+    timer.reset()
     response = event.waitKeys(keyList = ('c', 'u', "1")) #, timeStamped=clock
     responseNumber = response[0][0]
     TrialRT = timer.getTime()
@@ -119,9 +119,9 @@ def trial(prime, bob, bobName, behavior, Valence):
     #check if experiment should be aborted
     if responseNumber == "1":
         outputFile = open('./data/AbortMassage_OTM_'+str(ParticipantNumber)+'.dat', 'a') #Save create a txt and participantnumber in it
-        outputFile.write("%s\t%s" % ("This participant pressed the 1 key during the learning phase", timeStamp)) 
+        outputFile.write("%s\t%s" % ("This participant pressed the 1 key during the learning phase", timeStamp))
         outputFile.close()
-        core.quit() 
+        core.quit()
     #now check if answer was correct and give feedback
     if Block == 1 and ValenceBlock == 1 and Valence == "pos" and responseNumber == "c":
         posFeedback()
@@ -150,7 +150,7 @@ def trial(prime, bob, bobName, behavior, Valence):
 def liking1(InstructionLiking1):
     myRatingScale = visual.RatingScale(window, low= 1, high=9, skipKeys=None, stretch = 1.4, scale = ('Very Unlikable                             \t\t\t\t\t\t\t\t                           Very Likable'), \
[…]

### 2021-09-13 otm2/results/analysis2.Rmd
Adds analysis script draft for Experiment 2 and pilot data.

---
title             : "Analysis of OTM2"
author            : "Frederik Aust"
date              : "`r format(Sys.time(), '%d %B, %Y')`"

output:
  bookdown::html_document2:
    theme         : "spacelab"
    df_print      : "kable"
    code_folding  : "hide"
    toc           : true
    toc_float     : true
---

```{r init, include = FALSE}
library("magrittr")
library("tidyr")
library("dplyr")
library("assertthat")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("afex")
library("emmeans")
library("BayesFactor")

source("https://gist.githubusercontent.com/crsh/bd4d1f62d300462ea0c0f44b9ad38616/raw/edd9c74e24b68f42433c2526cafc888509b1b8bc/batch_download_github.R")
source("https://gist.githubusercontent.com/crsh/357458c41fd3d554fb24/raw/f7725d5c4894a055a1b2e461dc5c39f3db23b2b8/batch_read.R")

source("../../analysis_and_paper/modal_frame_rate.R")

# Set seed for random number generator
set.seed(1448571254)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Use multivariate models for emmeans contrasts and post-hoc tests
afex_options(emmeans_model = "multivariate")

# Configure df approximation for mixed model contrasts and post-hoc tests
emm_options(
  lmer.df = "satterthwaite"
  , lmerTest.limit = 22384
)
```

```{r otm2-analysis-preferences, cache = TRUE}
# Data wrangling
process_rawdata <- TRUE

# Data location
raw_data_path <- "data_raw/"
processed_data_path <- "data_processed/"

# Default ggplot theme
theme_set(theme_apa())

# Number of MCMC samples for Bayesian analysis
otm2_n_mcmc_samples <- 1e6
```

```{r otm2-load-data, cache = TRUE, dependson = "otm2-analysis-preferences", warning = FALSE}
# Process raw data
if(process_rawdata) {

  # Merge raw data
  otm2_eval <- batch_read(
    raw_data_path
    , pattern = "Eval"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm2_iat <- batch_read(
    raw_data_path
    , pattern = "IAT"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm2_mem <- batch_read(
    raw_data_path
    , pattern = "MemTest"
    , recursive = TRUE
    , read_fun = read.delim
  )

  otm2_demo <- batch_read(
    raw_data_path
    , pattern = "Demographics"
    , recursive = TRUE
    , read_fun = read.delim
    , quote = "~" # Participants used " in their input
  )

  otm2_log <- batch_read(
    raw_data_path
    , pattern = "ScreenLog"
    , recursive = TRUE
    , read_fun = read.csv
    , header = FALSE
  )

  # Recode, calculate indices, and filter data
  otm2_eval <- otm2_eval %>%
    mutate_at(vars(starts_with("Eval")), scale) %>%
    select(starts_with("Eval")) %>%
    rowwise %>%
    do(data.frame(Eval = mean(unlist(.)))) %>% 
    bind_cols(otm2_eval, .) %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
    )

  otm2_iat <- otm2_iat %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
      , IATBlock = factor(paste0("Block", IATBlock))
    ) %>%
    filter(IATBlock %in% c("Block34", "Block67")) %>%
    mutate(
      Correct = ifelse(Correct == "correct", 1, 0)
      , RT = ifelse(Correct == 1, RT, RTafterError)
      , cleanRT = ifelse(RT < 0.3, 0.3, RT)
      , cleanRT = ifelse(cleanRT > 3, 3, cleanRT)
      , logCleanRT = log(cleanRT)
    )

  otm2_analysis_factors <- c("ParticipantNumber", "Location", "Block", "ValenceBlock")

  otm2_attitudes <- otm2_iat %>%
    group_by(ParticipantNumber, Location, MeasureOrder, Block, IATBlock, Combination, ValenceBlock) %>%
    summarize(meanRT = mean(logCleanRT), nRT = length(logCleanRT)) %>%
    ungroup %>%
    spread(IATBlock, meanRT) %>%
    # Combination 1: Combination 1 (Bob = negative) in Block 3 & 4
    # Combination 2: Combination 1 (Bob = negative) in Block 6 & 7
    mutate(IATscore = ifelse(Combination == 1, Block34 - Block67, Block67 - Block34)) %>%
    select(c(all_of(otm2_analysis_factors), "IATscore")) %>%
    left_join(
      select(otm2_eval, c(all_of(otm2_analysis_factors), "Eval"))
      , by = otm2_analysis_factors
    )

  otm2_demo$frameRate <- modal_frame_rate(otm2_log)
  otm2_mem <- left_join(otm2_mem, otm2_demo, by = "ParticipantNumber") %>% 
    mutate(ParticipantNumber = factor(ParticipantNumber))

  # Add frame rate/presentation duration
  otm2_attitudes <- otm2_attitudes %>% 
    left_join(
      select(otm2_mem, ParticipantNumber, frameRate)
      , by = "ParticipantNumber"
    ) %>% 
    mutate(
      Duration = factor(
        ifelse(frameRate == 75, 13, 20)
        , levels = c("13", "20")
      )
      , Country = factor(
        ifelse(Location == "HongKong", "Hong Kong",  "USA")
      )
    )

  otm2_mem <- otm2_mem %>%
    mutate(
      ParticipantNumber = factor(ParticipantNumber)
      , ValenceBlock = ifelse(ValenceBlock == 1, "Positive-negative", "Negative-positive") %>% factor
      , MeasureOrder = ifelse(MeasureOrder == 1, "Implicit-explicit", "Explicit-implicit") %>% factor
      , Block = factor(Block)
      , Country = factor(
        ifelse(Location == "HongKong", "Hong Kong",  "USA")
      )
      , Duration = factor(
        ifelse(frameRate == 75, 13, 20)
        , levels = c("13", "20")
      )
      , Accuracy = NumbercorrectIdent / 20
    )

  rm("otm2_log", "otm2_demo", "otm2_eval")

  # Save processed data
  saveRDS(otm2_attitudes, paste0(processed_data_path, "otm2_attitudes.rds"))
  saveRDS(otm2_iat, paste0(processed_data_path, "otm2_iat_trial_data.rds"))
  saveRDS(otm2_mem, paste0(processed_data_path, "otm2_memory.rds"))
} else {
  otm2_attitudes <- readRDS(paste0(processed_data_path, "otm2_attitudes.rds"))
  otm2_iat <- readRDS(paste0(processed_data_path, "otm2_iat_trial_data.rds"))
  otm2_mem <- readRDS(paste0(processed_data_path, "otm2_memory.rds"))
}
```

# Participants

```{r otm2-check-data-integrity, cache = TRUE, dependson = "otm2-load-data"}
# Exclude participants due to technical failures
otm2_technical_failure <- c()
# otm2_technical_failure_expression <- expression(!as.character(ParticipantNumber) %in% otm2_technical_failure)
# 
# otm2_attitudes <- filter(otm2_attitudes, eval(otm2_technical_failure_expression)) %>%
#   mutate(ParticipantNumber = factor(ParticipantNumber))
# otm2_iat <- filter(otm2_iat, eval(otm2_technical_failure_expression)) %>% droplevels
# otm2_mem <- filter(otm2_mem, eval(otm2_technical_failure_expression)) %>% droplevels

# Check for incomplete data
otm2_n_trials <- aggregate(Eval ~ ParticipantNumber, otm2_attitudes, length) %>%
  full_join(
    aggregate(RT ~ ParticipantNumber, otm2_iat, length)
    , by = "ParticipantNumber"
    ) %>%
  full_join(
    aggregate(NumbercorrectIdent ~ ParticipantNumber, otm2_mem, length)
    , by = "ParticipantNumber"
  )

otm2_incomplete_data <- otm2_n_trials %>% 
  rowwise %>% 
  mutate(
    incomplete = (Eval != 2 || RT != 160 || NumbercorrectIdent != 1)
  ) %>% 
  filter(incomplete) %>% 
  pull(ParticipantNumber)

if(length(otm2_incomplete_data) > 0) warning(
  "Incomplete datasets: "
  , paste(otm2_incomplete_data, collapse = ", ")
)

# Check frame rate
# TODO: Update once labs have been assigned to presentation duration
otm2_frame_rate <- otm2_mem$ParticipantNumber[
  with(
    otm2_mem
    , (Location == "Florida" & frameRate != 75) ||
      (Location == "Indianna" & frameRate != 75) ||
      (Location == "Conneticut" & frameRate != 100) ||
      (Location == "Massachusetts" & frameRate != 100) ||
      (Location == "HongKong" & frameRate != 100)
  )
]

if(length(otm2_frame_rate) > 0) warning(
  "Incorrect frame rates: "
  , paste(otm2_frame_rate, collapse = ", ")
)
```

```{r otm2-exclusion, cache = TRUE, dependson = "otm2-check-data-integrity"}
otm2_noncompliance <- c()
otm2_exclude <- c(otm2_incomplete_data, otm2_frame_rate) %>%
  unique

otm2_n_excluded <- as.integer(length(c(otm2_exclude, otm2_technical_failure)))

# otm2_exclusion_expression <- expression(!ParticipantNumber %in% otm2_exclude)
# 
# otm2_attitudes <- filter(otm2_attitudes, eval(otm2_exclusion_expression)) %>% droplevels
# otm2_iat <- filter(otm2_iat, eval(otm2_exclusion_expression)) %>% droplevels
# otm2_mem <- filter(otm2_mem, eval(otm2_exclusion_expression)) %>% droplevels

# # Save cleaned data
# saveRDS(otm1_attitudes, paste0(processed_data_path, "otm1_attitudes_cleaned.rds"))
# saveRDS(otm1_iat, paste0(processed_data_path, "otm1_iat_trial_data_cleaned.rds"))
# saveRDS(otm1_mem, paste0(processed_data_path, "otm1_memory_cleaned.rds"))

otm2_n <- as.integer(nlevels(otm2_attitudes$ParticipantNumber))
```

We recruited `r otm2_n + otm2_n_excluded` participants; `r printnum(otm2_n_excluded, numerals = otm2_n_excluded < 10)` participants were excluded due to technical failure or noncompliance with instructions.
Hence, the following results are based on data of `r otm2_n` participants.

(ref:otm2-participant-table)
Demographics by location.

(ref:otm2-participant-table-note)
Mean age is given with range in brackets.

```{r otm2-participant-table, results = "asis"}
otm2_mem %>% 
  mutate(
    Gender = gsub("^w|weiblich|v|vrouw|woman|f$", "female", Gender, ignore.case = TRUE) %>%
      tolower
    , Age = as.numeric(gsub("\\W", "", Age))
  ) %>%
  group_by(Location) %>% 
  summarize(
    age_mean = mean(Age, na.rm = T)
    , age_min = min(Age)
    , age_max = max(Age)
    , "Female (%)" = printnum(sum(grepl("female", Gender)) / length(Accuracy) * 100)
    , "$n$" = length(Accuracy)
  ) %>%
  mutate(Age = paste0(printnum(age_mean), " [", age_min, ", ", age_max, "]")) %>%
  select(Location, Age, "Female (%)", "$n$") %>%
  apa_table(
    caption = "(ref:otm2-participant-table)"
    , note = "(ref:otm2-participant-table-note)"
    , escape = FALSE
  )
```

# Results

In the following "Valence block" and "Valence order" both refer to the joint valence order of the explicit description of Bob and briefly presented primes.
When we refer to one valence order (e.g. positive-negative) we specify the order of the explicit descriptions of Bob; the briefly presented primes in that condition were of the opposite valence.

```{r otm2-rating-plot, fig.cap = "(ref:omt1-rating-plot)", warning = FALSE}
otm2_results_legend <- guide_legend(
    title = expression(atop("Valence order", atop(scriptstyle("Behavioral information"), scriptstyle("(Briefly flashed words)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
  )

otm2_rating_plot <- otm2_attitudes %>%
  mutate(
    ValenceBlock = ifelse(
      ValenceBlock == "Positive-negative"
      , " Positive-negative\n(Negative-positive)"
      , " Negative-positive\n(Positive-negative)")
    , Duration = ifelse(
      Duration == "13"
      , "13-ms flashes"
      , "10-ms flashes"
    )
  ) %>%
  ggplot(aes(x = Block, y = Eval, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
  geom_violin(position = position_dodge(0.1), alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(position = position_dodge(0.1), maxwidth = 0.2, alpha = 0.5, size = 0.5) +
  stat_summary(fun = mean, aes(group = ValenceBlock, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1", guide = otm2_results_legend) +
  scale_fill_brewer(palette = "Set1", guide = otm2_results_legend) +
  scale_shape_manual(values = c(21, 23), guide = otm2_results_legend) +
  labs(
    x = "Block"
    , y = " \nRating score"
  ) +
  guides(linetype = otm2_results_legend) +
  facet_wrap(~ Duration, ncol = 2) +
  theme(
    legend.position = "top"
    , legend.justification = "center"
  )
```

```{r otm2-iatscore-plot, fig.cap = "(ref:omt1-iatscore-plot)", warning = FALSE}
otm2_iatscore_plot <- otm2_attitudes %>%
  mutate(
    ValenceBlock = ifelse(
      ValenceBlock == "Positive-negative"
      , " Positive-negative\n(Negative-positive)"
      , " Negative-positive\n(Positive-negative)")
    , Duration = ifelse(
      Duration == "13"
      , "13-ms flashes"
      , "10-ms flashes"
    )
  ) %>% 
  ggplot(aes(x = Block, y = IATscore, color = ValenceBlock, fill = ValenceBlock, shape = ValenceBlock)) +
  geom_violin(position = position_dodge(0.1), alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(position = position_dodge(0.1), maxwidth = 0.2, alpha = 0.5, size = 0.5) +
  stat_summary(fun = mean, aes(group = ValenceBlock, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21, 23)) +
  labs(
    x = "Block"
    , y = "IAT response time\ndifference [log(s)]"
  ) +
  facet_wrap(~ Duration, ncol = 2) +
  theme(legend.position = "none")
```

(ref:otm2-results-plot)
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participants' responses, and violins represent kernel density estimates of sample distributions.

```{r otm2-results-plot, fig.cap = "(ref:otm2-results-plot)", fig.height = 7, fig.width = 6.5, warning = FALSE}
plot_grid(
  otm2_rating_plot +
    theme(
      axis.title.x = element_blank()
      , axis.ticks.x = element_blank()
      , axis.text.x = element_blank()
      , axis.title.y = element_text(lineheight = 1.7)
      , strip.background = element_blank()
    )
  , NULL
  , otm2_iatscore_plot + 
    theme(strip.text.x = element_blank())
  , ncol = 1
  , rel_heights = c(1, 0.05, 0.8)
)
```

## Frequentist analysis

(ref:otm2-rydell-analysis-overall)
Results of the combined ANOVA of $z$ standardized attitude ratings and IAT scores.

```{r otm2-rydell-analysis-overall, results = "asis"}
otm2_attitudes_aov <- otm2_attitudes %>%
  mutate(
    Eval = scale(Eval) %>% as.numeric
    , IATscore = scale(IATscore) %>% as.numeric
  ) %>%
  gather("Measure", "Attitude", Eval, IATscore) %>%
  mutate(Measure = factor(Measure)) %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Attitude"
    , within = c("Block", "Measure")
    # , between = "ValenceBlock"
    , between = c("ValenceBlock", "Duration")
    , data = .
  )

otm2_attitudes_aov %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm2-rydell-analysis-overall)"
    , escape = FALSE
  )
```

(ref:otm2-rydell-analysis-overall-country)
Results of the combined ANOVA of $z$ standardized attitude ratings and IAT scores.

```{r otm2-rydell-analysis-overall-country, results = "asis"}
otm2_attitudes_country_aov <- otm2_attitudes %>%
  mutate(
    Eval = scale(Eval) %>% as.numeric
    , IATscore = scale(IATscore) %>% as.numeric
  ) %>%
  gather("Measure", "Attitude", Eval, IATscore) %>%
  mutate(Measure = factor(Measure)) %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Attitude"
    , within = c("Block", "Measure")
    # , between = "ValenceBlock"
    , between = c("ValenceBlock", "Duration", "Country")
    , data = .
  )

otm2_attitudes_country_aov %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm2-rydell-analysis-overall-country)"
    , escape = FALSE
  )

# Split analyses by Country
otm2_attitudes_country_split_aov <- otm2_attitudes_country_aov %>% 
  ref_grid %>% 
  joint_tests(by = "Country")# %>%
  # filter(`model term` == "ValenceBlock:Measure:Block")

otm2_attitudes_country_split_aov
```

<!-- We found the expected three-way interaction between valence order, block, and attitude measure. -->
<!-- Moreover, we found that the three-way interaction differed between labs. -->
<!-- Visual inspection of the data suggested that labs differed with respect to magnitude of the differences in the valence order $\times$ block interaction between attitude measures---the direction of the interaction was the same for both measures in all labs. -->
<!-- We will return to this point below. -->
<!-- As in the original analysis we followed the significant three-way interaction up with separate analysis of each attitude measure.  -->

### Explicit attitudes

(ref:otm2-rydell-analysis-explicit)
ANOVA results for attitude ratings.

```{r otm2-rydell-analysis-explicit, results = "asis"}
otm2_explicit_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "Eval"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Duration")
  , data = otm2_attitudes
)

otm2_explicit_aov %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm2-rydell-analysis-explicit)"
    , escape = FALSE
  )

# Split analyses by Location
otm2_explicit_country_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "Eval"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Duration", "Country")
  , data = otm2_attitudes
)

otm2_explicit_country_split_aov <- otm2_explicit_country_aov %>% 
  ref_grid %>% 
  joint_tests(by = "Country")# %>%
  # filter(`model term` == "ValenceBlock:Block")

otm2_explicit_country_split_aov
```

<!-- We found the expected two-way interaction between valence order and block. -->
<!-- Moreover, we found that the two-way interaction differed between labs. -->
<!-- The three-way interaction prompted us to test the differences between attitude ratings in Block 1 and 2 for each valence order of description of Bob in each lab. -->

(ref:otm2-rydell-analysis-explicit-contrasts)
Planned contrasts (Block 2 - Block 1) for the ANOVA of attitude ratings.

```{r otm2-rydell-analysis-explicit2, results = "asis"}
emmeans(otm2_explicit_aov, ~ Block | ValenceBlock * Duration) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  ) %>%
  apa_print %$%
  table %>%
  select(-contrast) %>%
  rename("Valence order" = ValenceBlock) %>%
  apa_table(
    caption = "(ref:otm2-rydell-analysis-explicit-contrasts)"
    , escape = FALSE
    , row.names = FALSE
  )
```

<!-- As expected, in all labs ratings of Bob were more favorable after the first than after the second block when descriptions of Bob were first positive and later negative. -->
<!-- Vice versa, in all labs ratings of Bob were more favorable after the second than after the first block when descriptions of Bob were first negative and later positive. -->
<!-- Hence, the expected differences were consistently detectable in all labs but differed somewhat in magnitude as indicated by the three-way interaction. -->

### Implicit attitudes

(ref:otm2-rydell-analysis-implicit)
ANOVA results for IAT scores.

```{r otm2-rydell-analysis-implicit, results = "asis"}
otm2_iat_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "IATscore"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Duration")
  , data = otm2_attitudes
)
otm2_iat_aov %>%
  apa_print %$%
  table %>%
  apa_table(
    caption = "(ref:otm2-rydell-analysis-implicit)"
    , escape = FALSE
  )

# Split analyses by Location
otm2_iat_country_aov <- aov_ez(
  id = "ParticipantNumber"
  , dv = "IATscore"
  , within = "Block"
  # , between = "ValenceBlock"
  , between = c("ValenceBlock", "Duration", "Country")
  , data = otm2_attitudes
)

otm2_iat_country_split_aov <- otm2_iat_country_aov %>% 
  ref_grid %>% 
  joint_tests(by = "Country")# %>%
  # filter(`model term` == "ValenceBlock:Block")

otm2_iat_country_split_aov
```

<!-- For IAT scores, we found the expected two-way interaction between valence order and block; in this case we detected no differences between labs. -->
<!-- Again, the significant two-way interaction prompted us to test the differences between IAT scores in Block 1 and 2 for each valence order of descriptions of Bob. -->

(ref:otm2-rydell-analysis-implicit-contrasts)
Planned contrasts (Block 2 - Block 1) for the ANOVA of IAT scores.

```{r otm2-rydell-analysis-implicit2, results = "asis"}
emmeans(otm2_iat_aov, ~ Block | ValenceBlock) %>%
  contrast(
    method = list("Block 2 - Block 1" = c(-1, 1))
    , adjust = "none"
  ) %>%
  apa_print %$%
  table %>%
  select(-contrast) %>%
  rename("Valence order" = ValenceBlock) %>%
  apa_table(
    caption = "(ref:otm2-rydell-analysis-implicit-contrasts)"
    , escape = FALSE
    , row.names = FALSE
  )
```

<!-- IAT scores for Bob were more favorable after the first than after the second block when descriptions of Bob were first positive and later negative. -->
<!-- Vice versa, IAT scores for Bob were more favorable after the second than after the first block when descriptions of Bob were first negative and later positive. -->
<!-- The pattern is the same pattern as reported by Heycke et al. (2018) and the opposite of that reported by Rydell et al. (2006). -->
<!-- These results indicate that the attitudes assessed with explicit ratings and IAT scores did not dissociate. -->

### Differences between implicit and explicit attitudes

As in the original study, we compared participants' $z$ standardized attitude toward Bob assessed by ratings and IAT scores.

(ref:otm2-rydell-attitude-differences)
Results of follow-up analysis comparing differences between attitude ratings and IAT scores in all experimental conditions.

```{r otm2-rydell-attitude-differences, results = "asis"}
otm2_attitudes_aov %>% 
    emmeans(~ Measure | ValenceBlock * Block) %>% 
    pairs
```

<!-- We found differences between the attitudes assessed by ratings and IAT scores in all conditions. -->
<!-- Given that the assessed attitudes were consistent across measures, these differences indicate that the attitudes expressed in ratings were more extreme than those assessed in IAT scores. -->

### Recognition task

Finally, we tested participants recognition memory for the primes presented during the learning procedure.

(ref:otm2-rydell-recognition-plot)
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples, small points represent individual participants' responses, and violins represent kernel density estimates of sample distributions.

```{r otm2-rydell-recognition-plot, fig.cap = "(ref:otm2-rydell-recognition-plot)", fig.width = 3.5, fig.height = 3}
otm2_results_legend2 <- guide_legend(
    title.position = "top"
    , title.hjust = 0.5
  )

otm2_mem %>%
  ggplot(aes(x = Duration, y = Accuracy, shape = Duration, fill = Duration)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm2_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm2_results_legend) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  guides(shape = otm2_results_legend2) +
  labs(
    x = "Duration"
    , y = "Prime recognition accuracy"
  ) +
  theme(
    legend.position = "top"
    , legend.justification = "center"
  )
```

(ref:otm2-rydell-recognition)
ANOVA results of prime recognition accuracy.

```{r otm2-rydell-recognition, results = "asis"}
otm2_mem %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  droplevels %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Accuracy"
    , between = "Duration"
    , data = .
    , anova_table = list(intercept = TRUE)
  ) %>%
  apa_print(intercept = TRUE) %$%
  table %>%
  apa_table(
    escape = FALSE
    , caption = "(ref:otm2-rydell-recognition)"
  )

otm2_mem_emm <- otm2_mem %>%
  droplevels %>%
  aov_ez(
    id = "ParticipantNumber"
    , dv = "Accuracy"
    , between = "Duration"
    , data = .
  ) %>%
  emmeans(~ Duration)

otm2_mem_emm %>% 
  summary(infer = TRUE, side = ">", null = 0.5)

otm2_mem_emm %>% 
  summary(infer = TRUE, side = "<", delta = 0.55)
```

## Bayesian analysis

The following analyses are targeted hypothesis tests that compare models that instantiate the patterns of mean differences observed by Rydell et al. (2006) and Heycke et al. (2018).
For simplicity we collapsed data across valence orders by reversing the coding of the blocks when Bob was first presented with negative and subsequently with positive descriptions.
Hence, in the following analysis the first block represents responses following trials in which Bob was presented with positive descriptions.
For both attitude measures we contrasted the first with the second block, such that positive values represent a more favorable attitude after the block in which Bob was presented with positive descriptions.

The first model of interest posits that the experimental manipulation has the same effect on attitude ratings and IAT scores, that is the direction of the effect is the same for both measures ($\mathcal{H}_\textrm{same direction}$; see Heycke et al., 2018).
The competing model of interest predicts effects in opposite directions ($\mathcal{H}_\textrm{opposite directions}$; see Rydell et al., 2006).
The following analysis assesses which of the two patterns is a better a priori-description of our findings.

We considered two additional control models: one model assumes no effect of the manipulation ($\mathcal{H}_\textrm{no effect}$), the other model is unconstrained and is compatible with any outcome ($\mathcal{H}_\textrm{unconstrained effect}$).
If the latter model provides the best a priori-description of the data, the results are inconsistent with both previously reported outcomes.

We implemented the unconstrained model as a hierarchical linear model that encompasses each of the other models as special cases:

$$
\begin{aligned}
\hat y_{ijk} = & \mu + \nu_i + \eta_l x_{1il} + \\
          & (\alpha + \tau_l x_{1il}) x_{2j} x_{3k} + \\
          & (\beta + \upsilon_l x_{1il}) (1 -  x_{2j}) x_{3k}
\end{aligned}
$$

The model predicts the $i$th participant's response to measure $j$ in the experimental block $k$.
Responses are predicted as a combination of a grand mean $\mu$, random participant intercepts $\nu_i$ (i.e., habitually higher or lower attitudes), a main effect of the labs $\eta_l$, and simple effects of experimental block for attitude ratings ($\alpha$) and IAT score ($\beta$).
Additionally, we allowed the simple effects to be moderated by the labs ($\tau_l$ and $\upsilon_l$ represent the lab-specific deviations from the overall simple effects).
The model does not include a main effect of attitude measure because any mean differences between attitude measures were leveled by the $z$ standardization.
$x_{1il}$ represents $l$ effect coded variables that indicate which lab participant $i$ belongs to; $x_{2j}$ indicates the attitude measure (1 for explicit attitude rating and 0 for IAT score), such that $\alpha + \tau_l$ is only relevant for attitude ratings and $\beta + \upsilon_l$ is only relevant for IAT scores; $x_{3k}$ is an effect coded variable that is set to 0.5 for block 1 and -0.5 for block 2.

This model allowed us to place priors on the simple effects (in units of $d$) for each attitude measure and implement the theoretically motivated order constraints:

$$
\begin{aligned}
\mathcal{H}_\textrm{no effect}:~ & \delta_\alpha = 0 \\ & \delta_\beta = 0 \\
\mathcal{H}_\textrm{same direction}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{H}_\textrm{opposite directions}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Negative-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{H}_\textrm{unconstrained effect}:~ & \delta_\alpha \sim \textrm{Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Cauchy}(r = \sqrt2/2)
\end{aligned}
$$

Additionally, placed default multivariate Cauchy priors ($r = \sqrt2/2$) on lab main effects $\eta_l$ and lab effects on attitude differences between blocks for attitude ratings ($\tau_l$) and IAT score ($\upsilon_l$).

```{r otm2-bayesian-replication-restructure, cache = TRUE, dependson = "otm2-exclusion"}
# Collapse across ValcenceOrder
otm2_attitudes_collapsed <- otm2_attitudes %>%
  mutate(
    Block = ifelse(ValenceBlock == "Negative-positive", 3 - as.numeric(as.character(Block)), Block) %>% factor
  ) %>%
  select(-ValenceBlock) %>%
  mutate(Eval = scale(Eval) %>% as.vector, IATscore = scale(IATscore) %>% as.vector) %>%
  gather("Measure", "Attitude", Eval, IATscore)
```

```{r otm2-bayesian-replication-design-matrix, cache = TRUE, dependson = "otm2-bayesian-replication-restructure"}
# Participant random intercepts
otm2_random_participant_intercept_matrix <- BayesFactor:::oneDesignMatrix(
  trm = "ParticipantNumber"
  , data = otm2_attitudes_collapsed
  , dataTypes = c("ParticipantNumber" = "random")
) %>% as.matrix

# Fixed effects
## No main effect of attitude measure due to z standardization
unconstrained_effect_model <- function(x, a, b = NULL) {
  coding <- c(
    eta = 0                 # Duration effect
    , alpha = 0, tau = 0    # Rating
    , beta = 0, upsilon = 0 # IATscore
  )

  # Main effect Duration
  if(!is.null(b)) {
    if(x["Duration"] == "13") {
      coding["eta"] <- a[2, 1]
    } else {
      coding["eta"] <- a[1, 1]
    }
  } else {
    coding <- coding[, c("alpha", "beta")]
  }

  # Simple block effects
  if(x["Measure"] == "Eval") {

    # alpha = Simple block effect for ratings
    if(x["Block"] == "1") {
      coding["alpha"] <- a[2, 1]
    } else {
      coding["alpha"] <- a[1, 1]
    }

    # tau = Interaction of alpha with duration
    if(!is.null(b)) {
      coding["tau"] <- coding["eta"] * coding["alpha"]
    }

  } else {

    # beta = Simple block effect for IATscore
    if(x["Block"] == "1") {
      coding["beta"] <- a[2, 1]
    } else {
      coding["beta"] <- a[1, 1]
    }

    # upsilon = Interaction of beta with duration
    if(!is.null(b)) {
      coding["upsilon"] <- coding["eta"] * coding["beta"]
    }
  }

  coding
}

a <- BayesFactor:::fixedFromRandomProjection(nlevels(otm2_attitudes_collapsed$Block))
b <- BayesFactor:::fixedFromRandomProjection(nlevels(otm2_attitudes_collapsed$Duration))

otm2_fixed_effects_matrix <- t(apply(
  otm2_attitudes_collapsed
  , 1
  , unconstrained_effect_model
  , a = a
  , b = b
))

otm2_unconstrained_model_matrix <- cbind(
  otm2_fixed_effects_matrix
  , otm2_random_participant_intercept_matrix
)

otm2_no_duration_effect_model_matrix <- otm2_unconstrained_model_matrix[, -which(colnames(otm2_unconstrained_model_matrix) %in% c("tau", "upsilon"))]

otm2_null_model_matrix <- otm2_unconstrained_model_matrix[, -which(colnames(otm2_unconstrained_model_matrix) %in% c("alpha", "tau", "beta", "upsilon"))]
```

```{r otm2-bayesian-replication-analysis, cache = TRUE, dependson = "otm2-bayesian-replication-analysis-design-matrix"}
# No effect model
otm2_no_effect <- nWayAOV(
  y = otm2_attitudes_collapsed$Attitude
  , X = otm2_null_model_matrix
  , gMap = c(
    eta = 0
    , nu = rep(1, otm2_n)
  )
  , rscale = c(fixed = 0.5, random = 1)
  , iterations = otm2_n_mcmc_samples
)

# Fixed effect model
otm2_unconstrained <- nWayAOV(
  y = otm2_attitudes_collapsed$Attitude
  , X = otm2_unconstrained_model_matrix
  , gMap = c(
    eta = 0
    , alpha = 1, tau = 2
    , beta = 3, upsilon = 4
    , nu = rep(5, otm2_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , iterations = otm2_n_mcmc_samples
)
otm2_unconstrained_bf <- exp(otm2_unconstrained$bf - otm2_no_effect$bf)

# otm2_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
#   otm2_unconstrained_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{unconstrained effect}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )

# No lab effects model
otm2_no_duration_effect <- nWayAOV(
  y = otm2_attitudes_collapsed$Attitude
  , X = otm2_no_duration_effect_model_matrix
  , gMap = c(
    eta = 0
    , alpha = 1
    , beta = 2
    , nu = rep(3, otm2_n)
  )
  , rscale = c(fixed = rep(0.5, 3), random = 1)
  , iterations = otm2_n_mcmc_samples
)
otm2_no_duration_effect_bf <- exp(otm2_no_duration_effect$bf - otm2_no_effect$bf)

# otm2_no_duration_effect_bf_res <- papaja:::apa_print_bf.numeric(
#   otm2_no_duration_effect_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{no lab effects}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm2-bayesian-replication-analysis-samples, cache = TRUE, cache.lazy = FALSE, dependson = "otm2-bayesian-replication-analysis-unconstrained"}
# Fixed effect model
otm2_unconstrained_samples <- nWayAOV(
  y = otm2_attitudes_collapsed$Attitude
  , X = otm2_unconstrained_model_matrix
  , gMap = c(
    eta = 0
    , alpha = 1, tau = 2
    , beta = 3, upsilon = 4
    , nu = rep(5, otm2_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , posterior = TRUE
  , iterations = otm2_n_mcmc_samples
)
colnames(otm2_unconstrained_samples)[1:ncol(otm2_unconstrained_model_matrix) + 1] <- colnames(otm2_unconstrained_model_matrix)

otm2_unconstrained_samples <- otm2_unconstrained_samples %>%
  as.data.frame %>%
  mutate(
    alpha_13 = alpha + tau
    , alpha_20 =  alpha - tau
    , beta_13 = beta + upsilon
    , beta_20 = beta - upsilon
  ) %>%
  as.matrix
```

```{r otm2-bayesian-replication-analysis-same}
# Fixed effect model
otm2_same_direction_boost <- 4 * (
  sum(
    otm2_unconstrained_samples[, "alpha"] > 0 &
    otm2_unconstrained_samples[, "beta"] > 0
  ) / nrow(otm2_unconstrained_samples)
)
otm2_same_direction_bf <- otm2_unconstrained_bf * otm2_same_direction_boost

otm2_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm2_same_direction_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{no effect}"
  , escape = FALSE
)

## Same direction in all labs
otm2_all_durations_same_direction_boost <- 8 * (
  sum(
    otm2_unconstrained_samples[, "alpha_13"] > 0 &
    otm2_unconstrained_samples[, "beta_13"] > 0 &
    otm2_unconstrained_samples[, "alpha_20"] > 0 &
    otm2_unconstrained_samples[, "beta_20"] > 0
  ) / nrow(otm2_unconstrained_samples)
)
otm2_all_durations_same_direction_bf <- otm2_unconstrained_bf * otm2_all_durations_same_direction_boost

# otm2_all_durations_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm2_all_durations_same_direction_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm2-bayesian-replication-analysis-opposite}
# Fixed effect model
otm2_opposite_direction_boost <- 4 * (
  sum(
    otm2_unconstrained_samples[, "alpha"] > 0 &
    otm2_unconstrained_samples[, "beta"] < 0
  ) / nrow(otm2_unconstrained_samples)
)
otm2_opposite_direction_bf <- otm2_unconstrained_bf * otm2_opposite_direction_boost

# otm2_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm2_opposite_direction_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{opposite direction}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
#   , auto_invert = FALSE
# )

## Opposite direction in all locations
# otm2_all_durations_opposite_direction_boost <- 12 * (
#   sum(
#     otm2_unconstrained_samples[, "alpha_cologne"] > 0 &
#     otm2_unconstrained_samples[, "beta_cologne"] < 0 &
#     otm2_unconstrained_samples[, "alpha_ghent"] > 0 &
#     otm2_unconstrained_samples[, "beta_ghent"] < 0 &
#     otm2_unconstrained_samples[, "alpha_harvard"] > 0 &
#     otm2_unconstrained_samples[, "beta_harvard"] < 0
#   ) / nrow(otm2_unconstrained_samples)
# )
# otm2_all_durations_opposite_direction_bf <- otm2_unconstrained_bf * otm2_all_durations_opposite_direction_boost
# 
# otm2_all_durations_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
#   otm2_all_opposite_direction_bf
#   , ratio_subscript = "\\mathcal{H}_\\textrm{opposite direction}/\\mathcal{H}_\\textrm{no effect}"
#   , escape = FALSE
# )
```

```{r otm2-bayesian-replication-analysis-targeted-comparisons}
otm2_same_vs_opposite_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm2_same_direction_bf / otm2_opposite_direction_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{opposite direction}"
  , escape = FALSE
)

otm2_same_direction_vs_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
  otm2_same_direction_bf / otm2_unconstrained_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{same direction}/\\mathcal{H}_\\textrm{unconstrained effect}"
  , escape = FALSE
)

# In all durations
otm2_all_durations_same_direction_vs_unconstrained_bf_res <- papaja:::apa_print_bf.numeric(
  otm2_all_durations_same_direction_bf / otm2_unconstrained_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{all same direction}/\\mathcal{H}_\\textrm{unconstrained effect}"
  , escape = FALSE
)

otm2_all_durations_same_vs_same_direction_bf_res <- papaja:::apa_print_bf.numeric(
  otm2_all_durations_same_direction_bf / otm2_same_direction_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{all same direction}/\\mathcal{H}_\\textrm{same effect}"
  , escape = FALSE
)

otm2_no_duration_effect_bf_res <- papaja:::apa_print_bf.numeric(
  otm2_no_duration_effect_bf / otm2_unconstrained_bf
  , ratio_subscript = "\\mathcal{H}_\\textrm{no lab effect}/\\mathcal{H}_\\textrm{unconstrained effect}"
  , escape = FALSE
)
```

(ref:bayesian-replication-analysis-plot)
Black-rimmed points represent means of observed attitude differences between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions. Ellipses represent 95% Bayesian credible intervals based on the unconstrained model.

```{r otm2-bayesian-replication-analysis-plot, fig.cap = "(ref:bayesian-replication-analysis-plot)", cache = TRUE}
otm2_unconstrained_pp <- otm2_unconstrained_samples %>%
  as.data.frame %>%
  select(alpha:upsilon) %>%
  mutate(
    Eval_13 =        a[2, 1] * alpha + b[1, 1] * a[2, 1] * tau -
                    (a[1, 1] * alpha + b[1, 1] * a[1, 1] * tau)
    , Eval_20 =      a[2, 1] * alpha + b[2, 1] * a[2, 1] * tau -
                    (a[1, 1] * alpha + b[2, 1] * a[1, 1] * tau)

    , IATscore_13 =  a[2, 1] * beta  + b[1, 1] * a[2, 1] * upsilon -
                    (a[1, 1] * beta  + b[1, 1] * a[1, 1] * upsilon)
    , IATscore_20 =  a[2, 1] * beta  + b[2, 1] * a[2, 1] * upsilon -
                    (a[1, 1] * beta  + b[2, 1] * a[1, 1] * upsilon)

    , Eval_Overall =     a[2, 1] * alpha - (a[1, 1] * alpha)
    , IATscore_Overall = a[2, 1] * beta  - (a[1, 1] * beta)
  ) %>%
  select(-c(alpha:upsilon)) %>%
  gather(effect, value) %>%
  mutate(iteration = rep(1:nrow(otm2_unconstrained_samples), 6)) %>%
  separate(effect, c("Measure", "Duration")) %>%
  spread(Measure, value)

otm2_attitudes_delta <- otm2_attitudes_collapsed %>%
  spread(Block, Attitude) %>%
  mutate(delta = `1` - `2`) %>%
  select(-`1`, -`2`)

otm2_attitudes_delta_summary <- otm2_attitudes_delta %>%
  group_by(Measure) %>%
  summarize(delta = mean(delta)) %>%
  ungroup %>%
  spread(Measure, delta)

otm2_attitudes_delta_summary <- otm2_attitudes_delta %>%
  group_by(Measure, Duration) %>%
  summarize(delta = mean(delta)) %>%
  ungroup %>%
  spread(Measure, delta) %>%
  rbind(cbind(Duration = "Overall", otm2_attitudes_delta_summary))

otm2_attitudes_delta_summary %>%
  ggplot(aes(x = Eval, y = IATscore, color = Duration, fill = Duration, shape = Duration)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  # stat_density_2d(
  #   data = otm2_unconstrained_effect_fixed_pp
  #   , aes(x = alpha, y = beta, color = Duration)
  #   , bins = 5
  #   , inherit.aes = FALSE
  # ) +
  stat_ellipse(
    data = otm2_unconstrained_pp
    , type = "norm"
    , level = 0.95
  ) +
  geom_point(size = 3, color = "black") +
  # geom_point(
  #   data = otm2_unconstrained_effect_fixed_pp %>%
  #     summarize(alpha = median(alpha), beta = median(beta))
  #   , aes(x = alpha, y = beta)
  #   , color = "black"
  #   , inherit.aes = FALSE
  # ) +
  annotate(geom = "text", x = 1.1, y = 2, label = "One~mind", parse = TRUE, hjust = 0.5) +
  annotate(geom = "text", x = 1.1, y = -2, label = "Two~minds", parse = TRUE, hjust = 0.5) +
  scale_color_viridis_d(option = "B", direction = -1, end = 0.8) +
  scale_fill_viridis_d(option = "B", direction = -1, end = 0.8) +
  scale_shape_manual(values = c(21, 23, 24)) +
  labs(
    x = expression(paste("Rating score difference [", Delta~italic(z)~score, "]"))
    , y = expression(paste("IAT score difference [", Delta~italic(z)~score, "]"))
  ) +
  coord_fixed(xlim = c(-2.15, 2.15), ylim = c(-2.15, 2.15)) +
  theme_apa(box = TRUE) + 
  theme(
    legend.justification = c(0, 1)
    , legend.position = c(-0.01, 1.03)
    , legend.background = element_blank()
    , legend.key.height = unit(1.1, "line")
    , legend.key.width = unit(1.5, "line")
  )
```

The direct comparison of the prior predictive accuracy of the previously reported result patterns indicated that our data were overall most consistent with the results reported by Heycke et al. (2018), `r otm2_same_vs_opposite_direction_bf_res` (the Bayes factor is estimated as infinitely large due to numerical imprecision of the MCMC sampling approach).
Additional comparisons with the control models confirmed that our experimental manipulations were effective (`r otm2_same_direction_bf_res`) and did not produce an unexpected result pattern (`r otm2_same_direction_vs_unconstrained_bf_res`, range $[0, 4]$[^bf_range]).

[^bf_range]:
The comparison of these models is asymmetric.
If, as in this case, the data are perfectly consistent with $\mathcal{M}_\textrm{same direction}$, they are also consistent with $\mathcal{M}_\textrm{unconstrained}$.
The order restriction enforced by $\mathcal{M}_\textrm{same direction}$ limits the prediction of the model to 1/4 of the outcome space predicted by $\mathcal{M}_\textrm{unconstrained}$ (i.e. the upper right quadrant of Figure \ \@ref(fig:otm2-bayesian-replication-analysis-plot)).
This four-fold greater parsimony of $\mathcal{M}_\textrm{same direction}$ constitutes the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{same direction}/\mathcal{M}_\textrm{unconstrained}}$ (assuming all regions of the outcome space are equally likely a priori).
Hence, for this model comparison we could not have obtained stronger evidence (notwithstanding numerical imprecision of the MCMC sampling approach).
Conversely, if the data had fallen outside the predicted outcome space of $\mathcal{M}_\textrm{same direction}$ there is no upper bound to the evidence in favor of $\mathcal{M}_\textrm{unconstrained}$.

To formally assess whether the data from all labs homogeneously exhibited effects in the same direction we added another model that enforced the order constrained of the $\mathcal{M}_\textrm{same direction}$ not only on the average block effects ($\alpha$ and $\beta$) but on each labs block effect ($\alpha + \tau_l$ and $\beta + \upsilon_l$, $\mathcal{H}_\textrm{all same direction}$).
The data provide evidence in favor of homogeneous result patterns in all labs, `r otm2_all_durations_same_vs_same_direction_bf_res` (range $[0, 2]$) and `r otm2_all_durations_same_direction_vs_unconstrained_bf_res` (range $[0, 8]$[^bf_range2]).

[^bf_range2]:
The additional order constraints enforced by $\mathcal{M}_\textrm{all same direction}$ limits the prediction of the model to 1/12 of the outcome space predicted by the unconstrained model.
Hence, for this model comparison the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{all same direction}/\mathcal{M}_\textrm{unconstrained}}$ is 12 (assuming all regions of the outcome space are equally likely a priori).
Baring the transitivity of Bayes factors in mind this implies that the upper bound for $\mathrm{BF}_{\mathcal{M}_\textrm{all same direction}/\mathcal{M}_\textrm{same direction}}$ is 3.
Hence, in both model comparisons we could not have obtained much stronger evidence in favor of $\mathcal{M}_\textrm{all same direction}$.

<!-- - Does the size of the effects differ between labs? -->

<!-- `r otm2_no_duration_effect_bf_res` -->

<!-- Do we need to try different priors for $\alpha$ and $\beta$, or $\tau$ and $\upsilon$? -->

### Recognition task

We tested participants recognition memory for the primes presented during the learning procedure using a one-tailed Bayesian $t$ test with default Cauchy prior ($r = \sqrt2/2$).

```{r otm2-bayesian-recognition, warning = FALSE, message = FALSE}
otm2_mem_accuracy_res <- ttestBF(otm2_mem$Accuracy, mu = 0.5, nullInterval = c(0, Inf))[1] %>%
  apa_print %$%
  full_result

otm2_mem_accuracy_duration_res <- otm2_mem %>%
  anovaBF(
    Accuracy ~ Duration
    , data = .
  ) %>%
  apa_print %$%
  statistic

otm2_mem_accuracy_13_res <- otm2_mem %>%
  filter(Duration == "13") %>%
  pull(Accuracy) %>% 
  { ttestBF(x = ., mu = 0.5, nullInterval = c(0, Inf))[1] } %>%
  apa_print %$%
  full_result

otm2_mem_accuracy_20_res <- otm2_mem %>%
  filter(Duration == "20") %>%
  pull(Accuracy) %>% 
  { ttestBF(x = ., mu = 0.5, nullInterval = c(0, Inf))[1] } %>%
  apa_print %$%
  full_result
```

The data strongly support the conclusion that participants' recognition accuracy was better than chance, `r otm2_mem_accuracy_res`.
We performed a Bayesian ANOVA to test whether prime recognition accuracy differed between labs but the result was inconclusive, `r otm2_mem_accuracy_duration_res`.

## Prime recogniton and implicit attitudes

In contrast to the original results reported by Rydell et al. (2006), prime recognition accuracy in this study was above chance.
Memory for primes may, thus, have interfered with the associative learning process and hence may have obscured the reversal of the implicit attitudes.
We therefore performed an exploratory regression analysis of prime recognition and the IAT score difference between blocks used in the Bayesian analysis above where positive values represent a more favorable attitude after the block in which Bob was presented with positive explicit descriptions. 
A negative value of the IAT score difference between blocks would therefore indicate that the IAT effects were in line with the prime valence.
If prime recognition indeed obstructed the formation of associations, we would expect to observe a positive relationship between prime recognition accuracy and IAT score differences between blocks:
When prime recognition is high we would expect IAT differences in line with the valence of the explicit descriptions of Bob but not with the prime valence; we would expect to observe smaller and eventually negative IAT differences as prime recognition memory declines and associative learning takes over.

(ref:prime-recognition-iat-difference)
Scatterplot of prime recognition accuracy and attitude differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.

```{r prime-recognition-iat-difference, fig.cap = "(ref:prime-recognition-iat-difference)", message = FALSE}
source("../../analysis_and_paper/error_in_variables.R")

otm2_iat_delta <- full_join(otm2_attitudes_delta, select(otm2_mem, ParticipantNumber, Accuracy)) %>% 
  filter(Measure == "IATscore")

otm2_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_point(aes(color = Duration), alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black", method.args = list(n.optim = 50)) +
  # geom_smooth(method = "lm") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  theme_apa()
```

(ref:prime-recognition-iat-difference-regression)
Results of linear regression predicting attitude differences in IAT scores between blocks with prime recognition accuracy.

```{r prime-recognition-iat-difference-regression, results = "asis"}
otm2_recognition_iat_lm_bf <- otm2_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  as.data.frame %>%
  generalTestBF(delta ~ Accuracy, data = ., whichModels = "top") %>%
  apa_print

# otm2_iat_delta %>%
#   filter(Measure == "IATscore") %>%
#   mutate(Accuracy = Accuracy - 0.5) %>%
#   lm(delta ~ Accuracy * Duration, data = .) %>% 
#   apa_print %$%
#   table %>%
#   apa_table(
#     caption = "(ref:prime-recognition-iat-difference-regression)"
#     , escape = FALSE
#   )

otm2_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 50) %>% 
  summary
```

We were unable to detect a relationship between prime recognition and IAT score differences between blocks and even found some evidence against such a relationship, `r otm2_recognition_iat_lm_bf$statistic`.
Moreover, we centered prime recognition at 0.5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance prime recognition.
Hence, even for participants who exhibited no memory for prime attitudes assessed with the IAT were in line with the explicit descriptions of Bob.
These results provide no indication that the deviation of our findings from those reported by Rydell et al. (2006) are attributable to the above-chance prime recognition accuracy in this study.
